### 2023-11-10 src/metrics.Rmd
Working Springer Nature template for BMC Med

---
title: "Metrics"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: "Richard Wen <richard.wen@unityhealth.to>"
output: html_notebook
---

### 2023-11-16 src/metrics.Rmd
Finish pccc func, work on CSMF acc
Fin csmf acc metric

@@
 ---
+
+```{r}
+calc_pccc <- function(actual, pred, k = 1, N = NULL) {
+
+    # Calc N if not known
+    N <- if (is.null(N)) length(unique(c(actual, pred))) else N
+
+    # Calc frac of deaths in top k causes
+    C <- sum(actual == pred) / len(actual)
+
+    # Calc PCCC
+    out <- (C - (k/N)) / (1 - (k/N))
+    return(out)
+}
+
+calc_csmf_acc <- function(actual, pred, causes = NULL) {
+
+    # Get all unique causes
+    causes <- unique(c(actual, pred))
+
+    # Get csmfs
+    cases <- length(actual)
+    csmf_true <- table(actual) / cases
+    csmf_pred <- table(pred) / cases
+
+    # Correct for missing causes in either actual or pred
+    csmf_true <- vapply(
+        causes,
+        function(x) if (x %in% names(csmf_true)) csmf_true[x] else 0,
+        FUN.VALUE = numeric(1)
+    )
+    csmf_pred <- vapply(
+        causes,
+        function(x) if (x %in% names(csmf_pred)) csmf_pred[x] else 0,
+        FUN.VALUE = numeric(1)
+    )
+
+    # Calc csmf max error
+    csmf_max_error <- 2 * (1 - min(csmf_true))
+
+    # Calc csmf acc
+    out <- 1 - (sum(abs(csmf_true - csmf_pred)) / csmf_max_error)
+    return(out)
+}
+```

### 2023-11-17 src/metrics.Rmd
Working on data preprocess

@@
 
+```{r, echo=FALSE}
+knitr::opts_chunk$set(
+  message=FALSE,
+  warning=FALSE
+)
+```
+
+## Libraries
+
+```{r}
+library(tidyverse)
+
+options(readr.show_col_types = FALSE)
+```
+
+## Functions
+
+Functions for PCCC and CSMF Accuracy.
+
 ```{r}
@@
 
-    # Calc N if not known
+    # Calc N num of causes if not known
     N <- if (is.null(N)) length(unique(c(actual, pred))) else N
@@
 
-calc_csmf_acc <- function(actual, pred, causes = NULL) {
+calc_csmf_acc <- function(actual, pred) {
 
@@
 ```
+
+## Data
+
+Load data from `data` and `tmp` folders.
+
+```{r}
+df <- list(
+    wva2016_icd10 = read_csv(
+        "../data/wva2016_icd10_v1.csv",
+        col_types = cols(wva2016_code = col_double())
+    ),
+    icd10_cghr10 = read_csv("../data/icd10_cghr10_v1.csv"),
+    adult = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_adult_v1.csv",
+            col_select = "rowid"
+        ) %>% mutate(round = 1, age = "adult"),
+        read_csv(
+            "../tmp/healsl_rd2_adult_v1.csv",
+            col_select = "rowid"
+        ) %>% mutate(round = 2, age = "adult"),
+    ),
+    child = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_child_v1.csv",
+            col_select = "rowid"
+        ) %>% mutate(round = 1, age = "child"),
+        read_csv(
+            "../tmp/healsl_rd2_child_v1.csv",
+            col_select = "rowid"
+        ) %>% mutate(round = 2, age = "child")
+    ),
+    neo = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_neo_v1.csv",
+            col_select = "rowid"
+        ) %>% mutate(round = 1, age = "neo"),
+        read_csv(
+            "../tmp/healsl_rd2_neo_v1.csv",
+            col_select = "rowid"
+        ) %>% mutate(round = 2, age = "neo")
+    ),
+    model_chatgpt3 = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_rapid_chatgpt3_v1.csv",
+            col_select = c("rowid", "round", "api_chat_icd")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_chatgpt3_v1.csv",
+            col_select = c("rowid", "round", "api_chat_icd")
+        )
+    ),
+    model_chatgpt4 = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_rapid_chatgpt4_v1.csv",
+            col_select = c("rowid", "round", "api_chat_icd")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_chatgpt4_v1.csv",
+            col_select = c("rowid", "round", "api_chat_icd")
+        )
+    ),
+    model_insilicova = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_rapid_insilicova_v1.csv",
+            col_select = c("rowid", "round", "cause1_wva")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_insilicova_v1.csv",
+            col_select = c("rowid", "round", "cause1_wva")
+        )
+    ),
+    model_interva5 = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_rapid_interva5_v1.csv",
+            col_select = c("rowid", "round", "cause1_wva")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_interva5_v1.csv",
+            col_select = c("rowid", "round", "cause1_wva")
+        )
+    )
+)
+```
+
+```{r, echo=FALSE}
+for (i in names(df)) {
+    print(i)
+    print(head(df[[i]]))
+}
+```
+
+## Preprocess
+
+Convert ICD-10 and WVA-2016 codes to CGHR-10 codes.
+
+```{r}
+
+# Combine all models
+models <- df[str_starts(names(df), "model_")]
+
+# Add age groups to predictions
+df$chatgpt3 <- df$chatgpt3 %>%
+    left_join(
+        df$adult,
+        by = c(
+            "rowid" = "rowid",
+            "round" = "round"
+        ),
+        multiple = "first"
+    )
+
+# Convert wva2016 to icd10 via join
+df$insilicova <- df$insilicova %>%
+    left_join(
+        df$wva2016_icd10,
+        by = c("cause1_wva" = "wva2016_code"),
+        multiple = "first"
+    )
+df$interva5 <- df$interva5 %>%
+    left_join(
+        df$wva2016_icd10,
+        by = c("cause1_wva" = "wva2016_code"),
+        multiple = "first"
+    )
+
+# Convert icd10 to cghr10 via join
+df$chatgpt3 <- df$chatgpt3 %>%
+    left_join(
+        df$icd10_cghr10,
+        by = c("api_chat_icd" = "icd10_code"),
+        multiple = "first"
+    )
+df$interva5 <- df$interva5 %>%
+    left_join(
+        df$wva2016_icd10,
+        by = c("cause1_wva" = "wva2016_code"),
+        multiple = "first"
+    )
+```

### 2023-11-17 src/metrics.Rmd
Working cod code conversions

--- 2023-11-16 src/metrics.Rmd
@@
 ```
+
+## Data
+
+Load data from `data` and `tmp` folders.
+
+```{r}
+df <- list(
+    wva2016_icd10 = read_csv(
+        "../data/wva2016_icd10_v1.csv",
+        col_types = cols(wva2016_code = col_double())
+    ),
+    icd10_cghr10 = read_csv("../data/icd10_cghr10_v1.csv"),
+    ages = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_adult_v1.csv",
+            col_select = "rowid"
+        ) %>% mutate(round = 1, age = "adult"),
+        read_csv(
+            "../tmp/healsl_rd2_adult_v1.csv",
+            col_select = "rowid"
+        ) %>% mutate(round = 2, age = "adult"),
+        read_csv(
+            "../tmp/healsl_rd1_child_v1.csv",
+            col_select = "rowid"
+        ) %>% mutate(round = 1, age = "child"),
+        read_csv(
+            "../tmp/healsl_rd2_child_v1.csv",
+            col_select = "rowid"
+        ) %>% mutate(round = 2, age = "child"),
+        read_csv(
+            "../tmp/healsl_rd1_neo_v1.csv",
+            col_select = "rowid"
+        ) %>% mutate(round = 1, age = "neo"),
+        read_csv(
+            "../tmp/healsl_rd2_neo_v1.csv",
+            col_select = "rowid"
+        ) %>% mutate(round = 2, age = "neo")
+    ),
+    model_chatgpt3 = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_rapid_chatgpt3_v1.csv",
+            col_select = c("rowid", "round", "api_chat_icd")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_chatgpt3_v1.csv",
+            col_select = c("rowid", "round", "api_chat_icd")
+        )
+    ) %>% rename(chatgpt3_icd10 = api_chat_icd),
+    model_chatgpt4 = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_rapid_chatgpt4_v1.csv",
+            col_select = c("rowid", "round", "api_chat_icd")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_chatgpt4_v1.csv",
+            col_select = c("rowid", "round", "api_chat_icd")
+        )
+    ) %>% rename(chatgpt4_icd10 = api_chat_icd),
+    model_insilicova = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_rapid_insilicova_v1.csv",
+            col_select = c("rowid", "round", "cause1_wva")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_insilicova_v1.csv",
+            col_select = c("rowid", "round", "cause1_wva")
+        )
+    ) %>% rename(insilicova_wva2016 = cause1_wva),
+    model_interva5 = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_rapid_interva5_v1.csv",
+            col_select = c("rowid", "round", "cause1_wva")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_interva5_v1.csv",
+            col_select = c("rowid", "round", "cause1_wva")
+        )
+    ) %>% rename(interva5_wva2016 = cause1_wva)
+)
+```
+
+```{r, echo=FALSE}
+for (i in names(df)) {
+    print(i)
+    print(head(df[[i]]))
+}
+```
+
+## Preprocess
+
+Combine all model predictions with their ages.
+
+```{r}
+models <- df[str_starts(names(df), "model_")]
+models$all <- df$ages
+for (i in 1:length(models)) {
+    models$all <- models$all %>%
+        left_join(
+            models[[i]],
+            by = c("rowid" = "rowid", "round" = "round"),
+            suffix = c("", "")
+        )
+}
+head(models$all)
+```
+
+Convert ICD-10 and WVA-2016 codes to CGHR-10 codes.
+
+```{r}
+
+# Get wva2016 cols for model preds
+wva_cols <- colnames(models$all)
+wva_cols <- wva_cols[!wva_cols %in% c("rowid", "round", "age")]
+wva_cols <- wva_cols[str_ends(wva_cols, "_wva2016")]
+
+# Convert wva2016 to icd10 via join
+for (wcol in wva_cols) {
+
+    # Create new converted col based on model name
+    mname <- str_remove(wcol, "_wva2016")
+    iname <- paste0(mname, "_icd10")
+
+    # Join model wva to mapping wva
+    models$all <- models$all %>%
+    left_join(
+        df$wva2016_icd10 %>%
+            select(wva2016_code, icd10_code) %>%
+            rename_with(~iname, icd10_code),
+        by = setNames("wva2016_code", wcol),
+        multiple = "first"
+    )
+}
+
+# Get icd10 cols for model preds
+icd_cols <- colnames(models$all)
+icd_cols <- icd_cols[!icd_cols %in% c("rowid", "round", "age")]
+icd_cols <- icd_cols[str_ends(icd_cols, "_icd10")]
+
+# Convert icd10 to cghr10 via join
+for (icol in icd_cols) {
+
+    # Create new converted col based on model name
+    mname <- str_remove(icol, "_icd10")
+    cname <- paste0(mname, "_cghr10")
+
+    # Join model wva to mapping wva
+    models$all <- models$all %>%
+    left_join(
+        df$icd10_cghr10 %>%
+            select(icd10_code, cghr10_title, cghr10_age) %>%
+            rename_with(~cname, cghr10_title),
+        by = setNames(c("icd10_code", "cghr10_age"), c(icol, "age")),
+        multiple = "first"
+    )
+}
+
+head(models$all)
+```

### 2023-11-17 src/metrics.Rmd
Add icd10 code cleanup for chatgpt multi codes
Added physician final codes

--- 2023-11-16 src/metrics.Rmd
@@
 ```
+
+## Data
+
+Load data from `data` and `tmp` folders.
+
+```{r}
+# Physicians cols to keep and rename for consistency
+phy_cols <- c(
+    "rowid",
+    "p1_icd",
+    "p2_icd",
+    "p1_recon_icd",
+    "p2_recon_icd",
+    "adj_icd"
+)
+phy_adult_cols <- c(
+    "rowid",
+    "p1_icd_cod",
+    "p2_icd_cod",
+    "p1_recon_icd_cod",
+    "p2_recon_icd_cod",
+    "adj_icd_cod"
+)
+phy_adult_rename <- c(
+    p1_icd = "p1_icd_cod",
+    p2_icd = "p2_icd_cod",
+    p1_recon_icd = "p1_recon_icd_cod",
+    p2_recon_icd = "p2_recon_icd_cod",
+    adj_icd = "adj_icd_cod"
+)
+
+# Read data
+df <- list(
+    wva2016_icd10 = read_csv(
+        "../data/wva2016_icd10_v1.csv",
+        col_types = cols(wva2016_code = col_double())
+    ),
+    icd10_cghr10 = read_csv("../data/icd10_cghr10_v1.csv"),
+    physician = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_adult_v1.csv",
+            col_select = phy_adult_cols
+        ) %>%
+            mutate(round = 1, age = "adult") %>%
+            rename(all_of(phy_adult_rename)),
+        read_csv(
+            "../tmp/healsl_rd2_adult_v1.csv",
+            col_select = phy_adult_cols
+        ) %>%
+            mutate(round = 2, age = "adult") %>%
+            rename(all_of(phy_adult_rename)),
+        read_csv(
+            "../tmp/healsl_rd1_child_v1.csv",
+            col_select = phy_cols
+        ) %>% mutate(round = 1, age = "child"),
+        read_csv(
+            "../tmp/healsl_rd2_child_v1.csv",
+            col_select = phy_cols
+        ) %>% mutate(round = 2, age = "child"),
+        read_csv(
+            "../tmp/healsl_rd1_neo_v1.csv",
+            col_select = phy_cols
+        ) %>% mutate(round = 1, age = "neo"),
+        read_csv(
+            "../tmp/healsl_rd2_neo_v1.csv",
+            col_select = phy_cols
+        ) %>% mutate(round = 2, age = "neo")
+    ),
+    model_chatgpt3 = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_rapid_chatgpt3_v1.csv",
+            col_select = c("rowid", "round", "api_chat_icd")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_chatgpt3_v1.csv",
+            col_select = c("rowid", "round", "api_chat_icd")
+        )
+    ) %>% rename(chatgpt3_icd10 = api_chat_icd),
+    model_chatgpt4 = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_rapid_chatgpt4_v1.csv",
+            col_select = c("rowid", "round", "api_chat_icd")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_chatgpt4_v1.csv",
+            col_select = c("rowid", "round", "api_chat_icd")
+        )
+    ) %>% rename(chatgpt4_icd10 = api_chat_icd),
+    model_insilicova = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_rapid_insilicova_v1.csv",
+            col_select = c("rowid", "round", "cause1_wva")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_insilicova_v1.csv",
+            col_select = c("rowid", "round", "cause1_wva")
+        )
+    ) %>% rename(insilicova_wva2016 = cause1_wva),
+    model_interva5 = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_rapid_interva5_v1.csv",
+            col_select = c("rowid", "round", "cause1_wva")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_interva5_v1.csv",
+            col_select = c("rowid", "round", "cause1_wva")
+        )
+    ) %>% rename(interva5_wva2016 = cause1_wva)
+)
+```
+
+```{r, echo=FALSE}
+for (i in names(df)) {
+    print(i)
+    print(head(df[[i]]))
+}
+```
+
+## Preprocess
+
+Create column for final physician ICD-10 codes based on the following rule:
+
+1. If an adjudicated code exists, use it as the final code
+2. If not, use physician 1's reconciled code if it exists
+3. Otherwise use physician 1's code
+
+```{r}
+df$physician <- df$physician %>%
+    mutate(physician_icd10 = coalesce(
+        adj_icd,
+        p1_recon_icd,
+        p1_icd
+    ))
+```
+
+Combine all model predictions with their ages.
+
+```{r}
+models <- df[str_starts(names(df), "model_")]
+models$all <- df$physician
+for (i in 1:length(models)) {
+    models$all <- models$all %>%
+        left_join(
+            models[[i]],
+            by = c("rowid" = "rowid", "round" = "round"),
+            suffix = c("", "")
+        )
+}
+head(models$all)
+```
+
+Convert ICD-10 and WVA-2016 codes to CGHR-10 codes.
+
+```{r}
+
+# Get wva2016 cols for model preds
+wva_cols <- colnames(models$all)
+wva_cols <- wva_cols[!wva_cols %in% c("rowid", "round", "age")]
+wva_cols <- wva_cols[str_ends(wva_cols, "_wva2016")]
+
+# Convert wva2016 to icd10 via join
+for (wcol in wva_cols) {
+
+    # Create new converted col based on model name
+    mname <- str_remove(wcol, "_wva2016")
+    iname <- paste0(mname, "_icd10")
+
+    # Join model wva to mapping wva
+    models$all <- models$all %>%
+    left_join(
+        df$wva2016_icd10 %>%
+            select(wva2016_code, icd10_code) %>%
+            rename_with(~iname, icd10_code),
+        by = setNames("wva2016_code", wcol),
+        multiple = "first"
+    )
+}
+
+# Get icd10 cols for model preds
+icd_cols <- colnames(models$all)
+icd_cols <- icd_cols[!icd_cols %in% c("rowid", "round", "age")]
+icd_cols <- icd_cols[str_ends(icd_cols, "_icd10")]
+
+# Convert icd10 to cghr10 via join
+for (icol in icd_cols) {
+
+    # Create new converted col based on model name
+    mname <- str_remove(icol, "_icd10")
+    cname <- paste0(mname, "_cghr10")
+
+    # Remove all whitespaces and keep only first icd10 code if multiple
+    models$all[[icol]] <- str_replace_all(models$all[[icol]], "\\s", "")
+    models$all[[icol]] <- str_extract(models$all[[icol]], "^[A-Za-z]\\d{2}")
+
+    # Join model wva to mapping wva
+    models$all <- models$all %>%
+    left_join(
+        df$icd10_cghr10 %>%
+            select(icd10_code, cghr10_title, cghr10_age) %>%
+            rename_with(~cname, cghr10_title),
+        by = setNames(c("icd10_code", "cghr10_age"), c(icol, "age")),
+        multiple = "first"
+    )
+}
+
+head(models$all)
+```
+
+## Methods
+
+Calculate PCCC for each model:
+
+```{r}
+```
+
+Calculate CSMF Accuracy for each model:
+
+```{r}
+```

### 2023-11-17 src/metrics.Rmd
Calculated metrics

--- 2023-11-17 src/metrics.Rmd
@@
 )
+options(readr.show_col_types = FALSE)
 ```
@@
 library(tidyverse)
-
-options(readr.show_col_types = FALSE)
 ```
@@
     # Calc N num of causes if not known
-    N <- if (is.null(N)) length(unique(c(actual, pred))) else N
+    N <- if (is.null(N)) length(unique(na.omit(c(actual, pred)))) else N
 
     # Calc frac of deaths in top k causes
-    C <- sum(actual == pred) / len(actual)
+    TP <- actual == pred
+    TP[is.na(TP) | is.null(TP)] <- FALSE # for no preds
+    C <- sum(TP) / length(actual)
 
@@
 
-Load data from `data` and `tmp` folders.
+Load data from `data` folder.
 
 ```{r}
-df <- list(
-    wva2016_icd10 = read_csv(
-        "../data/wva2016_icd10_v1.csv",
-        col_types = cols(wva2016_code = col_double())
+df <- read_csv("../data/healsl_rd1to2_cod_v1.csv")
+```
+
+```{r, echo=FALSE}
+
+# Display num of cases
+cat("Number of Cases: ", nrow(df), "\n")
+
+# Get actual and pred
+actual <- df$physician_cghr10
+pred <- df %>% select(ends_with("_cghr10"), -physician_cghr10)
+
+# Physician info
+cat(paste0(
+    "Physician Coded Cases (",
+    length(unique(na.omit(actual))), " CODs): ",
+    length(actual) - sum(is.na(actual) | is.null(actual)),
+    "\n"
+))
+
+# Models info
+for (mcol in colnames(pred)) {
+    cat(paste0(
+        toupper(str_remove(mcol, "_cghr10")), " Predicted Cases (", 
+        length(unique(na.omit(pred[[mcol]]))), " CODs): ",
+        length(pred[[mcol]]) - sum(is.na(pred[[mcol]]) | is.null(pred[[mcol]])),
+        "\n"
+    ))
+}
+
+print(head(df))
+```
+
+Filter for cases that were coded by physicians.
+
+```{r}
+df <- df %>%
+    filter(!is.na(physician_cghr10) & !is.null(physician_cghr10))
+```
+
+```{r, echo=FALSE}
+cat("Number of Cases for Metrics: ", nrow(df))
+print(head(df))
+```
+
+Create model combinations where if any of the models have the physician code, then set the combined model's output for the case to be the physician code.
+
+```{r}
+df <- df %>%
+    mutate(
+        "chatgpt3_insilicova_cghr10" = if_else(
+            chatgpt3_cghr10 == physician_cghr10 | 
+                insilicova_cghr10 == physician_cghr10,
+            physician_cghr10,
+            chatgpt3_cghr10
         ),
-    icd10_cghr10 = read_csv("../data/icd10_cghr10_v1.csv"),
-    adult = bind_rows(
-        read_csv(
-            "../tmp/healsl_rd1_adult_v1.csv",
-            col_select = "rowid"
-        ) %>% mutate(round = 1, age = "adult"),
-        read_csv(
-            "../tmp/healsl_rd2_adult_v1.csv",
-            col_select = "rowid"
-        ) %>% mutate(round = 2, age = "adult"),
+        "chatgpt4_insilicova_cghr10" = if_else(
+            chatgpt4_cghr10 == physician_cghr10 | 
+                insilicova_cghr10 == physician_cghr10,
+            physician_cghr10,
+            chatgpt4_cghr10
         ),
-    child = bind_rows(
-        read_csv(
-            "../tmp/healsl_rd1_child_v1.csv",
-            col_select = "rowid"
-        ) %>% mutate(round = 1, age = "child"),
-        read_csv(
-            "../tmp/healsl_rd2_child_v1.csv",
-            col_select = "rowid"
-        ) %>% mutate(round = 2, age = "child")
+        "chatgpt3_interva5_cghr10" = if_else(
+            chatgpt3_cghr10 == physician_cghr10 | 
+                interva5_cghr10 == physician_cghr10,
+            physician_cghr10,
+            chatgpt3_cghr10
         ),
-    neo = bind_rows(
-        read_csv(
-            "../tmp/healsl_rd1_neo_v1.csv",
-            col_select = "rowid"
-        ) %>% mutate(round = 1, age = "neo"),
-        read_csv(
-            "../tmp/healsl_rd2_neo_v1.csv",
-            col_select = "rowid"
-        ) %>% mutate(round = 2, age = "neo")
+        "chatgpt4_interva5_cghr10" = if_else(
+            chatgpt4_cghr10 == physician_cghr10 | 
+                interva5_cghr10 == physician_cghr10,
+            physician_cghr10,
+            chatgpt4_cghr10
         ),
-    model_chatgpt3 = bind_rows(
-        read_csv(
-            "../tmp/healsl_rd1_rapid_chatgpt3_v1.csv",
-            col_select = c("rowid", "round", "api_chat_icd")
+        "chatgpt3_insilicova_interva5_cghr10" = if_else(
+            chatgpt3_cghr10 == physician_cghr10 | 
+                insilicova_cghr10 == physician_cghr10 |
+                interva5_cghr10 == physician_cghr10,
+            physician_cghr10,
+            chatgpt3_cghr10
         ),
-        read_csv(
-            "../tmp/healsl_rd2_rapid_chatgpt3_v1.csv",
-            col_select = c("rowid", "round", "api_chat_icd")
-        )
-    ),
-    model_chatgpt4 = bind_rows(
-        read_csv(
-            "../tmp/healsl_rd1_rapid_chatgpt4_v1.csv",
-            col_select = c("rowid", "round", "api_chat_icd")
-        ),
-        read_csv(
-            "../tmp/healsl_rd2_rapid_chatgpt4_v1.csv",
-            col_select = c("rowid", "round", "api_chat_icd")
-        )
-    ),
-    model_insilicova = bind_rows(
-        read_csv(
-            "../tmp/healsl_rd1_rapid_insilicova_v1.csv",
-            col_select = c("rowid", "round", "cause1_wva")
-        ),
-        read_csv(
-            "../tmp/healsl_rd2_rapid_insilicova_v1.csv",
-            col_select = c("rowid", "round", "cause1_wva")
-        )
-    ),
-    model_interva5 = bind_rows(
-        read_csv(
-            "../tmp/healsl_rd1_rapid_interva5_v1.csv",
-            col_select = c("rowid", "round", "cause1_wva")
-        ),
-        read_csv(
-            "../tmp/healsl_rd2_rapid_interva5_v1.csv",
-            col_select = c("rowid", "round", "cause1_wva")
-        )
+        "chatgpt4_insilicova_interva5_cghr10" = if_else(
+            chatgpt4_cghr10 == physician_cghr10 | 
+                insilicova_cghr10 == physician_cghr10 |
+                interva5_cghr10 == physician_cghr10,
+            physician_cghr10,
+            chatgpt4_cghr10
         )
@@
 ```{r, echo=FALSE}
-for (i in names(df)) {
-    print(i)
-    print(head(df[[i]]))
+print(head(df %>% select(
+    chatgpt3_insilicova_cghr10,
+    chatgpt4_insilicova_cghr10,
+    chatgpt3_interva5_cghr10,
+    chatgpt4_interva5_cghr10,
+    chatgpt3_insilicova_interva5_cghr10,
+    chatgpt4_insilicova_interva5_cghr10
+)))
+```
+
+Separate physician (actual) and model (predicted) CODs.
+
+```{r}
+actual <- df$physician_cghr10
+pred <- df %>%
+    select(ends_with("_cghr10"), -physician_cghr10) %>%
+    rename_all(~toupper(str_replace(., "_cghr10", "")))
+```
+
+```{r, echo=FALSE}
+cat(paste0(
+    "Physician Coded Cases (",
+    length(unique(na.omit(actual))), " CODs): ",
+    length(actual) - sum(is.na(actual) | is.null(actual)),
+    "\n"
+))
+```
+
+```{r, echo=FALSE}
+for (mcol in colnames(pred)) {
+    cat(paste0(
+        mcol, " Predicted Cases (", 
+        length(unique(na.omit(pred[[mcol]]))), " CODs): ",
+        length(pred[[mcol]]) - sum(is.na(pred[[mcol]]) | is.null(pred[[mcol]])),
+        "\n"
+    ))
 }
@@
 
-## Preprocess
+## Methods
 
-Convert ICD-10 and WVA-2016 codes to CGHR-10 codes.
+### PCCC
+
+Calculate PCCC to evaluate indivudal performance for each model.
 
 ```{r}
+pccc <- pred %>%
+    pivot_longer(
+        everything(),
+        names_to = "Model",
+        values_to = "prediction"
+    ) %>%
+    group_by(Model) %>%
+    summarise(
+        PCCC = calc_pccc(actual, prediction, k = str_count(unique(Model), "_") + 1)
+    ) %>%
+    mutate(Model = str_replace_all(Model, "_", " & ")) %>%
+    arrange(desc(PCCC))
+pccc
+```
 
-# Combine all models
-models <- df[str_starts(names(df), "model_")]
+### CSMF Accuracy
 
-# Add age groups to predictions
-df$chatgpt3 <- df$chatgpt3 %>%
-    left_join(
-        df$adult,
-        by = c(
-            "rowid" = "rowid",
-            "round" = "round"
-        ),
-        multiple = "first"
-    )
+Calculate CSMF Accuracy to evaluate population performance for each model.
 
-# Convert wva2016 to icd10 via join
-df$insilicova <- df$insilicova %>%
-    left_join(
-        df$wva2016_icd10,
-        by = c("cause1_wva" = "wva2016_code"),
-        multiple = "first"
-    )
-df$interva5 <- df$interva5 %>%
-    left_join(
-        df$wva2016_icd10,
-        by = c("cause1_wva" = "wva2016_code"),
-        multiple = "first"
-    )
-
-# Convert icd10 to cghr10 via join
-df$chatgpt3 <- df$chatgpt3 %>%
-    left_join(
-        df$icd10_cghr10,
-        by = c("api_chat_icd" = "icd10_code"),
-        multiple = "first"
-    )
-df$interva5 <- df$interva5 %>%
-    left_join(
-        df$wva2016_icd10,
-        by = c("cause1_wva" = "wva2016_code"),
-        multiple = "first"
-    )
+```{r}
+csmf_acc <- pred %>%
+    pivot_longer(
+        everything(),
+        names_to = "Model",
+        values_to = "prediction"
+    ) %>%
+    group_by(Model) %>%
+    summarise(
+        "CSMF Accuracy" = calc_csmf_acc(actual, prediction)
+    ) %>%
+    mutate(Model = str_replace_all(Model, "_", " & ")) %>%
+    arrange(desc(`CSMF Accuracy`))
+csmf_acc
 ```

### 2023-11-17 src/preprocess.Rmd
Calculated metrics

---
title: "Preprocess"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: "Richard Wen <richard.wen@unityhealth.to>"
output: html_notebook
---

```{r, echo=FALSE}
knitr::opts_chunk$set(
  message=FALSE,
  warning=FALSE
)
options(readr.show_col_types = FALSE)
```

## Libraries

```{r}
library(tidyverse)
```

## Data

Load data from `data` and `tmp` folders.

```{r}
# Physicians cols to keep and rename for consistency
phy_cols <- c(
    "rowid",
    "p1_icd",
    "p2_icd",
    "p1_recon_icd",
    "p2_recon_icd",
    "adj_icd"
)
phy_adult_cols <- c(
    "rowid",
    "p1_icd_cod",
    "p2_icd_cod",
    "p1_recon_icd_cod",
    "p2_recon_icd_cod",
    "adj_icd_cod"
)
phy_adult_rename <- c(
    p1_icd = "p1_icd_cod",
    p2_icd = "p2_icd_cod",
    p1_recon_icd = "p1_recon_icd_cod",
    p2_recon_icd = "p2_recon_icd_cod",
    adj_icd = "adj_icd_cod"
)

# Read data
df <- list(
    wva2016_icd10 = read_csv(
        "../data/wva2016_icd10_v1.csv",
        col_types = cols(wva2016_code = col_double())
    ),
    icd10_cghr10 = read_csv("../data/icd10_cghr10_v1.csv"),
    physician = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_adult_v1.csv",
            col_select = phy_adult_cols
        ) %>%
            mutate(round = 1, age = "adult") %>%
            rename(all_of(phy_adult_rename)),
        read_csv(
            "../tmp/healsl_rd2_adult_v1.csv",
            col_select = phy_adult_cols
        ) %>%
            mutate(round = 2, age = "adult") %>%
            rename(all_of(phy_adult_rename)),
        read_csv(
            "../tmp/healsl_rd1_child_v1.csv",
            col_select = phy_cols
        ) %>% mutate(round = 1, age = "child"),
        read_csv(
            "../tmp/healsl_rd2_child_v1.csv",
            col_select = phy_cols
        ) %>% mutate(round = 2, age = "child"),
        read_csv(
            "../tmp/healsl_rd1_neo_v1.csv",
            col_select = phy_cols
        ) %>% mutate(round = 1, age = "neo"),
        read_csv(
            "../tmp/healsl_rd2_neo_v1.csv",
            col_select = phy_cols
        ) %>% mutate(round = 2, age = "neo")
    ),
    model_chatgpt3 = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_chatgpt3_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_chatgpt3_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        )
    ) %>% rename(chatgpt3_icd10 = api_chat_icd),
    model_chatgpt4 = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_chatgpt4_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_chatgpt4_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        )
    ) %>% rename(chatgpt4_icd10 = api_chat_icd),
    model_insilicova = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_insilicova_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_insilicova_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        )
    ) %>% rename(insilicova_wva2016 = cause1_wva),
    model_interva5 = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_interva5_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_interva5_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        )
    ) %>% rename(interva5_wva2016 = cause1_wva)
)
```

```{r, echo=FALSE}
for (i in names(df)) {
    print(i)
    print(head(df[[i]]))
}
```

## Method

Create column for final physician ICD-10 codes based on the following rule:

1. If an adjudicated code exists, use it as the final code
2. If not, use physician 1's reconciled code if it exists
3. Otherwise use physician 1's code

```{r}
df$physician <- df$physician %>%
    mutate(physician_icd10 = coalesce(
        adj_icd,
        p1_recon_icd,
        p1_icd
    ))
```

Combine all model and physician predictions with their ages.

```{r}
models <- df[str_starts(names(df), "model_")]
out <- df$physician
for (i in 1:length(models)) {
    out <- out %>%
        left_join(
            models[[i]],
            by = c("rowid" = "rowid", "round" = "round"),
            suffix = c("", "")
        )
}
head(out)
```

Convert ICD-10 and WVA-2016 codes to CGHR-10 codes.

```{r}

# Get wva2016 cols for model preds
wva_cols <- colnames(out)
wva_cols <- wva_cols[!wva_cols %in% c("rowid", "round", "age")]
wva_cols <- wva_cols[str_ends(wva_cols, "_wva2016")]

# Convert wva2016 to icd10 via join
for (wcol in wva_cols) {

    # Create new converted col based on model name
    mname <- str_remove(wcol, "_wva2016")
    iname <- paste0(mname, "_icd10")

    # Join model wva to mapping wva
    out <- out %>%
    left_join(
        df$wva2016_icd10 %>%
            select(wva2016_code, icd10_code) %>%
            rename_with(~iname, icd10_code),
        by = setNames("wva2016_code", wcol),
        multiple = "first"
    )
}

# Get icd10 cols for model preds
icd_cols <- colnames(out)
icd_cols <- icd_cols[!icd_cols %in% c("rowid", "round", "age")]
icd_cols <- icd_cols[str_ends(icd_cols, "_icd10")]

# Convert icd10 to cghr10 via join
for (icol in icd_cols) {

    # Create new converted col based on model name
    mname <- str_remove(icol, "_icd10")
    cname <- paste0(mname, "_cghr10")

    # Remove all whitespaces and keep only first icd10 code if multiple
    out[[icol]] <- str_replace_all(out[[icol]], "\\s", "")
    out[[icol]] <- str_extract(out[[icol]], "^[A-Za-z]\\d{2}")

    # Join model wva to mapping wva
    out <- out %>%
    left_join(
        df$icd10_cghr10 %>%
            select(icd10_code, cghr10_title, cghr10_age) %>%
            rename_with(~cname, cghr10_title),
        by = setNames(c("icd10_code", "cghr10_age"), c(icol, "age")),
        multiple = "first"
    )
}

head(out)
```

## Results

Save pre-processed data to `data` folder.

```{r}
write_csv(out, "../data/healsl_rd1to2_cod_v1.csv")
```

### 2023-11-19 src/metrics.Rmd
Calculated metrics
Working pccc loop metrics

@@
 
+```{r, echo=FALSE, eval=FALSE}
+install.packages("tidyverse")
+```
+
 ## Libraries
@@
 library(tidyverse)
+```
+
+## Settings
+
+```{r}
+
+# Name formatting vars
+models_format <- c(
+    "_cghr10" = "",
+    "_" = " & ",
+    "chatgpt3" = "ChatGPT-3",
+    "chatgpt4" = "ChatGPT-4",
+    "insilicova" = "InSilicoVA",
+    "interva5" = "InterVA-5"
+)
 ```
@@
 ```{r}
+
+# Calc PCCC
 calc_pccc <- function(actual, pred, k = 1, N = NULL) {
@@
 
+# Calc CSMF accuracy
 calc_csmf_acc <- function(actual, pred) {
@@
 }
+
+# Bulk calc per model
+calc_per_model <- function(actual, pred, func, name = "Metric", ...) {
+
+    # Prep data in long format grouped by model
+    out <- pred %>%
+        pivot_longer( # to long format
+            everything(),
+            names_to = "Model",
+            values_to = "prediction"
+        ) %>% group_by(Model)
+
+    # Calc k if pccc as it is diff for model combos
+    if (identical(func, calc_pccc)) {
+        out <- out %>%
+            summarise(
+                !!name := func(
+                    actual,
+                    prediction,
+                    k = str_count(unique(Model), "_") + 1,
+                    ...
+                )
+            )
+    } else { # otherwise apply func
+        out <- out %>%
+            summarise(
+                !!name := func(
+                    actual,
+                    prediction,
+                    ...
+                )
+            )
+    }
+
+    # Format display and return
+    out <- out %>%
+        mutate(Model = str_replace_all(Model, models_format)) %>%
+        arrange(across({{name}}, desc))
+    return(out)
+}
 ```
@@
 
+### Raw Data
+
 Load data from `data` folder.
@@
 ```{r}
-df <- read_csv("../data/healsl_rd1to2_cod_v1.csv")
+raw_df <- read_csv("../data/healsl_rd1to2_cod_v1.csv")
 ```
@@
 ```{r, echo=FALSE}
+cat("Cases: ", nrow(raw_df), "\n")
+print(head(raw_df))
+```
 
-# Display num of cases
-cat("Number of Cases: ", nrow(df), "\n")
-
-# Get actual and pred
-actual <- df$physician_cghr10
-pred <- df %>% select(ends_with("_cghr10"), -physician_cghr10)
-
-# Physician info
-cat(paste0(
-    "Physician Coded Cases (",
-    length(unique(na.omit(actual))), " CODs): ",
-    length(actual) - sum(is.na(actual) | is.null(actual)),
-    "\n"
-))
-
-# Models info
-for (mcol in colnames(pred)) {
-    cat(paste0(
-        toupper(str_remove(mcol, "_cghr10")), " Predicted Cases (", 
-        length(unique(na.omit(pred[[mcol]]))), " CODs): ",
-        length(pred[[mcol]]) - sum(is.na(pred[[mcol]]) | is.null(pred[[mcol]])),
-        "\n"
-    ))
-}
-
-print(head(df))
-```
+### Physician Cases
 
@@
 ```{r}
-df <- df %>%
+df <- raw_df %>%
     filter(!is.na(physician_cghr10) & !is.null(physician_cghr10))
@@
 ```{r, echo=FALSE}
-cat("Number of Cases for Metrics: ", nrow(df))
+cat("Physician Coded Cases: ", nrow(df))
 print(head(df))
 ```
+
+### Combined Models
 
@@
 
-Separate physician (actual) and model (predicted) CODs.
+### Prepared Data
+
+Display case counts for raw data and prepared data after combining models and filtering for physician coded cases.
 
 ```{r}
-actual <- df$physician_cghr10
-pred <- df %>%
-    select(ends_with("_cghr10"), -physician_cghr10) %>%
-    rename_all(~toupper(str_replace(., "_cghr10", "")))
-```
 
-```{r, echo=FALSE}
+cat("\nRaw Data\n--------\n\n")
+
+# Physician info
+raw_physicians <- raw_df$physician_cghr10
+cat(paste0(
+    "Cases (",
+    length(unique(na.omit(raw_physicians))), " CODs): ",
+    length(raw_physicians),
+    "\n"
+))
+
+# Models cases
+raw_models <- raw_df %>% select(ends_with("_cghr10"), -physician_cghr10)
+for (mcol in colnames(raw_models)) {
+    m <- raw_models[[mcol]]
+    cat(paste0(
+        str_replace_all(mcol, models_format), " Predicted Cases (", 
+        length(unique(na.omit(m))), " CODs): ",
+        length(m) - sum(is.na(m) | is.null(m)),
+        "\n"
+    ))
+}
+
+cat("\nPrepared Data\n--------------\n")
+
+# Physician cases
+physicians <- df$physician_cghr10
 cat(paste0(
     "Physician Coded Cases (",
-    length(unique(na.omit(actual))), " CODs): ",
-    length(actual) - sum(is.na(actual) | is.null(actual)),
+    length(unique(na.omit(physicians))), " CODs): ",
+    length(physicians) - sum(is.na(physicians) | is.null(physicians)),
     "\n"
 ))
-```
 
-```{r, echo=FALSE}
-for (mcol in colnames(pred)) {
+# Models cases
+models <- df %>% select(ends_with("_cghr10"), -physician_cghr10)
+for (mcol in colnames(models)) {
+    m <- models[[mcol]]
     cat(paste0(
-        mcol, " Predicted Cases (", 
-        length(unique(na.omit(pred[[mcol]]))), " CODs): ",
-        length(pred[[mcol]]) - sum(is.na(pred[[mcol]]) | is.null(pred[[mcol]])),
+        str_replace_all(mcol, models_format), " Predicted Cases (", 
+        length(unique(na.omit(m))), " CODs): ",
+        length(m) - sum(is.na(m) | is.null(m)),
         "\n"
@@
 
+Calculate metrics from model outputs compared to physician codes.
+
 ### PCCC
 
-Calculate PCCC to evaluate indivudal performance for each model.
+Calculate Partial Chance Corrected Concordance (PCCC) to evaluate indivudal performance for each model.
 
 ```{r}
-pccc <- pred %>%
-    pivot_longer(
-        everything(),
-        names_to = "Model",
-        values_to = "prediction"
+pccc <- list()
+
+# Calc overall pccc
+pccc$all <- calc_per_model(
+    actual = df %>% pull(physician_cghr10),
+    pred = df %>% select(ends_with("_cghr10"), -physician_cghr10),
+    func = calc_pccc
+) %>% rename(
+    PCCC = Metric
+)
+
+# Calc pcc for each age group
+for (age_group in c("adult", "child", "neo")) {
+
+    # Filter data for age
+    df_age <- df %>% filter(age == age_group)
+    metric_name = paste0("PCCC ", str_to_title(age_group))
+
+    # Calc metric for age
+    pccc[[age_group]] <- calc_per_model(
+        actual = df_age %>%
+            pull(physician_cghr10),
+        pred = df_age %>%
+            select(ends_with("_cghr10"), -physician_cghr10),
+        func = calc_pccc
+    ) %>% rename(
+         {{ metric_name }} := Metric
+    )
+}
+
+# Combine all pccc metrics
+pccc <- reduce(
+    pccc,
+    function(x, y) left_join(x, y, by = "Model")
 ) %>%
-    group_by(Model) %>%
-    summarise(
-        PCCC = calc_pccc(actual, prediction, k = str_count(unique(Model), "_") + 1)
-    ) %>%
-    mutate(Model = str_replace_all(Model, "_", " & ")) %>%
     arrange(desc(PCCC))
@@
 
-Calculate CSMF Accuracy to evaluate population performance for each model.
+Calculate Cause Specific Mortality Fraction (CSMF) Accuracy to evaluate population performance for each model.
 
 ```{r}
-csmf_acc <- pred %>%
-    pivot_longer(
-        everything(),
-        names_to = "Model",
-        values_to = "prediction"
-    ) %>%
-    group_by(Model) %>%
-    summarise(
-        "CSMF Accuracy" = calc_csmf_acc(actual, prediction)
-    ) %>%
-    mutate(Model = str_replace_all(Model, "_", " & ")) %>%
-    arrange(desc(`CSMF Accuracy`))
+csmf_acc <- list()
+```
+
+#### Overall CSMF Accuracy
+
+```{r}
+csmf_acc <- calc_per_model(
+    physicians,
+    models,
+    calc_csmf_acc,
+    "CSMF Accuracy"
+)
 csmf_acc
 ```
+
+#### Adult Accuracy
+
+#### Child Accuracy
+
+#### Neonate Accuracy

### 2023-11-19 src/preprocess.Rmd
Working pccc loop metrics

@@
 options(readr.show_col_types = FALSE)
+```
+
+```{r, echo=FALSE, eval=FALSE}
+install.packages("tidyverse")
 ```
@@
             "../tmp/healsl_rd1_adult_v1.csv",
-            col_select = phy_adult_cols
+            col_select = all_of(phy_adult_cols)
         ) %>%
@@
             "../tmp/healsl_rd2_adult_v1.csv",
-            col_select = phy_adult_cols
+            col_select = all_of(phy_adult_cols)
         ) %>%
@@
             "../tmp/healsl_rd1_child_v1.csv",
-            col_select = phy_cols
+            col_select = all_of(phy_cols)
         ) %>% mutate(round = 1, age = "child"),
@@
             "../tmp/healsl_rd2_child_v1.csv",
-            col_select = phy_cols
+            col_select = all_of(phy_cols)
         ) %>% mutate(round = 2, age = "child"),
@@
             "../tmp/healsl_rd1_neo_v1.csv",
-            col_select = phy_cols
+            col_select = all_of(phy_cols)
         ) %>% mutate(round = 1, age = "neo"),
@@
             "../tmp/healsl_rd2_neo_v1.csv",
-            col_select = phy_cols
+            col_select = all_of(phy_cols)
         ) %>% mutate(round = 2, age = "neo")
@@
 
-## Method
+## Methods
 
-Create column for final physician ICD-10 codes based on the following rule:
+### Final ICD
+
+Create one column for final physician ICD-10 codes and one column each for physician agreed, reconciled, and adjudicated records based on the following rule:
 
@@
 df$physician <- df$physician %>%
-    mutate(physician_icd10 = coalesce(
+    mutate(
+        physician_icd10 = coalesce(
             adj_icd,
@@
             p1_icd
-    ))
+        ),
+        is_agreed = if_else(
+            is.na(p1_recon_icd) & is.na(p2_recon_icd) & is.na(adj_icd),
+            TRUE,
+            FALSE
+        ),
+        is_recon = if_else(
+            !is.na(p1_recon_icd) | !is.na(p2_recon_icd),
+            TRUE,
+            FALSE
+        ),
+        is_adj = if_else(
+            !is.na(adj_icd),
+            TRUE,
+            FALSE
+        )
+    ) %>%
+    select(
+        rowid,
+        round,
+        age,
+        p1_icd,
+        p2_icd,
+        p1_recon_icd,
+        p2_recon_icd,
+        adj_icd,
+        is_agreed,
+        is_recon,
+        is_adj,
+        physician_icd10
+    )
+head(df$physician)
 ```
+
+### Combine Outputs
 
@@
 ```
+
+### Convert to CGHR-10
 

### 2023-11-19 src/metrics.Rmd
Finish pccc and csmf calcs

@@
 ```{r}
-
-# Name formatting vars
 models_format <- c(
@@
     "interva5" = "InterVA-5"
+)
+stage_format <- c(
+    "is_" = "",
+    "recon" = "Reconciliation",
+    "agreed" = "Agreement",
+    "adj" = "Adjudication"
 )
@@
         arrange(across({{name}}, desc))
+    return(out)
+}
+
+# Bulk calc per model based on age and physician coding stage
+calc_by_age_stage <- function(df, func, name = "Metric") {
+    out <- list()
+
+    # Calc overall metric
+    out[[name]] <- calc_per_model(
+        actual = df %>% pull(physician_cghr10),
+        pred = df %>% select(ends_with("_cghr10"), -physician_cghr10),
+        func = func
+    ) %>% rename(
+        {{ name }} := Metric
+    )
+
+    # Calc metric for va coding stage
+    for (stage in c("is_agreed", "is_recon", "is_adj")) {
+
+        # Filter data for stage
+        df_filter <- df %>% filter(.[[stage]] == TRUE)
+        metric_name = paste0(
+            name,
+            " ",
+            str_replace_all(stage, stage_format)
+        )
+
+        # Calc metric for stage
+        out[[metric_name]] <- calc_per_model(
+            actual = df_filter %>%
+                pull(physician_cghr10),
+            pred = df_filter %>%
+                select(ends_with("_cghr10"), -physician_cghr10),
+            func = func
+        ) %>% rename(
+             {{ metric_name }} := Metric
+        )
+    }
+
+    # Calc pcc for each age group
+    for (age_group in c("adult", "child", "neo")) {
+
+        # Filter data for age
+        df_filter <- df %>% filter(age == age_group)
+        metric_name = paste0(
+            name,
+            " ",
+            str_to_title(age_group)
+        )
+
+        # Calc metric for age
+        out[[metric_name]] <- calc_per_model(
+            actual = df_filter %>%
+                pull(physician_cghr10),
+            pred = df_filter %>%
+                select(ends_with("_cghr10"), -physician_cghr10),
+            func = func
+        ) %>% rename(
+             {{ metric_name }} := Metric
+        )
+
+        # Calc metric for each stage within age group
+        for (stage in c("is_agreed", "is_recon", "is_adj")) {
+
+            # Filter data for stage within age group
+            df_filter <- df %>% filter(
+                .[[stage]] == TRUE & age == age_group
+            )
+            metric_name = paste0(
+                name,
+                " ",
+                str_to_title(age_group),
+                " ",
+                str_replace_all(stage, stage_format)
+            )
+
+            # Calc metric for stage within age group
+            out[[metric_name]] <- calc_per_model(
+                actual = df_filter %>%
+                    pull(physician_cghr10),
+                pred = df_filter %>%
+                    select(ends_with("_cghr10"), -physician_cghr10),
+                func = func
+            ) %>% rename(
+                 {{ metric_name }} := Metric
+            )
+        }
+    }
+
+    # Combine all pccc metrics
+    out <- reduce(out,
+        function(x, y) left_join(x, y, by = "Model")
+    ) %>%
+        arrange(across({{ name }}, desc))
     return(out)
@@
 
-Calculate Partial Chance Corrected Concordance (PCCC) to evaluate indivudal performance for each model.
+Calculate Partial Chance Corrected Concordance (PCCC) to evaluate indivudal performance for each model by age and physician coding stage.
 
 ```{r}
-pccc <- list()
-
-# Calc overall pccc
-pccc$all <- calc_per_model(
-    actual = df %>% pull(physician_cghr10),
-    pred = df %>% select(ends_with("_cghr10"), -physician_cghr10),
-    func = calc_pccc
-) %>% rename(
-    PCCC = Metric
-)
-
-# Calc pcc for each age group
-for (age_group in c("adult", "child", "neo")) {
-
-    # Filter data for age
-    df_age <- df %>% filter(age == age_group)
-    metric_name = paste0("PCCC ", str_to_title(age_group))
-
-    # Calc metric for age
-    pccc[[age_group]] <- calc_per_model(
-        actual = df_age %>%
-            pull(physician_cghr10),
-        pred = df_age %>%
-            select(ends_with("_cghr10"), -physician_cghr10),
-        func = calc_pccc
-    ) %>% rename(
-         {{ metric_name }} := Metric
-    )
-}
-
-# Combine all pccc metrics
-pccc <- reduce(
-    pccc,
-    function(x, y) left_join(x, y, by = "Model")
-) %>%
-    arrange(desc(PCCC))
+pccc <- calc_by_age_stage(df, calc_pccc, "PCCC")
 pccc
@@
 
-Calculate Cause Specific Mortality Fraction (CSMF) Accuracy to evaluate population performance for each model.
+Calculate Cause Specific Mortality Fraction (CSMF) Accuracy to evaluate population performance for each model by age and physician coding stage.
 
 ```{r}
-csmf_acc <- list()
-```
-
-#### Overall CSMF Accuracy
-
-```{r}
-csmf_acc <- calc_per_model(
-    physicians,
-    models,
-    calc_csmf_acc,
-    "CSMF Accuracy"
-)
+csmf_acc <- calc_by_age_stage(df, calc_csmf_acc, "CSMF Accuracy")
 csmf_acc
 ```
-
-#### Adult Accuracy
-
-#### Child Accuracy
-
-#### Neonate Accuracy

### 2023-11-19 src/metrics.Rmd
Finish pccc and csmf calcs and save to csv

@@
 
+```{r}
+metrics <- list()
+```
+
 ### PCCC
@@
 ```{r}
-pccc <- calc_by_age_stage(df, calc_pccc, "PCCC")
-pccc
+metrics$pccc <- calc_by_age_stage(df, calc_pccc, "PCCC")
+metrics$pccc
 ```
@@
 ```{r}
-csmf_acc <- calc_by_age_stage(df, calc_csmf_acc, "CSMF Accuracy")
-csmf_acc
+metrics$csmf_acc <- calc_by_age_stage(df, calc_csmf_acc, "CSMF Accuracy")
+metrics$csmf_acc
 ```
+
+## Results
+
+Save calculated metrics to `data` folder.
+
+```{r}
+out <- reduce(metrics,
+              function(x, y) left_join(x, y, by = "Model")
+)
+write_csv(out, "../data/healsl_rd1to2_metrics_v1.csv")
+```

### 2023-11-19 src/metrics.Rmd
Make box plots

@@
 ```
+
+### Tables
+
+```{r}
+
+# Create cols with counts
+col_overall <- paste0(
+    "Overall\n(n=",
+    nrow(df),
+    ")"
+)
+col_agree <- paste0(
+    "Agreement\n(n=",
+    nrow(df %>% filter(age == "adult" & is_agreed == TRUE)),
+    ")"
+)
+col_recon <- paste0(
+    "Reconciliation\n(n=",
+    nrow(df %>% filter(age == "adult" & is_recon == TRUE)),
+    ")"
+)
+col_adj <- paste0(
+    "Adjudication\n(n=",
+    nrow(df %>% filter(age == "adult" & is_adj == TRUE)),
+    ")"
+)
+
+# Add count to col names
+col_rename <- list()
+col_rename[[col_overall]] <- "Overall"
+col_rename[[col_agree]] <- "Agreement"
+col_rename[[col_recon]] <- "Reconciliation"
+col_rename[[col_adj]] <- "Adjudication"
+
+# Create table
+out %>%
+    select(
+        Model,
+        `PCCC Adult`,
+        `PCCC Adult Agreement`,
+        `PCCC Adult Reconciliation`,
+        `PCCC Adult Adjudication`
+    ) %>%
+    rename(
+         Overall = `PCCC Adult`,
+         Agreement = `PCCC Adult Agreement`,
+         Reconciliation = `PCCC Adult Reconciliation`,
+         Adjudication = `PCCC Adult Adjudication`
+    ) %>%
+    rename(!!!col_rename)
+```
+
+```{r}
+out %>%
+    select(
+        Model,
+        `PCCC`,
+        `PCCC Agreement`,
+        `PCCC Reconciliation`,
+        `PCCC Adjudication`
+    ) %>%
+    rename(
+         All = `PCCC`,
+         Agreement = `PCCC Agreement`,
+         Reconciliation = `PCCC Reconciliation`,
+         Adjudication = `PCCC Adjudication`
+    ) %>%
+    pivot_longer(
+        cols = -Model,
+        names_to = "Stage",
+        values_to = "PCCC"
+    ) %>%
+    mutate(
+        Stage = factor(Stage, levels = c(
+            "Adjudication",
+            "Reconciliation",
+            "Agreement",
+            "All"
+        ))
+    ) %>%
+    ggplot(aes(x = Stage, y = PCCC)) +
+    geom_boxplot(width = 0.4) +
+    stat_summary(
+        geom = "label",
+        fun.y = min,
+        aes(label = sprintf("%1.2f", ..y..)),
+        position = position_nudge(y = -0.07),
+        size = 2.5
+    ) +
+    stat_summary(
+        geom = "label",
+        fun.y = max,
+        aes(label = sprintf("%1.2f", ..y..)),
+        position = position_nudge(y = 0.06),
+        size = 2.5
+    ) +
+    ylim(0, 1) +
+    coord_flip() +
+    theme_minimal()
+```

### 2023-11-26 src/metrics.Rmd
Add labels and values to plot

@@
 ```{r}
-out %>%
+
+# Calc stage counts
+nall <- nrow(df)
+nagree <- nrow(df %>% filter(is_agreed == TRUE))
+nrecon <- nrow(df %>% filter(is_recon == TRUE))
+nadj <- nrow(df %>% filter(is_adj == TRUE))
+
+# Calc stage perc
+pagree <- (nagree / nall) * 100
+precon <- (nrecon / nall) * 100
+padj <- (nadj / nall) * 100
+
+# Create stage with counts
+stage_remap <- c(
+    "All" = paste0("All\n(n=", nall, ", 100%)"),
+    "Agreed" = paste0("Agreed\n(n=", nagree, ", ", round(pagree), "%)"),
+    "Reconciled" = paste0("Reconciled\n(n=", nrecon, ", ", round(precon), "%)"),
+    "Adjudicated" = paste0("Adjudicated\n(n=", nadj, ", ", round(padj), "%)")
+)
+
+#
+
+# Prepare boxplot data
+pdata <- out %>%
     select(
@@
         `PCCC`,
-        `PCCC Agreement`,
-        `PCCC Reconciliation`,
-        `PCCC Adjudication`
+        `PCCC Agreement`
     ) %>%
@@
          All = `PCCC`,
-         Agreement = `PCCC Agreement`,
-         Reconciliation = `PCCC Reconciliation`,
-         Adjudication = `PCCC Adjudication`
+         Agreed = `PCCC Agreement`
     ) %>%
-    pivot_longer(
+    filter(!str_detect(Model, "&")) %>% # remove multi models
+    pivot_longer( # transform to long format
         cols = -Model,
@@
     ) %>%
-    mutate(
+    mutate( # re-order stage
         Stage = factor(Stage, levels = c(
-            "Adjudication",
-            "Reconciliation",
-            "Agreement",
+            "Agreed",
             "All"
@@
     ) %>%
+    mutate( # rename stages with counts
+        Stage = recode(Stage, !!!stage_remap)
+    ) %>%
+    group_by(Stage) %>%
+    mutate( # Add min, mid, and max model names to label
+        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.03, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
+        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
+    )
+
+# Plot boxplot
+pdata %>%
     ggplot(aes(x = Stage, y = PCCC)) +
-    geom_boxplot(width = 0.4) +
-    stat_summary(
-        geom = "label",
-        fun.y = min,
-        aes(label = sprintf("%1.2f", ..y..)),
-        position = position_nudge(y = -0.07),
-        size = 2.5
+    geom_boxplot(width = 0.25) +
+    geom_dotplot(
+        binaxis = "y",
+        binwidth = 0.03,
+        dotsize = 0.3,
+        fill = "white",
+        color = "darkgray",
+        stackdir = "center",
+        stackratio = 2,
+        position = position_nudge(x = -0.3)
     ) +
-    stat_summary(
-        geom = "label",
-        fun.y = max,
-        aes(label = sprintf("%1.2f", ..y..)),
-        position = position_nudge(y = 0.06),
-        size = 2.5
+    geom_text(
+        aes(label = `PCCC Min`),
+        color = "#3d3d3d",
+        size = 2,
+        position = position_nudge(y = -0.06, x = -0.3)
     ) +
-    ylim(0, 1) +
+    geom_text(
+        aes(label = `PCCC Max`),
+        color = "#3d3d3d",
+        size = 2,
+        position = position_nudge(y = 0.065, x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Mid`),
+        color = "#3d3d3d",
+        size = 2,
+        position = position_nudge(y = -0.065, x = -0.3)
+    ) +
+    stat_summary( # min pccc txt on boxplot
+        geom = "text",
+        fun = min,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = -0.025),
+        size = 3
+    ) +
+    stat_summary( # max pccc txt on boxplot
+        geom = "text",
+        fun = max,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = 0.025),
+        size = 3
+    ) +
+    labs(
+        x = element_blank(),
+        y = "PCCC (0=Low, 1=High)"
+    ) +
+    ylim(0.2, 0.8) +
     coord_flip() +
-    theme_minimal()
+    theme_minimal() +
+    theme(
+        panel.grid = element_blank(),
+        axis.line = element_line(color = "black"),
+        axis.title.x = element_text(margin = margin(t = 5)),
+        axis.title.y = element_text(margin = margin(r = 5))
+    )
 ```

### 2023-11-26 src/metrics.Rmd
Add save plot

--- 2023-11-19 src/metrics.Rmd
@@
 ```
+
+### All vs Agree Performance
+
+Display a plot of model performance for all records versus records where physicians agreed on the COD code.
+
+```{r}
+
+# Calc stage counts
+nall <- nrow(df)
+nagree <- nrow(df %>% filter(is_agreed == TRUE))
+nrecon <- nrow(df %>% filter(is_recon == TRUE))
+nadj <- nrow(df %>% filter(is_adj == TRUE))
+
+# Calc stage perc
+pagree <- (nagree / nall) * 100
+precon <- (nrecon / nall) * 100
+padj <- (nadj / nall) * 100
+
+# Create stage with counts
+stage_remap <- c(
+    "All" = paste0("All\nRecords\n(n=", nall, ", 100%)"),
+    "Agreed" = paste0("Physician\nAgreed Records\n(n=", nagree, ", ", round(pagree), "%)"),
+    "Reconciled" = paste0("Reconciled\n(n=", nrecon, ", ", round(precon), "%)"),
+    "Adjudicated" = paste0("Adjudicated\n(n=", nadj, ", ", round(padj), "%)")
+)
+
+# Prepare boxplot data
+pdata <- out %>%
+    select(
+        Model,
+        `PCCC`,
+        `PCCC Agreement`
+    ) %>%
+    rename(
+         All = `PCCC`,
+         Agreed = `PCCC Agreement`
+    ) %>%
+    filter(!str_detect(Model, "&")) %>% # remove multi models
+    pivot_longer( # transform to long format
+        cols = -Model,
+        names_to = "Stage",
+        values_to = "PCCC"
+    ) %>%
+    mutate( # re-order stage
+        Stage = factor(Stage, levels = c(
+            "Agreed",
+            "All"
+        ))
+    ) %>%
+    mutate( # rename stages with counts
+        Stage = recode(Stage, !!!stage_remap)
+    ) %>%
+    group_by(Stage) %>%
+    mutate( # Add min, mid, and max model names to label
+        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.03, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
+        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
+    )
+
+# Plot boxplot
+pplot <- pdata %>%
+    ggplot(aes(x = Stage, y = PCCC)) +
+    geom_boxplot(
+        linewidth = 0.5,
+        width = 0.25
+    ) +
+    geom_dotplot(
+        binaxis = "y",
+        binwidth = 0.03,
+        dotsize = 0.3,
+        fill = "white",
+        color = "darkgray",
+        stackdir = "center",
+        stackratio = 2,
+        position = position_nudge(x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Min`),
+        color = "#3d3d3d",
+        size = 2,
+        position = position_nudge(y = -0.06, x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Max`),
+        color = "#3d3d3d",
+        size = 2,
+        position = position_nudge(y = 0.065, x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Mid`),
+        color = "#3d3d3d",
+        size = 2,
+        position = position_nudge(y = -0.065, x = -0.3)
+    ) +
+    stat_summary( # min pccc txt on boxplot
+        geom = "text",
+        fun = min,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = -0.025),
+        size = 3
+    ) +
+    stat_summary( # max pccc txt on boxplot
+        geom = "text",
+        fun = max,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = 0.025),
+        size = 3
+    ) +
+    geom_segment(aes(x = -Inf, y = 0, xend = Inf, yend = 0), arrow = arrow(length = unit(1, "cm"))) +
+    labs(
+        x = element_blank(),
+        y = "PCCC (0=Low, 1=High)"
+    ) +
+    ylim(0.2, 0.8) +
+    coord_flip() +
+    theme_minimal() +
+    theme(
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        axis.line = element_line(color = "black"),
+        axis.title.x = element_text(margin = margin(t = 5)),
+        axis.title.y = element_text(margin = margin(r = 5)),
+        axis.line.x = element_line(
+            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
+        ),
+        axis.line.y = element_blank()
+    )
+
+# Save the plot
+pplot
+ggsave("../manuscript/fig-perf-allvsagree.pdf", plot = pplot, dpi = 300)
+```
+
+### Age Group Perfomance
+
+Display a plot of performance for agreed

### 2023-11-27 src/metrics.Rmd
Add age group plot perf

--- 2023-11-19 src/metrics.Rmd
@@
 
-### Tables
+### All vs Agree Performance
+
+Display a plot of model performance for all records versus records where physicians agreed on the COD code.
 
@@
 
-# Create cols with counts
-col_overall <- paste0(
-    "Overall\n(n=",
-    nrow(df),
-    ")"
-)
-col_agree <- paste0(
-    "Agreement\n(n=",
-    nrow(df %>% filter(age == "adult" & is_agreed == TRUE)),
-    ")"
-)
-col_recon <- paste0(
-    "Reconciliation\n(n=",
-    nrow(df %>% filter(age == "adult" & is_recon == TRUE)),
-    ")"
-)
-col_adj <- paste0(
-    "Adjudication\n(n=",
-    nrow(df %>% filter(age == "adult" & is_adj == TRUE)),
-    ")"
+# Calc stage counts
+nall <- nrow(df)
+nagree <- nrow(df %>% filter(is_agreed == TRUE))
+nrecon <- nrow(df %>% filter(is_recon == TRUE))
+nadj <- nrow(df %>% filter(is_adj == TRUE))
+
+# Calc stage perc
+pagree <- (nagree / nall) * 100
+precon <- (nrecon / nall) * 100
+padj <- (nadj / nall) * 100
+
+# Create stage with counts
+stage_remap <- c(
+    "All" = paste0("All\nRecords\n(n=", nall, ", 100%)"),
+    "Agreed" = paste0("Physician Agreed\nRecords\n(n=", nagree, ", ", round(pagree), "%)"),
+    "Reconciled" = paste0("Reconciled\n(n=", nrecon, ", ", round(precon), "%)"),
+    "Adjudicated" = paste0("Adjudicated\n(n=", nadj, ", ", round(padj), "%)")
 )
 
-# Add count to col names
-col_rename <- list()
-col_rename[[col_overall]] <- "Overall"
-col_rename[[col_agree]] <- "Agreement"
-col_rename[[col_recon]] <- "Reconciliation"
-col_rename[[col_adj]] <- "Adjudication"
-
-# Create table
-out %>%
-    select(
-        Model,
-        `PCCC Adult`,
-        `PCCC Adult Agreement`,
-        `PCCC Adult Reconciliation`,
-        `PCCC Adult Adjudication`
-    ) %>%
-    rename(
-         Overall = `PCCC Adult`,
-         Agreement = `PCCC Adult Agreement`,
-         Reconciliation = `PCCC Adult Reconciliation`,
-         Adjudication = `PCCC Adult Adjudication`
-    ) %>%
-    rename(!!!col_rename)
-```
-
-```{r}
-out %>%
+# Prepare boxplot data
+alldata <- out %>%
     select(
@@
     ) %>%
+    mutate( # rename stages with counts
+        Stage = recode(Stage, !!!stage_remap)
+    ) %>%
+    group_by(Stage) %>%
+    mutate( # Add min, mid, and max model names to label
+        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.03, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
+        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
+    )
+
+# Plot boxplot
+allplot <- alldata %>%
     ggplot(aes(x = Stage, y = PCCC)) +
-    geom_boxplot(width = 0.4) +
-    stat_summary(
-        geom = "label",
-        fun.y = min,
-        aes(label = sprintf("%1.2f", ..y..)),
-        position = position_nudge(y = -0.07),
-        size = 2.5
+    geom_boxplot(
+        linewidth = 0.5,
+        width = 0.25
     ) +
-    stat_summary(
-        geom = "label",
-        fun.y = max,
-        aes(label = sprintf("%1.2f", ..y..)),
-        position = position_nudge(y = 0.06),
-        size = 2.5
+    geom_dotplot(
+        binaxis = "y",
+        binwidth = 0.03,
+        dotsize = 0.3,
+        fill = "white",
+        color = "darkgray",
+        stackdir = "center",
+        stackratio = 2,
+        position = position_nudge(x = -0.3)
     ) +
-    ylim(0, 1) +
+    geom_text(
+        aes(label = `PCCC Min`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 1,
+        position = position_nudge(y = -0.015, x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Max`),
+        color = "#4d4d4d",
+        size = 2,
+        position = position_nudge(y = 0.065, x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Mid`),
+        color = "#4d4d4d",
+        size = 2,
+        position = position_nudge(y = -0.065, x = -0.3)
+    ) +
+    stat_summary( # min pccc txt on boxplot
+        geom = "text",
+        fun = min,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = -0.025),
+        size = 3
+    ) +
+    stat_summary( # max pccc txt on boxplot
+        geom = "text",
+        fun = max,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = 0.025),
+        size = 3
+    ) +
+    geom_segment(aes(x = -Inf, y = 0, xend = Inf, yend = 0), arrow = arrow(length = unit(1, "cm"))) +
+    labs(
+        x = element_blank(),
+        y = "PCCC (0=Low, 1=High)"
+    ) +
+    ylim(0.2, 0.8) +
     coord_flip() +
-    theme_minimal()
+    theme_minimal() +
+    theme(
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        axis.line = element_line(color = "black"),
+        axis.title.x = element_text(margin = margin(t = 5)),
+        axis.title.y = element_text(margin = margin(r = 5)),
+        axis.line.x = element_line(
+            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
+        ),
+        axis.line.y = element_blank()
+    )
+
+# Save the plot
+allplot
+ggsave("../manuscript/fig-perf-allvsagree.pdf", plot = allplot, dpi = 300)
 ```
+
+### Age Group Perfomance
+
+Display a plot of performance for physician agreed records by age group.
+
+```{r}
+
+# Calc age counts
+nagree <- nrow(df %>% filter(is_agreed == TRUE))
+nadult <- nrow(df %>% filter(age == "adult" & is_agreed == TRUE))
+nchild <- nrow(df %>% filter(age == "child" & is_agreed == TRUE))
+nneo <- nrow(df %>% filter(age == "neo" & is_agreed == TRUE))
+
+# Calc age perc
+padult <- (nadult / nagree) * 100
+pchild <- (nchild / nagree) * 100
+pneo <- (nneo / nagree) * 100
+
+# Create age with counts
+age_remap <- c(
+    "Adult" = paste0("Adult\n12+ years\n(n=", nadult, ", ", round(padult), "%)"),
+    "Child" = paste0("Child\n28 days to 11 years\n(n=", nchild, ", ", round(pchild), "%)"),
+    "Neonatal" = paste0("Neonatal\n<28 days\n(n=", nneo, ", ", round(pneo), "%)")
+)
+
+# Prepare boxplot data
+agedata <- out %>%
+    select(
+        Model,
+        `PCCC Adult Agreement`,
+        `PCCC Child Agreement`,
+        `PCCC Neo Agreement`
+    ) %>%
+    rename(
+         Adult = `PCCC Adult Agreement`,
+         Child = `PCCC Child Agreement`,
+         Neonatal = `PCCC Neo Agreement`
+    ) %>%
+    filter(!str_detect(Model, "&")) %>% # remove multi models
+    pivot_longer( # transform to long format
+        cols = -Model,
+        names_to = "Age Group",
+        values_to = "PCCC"
+    ) %>%
+    mutate( # re-order age
+        "Age Group" = factor(`Age Group`, levels = c(
+            "Neonatal",
+            "Child",
+            "Adult"
+        ))
+    ) %>%
+    mutate( # rename ages with counts
+        "Age Group" = recode(`Age Group`, !!!age_remap)
+    ) %>%
+    group_by(`Age Group`) %>%
+    mutate( # Add min, mid, and max model names to label
+        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.1, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.95, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
+        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
+        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
+    )
+
+# Plot boxplot
+ageplot <- agedata %>%
+    ggplot(aes(x = `Age Group`, y = PCCC)) +
+    geom_boxplot(
+        linewidth = 0.5,
+        width = 0.25
+    ) +
+    geom_dotplot(
+        binaxis = "y",
+        binwidth = 0.03,
+        dotsize = 0.3,
+        fill = "white",
+        color = "darkgray",
+        stackdir = "center",
+        stackratio = 2,
+        position = position_nudge(x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Min`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 1,
+        position = position_nudge(y = -0.015, x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Max`),
+        color = "#4d4d4d",
+        size = 2,
+        position = position_nudge(y = 0.055, x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Mid`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 1,
+        position = position_nudge(y = -0.015, x = -0.3)
+    ) +
+    stat_summary( # min pccc txt on boxplot
+        geom = "text",
+        fun = min,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = -0.025),
+        size = 3
+    ) +
+    stat_summary( # max pccc txt on boxplot
+        geom = "text",
+        fun = max,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = 0.025),
+        size = 3
+    ) +
+    geom_segment(aes(x = -Inf, y = 0, xend = Inf, yend = 0), arrow = arrow(length = unit(1, "cm"))) +
+    labs(
+        x = paste0("Agreed Records (n=", nagree, ", 100%)"),
+        y = "PCCC (0=Low, 1=High)"
+    ) +
+    ylim(0.2, 0.8) +
+    coord_flip() +
+    theme_minimal() +
+    theme(
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        axis.line = element_line(color = "black"),
+        axis.title.x = element_text(margin = margin(t = 5)),
+        axis.title.y = element_text(margin = margin(r = 5)),
+        axis.line.x = element_line(
+            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
+        ),
+        axis.line.y = element_blank()
+    )
+
+# Save the plot
+ageplot
+ggsave("../manuscript/fig-perf-ages.pdf", plot = ageplot, dpi = 300)
+```

### 2023-11-27 src/preprocess.Rmd
Add age ranges, await fix for neo age range data

@@
     "rowid",
+    "death_age_group",
     "p1_icd",
@@
 )
+phy_rename <- c(
+    age_range = "death_age_group"
+)
 phy_adult_cols <- c(
     "rowid",
+    "death_age_group",
     "p1_icd_cod",
@@
 phy_adult_rename <- c(
+    age_range = "death_age_group",
     p1_icd = "p1_icd_cod",
@@
             col_select = all_of(phy_cols)
-        ) %>% mutate(round = 1, age = "child"),
+        ) %>%
+            mutate(round = 1, age = "child") %>%
+            rename(all_of(phy_rename)),
         read_csv(
@@
             col_select = all_of(phy_cols)
-        ) %>% mutate(round = 2, age = "child"),
+        ) %>%
+            mutate(round = 2, age = "child") %>%
+            rename(all_of(phy_rename)),
         read_csv(
@@
             col_select = all_of(phy_cols)
-        ) %>% mutate(round = 1, age = "neo"),
+        ) %>%
+            mutate(round = 1, age = "neo") %>%
+            rename(all_of(phy_rename)),
         read_csv(
@@
             col_select = all_of(phy_cols)
-        ) %>% mutate(round = 2, age = "neo")
+        ) %>%
+            mutate(round = 2, age = "neo") %>%
+            rename(all_of(phy_rename))
     ),

### 2023-11-29 src/metrics.Rmd
Add in age range for preprocess

--- 2023-11-26 src/metrics.Rmd
@@
     "_" = " & ",
-    "chatgpt3" = "ChatGPT-3",
+    "chatgpt3" = "ChatGPT-3.5",
     "chatgpt4" = "ChatGPT-4",
@@
     "All" = paste0("All\nRecords\n(n=", nall, ", 100%)"),
-    "Agreed" = paste0("Physician\nAgreed Records\n(n=", nagree, ", ", round(pagree), "%)"),
+    "Agreed" = paste0("Physician Agreed\nRecords\n(n=", nagree, ", ", round(pagree), "%)"),
     "Reconciled" = paste0("Reconciled\n(n=", nrecon, ", ", round(precon), "%)"),
@@
 # Prepare boxplot data
-pdata <- out %>%
+alldata <- out %>%
     select(
@@
     mutate( # Add min, mid, and max model names to label
-        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.03, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.05, paste0(Model, " (", round(PCCC, 2), ")"), NA),
         "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
-        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
         "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
@@
 # Plot boxplot
-pplot <- pdata %>%
+allplot <- alldata %>%
     ggplot(aes(x = Stage, y = PCCC)) +
@@
         aes(label = `PCCC Min`),
-        color = "#3d3d3d",
+        color = "#4d4d4d",
         size = 2,
-        position = position_nudge(y = -0.06, x = -0.3)
+        hjust = 1,
+        position = position_nudge(y = -0.015, x = -0.3)
     ) +
@@
         aes(label = `PCCC Max`),
-        color = "#3d3d3d",
+        color = "#4d4d4d",
         size = 2,
@@
         aes(label = `PCCC Mid`),
-        color = "#3d3d3d",
+        color = "#4d4d4d",
         size = 2,
@@
     theme(
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank(),
+        panel.grid = element_blank(),
         axis.line = element_line(color = "black"),
@@
 # Save the plot
-pplot
-ggsave("../manuscript/fig-perf-allvsagree.pdf", plot = pplot, dpi = 300)
+allplot
+ggsave("../manuscript/fig-perf-allvsagree.pdf", plot = allplot, dpi = 300)
+```
+
+### COD Performance
+
+Plot model performance for physician agreed records by cause of death category.
+
+```{r}
 ```
@@
 
-Display a plot of performance for agreed
+Display a plot of performance for physician agreed records by age group.
+
+```{r}
+
+# Calc age counts
+nagree <- nrow(df %>% filter(is_agreed == TRUE))
+nadult <- nrow(df %>% filter(age == "adult" & is_agreed == TRUE))
+nchild <- nrow(df %>% filter(age == "child" & is_agreed == TRUE))
+nneo <- nrow(df %>% filter(age == "neo" & is_agreed == TRUE))
+
+# Calc age perc
+padult <- (nadult / nagree) * 100
+pchild <- (nchild / nagree) * 100
+pneo <- (nneo / nagree) * 100
+
+# Create age with counts
+age_remap <- c(
+    "Adult" = paste0("Adult\n12+ years\n(n=", nadult, ", ", round(padult), "%)"),
+    "Child" = paste0("Child\n28 days to 11 years\n(n=", nchild, ", ", round(pchild), "%)"),
+    "Neonatal" = paste0("Neonatal\n<28 days\n(n=", nneo, ", ", round(pneo), "%)")
+)
+
+# Prepare boxplot data
+agedata <- out %>%
+    select(
+        Model,
+        `PCCC Adult Agreement`,
+        `PCCC Child Agreement`,
+        `PCCC Neo Agreement`
+    ) %>%
+    rename(
+         Adult = `PCCC Adult Agreement`,
+         Child = `PCCC Child Agreement`,
+         Neonatal = `PCCC Neo Agreement`
+    ) %>%
+    filter(!str_detect(Model, "&")) %>% # remove multi models
+    pivot_longer( # transform to long format
+        cols = -Model,
+        names_to = "Age Group",
+        values_to = "PCCC"
+    ) %>%
+    mutate( # re-order age
+        "Age Group" = factor(`Age Group`, levels = c(
+            "Neonatal",
+            "Child",
+            "Adult"
+        ))
+    ) %>%
+    mutate( # rename ages with counts
+        "Age Group" = recode(`Age Group`, !!!age_remap)
+    ) %>%
+    group_by(`Age Group`) %>%
+    mutate( # Add min, mid, and max model names to label
+        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.15, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.95, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
+        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
+        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
+    )
+
+# Plot boxplot
+ageplot <- agedata %>%
+    ggplot(aes(x = `Age Group`, y = PCCC)) +
+    geom_boxplot(
+        linewidth = 0.5,
+        width = 0.25
+    ) +
+    geom_dotplot(
+        binaxis = "y",
+        binwidth = 0.03,
+        dotsize = 0.3,
+        fill = "white",
+        color = "darkgray",
+        stackdir = "center",
+        stackratio = 2,
+        position = position_nudge(x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Min`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 1,
+        position = position_nudge(y = -0.015, x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Max`),
+        color = "#4d4d4d",
+        size = 2,
+        position = position_nudge(y = 0.055, x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Mid`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 1,
+        position = position_nudge(y = -0.015, x = -0.3)
+    ) +
+    stat_summary( # min pccc txt on boxplot
+        geom = "text",
+        fun = min,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = -0.025),
+        size = 3
+    ) +
+    stat_summary( # max pccc txt on boxplot
+        geom = "text",
+        fun = max,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = 0.025),
+        size = 3
+    ) +
+    geom_segment(aes(x = -Inf, y = 0, xend = Inf, yend = 0), arrow = arrow(length = unit(1, "cm"))) +
+    labs(
+        x = paste0("Agreed Records (n=", nagree, ", 100%)"),
+        y = "PCCC (0=Low, 1=High)"
+    ) +
+    ylim(0.2, 0.8) +
+    coord_flip() +
+    theme_minimal() +
+    theme(
+        panel.grid = element_blank(),
+        axis.line = element_line(color = "black"),
+        axis.title.x = element_text(margin = margin(t = 5)),
+        axis.title.y = element_text(margin = margin(r = 5)),
+        axis.line.x = element_line(
+            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
+        ),
+        axis.line.y = element_blank()
+    )
+
+# Save the plot
+ageplot
+ggsave("../manuscript/fig-perf-ages.pdf", plot = ageplot, dpi = 300)
+```

### 2023-11-29 src/preprocess.Rmd
Add in age range for preprocess

@@
         age,
+        age_range,
         p1_icd,

### 2023-12-01 src/metrics.Rmd
Add cod plot and fix k for pccc

@@
                     prediction,
-                    k = str_count(unique(Model), "_") + 1,
+                    k = str_count(unique(Model), "_"),
                     ...
@@
 
-# Bulk calc per model based on age and physician coding stage
-calc_by_age_stage <- function(df, func, name = "Metric") {
+# Bulk calc per model based on age, physician coding stage, and cause of death
+calc_by <- function(
+        df,
+        func,
+        name = "Metric",
+        by_age = TRUE,
+        by_stage = TRUE,
+        by_cod = TRUE,
+        ...
+    ) {
     out <- list()
@@
         pred = df %>% select(ends_with("_cghr10"), -physician_cghr10),
-        func = func
+        func = func,
+        ...
     ) %>% rename(
@@
     # Calc metric for va coding stage
+    if (by_stage) {
         for (stage in c("is_agreed", "is_recon", "is_adj")) {
@@
                     select(ends_with("_cghr10"), -physician_cghr10),
-            func = func
+                func = func,
+                ...
             ) %>% rename(
@@
         }
+    }
 
     # Calc pcc for each age group
+    if (by_age) {
         for (age_group in c("adult", "child", "neo")) {
@@
                         select(ends_with("_cghr10"), -physician_cghr10),
-                func = func
+                    func = func,
+                    ...
+                ) %>% rename(
+                     {{ metric_name }} := Metric
+                )
+            }
+        }
+    }
+
+    # Calc metric by cause of death
+    if (by_cod) {
+
+        # Get unique causes of death
+        causes <- df %>%
+            select(ends_with("_cghr10")) %>%
+            pivot_longer(
+                everything(),
+                names_to = "column",
+                values_to = "cod"
+            ) %>%
+            distinct(cod) %>%
+            filter(!is.na(cod)) %>%
+            pull(cod)
+
+        # Calc metric by cod
+        for (cod in causes) {
+
+            # Filter data for cod
+            df_filter <- df %>% filter(physician_cghr10 == cod)
+            metric_name = paste0(name, " COD ", cod)
+
+            # Calc metric for cod
+            out[[metric_name]] <- calc_per_model(
+                actual = df_filter %>%
+                    pull(physician_cghr10),
+                pred = df_filter %>%
+                    select(ends_with("_cghr10"), -physician_cghr10),
+                func = func,
+                ...
             ) %>% rename(
@@
 ```{r}
-metrics$pccc <- calc_by_age_stage(df, calc_pccc, "PCCC")
+
+# Get num of unique causes
+ncauses <- df %>%
+    select(ends_with("_cghr10")) %>%
+    pivot_longer(
+        everything(),
+        names_to = "column",
+        values_to = "cod"
+    ) %>%
+    distinct(cod) %>%
+    filter(!is.na(cod)) %>%
+    pull(cod) %>%
+    length
+
+# Calc pccc for age, stage, and cod
+metrics$pccc <- calc_by(df, calc_pccc, "PCCC", N = ncauses)
 metrics$pccc
@@
 ```{r}
-metrics$csmf_acc <- calc_by_age_stage(df, calc_csmf_acc, "CSMF Accuracy")
+metrics$csmf_acc <- calc_by(
+    df,
+    calc_csmf_acc,
+    "CSMF Accuracy",
+    by_cod = FALSE
+)
 metrics$csmf_acc
@@
         size = 2,
-        position = position_nudge(y = -0.065, x = -0.3)
+        hjust = 1,
+        position = position_nudge(y = -0.015, x = -0.3)
     ) +
@@
     ) +
-    geom_segment(aes(x = -Inf, y = 0, xend = Inf, yend = 0), arrow = arrow(length = unit(1, "cm"))) +
     labs(
@@
 
-```{r}
+```{r, fig.height = 16, fig.width = 8}
+
+# Calc total agreed
+nagree <- df %>% filter(is_agreed == TRUE) %>% nrow
+
+# Get unique cause columns
+causes_col <- out %>% select(starts_with("PCCC COD ")) %>% names
+
+# Create cod with counts
+cod_remap <- list()
+for (cod_col in causes_col) {
+
+    # Get cod without prefix
+    cod <- gsub("PCCC COD ", "", cod_col)
+
+    # Calculate num and perc cases for cod
+    ncod <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE) %>% nrow
+    pcod <- (ncod / nagree) * 100
+    pcod_label <- if (round(pcod) >= 1) round(pcod) else "<1"
+
+    # Break cod into newlines if more than 3 words
+    if (str_count(cod, "\\s+") > 3) {
+        cod_label <- str_replace(cod, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
+    } else {
+        cod_label <- cod
+    }
+
+    # Add label for cod
+    cod_remap[[cod]] <- paste0(cod_label, "\n(n=", ncod, ", ", pcod_label, "%)")
+}
+
+# Prepare boxplot data
+coddata <- out %>%
+    select(
+        Model,
+        starts_with("PCCC COD ")
+    ) %>%
+    rename_at(
+         vars(-Model),
+         ~gsub("PCCC COD ", "", .)
+    ) %>%
+    filter(!str_detect(Model, "&")) %>% # remove multi models
+    pivot_longer( # transform to long format
+        cols = -Model,
+        names_to = "COD",
+        values_to = "PCCC"
+    ) %>%
+    mutate( # rename cod with counts
+        "COD" = recode(`COD`, !!!cod_remap)
+    ) %>%
+    group_by(`COD`) %>%
+    mutate( # Make values less than 0 equal to 0
+        PCCC = if_else(PCCC <= 0, 0, PCCC)
+    ) %>%
+    mutate( # Add min, mid, and max model names to label
+        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.03, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
+        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
+        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
+    )
+
+# Create cod order based on max pccc
+codorder <- coddata %>%
+    group_by(COD) %>%
+    summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
+    select(COD, `PCCC Max Value`) %>%
+    arrange(desc(`PCCC Max Value`)) %>%
+    pull(COD)
+coddata$COD <- factor(coddata$COD, levels = rev(codorder))
+
+# Plot boxplot
+codplot <- coddata %>%
+    ggplot(aes(x = COD, y = PCCC)) +
+    geom_boxplot(
+        linewidth = 0.5,
+        width = 0.25
+    ) +
+    geom_text(
+        aes(label = `PCCC Min`),
+        color = "#4d4d4d",
+        size = 2.5,
+        hjust = 1,
+        position = position_nudge(y = -0.12)
+    ) +
+    geom_text(
+        aes(label = `PCCC Max`),
+        color = "#4d4d4d",
+        size = 2.5,
+        hjust = 0,
+        position = position_nudge(y = 0.12)
+    ) +
+    stat_summary( # min pccc txt on boxplot
+        geom = "text",
+        fun = min,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = -0.06),
+        size = 3
+    ) +
+    stat_summary( # max pccc txt on boxplot
+        geom = "text",
+        fun = max,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = 0.06),
+        size = 3
+    ) +
+    labs(
+        x = paste0("Agreed Records (n=", nagree, ", 100%) for ", length(causes_col), " Causes of Death"),
+        y = "PCCC (0=Low, 1=High)"
+    ) +
+    ylim(-0.3, 1.25) +
+    coord_flip() +
+    theme_minimal() +
+    theme(
+        panel.grid = element_blank(),
+        axis.line = element_blank(),
+        axis.line.y = element_blank(),
+        axis.title.x = element_text(margin = margin(t = 5)),
+        axis.title.y = element_text(margin = margin(r = 5)),
+        axis.line.x = element_line(
+            color = "black",
+            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
+        )
+    )
+
+# Save the plot
+codplot
+ggsave("../manuscript/fig-perf-cod.pdf", plot = codplot, dpi = 300)
 ```

### 2023-12-01 src/metrics.Rmd
Regen plots for cod based on agreed records only

@@
             # Filter data for cod
-            df_filter <- df %>% filter(physician_cghr10 == cod)
-            metric_name = paste0(name, " COD ", cod)
+            df_filter <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE)
+            metric_name = paste0(name, " COD Agree ", cod)
 
@@
 # Get unique cause columns
-causes_col <- out %>% select(starts_with("PCCC COD ")) %>% names
+causes_col <- out %>% select(starts_with("PCCC COD Agree ")) %>% names
 
@@
     # Get cod without prefix
-    cod <- gsub("PCCC COD ", "", cod_col)
+    cod <- gsub("PCCC COD Agree ", "", cod_col)
 
@@
         Model,
-        starts_with("PCCC COD ")
+        starts_with("PCCC COD Agree ")
     ) %>%
@@
          vars(-Model),
-         ~gsub("PCCC COD ", "", .)
+         ~gsub("PCCC COD Agree ", "", .)
     ) %>%
@@
     ) +
-    ylim(-0.3, 1.25) +
+    ylim(-0.3, 1.3) +
     coord_flip() +

### 2023-12-01 src/metrics.Rmd
Regen plots

@@
 cod_remap <- list()
+cod_counts <- list()
 for (cod_col in causes_col) {
@@
     cod_remap[[cod]] <- paste0(cod_label, "\n(n=", ncod, ", ", pcod_label, "%)")
+
+    # Store cod count data
+    cod_counts[[cod]] <- ncod
 }
@@
     ) +
-    ylim(0.2, 0.8) +
+    ylim(0.1, 0.75) +
     coord_flip() +
@@
         panel.grid = element_blank(),
+        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
         axis.line = element_line(color = "black"),

### 2023-12-05 src/metrics.Rmd
Calc metrics by age range

@@
         by_cod = TRUE,
+        by_age_range = TRUE,
         ...
@@
                 )
-                metric_name = paste0(
+                metric_name <- paste0(
                     name,
@@
             df_filter <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE)
-            metric_name = paste0(name, " COD Agree ", cod)
+            metric_name <- paste0(name, " COD Agree ", cod)
+
+            # Calc metric for cod
+            out[[metric_name]] <- calc_per_model(
+                actual = df_filter %>%
+                    pull(physician_cghr10),
+                pred = df_filter %>%
+                    select(ends_with("_cghr10"), -physician_cghr10),
+                func = func,
+                ...
+            ) %>% rename(
+                 {{ metric_name }} := Metric
+            )
+        }
+    }
+
+    # Calc metric by age range
+    if (by_age_range) {
+
+        # Get unique age ranges
+        age_ranges <- df %>%
+            pull(age_range) %>%
+            unique
+
+        # Calc metric by age range
+        for (ar in age_ranges) {
+
+            # Filter for age range
+            df_filter <- df %>% filter(age_range == ar & is_agreed == TRUE)
+            metric_name = paste0(name, " Age Agree ", ar)
 
@@
 ```
+
+### Age Range Performance
+
+Display a plot of performance for physician agreed records by age ranges.
+
+```{r, fig.height = 16, fig.width = 8}
+
+# Calc total agreed
+nagree <- df %>% filter(is_agreed == TRUE) %>% nrow
+
+# Get unique age range columns
+arange_col <- out %>% select(starts_with("PCCC Age Agree ")) %>% names
+
+# Create age range with counts
+arange_remap <- list()
+arange_counts <- list()
+for (ar_col in arange_col) {
+
+    # Get cod without prefix
+    ar <- gsub("PCCC Age Agree ", "", ar_col)
+
+    # Calculate num and perc cases for age range
+    narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
+    parange <- (narange / nagree) * 100
+    parange_label <- if (round(parange) >= 1) round(parange) else "<1"
+
+    # Break age range into newlines if more than 3 words
+    if (str_count(ar, "\\s+") > 3) {
+        arange_label <- str_replace(ar, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
+    } else {
+        arange_label <- ar
+    }
+
+    # Add label for cod
+    arange_remap[[ar]] <- paste0(arange_label, "\n(n=", narange, ", ", parange_label, "%)")
+
+    # Store cod count data
+    arange_counts[[ar]] <- narange
+}
+
+# Prepare boxplot data
+ardata <- out %>%
+    select(
+        Model,
+        starts_with("PCCC COD Agree ")
+    ) %>%
+    rename_at(
+         vars(-Model),
+         ~gsub("PCCC COD Agree ", "", .)
+    ) %>%
+    filter(!str_detect(Model, "&")) %>% # remove multi models
+    pivot_longer( # transform to long format
+        cols = -Model,
+        names_to = "COD",
+        values_to = "PCCC"
+    ) %>%
+    mutate( # rename cod with counts
+        "COD" = recode(`COD`, !!!cod_remap)
+    ) %>%
+    group_by(`COD`) %>%
+    mutate( # Make values less than 0 equal to 0
+        PCCC = if_else(PCCC <= 0, 0, PCCC)
+    ) %>%
+    mutate( # Add min, mid, and max model names to label
+        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.03, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
+        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
+        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
+        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
+    )
+
+# Create cod order based on max pccc
+arorder <- ardata %>%
+    group_by(COD) %>%
+    summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
+    select(COD, `PCCC Max Value`) %>%
+    arrange(desc(`PCCC Max Value`)) %>%
+    pull(COD)
+coddata$COD <- factor(coddata$COD, levels = rev(codorder))
+
+# Plot boxplot
+codplot <- coddata %>%
+    ggplot(aes(x = COD, y = PCCC)) +
+    geom_boxplot(
+        linewidth = 0.5,
+        width = 0.25
+    ) +
+    geom_text(
+        aes(label = `PCCC Min`),
+        color = "#4d4d4d",
+        size = 2.5,
+        hjust = 1,
+        position = position_nudge(y = -0.12)
+    ) +
+    geom_text(
+        aes(label = `PCCC Max`),
+        color = "#4d4d4d",
+        size = 2.5,
+        hjust = 0,
+        position = position_nudge(y = 0.12)
+    ) +
+    stat_summary( # min pccc txt on boxplot
+        geom = "text",
+        fun = min,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = -0.06),
+        size = 3
+    ) +
+    stat_summary( # max pccc txt on boxplot
+        geom = "text",
+        fun = max,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = 0.06),
+        size = 3
+    ) +
+    labs(
+        x = paste0("Agreed Records (n=", nagree, ", 100%) for ", length(causes_col), " Causes of Death"),
+        y = "PCCC (0=Low, 1=High)"
+    ) +
+    ylim(-0.3, 1.3) +
+    coord_flip() +
+    theme_minimal() +
+    theme(
+        panel.grid = element_blank(),
+        axis.line = element_blank(),
+        axis.line.y = element_blank(),
+        axis.title.x = element_text(margin = margin(t = 5)),
+        axis.title.y = element_text(margin = margin(r = 5)),
+        axis.line.x = element_line(
+            color = "black",
+            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
+        )
+    )
+
+# Save the plot
+codplot
+ggsave("../manuscript/fig-perf-cod.pdf", plot = codplot, dpi = 300)
+```

### 2023-12-06 src/metrics.Rmd
Add age range plot

@@
 ageplot
-ggsave("../manuscript/fig-perf-ages.pdf", plot = ageplot, dpi = 300)
+ggsave("../manuscript/fig-perf-agegroup.pdf", plot = ageplot, dpi = 300)
 ```
@@
 
-    # Add label for cod
+    # Add label for age ranges
     arange_remap[[ar]] <- paste0(arange_label, "\n(n=", narange, ", ", parange_label, "%)")
 
-    # Store cod count data
+    # Store age range count data
     arange_counts[[ar]] <- narange
@@
         Model,
-        starts_with("PCCC COD Agree ")
+        starts_with("PCCC Age Agree ")
     ) %>%
@@
          vars(-Model),
-         ~gsub("PCCC COD Agree ", "", .)
+         ~gsub("PCCC Age Agree ", "", .)
     ) %>%
@@
         cols = -Model,
-        names_to = "COD",
+        names_to = "Age Range",
         values_to = "PCCC"
@@
     mutate( # rename cod with counts
-        "COD" = recode(`COD`, !!!cod_remap)
-    ) %>%
-    group_by(`COD`) %>%
+        "Age Range" = recode(`Age Range`, !!!arange_remap)
+    ) %>%
+    group_by(`Age Range`) %>%
     mutate( # Make values less than 0 equal to 0
@@
 arorder <- ardata %>%
-    group_by(COD) %>%
+    group_by(`Age Range`) %>%
     summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
-    select(COD, `PCCC Max Value`) %>%
+    select(`Age Range`, `PCCC Max Value`) %>%
     arrange(desc(`PCCC Max Value`)) %>%
-    pull(COD)
-coddata$COD <- factor(coddata$COD, levels = rev(codorder))
+    pull(`Age Range`)
+ardata$`Age Range` <- factor(ardata$`Age Range`, levels = rev(arorder))
 
 # Plot boxplot
-codplot <- coddata %>%
-    ggplot(aes(x = COD, y = PCCC)) +
+arplot <- ardata %>%
+    ggplot(aes(x = `Age Range`, y = PCCC)) +
     geom_boxplot(
@@
     labs(
-        x = paste0("Agreed Records (n=", nagree, ", 100%) for ", length(causes_col), " Causes of Death"),
+        x = paste0("Agreed Records (n=", nagree, ", 100%)"),
         y = "PCCC (0=Low, 1=High)"
@@
 # Save the plot
-codplot
-ggsave("../manuscript/fig-perf-cod.pdf", plot = codplot, dpi = 300)
-```
+arplot
+ggsave("../manuscript/fig-perf-agerange.pdf", plot = arplot, dpi = 300)
+```

### 2023-12-06 src/metrics.Rmd
Adjust plot dims
Clean up labels to disp values only if more than one model

@@
 
-```{r}
+```{r, fig.height = 4, fig.width = 6}
 
@@
     mutate( # Add min, mid, and max model names to label
-        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.03, paste0(Model, " (", round(PCCC, 2), ")"), NA),
-        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
-        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
-        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
-        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
+        "PCCC Min" = if_else(
+            PCCC <= min(PCCC) * 1.03,
+            paste0(Model, " (", round(PCCC, 2), ")"),
+            NA
+        ),
+        "PCCC Max" = if_else(
+            PCCC >= max(PCCC) * 0.97,
+            paste0(Model, " (", round(PCCC, 2), ")"),
+            NA
+        ),
+        "PCCC Mid" = if_else(
+            is.na(`PCCC Min`) & is.na(`PCCC Max`),
+            paste0(Model, "\n(", round(PCCC, 2), ")"),
+            NA
+        ),
+        "PCCC Min" = if_else( # Combine into one row if close PCCC
+            `PCCC` == min(PCCC),
+            if_else(
+                sum(!is.na(`PCCC Min`)) > 1,
+                paste0(na.omit(`PCCC Min`), collapse = "\n"),
+                paste0(
+                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
+                    collapse = "\n"
+                )
+            ),
+            NA
+        ),
+        "PCCC Max" = if_else(
+            `PCCC` == max(PCCC),
+            if_else(
+                sum(!is.na(`PCCC Max`)) > 1,
+                paste0(na.omit(`PCCC Max`), collapse = "\n"),
+                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
+                       collapse = "\n")
+            ),
+            NA
+        )
     )
@@
     ) +
-    ylim(0.1, 0.75) +
+    ylim(0.2, 0.8) +
     coord_flip() +
@@
 
-```{r, fig.height = 16, fig.width = 8}
+```{r, fig.height = 11, fig.width = 8}
 
@@
         hjust = 1,
-        position = position_nudge(y = -0.12)
+        position = position_nudge(y = -0.065)
     ) +
@@
         hjust = 0,
-        position = position_nudge(y = 0.12)
+        position = position_nudge(y = 0.065)
     ) +
@@
         aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = -0.06),
+        position = position_nudge(y = -0.03),
         size = 3
@@
         aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = 0.06),
+        position = position_nudge(y = 0.03),
         size = 3
@@
     ) +
-    ylim(-0.3, 1.3) +
+    ylim(0.1, 1) +
     coord_flip() +

### 2023-12-06 src/metrics.Rmd
Clean labels for smaller plots

@@
 df <- df %>%
-    mutate(
+    mutate( # Remove additional info on age range
+        "age_range" = str_replace(na.omit(age_range), "\\s*\\(.*\\)", "")
+    ) %>%
+    mutate( # Combine models
         "chatgpt3_insilicova_cghr10" = if_else(
@@
 
-```{r, fig.height = 4, fig.width = 6}
+```{r, fig.height = 3, fig.width = 6}
 
@@
     mutate( # Add min, mid, and max model names to label
-        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.05, paste0(Model, " (", round(PCCC, 2), ")"), NA),
-        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
-        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
-        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
-        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
-    )
-
-# Plot boxplot
-allplot <- alldata %>%
-    ggplot(aes(x = Stage, y = PCCC)) +
-    geom_boxplot(
-        linewidth = 0.5,
-        width = 0.25
-    ) +
-    geom_dotplot(
-        binaxis = "y",
-        binwidth = 0.03,
-        dotsize = 0.3,
-        fill = "white",
-        color = "darkgray",
-        stackdir = "center",
-        stackratio = 2,
-        position = position_nudge(x = -0.3)
-    ) +
-    geom_text(
-        aes(label = `PCCC Min`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 1,
-        position = position_nudge(y = -0.015, x = -0.3)
-    ) +
-    geom_text(
-        aes(label = `PCCC Max`),
-        color = "#4d4d4d",
-        size = 2,
-        position = position_nudge(y = 0.065, x = -0.3)
-    ) +
-    geom_text(
-        aes(label = `PCCC Mid`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 1,
-        position = position_nudge(y = -0.015, x = -0.3)
-    ) +
-    stat_summary( # min pccc txt on boxplot
-        geom = "text",
-        fun = min,
-        aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = -0.025),
-        size = 3
-    ) +
-    stat_summary( # max pccc txt on boxplot
-        geom = "text",
-        fun = max,
-        aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = 0.025),
-        size = 3
-    ) +
-    labs(
-        x = element_blank(),
-        y = "PCCC (0=Low, 1=High)"
-    ) +
-    ylim(0.2, 0.8) +
-    coord_flip() +
-    theme_minimal() +
-    theme(
-        panel.grid = element_blank(),
-        axis.line = element_line(color = "black"),
-        axis.title.x = element_text(margin = margin(t = 5)),
-        axis.title.y = element_text(margin = margin(r = 5)),
-        axis.line.x = element_line(
-            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
-        ),
-        axis.line.y = element_blank()
-    )
-
-# Save the plot
-allplot
-ggsave("../manuscript/fig-perf-allvsagree.pdf", plot = allplot, dpi = 300)
-```
-
-### COD Performance
-
-Plot model performance for physician agreed records by cause of death category.
-
-```{r, fig.height = 16, fig.width = 8}
-
-# Calc total agreed
-nagree <- df %>% filter(is_agreed == TRUE) %>% nrow
-
-# Get unique cause columns
-causes_col <- out %>% select(starts_with("PCCC COD Agree ")) %>% names
-
-# Create cod with counts
-cod_remap <- list()
-cod_counts <- list()
-for (cod_col in causes_col) {
-
-    # Get cod without prefix
-    cod <- gsub("PCCC COD Agree ", "", cod_col)
-
-    # Calculate num and perc cases for cod
-    ncod <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE) %>% nrow
-    pcod <- (ncod / nagree) * 100
-    pcod_label <- if (round(pcod) >= 1) round(pcod) else "<1"
-
-    # Break cod into newlines if more than 3 words
-    if (str_count(cod, "\\s+") > 3) {
-        cod_label <- str_replace(cod, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
-    } else {
-        cod_label <- cod
-    }
-
-    # Add label for cod
-    cod_remap[[cod]] <- paste0(cod_label, "\n(n=", ncod, ", ", pcod_label, "%)")
-
-    # Store cod count data
-    cod_counts[[cod]] <- ncod
-}
-
-# Prepare boxplot data
-coddata <- out %>%
-    select(
-        Model,
-        starts_with("PCCC COD Agree ")
-    ) %>%
-    rename_at(
-         vars(-Model),
-         ~gsub("PCCC COD Agree ", "", .)
-    ) %>%
-    filter(!str_detect(Model, "&")) %>% # remove multi models
-    pivot_longer( # transform to long format
-        cols = -Model,
-        names_to = "COD",
-        values_to = "PCCC"
-    ) %>%
-    mutate( # rename cod with counts
-        "COD" = recode(`COD`, !!!cod_remap)
-    ) %>%
-    group_by(`COD`) %>%
-    mutate( # Make values less than 0 equal to 0
-        PCCC = if_else(PCCC <= 0, 0, PCCC)
-    ) %>%
-    mutate( # Add min, mid, and max model names to label
         "PCCC Min" = if_else(
-            PCCC <= min(PCCC) * 1.03,
+            PCCC <= min(PCCC) * 1.05,
             paste0(Model, " (", round(PCCC, 2), ")"),
@@
             paste0(Model, "\n(", round(PCCC, 2), ")"),
+            NA
+        ),
+        "PCCC Mid Value" = if_else(
+            is.na(`PCCC Min`) & is.na(`PCCC Max`),
+            PCCC,
             NA
@@
 
+# Plot boxplot
+allplot <- alldata %>%
+    ggplot(aes(x = Stage, y = PCCC)) +
+    geom_boxplot(
+        linewidth = 0.5,
+        width = 0.25
+    ) +
+    geom_point(
+        aes(y = `PCCC Mid Value`),
+        shape = 1,
+        size = 1.5,
+        fill = "white",
+        color = "darkgray",
+        alpha = 0.8,
+        position = position_nudge(x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Min`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 1,
+        position = position_nudge(y = -0.055)
+    ) +
+    geom_text(
+        aes(label = `PCCC Max`),
+        color = "#4d4d4d",
+        size = 2,
+        position = position_nudge(y = 0.08)
+    ) +
+    geom_text(
+        aes(label = `PCCC Mid`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 1,
+        position = position_nudge(y = -0.015, x = -0.3)
+    ) +
+    stat_summary( # min pccc txt on boxplot
+        geom = "text",
+        fun = min,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = -0.025),
+        size = 3
+    ) +
+    stat_summary( # max pccc txt on boxplot
+        geom = "text",
+        fun = max,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = 0.025),
+        size = 3
+    ) +
+    labs(
+        x = element_blank(),
+        y = "PCCC (0=Low, 1=High)"
+    ) +
+    ylim(0.2, 0.85) +
+    coord_flip() +
+    theme_minimal() +
+    theme(
+        panel.grid = element_blank(),
+        axis.line = element_line(color = "black"),
+        axis.title.x = element_text(margin = margin(t = 10)),
+        axis.title.y = element_text(margin = margin(r = 10)),
+        axis.line.x = element_line(
+            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
+        ),
+        axis.line.y = element_blank()
+    )
+
+# Save the plot
+allplot
+ggsave("../manuscript/fig-perf-allvsagree.pdf", plot = allplot, dpi = 300)
+```
+
+### COD Performance
+
+Plot model performance for physician agreed records by cause of death category.
+
+```{r, fig.height = 16.5, fig.width = 8}
+
+# Calc total agreed
+nagree <- df %>% filter(is_agreed == TRUE) %>% nrow
+
+# Get unique cause columns
+causes_col <- out %>% select(starts_with("PCCC COD Agree ")) %>% names
+
+# Create cod with counts
+cod_remap <- list()
+cod_counts <- list()
+for (cod_col in causes_col) {
+
+    # Get cod without prefix
+    cod <- gsub("PCCC COD Agree ", "", cod_col)
+
+    # Calculate num and perc cases for cod
+    ncod <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE) %>% nrow
+    pcod <- (ncod / nagree) * 100
+    pcod_label <- if (round(pcod) >= 1) round(pcod) else "<1"
+
+    # Break cod into newlines if more than 3 words
+    if (str_count(cod, "\\s+") > 3) {
+        cod_label <- str_replace(cod, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
+    } else {
+        cod_label <- cod
+    }
+
+    # Add label for cod
+    cod_remap[[cod]] <- paste0(cod_label, "\n(n=", ncod, ", ", pcod_label, "%)")
+
+    # Store cod count data
+    cod_counts[[cod]] <- ncod
+}
+
+# Prepare boxplot data
+coddata <- out %>%
+    select(
+        Model,
+        starts_with("PCCC COD Agree ")
+    ) %>%
+    rename_at(
+         vars(-Model),
+         ~gsub("PCCC COD Agree ", "", .)
+    ) %>%
+    filter(!str_detect(Model, "&")) %>% # remove multi models
+    pivot_longer( # transform to long format
+        cols = -Model,
+        names_to = "COD",
+        values_to = "PCCC"
+    ) %>%
+    mutate( # rename cod with counts
+        "COD" = recode(`COD`, !!!cod_remap)
+    ) %>%
+    group_by(`COD`) %>%
+    mutate( # Make values less than 0 equal to 0
+        PCCC = if_else(PCCC <= 0, 0, PCCC)
+    ) %>%
+    mutate( # Add min, mid, and max model names to label
+        "PCCC Min" = if_else(
+            PCCC <= min(PCCC) * 1.03,
+            paste0(Model, " (", round(PCCC, 2), ")"),
+            NA
+        ),
+        "PCCC Max" = if_else(
+            PCCC >= max(PCCC) * 0.97,
+            paste0(Model, " (", round(PCCC, 2), ")"),
+            NA
+        ),
+        "PCCC Mid" = if_else(
+            is.na(`PCCC Min`) & is.na(`PCCC Max`),
+            paste0(Model, "\n(", round(PCCC, 2), ")"),
+            NA
+        ),
+        "PCCC Min" = if_else( # Combine into one row if close PCCC
+            `PCCC` == min(PCCC),
+            if_else(
+                sum(!is.na(`PCCC Min`)) > 1,
+                paste0(na.omit(`PCCC Min`), collapse = "\n"),
+                paste0(
+                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
+                    collapse = "\n"
+                )
+            ),
+            NA
+        ),
+        "PCCC Max" = if_else(
+            `PCCC` == max(PCCC),
+            if_else(
+                sum(!is.na(`PCCC Max`)) > 1,
+                paste0(na.omit(`PCCC Max`), collapse = "\n"),
+                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
+                       collapse = "\n")
+            ),
+            NA
+        )
+    )
+
 # Create cod order based on max pccc
@@
     labs(
-        x = paste0("Agreed Records (n=", nagree, ", 100%) for ", length(causes_col), " Causes of Death"),
+        x = paste0("Physician Agreed Records (n=", nagree, ", 100%) for ", length(causes_col), " Causes of Death"),
         y = "PCCC (0=Low, 1=High)"
@@
         axis.line.y = element_blank(),
-        axis.title.x = element_text(margin = margin(t = 5)),
-        axis.title.y = element_text(margin = margin(r = 5)),
+        axis.title.x = element_text(margin = margin(t = 10)),
+        axis.title.y = element_text(margin = margin(r = 10)),
         axis.line.x = element_line(
@@
     mutate( # Add min, mid, and max model names to label
-        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.15, paste0(Model, " (", round(PCCC, 2), ")"), NA),
-        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.95, paste0(Model, " (", round(PCCC, 2), ")"), NA),
-        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
-        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
-        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
-    )
-
-# Plot boxplot
-ageplot <- agedata %>%
-    ggplot(aes(x = `Age Group`, y = PCCC)) +
-    geom_boxplot(
-        linewidth = 0.5,
-        width = 0.25
-    ) +
-    geom_dotplot(
-        binaxis = "y",
-        binwidth = 0.03,
-        dotsize = 0.3,
-        fill = "white",
-        color = "darkgray",
-        stackdir = "center",
-        stackratio = 2,
-        position = position_nudge(x = -0.3)
-    ) +
-    geom_text(
-        aes(label = `PCCC Min`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 1,
-        position = position_nudge(y = -0.015, x = -0.3)
-    ) +
-    geom_text(
-        aes(label = `PCCC Max`),
-        color = "#4d4d4d",
-        size = 2,
-        position = position_nudge(y = 0.055, x = -0.3)
-    ) +
-    geom_text(
-        aes(label = `PCCC Mid`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 1,
-        position = position_nudge(y = -0.015, x = -0.3)
-    ) +
-    stat_summary( # min pccc txt on boxplot
-        geom = "text",
-        fun = min,
-        aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = -0.025),
-        size = 3
-    ) +
-    stat_summary( # max pccc txt on boxplot
-        geom = "text",
-        fun = max,
-        aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = 0.025),
-        size = 3
-    ) +
-    labs(
-        x = paste0("Agreed Records (n=", nagree, ", 100%)"),
-        y = "PCCC (0=Low, 1=High)"
-    ) +
-    ylim(0.2, 0.8) +
-    coord_flip() +
-    theme_minimal() +
-    theme(
-        panel.grid = element_blank(),
-        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
-        axis.line = element_line(color = "black"),
-        axis.title.x = element_text(margin = margin(t = 5)),
-        axis.title.y = element_text(margin = margin(r = 5)),
-        axis.line.x = element_line(
-            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
-        ),
-        axis.line.y = element_blank()
-    )
-
-# Save the plot
-ageplot
-ggsave("../manuscript/fig-perf-agegroup.pdf", plot = ageplot, dpi = 300)
-```
-
-### Age Range Performance
-
-Display a plot of performance for physician agreed records by age ranges.
-
-```{r, fig.height = 11, fig.width = 8}
-
-# Calc total agreed
-nagree <- df %>% filter(is_agreed == TRUE) %>% nrow
-
-# Get unique age range columns
-arange_col <- out %>% select(starts_with("PCCC Age Agree ")) %>% names
-
-# Create age range with counts
-arange_remap <- list()
-arange_counts <- list()
-for (ar_col in arange_col) {
-
-    # Get cod without prefix
-    ar <- gsub("PCCC Age Agree ", "", ar_col)
-
-    # Calculate num and perc cases for age range
-    narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
-    parange <- (narange / nagree) * 100
-    parange_label <- if (round(parange) >= 1) round(parange) else "<1"
-
-    # Break age range into newlines if more than 3 words
-    if (str_count(ar, "\\s+") > 3) {
-        arange_label <- str_replace(ar, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
-    } else {
-        arange_label <- ar
-    }
-
-    # Add label for age ranges
-    arange_remap[[ar]] <- paste0(arange_label, "\n(n=", narange, ", ", parange_label, "%)")
-
-    # Store age range count data
-    arange_counts[[ar]] <- narange
-}
-
-# Prepare boxplot data
-ardata <- out %>%
-    select(
-        Model,
-        starts_with("PCCC Age Agree ")
-    ) %>%
-    rename_at(
-         vars(-Model),
-         ~gsub("PCCC Age Agree ", "", .)
-    ) %>%
-    filter(!str_detect(Model, "&")) %>% # remove multi models
-    pivot_longer( # transform to long format
-        cols = -Model,
-        names_to = "Age Range",
-        values_to = "PCCC"
-    ) %>%
-    mutate( # rename cod with counts
-        "Age Range" = recode(`Age Range`, !!!arange_remap)
-    ) %>%
-    group_by(`Age Range`) %>%
-    mutate( # Make values less than 0 equal to 0
-        PCCC = if_else(PCCC <= 0, 0, PCCC)
-    ) %>%
-    mutate( # Add min, mid, and max model names to label
         "PCCC Min" = if_else(
-            PCCC <= min(PCCC) * 1.03,
+            PCCC <= min(PCCC) * 1.15,
             paste0(Model, " (", round(PCCC, 2), ")"),
@@
         "PCCC Max" = if_else(
-            PCCC >= max(PCCC) * 0.97,
+            PCCC >= max(PCCC) * 0.95,
             paste0(Model, " (", round(PCCC, 2), ")"),
@@
 
+# Plot boxplot
+ageplot <- agedata %>%
+    ggplot(aes(x = `Age Group`, y = PCCC)) +
+    geom_boxplot(
+        linewidth = 0.5,
+        width = 0.25
+    ) +
+    geom_point(
+        aes(y = `PCCC Mid Value`),
+        shape = 1,
+        size = 1.5,
+        fill = "white",
+        color = "darkgray",
+        alpha = 0.8,
+        position = position_nudge(x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Min`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 1,
+        position = position_nudge(y = -0.055)
+    ) +
+    geom_text(
+        aes(label = `PCCC Max`),
+        color = "#4d4d4d",
+        size = 2,
+        position = position_nudge(y = 0.08)
+    ) +
+    geom_text(
+        aes(label = `PCCC Mid`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 1,
+        position = position_nudge(y = -0.015, x = -0.3)
+    ) +
+    stat_summary( # min pccc txt on boxplot
+        geom = "text",
+        fun = min,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = -0.025),
+        size = 3
+    ) +
+    stat_summary( # max pccc txt on boxplot
+        geom = "text",
+        fun = max,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = 0.025),
+        size = 3
+    ) +
+    labs(
+        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
+        y = "PCCC (0=Low, 1=High)"
+    ) +
+    ylim(0.25, 0.85) +
+    coord_flip() +
+    theme_minimal() +
+    theme(
+        panel.grid = element_blank(),
+        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
+        axis.line = element_line(color = "black"),
+        axis.title.x = element_text(margin = margin(t = 10)),
+        axis.title.y = element_text(margin = margin(r = 10)),
+        axis.line.x = element_line(
+            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
+        ),
+        axis.line.y = element_blank()
+    )
+
+# Save the plot
+ageplot
+ggsave("../manuscript/fig-perf-agegroup.pdf", plot = ageplot, dpi = 300)
+```
+
+### Age Range Performance
+
+Display a plot of performance for physician agreed records by age ranges.
+
+```{r, fig.height = 11, fig.width = 8}
+
+# Calc total agreed
+nagree <- df %>% filter(is_agreed == TRUE) %>% nrow
+
+# Get unique age range columns
+arange_col <- out %>% select(starts_with("PCCC Age Agree ")) %>% names
+
+# Create age range with counts
+arange_remap <- list()
+arange_counts <- list()
+for (ar_col in arange_col) {
+
+    # Get cod without prefix
+    ar <- gsub("PCCC Age Agree ", "", ar_col)
+
+    # Calculate num and perc cases for age range
+    narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
+    parange <- (narange / nagree) * 100
+    parange_label <- if (round(parange) >= 1) round(parange) else "<1"
+
+    # Break age range into newlines if more than 3 words
+    if (str_count(ar, "\\s+") > 3) {
+        arange_label <- str_replace(ar, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
+    } else {
+        arange_label <- ar
+    }
+
+    # Add label for age ranges
+    arange_remap[[ar]] <- paste0(arange_label, "\n(n=", narange, ", ", parange_label, "%)")
+
+    # Store age range count data
+    arange_counts[[ar]] <- narange
+}
+
+# Prepare boxplot data
+ardata <- out %>%
+    select(
+        Model,
+        starts_with("PCCC Age Agree ")
+    ) %>%
+    rename_at(
+         vars(-Model),
+         ~gsub("PCCC Age Agree ", "", .)
+    ) %>%
+    filter(!str_detect(Model, "&")) %>% # remove multi models
+    pivot_longer( # transform to long format
+        cols = -Model,
+        names_to = "Age Range",
+        values_to = "PCCC"
+    ) %>%
+    mutate( # rename cod with counts
+        "Age Range" = recode(`Age Range`, !!!arange_remap)
+    ) %>%
+    group_by(`Age Range`) %>%
+    mutate( # Make values less than 0 equal to 0
+        PCCC = if_else(PCCC <= 0, 0, PCCC)
+    ) %>%
+    mutate( # Add min, mid, and max model names to label
+        "PCCC Min" = if_else(
+            PCCC <= min(PCCC) * 1.03,
+            paste0(Model, " (", round(PCCC, 2), ")"),
+            NA
+        ),
+        "PCCC Max" = if_else(
+            PCCC >= max(PCCC) * 0.97,
+            paste0(Model, " (", round(PCCC, 2), ")"),
+            NA
+        ),
+        "PCCC Mid" = if_else(
+            is.na(`PCCC Min`) & is.na(`PCCC Max`),
+            paste0(Model, "\n(", round(PCCC, 2), ")"),
+            NA
+        ),
+        "PCCC Min" = if_else( # Combine into one row if close PCCC
+            `PCCC` == min(PCCC),
+            if_else(
+                sum(!is.na(`PCCC Min`)) > 1,
+                paste0(na.omit(`PCCC Min`), collapse = "\n"),
+                paste0(
+                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
+                    collapse = "\n"
+                )
+            ),
+            NA
+        ),
+        "PCCC Max" = if_else(
+            `PCCC` == max(PCCC),
+            if_else(
+                sum(!is.na(`PCCC Max`)) > 1,
+                paste0(na.omit(`PCCC Max`), collapse = "\n"),
+                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
+                       collapse = "\n")
+            ),
+            NA
+        )
+    )
+
 # Create cod order based on max pccc
@@
     labs(
-        x = paste0("Agreed Records (n=", nagree, ", 100%)"),
+        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
         y = "PCCC (0=Low, 1=High)"

### 2023-12-06 src/plots.Rmd
Add label clean step in plotting

--- 2023-12-06 src/metrics.Rmd
@@
 library(tidyverse)
+```
+
+```{r, echo=FALSE}
+cat("R Version\n---")
+R.version
+
+cat("\nPackage Versions\n---")
+cat(paste0("\ntidyverse ", packageVersion("tidyverse")))
 ```
@@
 
+### Clean Labels
+
+Clean `age_range` labels to include only values and unit of measure.
+
+```{r}
+df <- df %>% mutate(
+    "age_range" = str_replace(
+        na.omit(age_range),
+        "\\s*\\(.*\\)",
+        ""
+    ))
+```
+
 ### Physician Cases
@@
 df <- df %>%
-    mutate( # Remove additional info on age range
-        "age_range" = str_replace(na.omit(age_range), "\\s*\\(.*\\)", "")
-    ) %>%
     mutate( # Combine models

### 2023-12-07 src/plots.Rmd
Fix plots script

@@
 ```{r}
-df <- df %>% mutate(
+df <- raw_df %>% mutate(
     "age_range" = str_replace(
-        na.omit(age_range),
+        age_range,
         "\\s*\\(.*\\)",
@@
 ```{r}
-df <- raw_df %>%
+df <- df %>%
     filter(!is.na(physician_cghr10) & !is.null(physician_cghr10))

### 2023-12-07 src/preprocess.Rmd
regen pdfs
Add sex to preprocess

--- 2023-11-27 src/preprocess.Rmd
@@
 
+```{r, echo=FALSE}
+cat("R Version\n---")
+R.version
+
+cat("\nPackage Versions\n---")
+cat(paste0("\ntidyverse ", packageVersion("tidyverse")))
+```
+
 ## Data
@@
     "death_age_group",
+    "sex_death",
     "p1_icd",
@@
 phy_rename <- c(
+    sex = "sex_death",
     age_range = "death_age_group"
@@
     "death_age_group",
+    "sex_death",
     "p1_icd_cod",
@@
     age_range = "death_age_group",
+    sex = "sex_death",
     p1_icd = "p1_icd_cod",
@@
         age,
+        age_range,
+        sex,
         p1_icd,

### 2023-12-07 src/plots.Rmd
Add sex to preprocess
Add CSMF to overall plots and reduce redundant info on min/max pccc labels

@@
     ))
+df
 ```
@@
 
-## Methods
+## Metrics
 
@@
 
-## Results
+## Plots
 
@@
 
-### All vs Agree Performance
+### Exploration
+
+#### Cases by Sex
+
+#### Cases by Age Group
+
+#### Cases by Age Range
+
+#### Cases by COD
+
+### Performance
+
+#### All vs Agree Performance
 
@@
         `PCCC`,
-        `PCCC Agreement`
+        `PCCC Agreement`,
+        `CSMF Accuracy`,
+        `CSMF Accuracy Agreement`
     ) %>%
@@
     pivot_longer( # transform to long format
-        cols = -Model,
+        cols = -c(
+            Model,
+            `CSMF Accuracy`,
+            `CSMF Accuracy Agreement`
+        ),
         names_to = "Stage",
         values_to = "PCCC"
-    ) %>%
-    mutate( # re-order stage
-        Stage = factor(Stage, levels = c(
-            "Agreed",
-            "All"
-        ))
-    ) %>%
-    mutate( # rename stages with counts
-        Stage = recode(Stage, !!!stage_remap)
     ) %>%
@@
             PCCC <= min(PCCC) * 1.05,
-            paste0(Model, " (", round(PCCC, 2), ")"),
+            paste0(Model, "\n(", round(PCCC, 2), ", CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
             NA
@@
             PCCC >= max(PCCC) * 0.97,
-            paste0(Model, " (", round(PCCC, 2), ")"),
+            paste0(Model, "\n(", round(PCCC, 2), ", CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
             NA
@@
             is.na(`PCCC Min`) & is.na(`PCCC Max`),
-            paste0(Model, "\n(", round(PCCC, 2), ")"),
+            paste0(Model, "\n(", round(PCCC, 2), ", CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
             NA
@@
                 paste0(
-                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
+                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
                     collapse = "\n"
@@
                 paste0(na.omit(`PCCC Max`), collapse = "\n"),
-                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
-                       collapse = "\n")
-            ),
-            NA
-        )
+                paste0(
+                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
+                    collapse = "\n"
+                )
+            ),
+            NA
+        )
+    ) %>%
+    mutate( # re-order stage
+        Stage = factor(Stage, levels = c(
+            "Agreed",
+            "All"
+        ))
+    ) %>%
+    mutate( # rename stages with counts
+        Stage = recode(Stage, !!!stage_remap)
     )
@@
         size = 2,
-        position = position_nudge(y = 0.08)
+        hjust = 0,
+        position = position_nudge(y = 0.055)
     ) +
@@
 
-### COD Performance
+#### Age Group Perfomance
+
+Display a plot of performance for physician agreed records by age group.
+
+```{r, fig.height = 4, fig.width = 6}
+
+# Calc age counts
+nagree <- nrow(df %>% filter(is_agreed == TRUE))
+nadult <- nrow(df %>% filter(age == "adult" & is_agreed == TRUE))
+nchild <- nrow(df %>% filter(age == "child" & is_agreed == TRUE))
+nneo <- nrow(df %>% filter(age == "neo" & is_agreed == TRUE))
+
+# Calc age perc
+padult <- (nadult / nagree) * 100
+pchild <- (nchild / nagree) * 100
+pneo <- (nneo / nagree) * 100
+
+# Create age with counts
+age_remap <- c(
+    "Adult" = paste0("Adult\n12+ years\n(n=", nadult, ", ", round(padult), "%)"),
+    "Child" = paste0("Child\n28 days to 11 years\n(n=", nchild, ", ", round(pchild), "%)"),
+    "Neonatal" = paste0("Neonatal\n<28 days\n(n=", nneo, ", ", round(pneo), "%)")
+)
+
+# Prepare boxplot data
+agedata <- out %>%
+    select(
+        Model,
+        `PCCC Adult Agreement`,
+        `PCCC Child Agreement`,
+        `PCCC Neo Agreement`,
+        `CSMF Accuracy Adult Agreement`,
+        `CSMF Accuracy Child Agreement`,
+        `CSMF Accuracy Neo Agreement`
+    ) %>%
+    rename(
+         Adult = `PCCC Adult Agreement`,
+         Child = `PCCC Child Agreement`,
+         Neonatal = `PCCC Neo Agreement`
+    ) %>%
+    filter(!str_detect(Model, "&")) %>% # remove multi models
+    pivot_longer( # transform to long format
+        cols = -c(
+            Model,
+            `CSMF Accuracy Adult Agreement`,
+            `CSMF Accuracy Child Agreement`,
+            `CSMF Accuracy Neo Agreement`
+        ),
+        names_to = "Age Group",
+        values_to = "PCCC"
+    ) %>%
+    group_by(`Age Group`) %>%
+    mutate( # Add min, mid, and max model names to label
+        "PCCC Min" = if_else(
+            PCCC <= min(PCCC) * 1.15,
+            paste0(
+                Model, "\n(",
+                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
+                "CSMF=", round(case_when(
+                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
+                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
+                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
+                ),2), ")"),
+            NA
+        ),
+        "PCCC Max" = if_else(
+            PCCC >= max(PCCC) * 0.95,
+            paste0(
+                Model, "\n(",
+                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
+                ", CSMF=", round(case_when(
+                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
+                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
+                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
+                ),2), ")"),
+            NA
+        ),
+        "PCCC Mid" = if_else(
+            is.na(`PCCC Min`) & is.na(`PCCC Max`),
+            paste0(
+                Model, "\n(", round(PCCC, 2),
+                ", CSMF=", round(case_when(
+                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
+                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
+                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
+                ),2), ")"),
+            NA
+        ),
+        "PCCC Mid Value" = if_else(
+            is.na(`PCCC Min`) & is.na(`PCCC Max`),
+            PCCC,
+            NA
+        ),
+        "PCCC Min" = if_else( # Combine into one row if close PCCC
+            `PCCC` == min(PCCC),
+            if_else(
+                sum(!is.na(`PCCC Min`)) > 1,
+                paste0(na.omit(`PCCC Min`), collapse = "\n"),
+                paste0(
+                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
+                    collapse = "\n"
+                )
+            ),
+            NA
+        ),
+        "PCCC Max" = if_else(
+            `PCCC` == max(PCCC),
+            if_else(
+                sum(!is.na(`PCCC Max`)) > 1,
+                paste0(na.omit(`PCCC Max`), collapse = "\n"),
+                paste0(
+                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
+                    collapse = "\n"
+                )
+            ),
+            NA
+        )
+    )%>%
+    mutate( # re-order age
+        "Age Group" = factor(`Age Group`, levels = c(
+            "Neonatal",
+            "Child",
+            "Adult"
+        ))
+    ) %>%
+    mutate( # rename ages with counts
+        "Age Group" = recode(`Age Group`, !!!age_remap)
+    )
+
+# Plot boxplot
+ageplot <- agedata %>%
+    ggplot(aes(x = `Age Group`, y = PCCC)) +
+    geom_boxplot(
+        linewidth = 0.5,
+        width = 0.25
+    ) +
+    geom_point(
+        aes(y = `PCCC Mid Value`),
+        shape = 1,
+        size = 1.5,
+        fill = "white",
+        color = "darkgray",
+        alpha = 0.8,
+        position = position_nudge(x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Min`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 1,
+        position = position_nudge(y = -0.055)
+    ) +
+    geom_text(
+        aes(label = `PCCC Max`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 0,
+        position = position_nudge(y = 0.055)
+    ) +
+    geom_text(
+        aes(label = `PCCC Mid`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 1,
+        position = position_nudge(y = -0.015, x = -0.3)
+    ) +
+    stat_summary( # min pccc txt on boxplot
+        geom = "text",
+        fun = min,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = -0.025),
+        size = 3
+    ) +
+    stat_summary( # max pccc txt on boxplot
+        geom = "text",
+        fun = max,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = 0.025),
+        size = 3
+    ) +
+    labs(
+        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
+        y = "PCCC (0=Low, 1=High)"
+    ) +
+    ylim(0.25, 0.85) +
+    coord_flip() +
+    theme_minimal() +
+    theme(
+        panel.grid = element_blank(),
+        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
+        axis.line = element_line(color = "black"),
+        axis.title.x = element_text(margin = margin(t = 10)),
+        axis.title.y = element_text(margin = margin(r = 10)),
+        axis.line.x = element_line(
+            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
+        ),
+        axis.line.y = element_blank()
+    )
+
+# Save the plot
+ageplot
+ggsave("../manuscript/fig-perf-agegroup.pdf", plot = ageplot, dpi = 300)
+```
+
+#### Age Range Performance
+
+Display a plot of performance for physician agreed records by age ranges.
+
+```{r, fig.height = 11, fig.width = 8}
+
+# Calc total agreed
+nagree <- df %>% filter(is_agreed == TRUE) %>% nrow
+
+# Get unique age range columns
+arange_col <- out %>% select(starts_with("PCCC Age Agree ")) %>% names
+
+# Create age range with counts
+arange_remap <- list()
+arange_counts <- list()
+for (ar_col in arange_col) {
+
+    # Get cod without prefix
+    ar <- gsub("PCCC Age Agree ", "", ar_col)
+
+    # Calculate num and perc cases for age range
+    narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
+    parange <- (narange / nagree) * 100
+    parange_label <- if (round(parange) >= 1) round(parange) else "<1"
+
+    # Break age range into newlines if more than 3 words
+    if (str_count(ar, "\\s+") > 3) {
+        arange_label <- str_replace(ar, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
+    } else {
+        arange_label <- ar
+    }
+
+    # Add label for age ranges
+    arange_remap[[ar]] <- paste0(arange_label, "\n(n=", narange, ", ", parange_label, "%)")
+
+    # Store age range count data
+    arange_counts[[ar]] <- narange
+}
+
+# Prepare boxplot data
+ardata <- out %>%
+    select(
+        Model,
+        starts_with("PCCC Age Agree ")
+    ) %>%
+    rename_at(
+         vars(-Model),
+         ~gsub("PCCC Age Agree ", "", .)
+    ) %>%
+    filter(!str_detect(Model, "&")) %>% # remove multi models
+    pivot_longer( # transform to long format
+        cols = -Model,
+        names_to = "Age Range",
+        values_to = "PCCC"
+    ) %>%
+    mutate( # rename cod with counts
+        "Age Range" = recode(`Age Range`, !!!arange_remap)
+    ) %>%
+    group_by(`Age Range`) %>%
+    mutate( # Make values less than 0 equal to 0
+        PCCC = if_else(PCCC <= 0, 0, PCCC)
+    ) %>%
+    mutate( # Add min, mid, and max model names to label
+        "PCCC Min" = if_else(
+            PCCC <= min(PCCC) * 1.03,
+            paste0(
+                Model,
+                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
+            ),
+            NA
+        ),
+        "PCCC Max" = if_else(
+            PCCC >= max(PCCC) * 0.97,
+            paste0(
+                Model,
+                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
+            ),
+            NA
+        ),
+        "PCCC Mid" = if_else(
+            is.na(`PCCC Min`) & is.na(`PCCC Max`),
+            paste0(Model, "\n(", round(PCCC, 2), ")"),
+            NA
+        ),
+        "PCCC Min" = if_else( # Combine into one row if close PCCC
+            `PCCC` == min(PCCC),
+            if_else(
+                sum(!is.na(`PCCC Min`)) > 1,
+                paste0(na.omit(`PCCC Min`), collapse = "\n"),
+                paste0(
+                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
+                    collapse = "\n"
+                )
+            ),
+            NA
+        ),
+        "PCCC Max" = if_else(
+            `PCCC` == max(PCCC),
+            if_else(
+                sum(!is.na(`PCCC Max`)) > 1,
+                paste0(na.omit(`PCCC Max`), collapse = "\n"),
+                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
+                       collapse = "\n")
+            ),
+            NA
+        )
+    )
+
+# Create cod order based on max pccc
+arorder <- ardata %>%
+    group_by(`Age Range`) %>%
+    summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
+    select(`Age Range`, `PCCC Max Value`) %>%
+    arrange(desc(`PCCC Max Value`)) %>%
+    pull(`Age Range`)
+ardata$`Age Range` <- factor(ardata$`Age Range`, levels = rev(arorder))
+
+# Plot boxplot
+arplot <- ardata %>%
+    ggplot(aes(x = `Age Range`, y = PCCC)) +
+    geom_boxplot(
+        linewidth = 0.5,
+        width = 0.25
+    ) +
+    geom_text(
+        aes(label = `PCCC Min`),
+        color = "#4d4d4d",
+        size = 2.5,
+        hjust = 1,
+        position = position_nudge(y = -0.065)
+    ) +
+    geom_text(
+        aes(label = `PCCC Max`),
+        color = "#4d4d4d",
+        size = 2.5,
+        hjust = 0,
+        position = position_nudge(y = 0.065)
+    ) +
+    stat_summary( # min pccc txt on boxplot
+        geom = "text",
+        fun = min,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = -0.03),
+        size = 3
+    ) +
+    stat_summary( # max pccc txt on boxplot
+        geom = "text",
+        fun = max,
+        aes(label = sprintf("%1.2f", after_stat(y))),
+        position = position_nudge(y = 0.03),
+        size = 3
+    ) +
+    labs(
+        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
+        y = "PCCC (0=Low, 1=High)"
+    ) +
+    ylim(0.1, 1) +
+    coord_flip() +
+    theme_minimal() +
+    theme(
+        panel.grid = element_blank(),
+        axis.line = element_blank(),
+        axis.line.y = element_blank(),
+        axis.title.x = element_text(margin = margin(t = 10)),
+        axis.title.y = element_text(margin = margin(r = 10)),
+        axis.line.x = element_line(
+            color = "black",
+            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
+        )
+    )
+
+# Save the plot
+arplot
+ggsave("../manuscript/fig-perf-agerange.pdf", plot = arplot, dpi = 300)
+```
+
+#### COD Performance
 
@@
             PCCC <= min(PCCC) * 1.03,
-            paste0(Model, " (", round(PCCC, 2), ")"),
+            paste0(
+                Model,
+                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
+            ),
             NA
@@
             PCCC >= max(PCCC) * 0.97,
-            paste0(Model, " (", round(PCCC, 2), ")"),
+            paste0(
+                Model,
+                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
+            ),
             NA
@@
 ```
-
-### Age Group Perfomance
-
-Display a plot of performance for physician agreed records by age group.
-
-```{r, fig.height = 4, fig.width = 6}
-
-# Calc age counts
-nagree <- nrow(df %>% filter(is_agreed == TRUE))
-nadult <- nrow(df %>% filter(age == "adult" & is_agreed == TRUE))
-nchild <- nrow(df %>% filter(age == "child" & is_agreed == TRUE))
-nneo <- nrow(df %>% filter(age == "neo" & is_agreed == TRUE))
-
-# Calc age perc
-padult <- (nadult / nagree) * 100
-pchild <- (nchild / nagree) * 100
-pneo <- (nneo / nagree) * 100
-
-# Create age with counts
-age_remap <- c(
-    "Adult" = paste0("Adult\n12+ years\n(n=", nadult, ", ", round(padult), "%)"),
-    "Child" = paste0("Child\n28 days to 11 years\n(n=", nchild, ", ", round(pchild), "%)"),
-    "Neonatal" = paste0("Neonatal\n<28 days\n(n=", nneo, ", ", round(pneo), "%)")
-)
-
-# Prepare boxplot data
-agedata <- out %>%
-    select(
-        Model,
-        `PCCC Adult Agreement`,
-        `PCCC Child Agreement`,
-        `PCCC Neo Agreement`
-    ) %>%
-    rename(
-         Adult = `PCCC Adult Agreement`,
-         Child = `PCCC Child Agreement`,
-         Neonatal = `PCCC Neo Agreement`
-    ) %>%
-    filter(!str_detect(Model, "&")) %>% # remove multi models
-    pivot_longer( # transform to long format
-        cols = -Model,
-        names_to = "Age Group",
-        values_to = "PCCC"
-    ) %>%
-    mutate( # re-order age
-        "Age Group" = factor(`Age Group`, levels = c(
-            "Neonatal",
-            "Child",
-            "Adult"
-        ))
-    ) %>%
-    mutate( # rename ages with counts
-        "Age Group" = recode(`Age Group`, !!!age_remap)
-    ) %>%
-    group_by(`Age Group`) %>%
-    mutate( # Add min, mid, and max model names to label
-        "PCCC Min" = if_else(
-            PCCC <= min(PCCC) * 1.15,
-            paste0(Model, " (", round(PCCC, 2), ")"),
-            NA
-        ),
-        "PCCC Max" = if_else(
-            PCCC >= max(PCCC) * 0.95,
-            paste0(Model, " (", round(PCCC, 2), ")"),
-            NA
-        ),
-        "PCCC Mid" = if_else(
-            is.na(`PCCC Min`) & is.na(`PCCC Max`),
-            paste0(Model, "\n(", round(PCCC, 2), ")"),
-            NA
-        ),
-        "PCCC Mid Value" = if_else(
-            is.na(`PCCC Min`) & is.na(`PCCC Max`),
-            PCCC,
-            NA
-        ),
-        "PCCC Min" = if_else( # Combine into one row if close PCCC
-            `PCCC` == min(PCCC),
-            if_else(
-                sum(!is.na(`PCCC Min`)) > 1,
-                paste0(na.omit(`PCCC Min`), collapse = "\n"),
-                paste0(
-                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
-                    collapse = "\n"
-                )
-            ),
-            NA
-        ),
-        "PCCC Max" = if_else(
-            `PCCC` == max(PCCC),
-            if_else(
-                sum(!is.na(`PCCC Max`)) > 1,
-                paste0(na.omit(`PCCC Max`), collapse = "\n"),
-                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
-                       collapse = "\n")
-            ),
-            NA
-        )
-    )
-
-# Plot boxplot
-ageplot <- agedata %>%
-    ggplot(aes(x = `Age Group`, y = PCCC)) +
-    geom_boxplot(
-        linewidth = 0.5,
-        width = 0.25
-    ) +
-    geom_point(
-        aes(y = `PCCC Mid Value`),
-        shape = 1,
-        size = 1.5,
-        fill = "white",
-        color = "darkgray",
-        alpha = 0.8,
-        position = position_nudge(x = -0.3)
-    ) +
-    geom_text(
-        aes(label = `PCCC Min`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 1,
-        position = position_nudge(y = -0.055)
-    ) +
-    geom_text(
-        aes(label = `PCCC Max`),
-        color = "#4d4d4d",
-        size = 2,
-        position = position_nudge(y = 0.08)
-    ) +
-    geom_text(
-        aes(label = `PCCC Mid`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 1,
-        position = position_nudge(y = -0.015, x = -0.3)
-    ) +
-    stat_summary( # min pccc txt on boxplot
-        geom = "text",
-        fun = min,
-        aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = -0.025),
-        size = 3
-    ) +
-    stat_summary( # max pccc txt on boxplot
-        geom = "text",
-        fun = max,
-        aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = 0.025),
-        size = 3
-    ) +
-    labs(
-        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
-        y = "PCCC (0=Low, 1=High)"
-    ) +
-    ylim(0.25, 0.85) +
-    coord_flip() +
-    theme_minimal() +
-    theme(
-        panel.grid = element_blank(),
-        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
-        axis.line = element_line(color = "black"),
-        axis.title.x = element_text(margin = margin(t = 10)),
-        axis.title.y = element_text(margin = margin(r = 10)),
-        axis.line.x = element_line(
-            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
-        ),
-        axis.line.y = element_blank()
-    )
-
-# Save the plot
-ageplot
-ggsave("../manuscript/fig-perf-agegroup.pdf", plot = ageplot, dpi = 300)
-```
-
-### Age Range Performance
-
-Display a plot of performance for physician agreed records by age ranges.
-
-```{r, fig.height = 11, fig.width = 8}
-
-# Calc total agreed
-nagree <- df %>% filter(is_agreed == TRUE) %>% nrow
-
-# Get unique age range columns
-arange_col <- out %>% select(starts_with("PCCC Age Agree ")) %>% names
-
-# Create age range with counts
-arange_remap <- list()
-arange_counts <- list()
-for (ar_col in arange_col) {
-
-    # Get cod without prefix
-    ar <- gsub("PCCC Age Agree ", "", ar_col)
-
-    # Calculate num and perc cases for age range
-    narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
-    parange <- (narange / nagree) * 100
-    parange_label <- if (round(parange) >= 1) round(parange) else "<1"
-
-    # Break age range into newlines if more than 3 words
-    if (str_count(ar, "\\s+") > 3) {
-        arange_label <- str_replace(ar, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
-    } else {
-        arange_label <- ar
-    }
-
-    # Add label for age ranges
-    arange_remap[[ar]] <- paste0(arange_label, "\n(n=", narange, ", ", parange_label, "%)")
-
-    # Store age range count data
-    arange_counts[[ar]] <- narange
-}
-
-# Prepare boxplot data
-ardata <- out %>%
-    select(
-        Model,
-        starts_with("PCCC Age Agree ")
-    ) %>%
-    rename_at(
-         vars(-Model),
-         ~gsub("PCCC Age Agree ", "", .)
-    ) %>%
-    filter(!str_detect(Model, "&")) %>% # remove multi models
-    pivot_longer( # transform to long format
-        cols = -Model,
-        names_to = "Age Range",
-        values_to = "PCCC"
-    ) %>%
-    mutate( # rename cod with counts
-        "Age Range" = recode(`Age Range`, !!!arange_remap)
-    ) %>%
-    group_by(`Age Range`) %>%
-    mutate( # Make values less than 0 equal to 0
-        PCCC = if_else(PCCC <= 0, 0, PCCC)
-    ) %>%
-    mutate( # Add min, mid, and max model names to label
-        "PCCC Min" = if_else(
-            PCCC <= min(PCCC) * 1.03,
-            paste0(Model, " (", round(PCCC, 2), ")"),
-            NA
-        ),
-        "PCCC Max" = if_else(
-            PCCC >= max(PCCC) * 0.97,
-            paste0(Model, " (", round(PCCC, 2), ")"),
-            NA
-        ),
-        "PCCC Mid" = if_else(
-            is.na(`PCCC Min`) & is.na(`PCCC Max`),
-            paste0(Model, "\n(", round(PCCC, 2), ")"),
-            NA
-        ),
-        "PCCC Min" = if_else( # Combine into one row if close PCCC
-            `PCCC` == min(PCCC),
-            if_else(
-                sum(!is.na(`PCCC Min`)) > 1,
-                paste0(na.omit(`PCCC Min`), collapse = "\n"),
-                paste0(
-                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
-                    collapse = "\n"
-                )
-            ),
-            NA
-        ),
-        "PCCC Max" = if_else(
-            `PCCC` == max(PCCC),
-            if_else(
-                sum(!is.na(`PCCC Max`)) > 1,
-                paste0(na.omit(`PCCC Max`), collapse = "\n"),
-                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
-                       collapse = "\n")
-            ),
-            NA
-        )
-    )
-
-# Create cod order based on max pccc
-arorder <- ardata %>%
-    group_by(`Age Range`) %>%
-    summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
-    select(`Age Range`, `PCCC Max Value`) %>%
-    arrange(desc(`PCCC Max Value`)) %>%
-    pull(`Age Range`)
-ardata$`Age Range` <- factor(ardata$`Age Range`, levels = rev(arorder))
-
-# Plot boxplot
-arplot <- ardata %>%
-    ggplot(aes(x = `Age Range`, y = PCCC)) +
-    geom_boxplot(
-        linewidth = 0.5,
-        width = 0.25
-    ) +
-    geom_text(
-        aes(label = `PCCC Min`),
-        color = "#4d4d4d",
-        size = 2.5,
-        hjust = 1,
-        position = position_nudge(y = -0.065)
-    ) +
-    geom_text(
-        aes(label = `PCCC Max`),
-        color = "#4d4d4d",
-        size = 2.5,
-        hjust = 0,
-        position = position_nudge(y = 0.065)
-    ) +
-    stat_summary( # min pccc txt on boxplot
-        geom = "text",
-        fun = min,
-        aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = -0.03),
-        size = 3
-    ) +
-    stat_summary( # max pccc txt on boxplot
-        geom = "text",
-        fun = max,
-        aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = 0.03),
-        size = 3
-    ) +
-    labs(
-        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
-        y = "PCCC (0=Low, 1=High)"
-    ) +
-    ylim(0.1, 1) +
-    coord_flip() +
-    theme_minimal() +
-    theme(
-        panel.grid = element_blank(),
-        axis.line = element_blank(),
-        axis.line.y = element_blank(),
-        axis.title.x = element_text(margin = margin(t = 10)),
-        axis.title.y = element_text(margin = margin(r = 10)),
-        axis.line.x = element_line(
-            color = "black",
-            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
-        )
-    )
-
-# Save the plot
-arplot
-ggsave("../manuscript/fig-perf-agerange.pdf", plot = arplot, dpi = 300)
-```

### 2023-12-10 src/plots.Rmd
Add plot for cases by age and sex

@@
 
-Clean `age_range` labels to include only values and unit of measure.
+Clean `age_range` labels to include only values and unit of measure in titlecase.
 
@@
 df <- raw_df %>% mutate(
-    "age_range" = str_replace(
+    "age_range" = str_to_title(str_replace(
         age_range,
@@
         ""
-    ))
+    )),
+    "age_range" = if_else(
+        !str_detect(age_range, "Year|Years|Day|Days|month|Months|week|Weeks"),
+        paste0(age_range, " Years"),
+        age_range
+    )
+)
 df
@@
 
-#### Cases by Sex
-
-#### Cases by Age Group
+```{r}
+
+# Num and perc of agreed cases
+nall <- nrow(df)
+nagree <- nrow(df %>% filter(is_agreed == TRUE))
+pagree <- (nagree / nall) * 100
+
+# Create labels to axis titles
+y_title <- paste0("Physician Agreed Records (n=", nagree, ", 100%)")
+
+```
+
+#### Cases by Age Group and Sex
+
+Display a plot of cases by age group separated by sex.
+
+```{r}
+
+# Calc age and sex counts
+nadult <- nrow(df %>% filter(age == "adult" & is_agreed == TRUE))
+nchild <- nrow(df %>% filter(age == "child" & is_agreed == TRUE))
+nneo <- nrow(df %>% filter(age == "neo" & is_agreed == TRUE))
+
+# Calc age and sex perc
+padult <- (nadult / nagree) * 100
+pchild <- (nchild / nagree) * 100
+pneo <- (nneo / nagree) * 100
+
+# Create age with counts
+age_remap <- c(
+    "Adult" = paste0("Adult, 12+ years\n(n=", nadult, ", ", round(padult), "%)"),
+    "Child" = paste0("Child, 28 days to 11 years\n(n=", nchild, ", ", round(pchild), "%)"),
+    "Neo" = paste0("Neonatal, <28 days\n(n=", nneo, ", ", round(pneo), "%)")
+)
+
+# Get counts for ages
+
+# Format the data for plotting
+asdata <- df %>%
+    filter(is_agreed == TRUE) %>%
+    group_by(age, sex) %>%
+    summarize(count = n()) %>%
+    mutate(
+        age = str_to_title(age),
+        sex = paste0(
+            sex, " (n=", count, ", ",
+            round(count / case_when(
+                age == "Adult" ~ nadult,
+                age == "Child" ~ nchild,
+                age == "Neo" ~ nneo
+            ) * 100), "%)"
+        )
+    ) %>%
+    mutate( # re-order age
+        age = factor(age, levels = c(
+            "Adult",
+            "Child",
+            "Neo"
+        ))
+    ) %>%
+    mutate( # rename ages with counts
+        age = recode(age, !!!age_remap)
+    )
+
+# Plot the data
+asplot <- asdata %>%
+    ggplot(aes(x = factor(age), y = count, fill = sex)) +
+    geom_bar(
+        stat = "identity",
+        fill = "white",
+        color = "black"
+    ) +
+    geom_text(
+        aes(label = sex),
+        position = position_stack(vjust = 0.5),
+        size = 2.5,
+        color = "black"
+    ) +
+    labs(
+        y = y_title,
+        x = element_blank(),
+        fill = "Sex"
+    ) +
+    theme_minimal() +
+    theme(
+        panel.grid = element_blank(),
+        axis.title.x = element_text(margin = margin(t = 10)),
+        axis.title.y = element_text(margin = margin(r = 10))
+    )
+
+# Save the plot
+asplot
+ggsave("../manuscript/fig-data-agegroup.pdf", plot = asplot, dpi = 300)
+```
 
@@
         "PCCC Min" = if_else(
-            PCCC <= min(PCCC) * 1.05,
-            paste0(Model, "\n(", round(PCCC, 2), ", CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
+            PCCC <= min(PCCC) + 0.05,
+            paste0(
+                Model, "\n(",
+                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
+                "CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
             NA
@@
         "PCCC Max" = if_else(
-            PCCC >= max(PCCC) * 0.97,
-            paste0(Model, "\n(", round(PCCC, 2), ", CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
+            PCCC >= max(PCCC) - 0.05,
+            paste0(
+                Model, "\n(",
+                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
+                "CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
             NA
@@
         "PCCC Min" = if_else(
-            PCCC <= min(PCCC) * 1.15,
+            PCCC <= min(PCCC) + 0.05,
             paste0(
@@
         "PCCC Max" = if_else(
-            PCCC >= max(PCCC) * 0.95,
+            PCCC >= max(PCCC) - 0.05,
             paste0(
@@
                 if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
-                ", CSMF=", round(case_when(
+                "CSMF=", round(case_when(
                     `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
@@
         )
-    )%>%
+    ) %>%
     mutate( # re-order age
@@
     ) +
-    ylim(0.25, 0.85) +
+    ylim(0.25, 0.9) +
     coord_flip() +
@@
 
-    # Calculate num and perc cases for age range
+    # Calc num and perc cases for age range
     narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
@@
 
-    # Break age range into newlines if more than 3 words
-    if (str_count(ar, "\\s+") > 3) {
-        arange_label <- str_replace(ar, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
-    } else {
-        arange_label <- ar
-    }
-
     # Add label for age ranges
-    arange_remap[[ar]] <- paste0(arange_label, "\n(n=", narange, ", ", parange_label, "%)")
+    arange_remap[[ar]] <- paste0(
+        ar,
+        "\n(n=", narange, ", ", parange_label, "%)"
+    )
 
@@
         "PCCC Min" = if_else(
-            PCCC <= min(PCCC) * 1.03,
+            PCCC <= min(PCCC) + 0.05,
             paste0(
@@
         "PCCC Max" = if_else(
-            PCCC >= max(PCCC) * 0.97,
+            PCCC >= max(PCCC) - 0.05,
             paste0(

### 2023-12-11 src/plots.Rmd
Add exploratory age range plot

@@
 )
-
-# Get counts for ages
 
@@
 asplot
-ggsave("../manuscript/fig-data-agegroup.pdf", plot = asplot, dpi = 300)
+ggsave("../manuscript/fig-data-agesex.pdf", plot = asplot, dpi = 300)
 ```
@@
 #### Cases by Age Range
+
+Display a plot of cases by age range.
+
+```{r, fig.height = 8, fig.width = 6}
+
+# Format plot data
+eardata <- df %>%
+    filter(is_agreed == TRUE) %>%
+    group_by(age_range) %>%
+    summarize(count = n()) %>%
+    separate(
+        age_range,
+        into = c("age_range_value", "age_range_unit"),
+        sep = " "
+    ) %>%
+    separate(
+        age_range_value,
+        into = c("age_range_min", "age_range_max"),
+        sep = "-"
+    ) %>%
+    mutate(
+        age_range_min = as.integer(age_range_min),
+        age_range_max = as.integer(age_range_max),
+        age_range_unit = factor(age_range_unit, levels = c(
+            "Weeks",
+            "Days",
+            "Months",
+            "Years"
+        )),
+        age_range_label = paste0(
+            age_range_min,
+            "-",
+            age_range_max,
+            " ",
+            age_range_unit,
+            "\n(n=", count, ", ", round((count / nagree) * 100), "%)"
+        )
+    ) %>%
+    arrange(age_range_unit, age_range_min, age_range_max) %>%
+    mutate(
+        age_range_label = factor(age_range_label, levels = unique(age_range_label))
+    )
+
+# Plot the data
+earplot <- eardata %>%
+    ggplot(aes(x = age_range_label, y = count)) +
+    geom_bar(
+        stat = "identity",
+        fill = "#1d1d1d",
+        color = "white",
+        width = 0.5
+    ) +
+    labs(
+        y = y_title,
+        x = element_blank()
+    ) +
+    theme_minimal() +
+    theme(
+        panel.grid = element_blank(),
+        axis.title.x = element_text(margin = margin(t = 10)),
+        axis.title.y = element_text(margin = margin(r = 10))
+    ) +
+    coord_flip()
+
+# Save the plot
+earplot
+ggsave("../manuscript/fig-data-agerange.pdf", plot = earplot, dpi = 300)
+```
 

### 2023-12-11 src/plots.Rmd
Add exploratiomn cod plot

@@
 
+Display a plot of cases by cause of death.
+
+```{r, fig.height = 11, fig.width = 8}
+
+# Format plot data
+ecoddata <- df %>%
+    filter(is_agreed == TRUE) %>%
+    group_by(physician_cghr10) %>%
+    summarize(count = n()) %>%
+    mutate(
+        cod_label = paste0(
+            physician_cghr10,
+            "\n(n=", count, ", ",
+            if_else(
+                ((count / nagree) * 100) < 1,
+                "<1",
+                as.character(round((count / nagree) * 100))
+            ), "%)"
+        )
+    ) %>%
+    arrange(count) %>%
+    mutate(
+        cod_label = factor(cod_label, levels = unique(cod_label))
+    )
+
+# Plot the data
+ecodplot <- ecoddata %>%
+    ggplot(aes(x = cod_label, y = count)) +
+    geom_bar(
+        stat = "identity",
+        fill = "#1d1d1d",
+        color = "white",
+        width = 0.5
+    ) +
+    labs(
+        y = y_title,
+        x = element_blank()
+    ) +
+    theme_minimal() +
+    theme(
+        panel.grid = element_blank(),
+        axis.title.x = element_text(margin = margin(t = 10)),
+        axis.title.y = element_text(margin = margin(r = 10))
+    ) +
+    coord_flip()
+
+# Save the plot
+ecodplot
+ggsave("../manuscript/fig-data-cod.pdf", plot = ecodplot, dpi = 300)
+```
+
 ### Performance

### 2023-12-11 src/plots.Rmd
Fix exploration cod plot labels

@@
 
-```{r, fig.height = 11, fig.width = 8}
+```{r, fig.height = 16.5, fig.width = 8}
 
@@
         cod_label = paste0(
-            physician_cghr10,
+            if_else(
+                str_count(physician_cghr10, "\\s+") > 3,
+                str_replace(physician_cghr10, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n"),
+                physician_cghr10
+            ),
             "\n(n=", count, ", ",

### 2023-12-15 src/plots.Rmd
Split plots by age group

--- 2023-12-11 src/plots.Rmd
@@
 
-    # Calc metric by cause of death
+    # Calc metric by cause of death for each age group
     if (by_cod) {
@@
         # Calc metric by cod
+        for (a in c("adult", "child", "neo")) {
             for (cod in causes) {
@@
                 # Filter data for cod
-            df_filter <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE)
-            metric_name <- paste0(name, " COD Agree ", cod)
+                df_filter <- df %>% filter(
+                    physician_cghr10 == cod & is_agreed == TRUE & age == a
+                )
+                metric_name <- sprintf(
+                    "%s %s COD Agree %s", name, str_to_title(a), cod
+                )
 
                 # Calc metric for cod
+                if (nrow(df_filter) > 0) {
                     out[[metric_name]] <- calc_per_model(
@@
             }
+        }
+    }
 
@@
         # Calc metric by age range
+        for (a in c("adult", "child", "neo")) {
             for (ar in age_ranges) {
@@
                 # Filter for age range
-            df_filter <- df %>% filter(age_range == ar & is_agreed == TRUE)
-            metric_name = paste0(name, " Age Agree ", ar)
+                df_filter <- df %>% filter(
+                    age_range == ar & is_agreed == TRUE & age == a
+                )
+                metric_name <- sprintf(
+                    "%s %s Age Agree %s", name, str_to_title(a), ar
+                )
 
                 # Calc metric for cod
+                if (nrow(df_filter) > 0) {
                     out[[metric_name]] <- calc_per_model(
@@
                     )
+                }
+            }
         }
@@
 y_title <- paste0("Physician Agreed Records (n=", nagree, ", 100%)")
-
 ```
@@
 
-Display a plot of cases by age range.
-
-```{r, fig.height = 8, fig.width = 6}
+Display a plot for each age group of cases by age range.
+
+```{r}
+for (a in c("adult", "child", "neo")) {
+
+    # Create label for age group
+    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
+    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
+    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
 
@@
     eardata <- df %>%
-    filter(is_agreed == TRUE) %>%
+        filter(is_agreed == TRUE & age == a) %>%
         group_by(age_range) %>%
@@
                 age_range_unit,
-            "\n(n=", count, ", ", round((count / nagree) * 100), "%)"
+                "\n(n=", count, ", ", round((count / arows) * 100), "%)"
             )
@@
         labs(
-        y = y_title,
+            y = atitle,
             x = element_blank()
@@
     # Save the plot
-earplot
-ggsave("../manuscript/fig-data-agerange.pdf", plot = earplot, dpi = 300)
+    print(earplot)
+    ggsave(
+        sprintf("../manuscript/fig-data-agerange-%s.pdf", a),
+        plot = earplot,
+        dpi = 300
+    )
+}
 ```
@@
 #### Cases by COD
+
+Display a plot for each age group of cases by cause of death.
+
+```{r}
+for (a in c("adult", "child", "neo")) {
+
+    # Create label for age group
+    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
+    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
+    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
+
+    # Format plot data
+    ecoddata <- df %>%
+        filter(is_agreed == TRUE & age == a) %>%
+        group_by(physician_cghr10) %>%
+        summarize(count = n()) %>%
+        mutate(
+            cod_label = paste0(
+                if_else(
+                    str_count(physician_cghr10, "\\s+") > 3,
+                    str_replace(physician_cghr10, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n"),
+                    physician_cghr10
+                ),
+                "\n(n=", count, ", ",
+                if_else(
+                    ((count / arows) * 100) < 1,
+                    "<1",
+                    as.character(round((count / arows) * 100))
+                ), "%)"
+            )
+        ) %>%
+        arrange(count) %>%
+        mutate(
+            cod_label = factor(cod_label, levels = unique(cod_label))
+        )
+
+    # Plot the data
+    ecodplot <- ecoddata %>%
+        ggplot(aes(x = cod_label, y = count)) +
+        geom_bar(
+            stat = "identity",
+            fill = "#1d1d1d",
+            color = "white",
+            width = 0.5
+        ) +
+        labs(
+            y = atitle,
+            x = element_blank()
+        ) +
+        theme_minimal() +
+        theme(
+            panel.grid = element_blank(),
+            axis.title.x = element_text(margin = margin(t = 10)),
+            axis.title.y = element_text(margin = margin(r = 10)),
+            axis.text.x = element_text(hjust = 1)
+        ) +
+        coord_flip()
+
+    # Save the plot
+    print(ecodplot)
+    ggsave(
+        sprintf("../manuscript/fig-data-cod-%s.pdf", a),
+        plot = ecodplot,
+        dpi = 300,
+        width = if (a == "adult") 6 else NA,
+        height = if (a == "adult") 8 else NA
+    )
+}
+```
 
@@
 
-Display a plot of performance for physician agreed records by age ranges.
-
-```{r, fig.height = 11, fig.width = 8}
-
-# Calc total agreed
-nagree <- df %>% filter(is_agreed == TRUE) %>% nrow
+Display a plot for each age group of performance for physician agreed records by age ranges.
+
+```{r}
+for (a in c("adult", "child", "neo")) {
+
+    # Create label and ref for age group
+    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
+    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
+    atitle <- if (a == "neo") {
+        paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
+    } else {
+        paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
+    }
+    aref <- str_to_title(a)
 
     # Get unique age range columns
-arange_col <- out %>% select(starts_with("PCCC Age Agree ")) %>% names
+    arange_col <- out %>% select(starts_with(sprintf(
+            "PCCC %s Age Agree ",
+            aref
+        ))) %>%
+        names
 
@@
         # Get cod without prefix
-    ar <- gsub("PCCC Age Agree ", "", ar_col)
+        ar <- gsub(sprintf("PCCC %s Age Agree ", aref), "", ar_col)
 
@@
         narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
-    parange <- (narange / nagree) * 100
+        parange <- (narange / arows) * 100
         parange_label <- if (round(parange) >= 1) round(parange) else "<1"
@@
             Model,
-        starts_with("PCCC Age Agree ")
+            starts_with(sprintf("PCCC %s Age Agree", aref))
         ) %>%
@@
              vars(-Model),
-         ~gsub("PCCC Age Agree ", "", .)
+             ~gsub(sprintf("PCCC %s Age Agree ", aref), "", .)
         ) %>%
@@
         labs(
-        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
+            x = atitle,
             y = "PCCC (0=Low, 1=High)"
@@
     # Save the plot
-arplot
-ggsave("../manuscript/fig-perf-agerange.pdf", plot = arplot, dpi = 300)
+    print(arplot)
+    ggsave(
+        sprintf("../manuscript/fig-perf-agerange-%s.pdf", a),
+        plot = arplot,
+        dpi = 300,
+        width = if (a == "adult") 6 else if (a == "neo") 6 else NA,
+        height = if (a == "adult") 8 else if (a == "neo") 2.5 else NA
+    )
+}
 ```
@@
 
-```{r, fig.height = 16.5, fig.width = 8}
-
-# Calc total agreed
-nagree <- df %>% filter(is_agreed == TRUE) %>% nrow
+```{r}
+for (a in c("adult", "child", "neo")) {
+
+    # Create label for age group
+    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
+    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
+    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
+    aref <- str_to_title(a)
 
     # Get unique cause columns
-causes_col <- out %>% select(starts_with("PCCC COD Agree ")) %>% names
+    causes_col <- out %>% select(starts_with(sprintf(
+        "PCCC %s COD Agree ", aref
+    ))) %>% names
 
@@
         # Get cod without prefix
-    cod <- gsub("PCCC COD Agree ", "", cod_col)
+        cod <- gsub(sprintf("PCCC %s COD Agree ", aref), "", cod_col)
 
@@
             Model,
-        starts_with("PCCC COD Agree ")
+            starts_with(sprintf("PCCC %s COD Agree ", aref))
         ) %>%
@@
              vars(-Model),
-         ~gsub("PCCC COD Agree ", "", .)
+             ~gsub(sprintf("PCCC %s COD Agree ", aref), "", .)
         ) %>%
@@
         labs(
-        x = paste0("Physician Agreed Records (n=", nagree, ", 100%) for ", length(causes_col), " Causes of Death"),
+            x = atitle,
             y = "PCCC (0=Low, 1=High)"
@@
     # Save the plot
-codplot
-ggsave("../manuscript/fig-perf-cod.pdf", plot = codplot, dpi = 300)
-```
+    print(codplot)
+    ggsave(
+        sprintf("../manuscript/fig-perf-cod-%s.pdf", a),
+        plot = codplot,
+        dpi = 300,
+        width = if (a == "adult") 8 else NA,
+        height = if (a == "adult") 10 else NA
+    )
+}
+```

### 2023-12-15 src/plots.Rmd
Add perf by sex plots

@@
         by_stage = TRUE,
+        by_sex = TRUE,
         by_cod = TRUE,
@@
 
-    # Calc metric by cause of death for each age group
-    if (by_cod) {
-
-        # Get unique causes of death
-        causes <- df %>%
-            select(ends_with("_cghr10")) %>%
-            pivot_longer(
-                everything(),
-                names_to = "column",
-                values_to = "cod"
-            ) %>%
-            distinct(cod) %>%
-            filter(!is.na(cod)) %>%
-            pull(cod)
+    # Calc metric by sex for each age group
+    if (by_sex) {
 
@@
         for (a in c("adult", "child", "neo")) {
-            for (cod in causes) {
+            for (sx in c("Male", "Female")) {
 
@@
                 df_filter <- df %>% filter(
-                    physician_cghr10 == cod & is_agreed == TRUE & age == a
+                    sex == sx & is_agreed == TRUE & age == a
                 )
                 metric_name <- sprintf(
-                    "%s %s COD Agree %s", name, str_to_title(a), cod
+                    "%s %s Sex Agree %s", name, str_to_title(a), sx
                 )
@@
 
-    # Calc metric by age range
-    if (by_age_range) {
-
-        # Get unique age ranges
-        age_ranges <- df %>%
-            pull(age_range) %>%
-            unique
-
-        # Calc metric by age range
+    # Calc metric by cause of death for each age group
+    if (by_cod) {
+
+        # Get unique causes of death
+        causes <- df %>%
+            select(ends_with("_cghr10")) %>%
+            pivot_longer(
+                everything(),
+                names_to = "column",
+                values_to = "cod"
+            ) %>%
+            distinct(cod) %>%
+            filter(!is.na(cod)) %>%
+            pull(cod)
+
+        # Calc metric by cod
         for (a in c("adult", "child", "neo")) {
-            for (ar in age_ranges) {
-
-                # Filter for age range
+            for (cod in causes) {
+
+                # Filter data for cod
                 df_filter <- df %>% filter(
-                    age_range == ar & is_agreed == TRUE & age == a
+                    physician_cghr10 == cod & is_agreed == TRUE & age == a
                 )
                 metric_name <- sprintf(
-                    "%s %s Age Agree %s", name, str_to_title(a), ar
+                    "%s %s COD Agree %s", name, str_to_title(a), cod
                 )
@@
 
+    # Calc metric by age range
+    if (by_age_range) {
+
+        # Get unique age ranges
+        age_ranges <- df %>%
+            pull(age_range) %>%
+            unique
+
+        # Calc metric by age range
+        for (a in c("adult", "child", "neo")) {
+            for (ar in age_ranges) {
+
+                # Filter for age range
+                df_filter <- df %>% filter(
+                    age_range == ar & is_agreed == TRUE & age == a
+                )
+                metric_name <- sprintf(
+                    "%s %s Age Agree %s", name, str_to_title(a), ar
+                )
+
+                # Calc metric for cod
+                if (nrow(df_filter) > 0) {
+                    out[[metric_name]] <- calc_per_model(
+                        actual = df_filter %>%
+                            pull(physician_cghr10),
+                        pred = df_filter %>%
+                            select(ends_with("_cghr10"), -physician_cghr10),
+                        func = func,
+                        ...
+                    ) %>% rename(
+                         {{ metric_name }} := Metric
+                    )
+                }
+            }
+        }
+    }
+
     # Combine all pccc metrics
@@
 
-#### Cases by Age Group and Sex
+#### Cases by Sex and Age Group
 
@@
 
-#### Age Range Performance
-
-Display a plot for each age group of performance for physician agreed records by age ranges.
-
-```{r}
+#### Sex Performance
+
+Display a plot for each age group of performance for physician agreed records by sex.
+
+```{r, fig.width = 6, fig.height = 2.5}
 for (a in c("adult", "child", "neo")) {
@@
     alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
-    atitle <- if (a == "neo") {
-        paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
-    } else {
-        paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
-    }
+    atitle <- paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
     aref <- str_to_title(a)
 
-    # Get unique age range columns
-    arange_col <- out %>% select(starts_with(sprintf(
-            "PCCC %s Age Agree ",
+    # Get unique sex columns
+    sex_col <- out %>% select(starts_with(sprintf(
+            "PCCC %s Sex Agree ",
             aref
@@
 
-    # Create age range with counts
-    arange_remap <- list()
-    arange_counts <- list()
-    for (ar_col in arange_col) {
-
-        # Get cod without prefix
-        ar <- gsub(sprintf("PCCC %s Age Agree ", aref), "", ar_col)
+    # Create sex with counts
+    sex_remap <- list()
+    sex_counts <- list()
+    for (sx_col in sex_col) {
+
+        # Get sex without prefix
+        sx <- gsub(sprintf("PCCC %s Sex Agree ", aref), "", sx_col)
 
         # Calc num and perc cases for age range
-        narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
-        parange <- (narange / arows) * 100
-        parange_label <- if (round(parange) >= 1) round(parange) else "<1"
+        nsex <- df %>% filter(sex == sx & is_agreed == TRUE & age == a) %>% nrow
+        psex <- (nsex / arows) * 100
+        psex_label <- if (round(psex) >= 1) round(psex) else "<1"
 
         # Add label for age ranges
-        arange_remap[[ar]] <- paste0(
-            ar,
-            "\n(n=", narange, ", ", parange_label, "%)"
+        sex_remap[[sx]] <- paste0(
+            sprintf("%s %s", alabel, sx),
+            "\n(n=", nsex, ", ", psex_label, "%)"
         )
@@
         # Store age range count data
-        arange_counts[[ar]] <- narange
+        sex_counts[[sx]] <- nsex
     }
@@
     # Prepare boxplot data
-    ardata <- out %>%
+    sxdata <- out %>%
         select(
             Model,
-            starts_with(sprintf("PCCC %s Age Agree", aref))
+            starts_with(sprintf("PCCC %s Sex Agree", aref))
         ) %>%
@@
              vars(-Model),
-             ~gsub(sprintf("PCCC %s Age Agree ", aref), "", .)
+             ~gsub(sprintf("PCCC %s Sex Agree ", aref), "", .)
         ) %>%
@@
             cols = -Model,
-            names_to = "Age Range",
+            names_to = "Sex",
             values_to = "PCCC"
@@
         mutate( # rename cod with counts
-            "Age Range" = recode(`Age Range`, !!!arange_remap)
-        ) %>%
-        group_by(`Age Range`) %>%
+            "Sex" = recode(Sex, !!!sex_remap)
+        ) %>%
+        group_by(Sex) %>%
         mutate( # Make values less than 0 equal to 0
@@
                 paste0(Model, "\n(", round(PCCC, 2), ")"),
+                NA
+            ),
+            "PCCC Mid Value" = if_else(
+                is.na(`PCCC Min`) & is.na(`PCCC Max`),
+                PCCC,
                 NA
@@
     # Create cod order based on max pccc
-    arorder <- ardata %>%
-        group_by(`Age Range`) %>%
+    sxorder <- sxdata %>%
+        group_by(Sex) %>%
         summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
-        select(`Age Range`, `PCCC Max Value`) %>%
+        select(Sex, `PCCC Max Value`) %>%
         arrange(desc(`PCCC Max Value`)) %>%
-        pull(`Age Range`)
-    ardata$`Age Range` <- factor(ardata$`Age Range`, levels = rev(arorder))
+        pull(Sex)
+    sxdata$Sex <- factor(sxdata$Sex, levels = rev(sxorder))
 
     # Plot boxplot
-    arplot <- ardata %>%
-        ggplot(aes(x = `Age Range`, y = PCCC)) +
+    sxplot <- sxdata %>%
+        ggplot(aes(x = Sex, y = PCCC)) +
         geom_boxplot(
@@
             width = 0.25
+        ) +
+        geom_point(
+            aes(y = `PCCC Mid Value`),
+            shape = 1,
+            size = 1.5,
+            fill = "white",
+            color = "darkgray",
+            alpha = 0.8,
+            position = position_nudge(x = -0.35)
         ) +
@@
             hjust = 1,
-            position = position_nudge(y = -0.065)
+            position = position_nudge(y = -0.09)
+        ) +
+        geom_text(
+            aes(label = `PCCC Mid`),
+            color = "#4d4d4d",
+            size = 2,
+            hjust = 1,
+            position = position_nudge(y = -0.025, x = -0.35)
         ) +
@@
             hjust = 0,
-            position = position_nudge(y = 0.065)
+            position = position_nudge(y = 0.09)
         ) +
@@
             aes(label = sprintf("%1.2f", after_stat(y))),
-            position = position_nudge(y = -0.03),
+            position = position_nudge(y = -0.04),
             size = 3
@@
             aes(label = sprintf("%1.2f", after_stat(y))),
-            position = position_nudge(y = 0.03),
+            position = position_nudge(y = 0.04),
             size = 3
@@
     # Save the plot
+    print(sxplot)
+    ggsave(
+        sprintf("../manuscript/fig-perf-sex-%s.pdf", a),
+        plot = sxplot,
+        dpi = 300
+    )
+}
+```
+
+#### Age Range Performance
+
+Display a plot for each age group of performance for physician agreed records by age ranges.
+
+```{r}
+for (a in c("adult", "child", "neo")) {
+
+    # Create label and ref for age group
+    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
+    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
+    atitle <- if (a == "neo") {
+        paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
+    } else {
+        paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
+    }
+    aref <- str_to_title(a)
+
+    # Get unique age range columns
+    arange_col <- out %>% select(starts_with(sprintf(
+            "PCCC %s Age Agree ",
+            aref
+        ))) %>%
+        names
+
+    # Create age range with counts
+    arange_remap <- list()
+    arange_counts <- list()
+    for (ar_col in arange_col) {
+
+        # Get cod without prefix
+        ar <- gsub(sprintf("PCCC %s Age Agree ", aref), "", ar_col)
+
+        # Calc num and perc cases for age range
+        narange <- df %>% filter(age_range == ar & is_agreed == TRUE & age == a) %>% nrow
+        parange <- (narange / arows) * 100
+        parange_label <- if (round(parange) >= 1) round(parange) else "<1"
+
+        # Add label for age ranges
+        arange_remap[[ar]] <- paste0(
+            ar,
+            "\n(n=", narange, ", ", parange_label, "%)"
+        )
+
+        # Store age range count data
+        arange_counts[[ar]] <- narange
+    }
+
+    # Prepare boxplot data
+    ardata <- out %>%
+        select(
+            Model,
+            starts_with(sprintf("PCCC %s Age Agree", aref))
+        ) %>%
+        rename_at(
+             vars(-Model),
+             ~gsub(sprintf("PCCC %s Age Agree ", aref), "", .)
+        ) %>%
+        filter(!str_detect(Model, "&")) %>% # remove multi models
+        pivot_longer( # transform to long format
+            cols = -Model,
+            names_to = "Age Range",
+            values_to = "PCCC"
+        ) %>%
+        mutate( # rename cod with counts
+            "Age Range" = recode(`Age Range`, !!!arange_remap)
+        ) %>%
+        group_by(`Age Range`) %>%
+        mutate( # Make values less than 0 equal to 0
+            PCCC = if_else(PCCC <= 0, 0, PCCC)
+        ) %>%
+        mutate( # Add min, mid, and max model names to label
+            "PCCC Min" = if_else(
+                PCCC <= min(PCCC) + 0.05,
+                paste0(
+                    Model,
+                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
+                ),
+                NA
+            ),
+            "PCCC Max" = if_else(
+                PCCC >= max(PCCC) - 0.05,
+                paste0(
+                    Model,
+                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
+                ),
+                NA
+            ),
+            "PCCC Mid" = if_else(
+                is.na(`PCCC Min`) & is.na(`PCCC Max`),
+                paste0(Model, "\n(", round(PCCC, 2), ")"),
+                NA
+            ),
+            "PCCC Min" = if_else( # Combine into one row if close PCCC
+                `PCCC` == min(PCCC),
+                if_else(
+                    sum(!is.na(`PCCC Min`)) > 1,
+                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
+                    paste0(
+                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
+                        collapse = "\n"
+                    )
+                ),
+                NA
+            ),
+            "PCCC Max" = if_else(
+                `PCCC` == max(PCCC),
+                if_else(
+                    sum(!is.na(`PCCC Max`)) > 1,
+                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
+                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
+                           collapse = "\n")
+                ),
+                NA
+            )
+        )
+
+    # Create cod order based on max pccc
+    arorder <- ardata %>%
+        group_by(`Age Range`) %>%
+        summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
+        select(`Age Range`, `PCCC Max Value`) %>%
+        arrange(desc(`PCCC Max Value`)) %>%
+        pull(`Age Range`)
+    ardata$`Age Range` <- factor(ardata$`Age Range`, levels = rev(arorder))
+
+    # Plot boxplot
+    arplot <- ardata %>%
+        ggplot(aes(x = `Age Range`, y = PCCC)) +
+        geom_boxplot(
+            linewidth = 0.5,
+            width = 0.25
+        ) +
+        geom_text(
+            aes(label = `PCCC Min`),
+            color = "#4d4d4d",
+            size = 2.5,
+            hjust = 1,
+            position = position_nudge(y = -0.065)
+        ) +
+        geom_text(
+            aes(label = `PCCC Max`),
+            color = "#4d4d4d",
+            size = 2.5,
+            hjust = 0,
+            position = position_nudge(y = 0.065)
+        ) +
+        stat_summary( # min pccc txt on boxplot
+            geom = "text",
+            fun = min,
+            aes(label = sprintf("%1.2f", after_stat(y))),
+            position = position_nudge(y = -0.03),
+            size = 3
+        ) +
+        stat_summary( # max pccc txt on boxplot
+            geom = "text",
+            fun = max,
+            aes(label = sprintf("%1.2f", after_stat(y))),
+            position = position_nudge(y = 0.03),
+            size = 3
+        ) +
+        labs(
+            x = atitle,
+            y = "PCCC (0=Low, 1=High)"
+        ) +
+        ylim(0.1, 1) +
+        coord_flip() +
+        theme_minimal() +
+        theme(
+            panel.grid = element_blank(),
+            axis.line = element_blank(),
+            axis.line.y = element_blank(),
+            axis.title.x = element_text(margin = margin(t = 10)),
+            axis.title.y = element_text(margin = margin(r = 10)),
+            axis.line.x = element_line(
+                color = "black",
+                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
+            )
+        )
+
+    # Save the plot
     print(arplot)
@@
         # Calculate num and perc cases for cod
-        ncod <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE) %>% nrow
+        ncod <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE & age == a) %>% nrow
         pcod <- (ncod / nagree) * 100

### 2023-12-15 src/plots.Rmd
Plot adjustments'

@@
 
-```{r, fig.height = 3, fig.width = 6}
+```{r, fig.height = 2.5, fig.width = 6}
 
@@
 
-```{r, fig.height = 4, fig.width = 6}
+```{r, fig.height = 3.5, fig.width = 6}
 
@@
             hjust = 1,
-            position = position_nudge(y = -0.065)
+            position = position_nudge(y = -0.08)
         ) +
@@
             hjust = 0,
-            position = position_nudge(y = 0.065)
+            position = position_nudge(y = 0.08)
         ) +

### 2024-01-17 src/plots.Rmd
Checking counts

@@
 
+# Physician agreed cases
+raw_physicians_agree <- raw_df %>%
+    filter(is_agreed == TRUE) %>%
+    pull(physician_cghr10)
+cat(paste0(
+    "Agreed Cases (",
+    length(unique(na.omit(raw_physicians_agree))), " CODs): ",
+    length(raw_physicians_agree),
+    "\n"
+))
+
 # Models cases
@@
 
+# Physician agreed cases
+physicians_agree <- df %>%
+    filter(is_agreed == TRUE) %>%
+    pull(physician_cghr10)
+cat(paste0(
+    "Physician Agreed Coded Cases (",
+    length(unique(na.omit(physicians_agree))), " CODs): ",
+    length(physicians_agree) - sum(is.na(physicians_agree) | is.null(physicians_agree)),
+    "\n"
+))
+
 # Models cases
@@
         str_replace_all(mcol, models_format), " Predicted Cases (", 
+        length(unique(na.omit(m))), " CODs): ",
+        length(m) - sum(is.na(m) | is.null(m)),
+        "\n"
+    ))
+}
+
+# Models agreed cases
+models_agree <- df %>%
+    filter(is_agreed == TRUE) %>%
+    select(ends_with("_cghr10"), -physician_cghr10)
+for (mcol in colnames(models_agree)) {
+    m <- models_agree[[mcol]]
+    cat(paste0(
+        str_replace_all(mcol, models_format), " Agreed Predicted Cases (", 
         length(unique(na.omit(m))), " CODs): ",

### 2024-01-17 src/preprocess.Rmd
Checking counts

@@
         )
-    ) %>% rename(interva5_wva2016 = cause1_wva)
+    ) %>% rename(interva5_wva2016 = cause1_wva),
+    narrative = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_adult_narrative_v1.csv",
+            col_select = c("rowid", "summary")
+        ),
+        read_csv(
+            "../tmp/healsl_rd1_child_narrative_v1.csv",
+            col_select = c("rowid", "summary")
+        ),
+        read_csv(
+            "../tmp/healsl_rd1_neo_narrative_v1.csv",
+            col_select = c("rowid", "summary")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_adult_narrative_v1.csv",
+            col_select = c("rowid", "summary")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_child_narrative_v1.csv",
+            col_select = c("rowid", "summary")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_neo_narrative_v1.csv",
+            col_select = c("rowid", "summary")
+        )
+    ),
+    who = bind_rows(
+        read_csv(
+            "../tmp/healsl_rd1_who_adult_v1.csv",
+            col_select = c("rowid")
+        ),
+        read_csv(
+            "../tmp/healsl_rd1_who_child_v1.csv",
+            col_select = c("rowid")
+        ),
+        read_csv(
+            "../tmp/healsl_rd1_who_neo_v1.csv",
+            col_select = c("rowid")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_who_adult_v1.csv",
+            col_select = c("rowid")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_who_child_v1.csv",
+            col_select = c("rowid")
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_who_neo_v1.csv",
+            col_select = c("rowid")
+        )
+    )
 )
@@
 
+## Checks
+
+### Physician Coded Counts
+
+Check physician coded record counts:
+
+```{r}
+
+# Get icd10 counts
+phy_icd10 <- out %>% filter(
+    !is.na(physician_icd10) & !is.null(physician_icd10)
+) %>% nrow
+phy_icd10_agree <- out %>% filter(
+     !is.na(physician_icd10) & !is.null(physician_icd10) & is_agreed == TRUE
+) %>% nrow
+
+# Get cghr10 counts
+phy_cghr10 <- out %>% filter(
+    !is.na(physician_cghr10) & !is.null(physician_cghr10)
+) %>% nrow
+phy_cghr10_agree <- out %>% filter(
+     !is.na(physician_cghr10) & !is.null(physician_cghr10) & is_agreed == TRUE
+) %>% nrow
+
+# Print results
+cat(paste0(
+    "Physican ICD-10 Coded: ", phy_icd10,
+    "\nPhysician ICD-10 Coded (Agree): ", phy_icd10_agree,
+    "\nPhysican CGHR-10 Coded: ", phy_cghr10,
+    "\nPhysician CGHR-10 Coded (Agree): ", phy_cghr10_agree
+))
+```
+
+### ChatGPT-3.5 Counts
+
+Check ChatGPT-3.5 Counts:
+
+```{r}
+
+# Get phy coded records only
+out_coded <- out %>% filter(
+    !is.na(physician_icd10) & !is.null(physician_icd10)
+)
+out_coded_agree <- out_coded %>% filter(is_agreed == TRUE)
+
+# Get chatgpt3 coded records
+out_cgpt3 <- out_coded %>% filter(
+    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
+)
+out_cgpt3_agree <- out_coded_agree %>% filter(
+    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
+)
+
+# Get chatgpt3 coded records converted to cghr10
+out_cgpt3_cghr10 <- out_cgpt3 %>% filter(
+    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
+)
+out_cgpt3_cghr10_agree <- out_cgpt3_agree %>% filter(
+    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
+)
+
+# Print results
+cat(paste0(
+    "ICD-10 Output\n-------------",
+    "\nChatGPT-3.5 ICD-10 Coded (Phy. ICD-10 Coded): ", out_cgpt3 %>% nrow,
+    "\nChatGPT-3.5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt3_agree %>% nrow,
+    "\n\nAfter Conversion to CGHR-10\n---------------------------",
+    "\nChatGPT-3.5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt3_cghr10 %>% nrow,
+    "\nChatGPT-3.5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt3_cghr10_agree %>% nrow
+))
+```
+
+### ChatGPT-4 Counts
+
+Check ChatGPT-4 Counts:
+
+```{r}
+
+# Get phy coded records only
+out_coded <- out %>% filter(
+    !is.na(physician_icd10) & !is.null(physician_icd10)
+)
+out_coded_agree <- out_coded %>% filter(is_agreed == TRUE)
+
+# Get chatgpt4 coded records
+out_cgpt4 <- out_coded %>% filter(
+    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
+)
+out_cgpt4_agree <- out_coded_agree %>% filter(
+    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
+)
+
+# Get chatgpt4 coded records converted to cghr10
+out_cgpt4_cghr10 <- out_cgpt4 %>% filter(
+    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
+)
+out_cgpt4_cghr10_agree <- out_cgpt4_agree %>% filter(
+    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
+)
+
+# Print results
+cat(paste0(
+    "ICD-10 Output\n-------------",
+    "\nChatGPT-4 ICD-10 Coded (Phy. ICD-10 Coded): ", out_cgpt4 %>% nrow,
+    "\nChatGPT-4 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt4_agree %>% nrow,
+    "\n\nAfter Conversion to CGHR-10\n---------------------------",
+    "\nChatGPT-4 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt4_cghr10 %>% nrow,
+    "\nChatGPT-4 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt4_cghr10_agree %>% nrow
+))
+```
+
+### Narrative Counts
+
+Check narrative counts:
+
+```{r}
+
+# Add narr
+out_narr <- out %>% left_join(
+    df$narrative,
+    by = c("rowid" = "rowid"),
+    suffix = c("", "")
+) %>% filter(
+    !is.na(summary)
+)
+
+# Display counts
+narr_raw <- out_narr %>% nrow
+narr_agree <- out_narr %>% filter(
+    is_agreed == TRUE
+) %>% nrow
+narr_icd10 <- out_narr %>% filter(
+    !is.na(physician_icd10)
+) %>% nrow
+narr_cghr10 <- out_narr %>% filter(
+    !is.na(physician_cghr10)
+) %>% nrow
+narr_icd10_agree <- out_narr %>% filter(
+    is_agreed == TRUE & !is.na(physician_icd10)
+) %>% nrow
+narr_cghr10_agree <- out_narr %>% filter(
+    is_agreed == TRUE & !is.na(physician_cghr10)
+) %>% nrow
+cat(paste0(
+    "Narratives: ", narr_raw,
+    "\nNarratives (Agreed): ", narr_agree,
+    "\nNarratives (Phy. ICD-10 Coded): ", narr_icd10,
+    "\nNarratives (Phy. CGHR-10 Coded): ", narr_cghr10,
+    "\nNarratives (Agreed, Phy. ICD-10 Coded): ", narr_icd10_agree,
+    "\nNarratives (Agreed, Phy. CGHR-10 Coded): ", narr_cghr10_agree
+))
+```
+
+### WHO Formatted Record Counts
+
+Check WHO VA v1.5.1 formatted counts:
+
+```{r}
+
+# Add who
+out_who <- out %>% left_join(
+    df$who %>% mutate(rowid_who = rowid),
+    by = c("rowid" = "rowid"),
+    suffix = c("", "")
+) %>% filter(!is.na(rowid_who))
+
+# Display counts
+who_raw <- out_who %>% nrow
+who_agree <- out_who %>% filter(
+    is_agreed == TRUE
+) %>% nrow
+who_icd10 <- out_who %>% filter(
+    !is.na(physician_icd10)
+) %>% nrow
+who_cghr10 <- out_who %>% filter(
+    !is.na(physician_cghr10)
+) %>% nrow
+who_icd10_agree <- out_who %>% filter(
+    is_agreed == TRUE & !is.na(physician_icd10)
+) %>% nrow
+who_cghr10_agree <- out_who %>% filter(
+    is_agreed == TRUE & !is.na(physician_cghr10)
+) %>% nrow
+cat(paste0(
+    "WHO Format Records: ", who_raw,
+    "\nWHO Format Records (Agreed): ", who_agree,
+    "\nWHO Format Records (Phy. ICD-10 Coded): ", narr_icd10,
+    "\nWHO Format Records (Phy. CGHR-10 Coded): ", narr_cghr10,
+    "\nWHO Format Records (Agreed, Phy. ICD-10 Coded): ", who_icd10_agree,
+    "\nWHO Format Records (Agreed, Phy. CGHR-10 Coded): ", who_cghr10_agree
+))
+```
+
 ## Results

### 2024-01-17 src/preprocess.Rmd
Working on methods

@@
 
+### InterVA-5 Counts
+
+Check InterVA-5 Counts:
+
+```{r}
+
+# Get who with physician coded records
+out_who <- out %>% left_join(
+    df$who %>% mutate(rowid_who = rowid),
+    by = c("rowid" = "rowid"),
+    suffix = c("", "")
+) %>% filter(!is.na(rowid_who) & !is.na(physician_icd10))
+out_who_agree <- out_who %>% filter(is_agreed == TRUE)
+
+# Get interva5 coded records in wva2016
+out_iva5 <- out_who %>% filter(
+    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
+)
+out_iva5_agree <- out_who_agree %>% filter(
+    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
+)
+
+# Get interva5 wva2016 coded records converted to icd10
+out_iva5_icd10 <- out_iva5 %>% filter(
+    !is.na(interva5_icd10) & !is.null(interva5_icd10)
+)
+out_iva5_icd10_agree <- out_iva5_agree %>% filter(
+    !is.na(interva5_icd10) & !is.null(interva5_icd10)
+)
+
+# Get interva5 icd10 coded records converted to cghr10
+out_iva5_cghr10 <- out_iva5_icd10 %>% filter(
+    !is.na(interva5_cghr10) & !is.null(interva5_cghr10)
+)
+out_iva5_cghr10_agree <- out_iva5_icd10_agree %>% filter(
+    !is.na(interva5_cghr10) & !is.null(interva5_cghr10)
+)
+
+# Print results
+cat(paste0(
+    "InterVA-5 WVA-2016 Output\n-------------------------",
+    "\nInterVA-5 ICD-10 Coded (Phy. ICD-10 Coded): ", out_iva5 %>% nrow,
+    "\nInterVA-5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_agree %>% nrow,
+    "\n\nAfter Conversion from WVA-2016 to ICD-10\n----------------------------------------",
+    "\nInterVA-5 ICD-10 Coded (Phy. ICD-10 Coded): ", out_iva5_icd10 %>% nrow,
+    "\nInterVA-5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_icd10_agree %>% nrow,
+    "\n\nAfter Conversion from ICD-10 to CGHR-10\n---------------------------------------",
+    "\nInterVA-5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_iva5_cghr10 %>% nrow,
+    "\nInterVA-5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_cghr10_agree %>% nrow
+))
+```
+
+### InSilicoVA Counts
+
+Check InSilicoVA Counts:
+
+```{r}
+
+# Get who
+out_who <- out %>% left_join(
+    df$who %>% mutate(rowid_who = rowid),
+    by = c("rowid" = "rowid"),
+    suffix = c("", "")
+) %>% filter(!is.na(rowid_who) & !is.na(physician_icd10))
+out_who_agree <- out_who %>% filter(is_agreed == TRUE)
+
+# Get insilicova coded records in wva2016
+out_isva <- out_who %>% filter(
+    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
+)
+out_isva_agree <- out_who_agree %>% filter(
+    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
+)
+
+# Get insilicova wva2016 coded records converted to icd10
+out_isva_icd10 <- out_isva %>% filter(
+    !is.na(insilicova_icd10) & !is.null(insilicova_icd10)
+)
+out_isva_icd10_agree <- out_isva_agree %>% filter(
+    !is.na(insilicova_icd10) & !is.null(insilicova_icd10)
+)
+
+# Get insilicova icd10 coded records converted to cghr10
+out_isva_cghr10 <- out_isva_icd10 %>% filter(
+    !is.na(insilicova_cghr10) & !is.null(insilicova_cghr10)
+)
+out_isva_cghr10_agree <- out_isva_icd10_agree %>% filter(
+    !is.na(insilicova_cghr10) & !is.null(insilicova_cghr10)
+)
+
+# Print results
+cat(paste0(
+    "InSilicoVA WVA-2016 Output\n-------------------------",
+    "\nInSilicoVA ICD-10 Coded (Phy. ICD-10 Coded): ", out_isva %>% nrow,
+    "\nInSilicoVA ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_agree %>% nrow,
+    "\n\nAfter Conversion from WVA-2016 to ICD-10\n----------------------------------------",
+    "\nInSilicoVA ICD-10 Coded (Phy. ICD-10 Coded): ", out_isva_icd10 %>% nrow,
+    "\nInSilicoVA ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_icd10_agree %>% nrow,
+    "\n\nAfter Conversion from ICD-10 to CGHR-10\n---------------------------------------",
+    "\nInSilicoVA CGHR-10 Coded (Phy. ICD-10 Coded): ", out_isva_cghr10 %>% nrow,
+    "\nInSilicoVA CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_cghr10_agree %>% nrow
+))
+```
+
 ### Narrative Counts

### 2024-01-24 src/insilicova.R
Add minimal interva and insilicova code

@@ -1,0 +1,16 @@
+library(openVA)
+library(tidyverse)
+
+# Read transformed input from pyCrossVA
+# Replace <OUTPATH2> with the path of your transformed InSilicoVA input data
+who_input <- as.data.frame(read_csv("<OUTPATH2>"))
+
+# Run InSilicoVA model
+model <- codeVA(
+    data.type = "WHO2016",
+    model = "InSilicoVA",
+    Nsim = 10000
+)
+
+# Get the top COD assignment per record
+out_cod <- getTopCOD(model, n = 1, include.prob = TRUE)

### 2024-01-24 src/interva5.R

@@ -1,0 +1,19 @@
+library(openVA)
+library(tidyverse)
+
+# Read transformed input from pyCrossVA
+# Replace <OUTPATH1> with the path of your transformed InterVA-5 input data
+who_input <- as.data.frame(read_csv("<OUTPATH1>"))
+
+# Run InterVA-5 model
+model <- codeVA(
+    data = ova_input,
+    data.type = "WHO2016",
+    model = "InterVA",
+    version = "5",
+    HIV = "h",
+    Malaria = "h"
+)
+
+# Get the top COD assignment per record
+out_cod <- getTopCOD(model, n = 1, include.prob = TRUE)

### 2024-01-24 src/pycrossva.py

@@ -1,0 +1,18 @@
+import pandas as pd
+from pycrossva.transform import transform
+
+# Read your WHO v1.5.1 raw input csv data
+# Replace <INPATH> with the path of your input csv file
+who151_input = pd.read_csv('<INPATH>')
+
+# Transform raw input csv data in WHO v1.5.1 format to InterVA-5 format
+interva5_input <- transform(('2016WHOv151', 'InterVA5'), who151_input)
+
+# Transform raw input csv data in WHO v1.5.1 format to InSilicoVA format
+insilicova_input <- transform(('2016WHOv151', 'InSilicoVA'), who151_input)
+
+# Save openva formatted data to csvs
+# Replace <OUTPATH1> with the path of your transformed InterVA-5 input data
+# Replace <OUTPATH2> with the path of your transformed InSilicoVA input data
+interva5_input.to_csv('<OUTPATH1>')
+insilicova_input.to_csv('OUTPATH2>')

### 2024-01-24 src/preprocess.Rmd
Working on odk variables cite, and adding age counts for raw data

@@
     !is.na(physician_icd10) & !is.null(physician_icd10)
-) %>% nrow
+)
 phy_icd10_agree <- out %>% filter(
      !is.na(physician_icd10) & !is.null(physician_icd10) & is_agreed == TRUE
-) %>% nrow
+)
 
@@
     !is.na(physician_cghr10) & !is.null(physician_cghr10)
-) %>% nrow
+)
 phy_cghr10_agree <- out %>% filter(
      !is.na(physician_cghr10) & !is.null(physician_cghr10) & is_agreed == TRUE
-) %>% nrow
+)
+
+# Get age icd10 counts
+phy_icd10_adult <- phy_icd10 %>% filter(age == "adult")
+phy_icd10_child <- phy_icd10 %>% filter(age == "child")
+phy_icd10_neo <- phy_icd10 %>% filter(age == "neo")
+phy_icd10_agree_adult <- phy_icd10_agree %>% filter(age == "adult")
+phy_icd10_agree_child <- phy_icd10_agree %>% filter(age == "child")
+phy_icd10_agree_neo <- phy_icd10_agree %>% filter(age == "neo")
+
+# Get age cghr10 counts
+phy_cghr10_adult <- phy_cghr10 %>% filter(age == "adult")
+phy_cghr10_child <- phy_cghr10 %>% filter(age == "child")
+phy_cghr10_neo <- phy_cghr10 %>% filter(age == "neo")
+phy_cghr10_agree_adult <- phy_cghr10_agree %>% filter(age == "adult")
+phy_cghr10_agree_child <- phy_cghr10_agree %>% filter(age == "child")
+phy_cghr10_agree_neo <- phy_cghr10_agree %>% filter(age == "neo")
 
@@
 cat(paste0(
-    "Physican ICD-10 Coded: ", phy_icd10,
-    "\nPhysician ICD-10 Coded (Agree): ", phy_icd10_agree,
-    "\nPhysican CGHR-10 Coded: ", phy_cghr10,
-    "\nPhysician CGHR-10 Coded (Agree): ", phy_cghr10_agree
+    "Overall\n-------",
+    "\nPhysican ICD-10 Coded: ", phy_icd10 %>% nrow,
+    "\nPhysician ICD-10 Coded (Agree): ", phy_icd10_agree %>% nrow,
+    "\nPhysican CGHR-10 Coded: ", phy_cghr10 %>% nrow,
+    "\nPhysician CGHR-10 Coded (Agree): ", phy_cghr10_agree %>% nrow,
+    "\n\nAdult\n-----",
+    "\nPhysican ICD-10 Coded: ", phy_icd10_adult %>% nrow,
+    "\nPhysician ICD-10 Coded (Agree): ", phy_icd10_agree_adult %>% nrow,
+    "\nPhysican CGHR-10 Coded: ", phy_cghr10_adult %>% nrow,
+    "\nPhysician CGHR-10 Coded (Agree): ", phy_cghr10_agree_adult %>% nrow,
+    "\n\nChild\n-----",
+    "\nPhysican ICD-10 Coded: ", phy_icd10_child %>% nrow,
+    "\nPhysician ICD-10 Coded (Agree): ", phy_icd10_agree_child %>% nrow,
+    "\nPhysican CGHR-10 Coded: ", phy_cghr10_child %>% nrow,
+    "\nPhysician CGHR-10 Coded (Agree): ", phy_cghr10_agree_child %>% nrow,
+    "\n\nNeonatal\n--------",
+    "\nPhysican ICD-10 Coded: ", phy_icd10_neo %>% nrow,
+    "\nPhysician ICD-10 Coded (Agree): ", phy_icd10_agree_neo %>% nrow,
+    "\nPhysican CGHR-10 Coded: ", phy_cghr10_neo %>% nrow,
+    "\nPhysician CGHR-10 Coded (Agree): ", phy_cghr10_agree_neo %>% nrow
 ))

### 2024-01-24 src/insilicova.R
Working on reproducibility

@@ -2,8 +2,8 @@ library(openVA)
 library(tidyverse)
 
 # Read transformed input from pyCrossVA
-# Replace <OUTPATH2> with the path of your transformed InSilicoVA input data
-who_input <- as.data.frame(read_csv("<OUTPATH2>"))
+# Replace "tmp/healsl_rd1to2_ova_insilicova_v1.csv" with the path of your transformed InSilicoVA input data
+who_input <- as.data.frame(read_csv("tmp/healsl_rd1to2_ova_insilicova_v1.csv"))
 
 # Run InSilicoVA model
 model <- codeVA(
@@ -13,4 +13,4 @@ model <- codeVA(
 )
 
 # Get the top COD assignment per record
-out_cod <- getTopCOD(model, n = 1, include.prob = TRUE)
+insilicova_cod <- getTopCOD(model, n = 1, include.prob = TRUE)

### 2024-01-24 src/interva5.R

@@ -2,8 +2,8 @@ library(openVA)
 library(tidyverse)
 
 # Read transformed input from pyCrossVA
-# Replace <OUTPATH1> with the path of your transformed InterVA-5 input data
-who_input <- as.data.frame(read_csv("<OUTPATH1>"))
+# Replace "tmp/healsl_rd1to2_ova_interva5_v1.csv" with the path of your transformed InterVA-5 input data
+who_input <- as.data.frame(read_csv("tmp/healsl_rd1to2_ova_interva5_v1.csv"))
 
 # Run InterVA-5 model
 model <- codeVA(
@@ -16,4 +16,4 @@ model <- codeVA(
 )
 
 # Get the top COD assignment per record
-out_cod <- getTopCOD(model, n = 1, include.prob = TRUE)
+interva5_cod <- getTopCOD(model, n = 1, include.prob = TRUE)

### 2024-01-24 src/pycrossva.py

@@ -2,8 +2,8 @@ import pandas as pd
 from pycrossva.transform import transform
 
 # Read your WHO v1.5.1 raw input csv data
-# Replace <INPATH> with the path of your input csv file
-who151_input = pd.read_csv('<INPATH>')
+# Replace 'tmp/healsl_rd1to2_who151_v1.csv' with the path of your input csv file
+who151_input = pd.read_csv('tmp/healsl_rd1to2_who151_v1.csv')
 
 # Transform raw input csv data in WHO v1.5.1 format to InterVA-5 format
 interva5_input <- transform(('2016WHOv151', 'InterVA5'), who151_input)
@@ -12,7 +12,7 @@ interva5_input <- transform(('2016WHOv151', 'InterVA5'), who151_input)
 insilicova_input <- transform(('2016WHOv151', 'InSilicoVA'), who151_input)
 
 # Save openva formatted data to csvs
-# Replace <OUTPATH1> with the path of your transformed InterVA-5 input data
-# Replace <OUTPATH2> with the path of your transformed InSilicoVA input data
-interva5_input.to_csv('<OUTPATH1>')
-insilicova_input.to_csv('OUTPATH2>')
+# Replace 'tmp/healsl_rd1to2_ova_interva5_v1.csv' with the path of your transformed InterVA-5 input data
+# Replace 'tmp/healsl_rd1to2_ova_insilicova_v1.csv' with the path of your transformed InSilicoVA input data
+interva5_input.to_csv('tmp/healsl_rd1to2_ova_interva5_v1.csv')
+insilicova_input.to_csv('tmp/healsl_rd1to2_ova_insilicova_v1.csv')

### 2024-01-25 src/plots.Rmd
Check code and run for reproducibility

@@
 ```{r}
-raw_df <- read_csv("../data/healsl_rd1to2_cod_v1.csv")
+raw_df <- read_csv("/data/healsl_rd1to2_cod_v1.csv")
 ```
@@
 )
-write_csv(out, "../data/healsl_rd1to2_metrics_v1.csv")
+write_csv(out, "/data/healsl_rd1to2_metrics_v1.csv")
 ```
@@
 asplot
-ggsave("../manuscript/fig-data-agesex.pdf", plot = asplot, dpi = 300)
+ggsave("/manuscript/fig-data-agesex.pdf", plot = asplot, dpi = 300)
 ```
@@
     ggsave(
-        sprintf("../manuscript/fig-data-agerange-%s.pdf", a),
+        sprintf("/manuscript/fig-data-agerange-%s.pdf", a),
         plot = earplot,
@@
     ggsave(
-        sprintf("../manuscript/fig-data-cod-%s.pdf", a),
+        sprintf("/manuscript/fig-data-cod-%s.pdf", a),
         plot = ecodplot,
@@
 allplot
-ggsave("../manuscript/fig-perf-allvsagree.pdf", plot = allplot, dpi = 300)
+ggsave("/manuscript/fig-perf-allvsagree.pdf", plot = allplot, dpi = 300)
 ```
@@
 ageplot
-ggsave("../manuscript/fig-perf-agegroup.pdf", plot = ageplot, dpi = 300)
+ggsave("/manuscript/fig-perf-agegroup.pdf", plot = ageplot, dpi = 300)
 ```
@@
     ggsave(
-        sprintf("../manuscript/fig-perf-sex-%s.pdf", a),
+        sprintf("/manuscript/fig-perf-sex-%s.pdf", a),
         plot = sxplot,
@@
     ggsave(
-        sprintf("../manuscript/fig-perf-agerange-%s.pdf", a),
+        sprintf("/manuscript/fig-perf-agerange-%s.pdf", a),
         plot = arplot,
@@
     ggsave(
-        sprintf("../manuscript/fig-perf-cod-%s.pdf", a),
+        sprintf("/manuscript/fig-perf-cod-%s.pdf", a),
         plot = codplot,

### 2024-01-25 src/preprocess.Rmd
Check code and run for reproducibility

@@
     wva2016_icd10 = read_csv(
-        "../data/wva2016_icd10_v1.csv",
+        "data/wva2016_icd10_v1.csv",
         col_types = cols(wva2016_code = col_double())
     ),
-    icd10_cghr10 = read_csv("../data/icd10_cghr10_v1.csv"),
+    icd10_cghr10 = read_csv("data/icd10_cghr10_v1.csv"),
     physician = bind_rows(
         read_csv(
-            "../tmp/healsl_rd1_adult_v1.csv",
+            "tmp/healsl_rd1_adult_v1.csv",
             col_select = all_of(phy_adult_cols)
@@
         read_csv(
-            "../tmp/healsl_rd2_adult_v1.csv",
+            "tmp/healsl_rd2_adult_v1.csv",
             col_select = all_of(phy_adult_cols)
@@
         read_csv(
-            "../tmp/healsl_rd1_child_v1.csv",
+            "tmp/healsl_rd1_child_v1.csv",
             col_select = all_of(phy_cols)
@@
         read_csv(
-            "../tmp/healsl_rd2_child_v1.csv",
+            "tmp/healsl_rd2_child_v1.csv",
             col_select = all_of(phy_cols)
@@
         read_csv(
-            "../tmp/healsl_rd1_neo_v1.csv",
+            "tmp/healsl_rd1_neo_v1.csv",
             col_select = all_of(phy_cols)
@@
         read_csv(
-            "../tmp/healsl_rd2_neo_v1.csv",
+            "tmp/healsl_rd2_neo_v1.csv",
             col_select = all_of(phy_cols)
@@
         read_csv(
-            "../tmp/healsl_rd1_rapid_chatgpt3_v1.csv",
+            "tmp/healsl_rd1_rapid_chatgpt3_v1.csv",
             col_select = c("rowid", "round", "api_chat_icd")
@@
         read_csv(
-            "../tmp/healsl_rd2_rapid_chatgpt3_v1.csv",
+            "tmp/healsl_rd2_rapid_chatgpt3_v1.csv",
             col_select = c("rowid", "round", "api_chat_icd")
@@
         read_csv(
-            "../tmp/healsl_rd1_rapid_chatgpt4_v1.csv",
+            "tmp/healsl_rd1_rapid_chatgpt4_v1.csv",
             col_select = c("rowid", "round", "api_chat_icd")
@@
         read_csv(
-            "../tmp/healsl_rd2_rapid_chatgpt4_v1.csv",
+            "tmp/healsl_rd2_rapid_chatgpt4_v1.csv",
             col_select = c("rowid", "round", "api_chat_icd")
@@
         read_csv(
-            "../tmp/healsl_rd1_rapid_insilicova_v1.csv",
+            "tmp/healsl_rd1_rapid_insilicova_v1.csv",
             col_select = c("rowid", "round", "cause1_wva")
@@
         read_csv(
-            "../tmp/healsl_rd2_rapid_insilicova_v1.csv",
+            "tmp/healsl_rd2_rapid_insilicova_v1.csv",
             col_select = c("rowid", "round", "cause1_wva")
@@
         read_csv(
-            "../tmp/healsl_rd1_rapid_interva5_v1.csv",
+            "tmp/healsl_rd1_rapid_interva5_v1.csv",
             col_select = c("rowid", "round", "cause1_wva")
@@
         read_csv(
-            "../tmp/healsl_rd2_rapid_interva5_v1.csv",
+            "tmp/healsl_rd2_rapid_interva5_v1.csv",
             col_select = c("rowid", "round", "cause1_wva")
@@
         read_csv(
-            "../tmp/healsl_rd1_adult_narrative_v1.csv",
+            "tmp/healsl_rd1_adult_narrative_v1.csv",
             col_select = c("rowid", "summary")
@@
         read_csv(
-            "../tmp/healsl_rd1_child_narrative_v1.csv",
+            "tmp/healsl_rd1_child_narrative_v1.csv",
             col_select = c("rowid", "summary")
@@
         read_csv(
-            "../tmp/healsl_rd1_neo_narrative_v1.csv",
+            "tmp/healsl_rd1_neo_narrative_v1.csv",
             col_select = c("rowid", "summary")
@@
         read_csv(
-            "../tmp/healsl_rd2_adult_narrative_v1.csv",
+            "tmp/healsl_rd2_adult_narrative_v1.csv",
             col_select = c("rowid", "summary")
@@
         read_csv(
-            "../tmp/healsl_rd2_child_narrative_v1.csv",
+            "tmp/healsl_rd2_child_narrative_v1.csv",
             col_select = c("rowid", "summary")
@@
         read_csv(
-            "../tmp/healsl_rd2_neo_narrative_v1.csv",
+            "tmp/healsl_rd2_neo_narrative_v1.csv",
             col_select = c("rowid", "summary")
@@
         read_csv(
-            "../tmp/healsl_rd1_who_adult_v1.csv",
+            "tmp/healsl_rd1_who_adult_v1.csv",
             col_select = c("rowid")
@@
         read_csv(
-            "../tmp/healsl_rd1_who_child_v1.csv",
+            "tmp/healsl_rd1_who_child_v1.csv",
             col_select = c("rowid")
@@
         read_csv(
-            "../tmp/healsl_rd1_who_neo_v1.csv",
+            "tmp/healsl_rd1_who_neo_v1.csv",
             col_select = c("rowid")
@@
         read_csv(
-            "../tmp/healsl_rd2_who_adult_v1.csv",
+            "tmp/healsl_rd2_who_adult_v1.csv",
             col_select = c("rowid")
@@
         read_csv(
-            "../tmp/healsl_rd2_who_child_v1.csv",
+            "tmp/healsl_rd2_who_child_v1.csv",
             col_select = c("rowid")
@@
         read_csv(
-            "../tmp/healsl_rd2_who_neo_v1.csv",
+            "tmp/healsl_rd2_who_neo_v1.csv",
             col_select = c("rowid")
@@
 ```{r}
-write_csv(out, "../data/healsl_rd1to2_cod_v1.csv")
+write_csv(out, "data/healsl_rd1to2_cod_v1.csv")
 ```

### 2024-01-25 src/insilicova.R

@@ -3,7 +3,10 @@ library(tidyverse)
 
 # Read transformed input from pyCrossVA
 # Replace "tmp/healsl_rd1to2_ova_insilicova_v1.csv" with the path of your transformed InSilicoVA input data
-who_input <- as.data.frame(read_csv("tmp/healsl_rd1to2_ova_insilicova_v1.csv"))
+ova_input <- as.data.frame(read_csv("tmp/healsl_rd1to2_ova_insilicova_v1.csv"))
+
+# Track start time
+start_time <- Sys.time()
 
 # Run InSilicoVA model
 model <- codeVA(
@@ -12,5 +15,13 @@ model <- codeVA(
     Nsim = 10000
 )
 
+# Track end time
+end_time <- Sys.time()
+
 # Get the top COD assignment per record
+# Replace "tmp/healsl_rd1to2_cod_insilicova_v1.csv" with the path of your InSilicoVA output data
 insilicova_cod <- getTopCOD(model, n = 1, include.prob = TRUE)
+write.csv(insilicova_cod, "tmp/healsl_rd1to2_cod_insilicova_v1.csv")
+
+# Print run time
+print(end_time - start_time)

### 2024-01-25 src/install.R

@@ -1,0 +1,2 @@
+install.packages("openVA")
+install.packages("tidyverse")

### 2024-01-25 src/interva5.R

@@ -3,7 +3,10 @@ library(tidyverse)
 
 # Read transformed input from pyCrossVA
 # Replace "tmp/healsl_rd1to2_ova_interva5_v1.csv" with the path of your transformed InterVA-5 input data
-who_input <- as.data.frame(read_csv("tmp/healsl_rd1to2_ova_interva5_v1.csv"))
+ova_input <- as.data.frame(read_csv("tmp/healsl_rd1to2_ova_interva5_v1.csv"))
+
+# Track start time
+start_time <- Sys.time()
 
 # Run InterVA-5 model
 model <- codeVA(
@@ -12,8 +15,17 @@ model <- codeVA(
     model = "InterVA",
     version = "5",
     HIV = "h",
-    Malaria = "h"
+    Malaria = "h",
+    write = FALSE
 )
 
+# Track end time
+end_time <- Sys.time()
+
 # Get the top COD assignment per record
+# Replace "tmp/healsl_rd1to2_cod_interva5_v1.csv" with the path of your InterVA-5 output data
 interva5_cod <- getTopCOD(model, n = 1, include.prob = TRUE)
+write.csv(interva5_cod, "tmp/healsl_rd1to2_cod_interva5_v1.csv", row.names = FALSE)
+
+# Print run time
+print(end_time - start_time)

### 2024-01-25 src/pycrossva.py

@@ -6,13 +6,21 @@ from pycrossva.transform import transform
 who151_input = pd.read_csv('tmp/healsl_rd1to2_who151_v1.csv')
 
 # Transform raw input csv data in WHO v1.5.1 format to InterVA-5 format
-interva5_input <- transform(('2016WHOv151', 'InterVA5'), who151_input)
+interva5_input = transform(
+    ('2016WHOv151', 'InterVA5'),
+    who151_input,
+    raw_data_id = 'rowid'
+)
 
 # Transform raw input csv data in WHO v1.5.1 format to InSilicoVA format
-insilicova_input <- transform(('2016WHOv151', 'InSilicoVA'), who151_input)
+insilicova_input = transform(
+    ('2016WHOv151', 'InSilicoVA'),
+    who151_input,
+    raw_data_id = 'rowid'
+)
 
 # Save openva formatted data to csvs
 # Replace 'tmp/healsl_rd1to2_ova_interva5_v1.csv' with the path of your transformed InterVA-5 input data
 # Replace 'tmp/healsl_rd1to2_ova_insilicova_v1.csv' with the path of your transformed InSilicoVA input data
-interva5_input.to_csv('tmp/healsl_rd1to2_ova_interva5_v1.csv')
-insilicova_input.to_csv('tmp/healsl_rd1to2_ova_insilicova_v1.csv')
+interva5_input.to_csv('tmp/healsl_rd1to2_ova_interva5_v1.csv', index = False)
+insilicova_input.to_csv('tmp/healsl_rd1to2_ova_insilicova_v1.csv', index = False)

### 2024-01-25 src/preprocess.Rmd
Sanitized counts

--- 2024-01-24 src/preprocess.Rmd
@@
 
-# Get phy coded records only
+# Get phy coded icd10 records only
 out_coded <- out %>% filter(
@@
 out_coded_agree <- out_coded %>% filter(is_agreed == TRUE)
+
+# Get phy coded cghr10 records only
+out_coded_cghr10 <- out_coded %>% filter(
+    !is.na(physician_cghr10) & !is.null(physician_cghr10)
+)
+out_coded_cghr10_agree <- out_coded_cghr10 %>% filter(is_agreed == TRUE)
 
@@
 )
+out_cgpt3_cghr10 <- out_coded_cghr10 %>% filter(
+    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
+)
+out_cgpt3_cghr10_agree <- out_coded_cghr10_agree %>% filter(
+    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
+)
 
 # Get chatgpt3 coded records converted to cghr10
-out_cgpt3_cghr10 <- out_cgpt3 %>% filter(
+out_cgpt3_xcghr10 <- out_cgpt3 %>% filter(
     !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
 )
-out_cgpt3_cghr10_agree <- out_cgpt3_agree %>% filter(
+out_cgpt3_xcghr10_agree <- out_cgpt3_agree %>% filter(
+    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
+)
+out_cgpt3_xcghr10_cghr10 <- out_cgpt3_cghr10 %>% filter(
+    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
+)
+out_cgpt3_xcghr10_cghr10_agree <- out_cgpt3_cghr10_agree %>% filter(
     !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
@@
     "\nChatGPT-3.5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt3_agree %>% nrow,
+    "\nChatGPT-3.5 ICD-10 Coded (Phy. CGHR-10 Coded): ", out_cgpt3_cghr10 %>% nrow,
+    "\nChatGPT-3.5 ICD-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_cgpt3_cghr10_agree %>% nrow,
     "\n\nAfter Conversion to CGHR-10\n---------------------------",
-    "\nChatGPT-3.5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt3_cghr10 %>% nrow,
-    "\nChatGPT-3.5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt3_cghr10_agree %>% nrow
+    "\nChatGPT-3.5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt3_xcghr10 %>% nrow,
+    "\nChatGPT-3.5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt3_xcghr10_agree %>% nrow,
+    "\nChatGPT-3.5 CGHR-10 Coded (Phy. CGHR-10 Coded): ", out_cgpt3_xcghr10_cghr10 %>% nrow,
+    "\nChatGPT-3.5 CGHR-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_cgpt3_xcghr10_cghr10_agree %>% nrow
 ))
@@
 )
+out_cgpt4_cghr10 <- out_coded_cghr10 %>% filter(
+    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
+)
+out_cgpt4_cghr10_agree <- out_coded_cghr10_agree %>% filter(
+    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
+)
 
 # Get chatgpt4 coded records converted to cghr10
-out_cgpt4_cghr10 <- out_cgpt4 %>% filter(
+out_cgpt4_xcghr10 <- out_cgpt4 %>% filter(
     !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
 )
-out_cgpt4_cghr10_agree <- out_cgpt4_agree %>% filter(
+out_cgpt4_xcghr10_agree <- out_cgpt4_agree %>% filter(
+    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
+)
+out_cgpt4_xcghr10_cghr10 <- out_cgpt4_cghr10 %>% filter(
+    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
+)
+out_cgpt4_xcghr10_cghr10_agree <- out_cgpt4_cghr10_agree %>% filter(
     !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
@@
     "\nChatGPT-4 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt4_agree %>% nrow,
+    "\nChatGPT-4 ICD-10 Coded (Phy. CGHR-10 Coded): ", out_cgpt4_cghr10 %>% nrow,
+    "\nChatGPT-4 ICD-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_cgpt4_cghr10_agree %>% nrow,
     "\n\nAfter Conversion to CGHR-10\n---------------------------",
-    "\nChatGPT-4 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt4_cghr10 %>% nrow,
-    "\nChatGPT-4 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt4_cghr10_agree %>% nrow
+    "\nChatGPT-4 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt4_xcghr10 %>% nrow,
+    "\nChatGPT-4 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt4_xcghr10_agree %>% nrow,
+    "\nChatGPT-4 CGHR-10 Coded (Phy. CGHR-10 Coded): ", out_cgpt4_xcghr10_cghr10 %>% nrow,
+    "\nChatGPT-4 CGHR-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_cgpt4_xcghr10_cghr10_agree %>% nrow
 ))
@@
 
+# Get who with physician coded records converted to CGHR-10
+out_who_cghr10 <- out %>% filter(!is.na(physician_cghr10))
+out_who_cghr10_agree <- out_who_cghr10 %>% filter(is_agreed == TRUE)
+
 # Get interva5 coded records in wva2016
@@
 out_iva5_agree <- out_who_agree %>% filter(
+    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
+)
+out_iva5_cghr10 <- out_who_cghr10 %>% filter(
+    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
+)
+out_iva5_chr10_agree <- out_who_cghr10_agree %>% filter(
     !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
@@
 )
+out_iva5_icd10_cghr10 <- out_iva5_cghr10 %>% filter(
+    !is.na(interva5_icd10) & !is.null(interva5_icd10)
+)
+out_iva5_icd10_cghr10_agree <- out_iva5_cghr10_agree %>% filter(
+    !is.na(interva5_icd10) & !is.null(interva5_icd10)
+)
 
 # Get interva5 icd10 coded records converted to cghr10
-out_iva5_cghr10 <- out_iva5_icd10 %>% filter(
+out_iva5_xcghr10 <- out_iva5_icd10 %>% filter(
     !is.na(interva5_cghr10) & !is.null(interva5_cghr10)
 )
-out_iva5_cghr10_agree <- out_iva5_icd10_agree %>% filter(
+out_iva5_xcghr10_agree <- out_iva5_icd10_agree %>% filter(
+    !is.na(interva5_cghr10) & !is.null(interva5_cghr10)
+)
+out_iva5_xcghr10_cghr10 <- out_iva5_icd10_cghr10 %>% filter(
+    !is.na(interva5_cghr10) & !is.null(interva5_cghr10)
+)
+out_iva5_xcghr10_cghr10_agree <- out_iva5_icd10_cghr10_agree %>% filter(
     !is.na(interva5_cghr10) & !is.null(interva5_cghr10)
@@
     "InterVA-5 WVA-2016 Output\n-------------------------",
-    "\nInterVA-5 ICD-10 Coded (Phy. ICD-10 Coded): ", out_iva5 %>% nrow,
-    "\nInterVA-5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_agree %>% nrow,
+    "\nInterVA-5 WVA-2016 Coded (Phy. ICD-10 Coded): ", out_iva5 %>% nrow,
+    "\nInterVA-5 WVA-2016 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_agree %>% nrow,
+    "\nInterVA-5 WVA-2016 Coded (Phy. CGHR-10 Coded): ", out_iva5_cghr10 %>% nrow,
+    "\nInterVA-5 WVA-2016 Coded (Agree, Phy. CGHR-10 Coded): ", out_iva5_cghr10_agree %>% nrow,
     "\n\nAfter Conversion from WVA-2016 to ICD-10\n----------------------------------------",
@@
     "\nInterVA-5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_icd10_agree %>% nrow,
+    "\nInterVA-5 ICD-10 Coded (Phy. CGHR-10 Coded): ", out_iva5_icd10_cghr10 %>% nrow,
+    "\nInterVA-5 ICD-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_iva5_icd10_cghr10_agree %>% nrow,
     "\n\nAfter Conversion from ICD-10 to CGHR-10\n---------------------------------------",
-    "\nInterVA-5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_iva5_cghr10 %>% nrow,
-    "\nInterVA-5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_cghr10_agree %>% nrow
+    "\nInterVA-5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_iva5_xcghr10 %>% nrow,
+    "\nInterVA-5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_xcghr10_agree %>% nrow,
+    "\nInterVA-5 CGHR-10 Coded (Phy. CGHR-10 Coded): ", out_iva5_xcghr10_cghr10 %>% nrow,
+    "\nInterVA-5 CGHR-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_iva5_xcghr10_cghr10_agree %>% nrow
 ))
@@
 
-# Get who
+# Get who with physician coded records
 out_who <- out %>% left_join(
@@
 
+# Get who with physician coded records converted to CGHR-10
+out_who_cghr10 <- out %>% filter(!is.na(physician_cghr10))
+out_who_cghr10_agree <- out_who_cghr10 %>% filter(is_agreed == TRUE)
+
 # Get insilicova coded records in wva2016
@@
 out_isva_agree <- out_who_agree %>% filter(
+    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
+)
+out_isva_cghr10 <- out_who_cghr10 %>% filter(
+    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
+)
+out_isva_chr10_agree <- out_who_cghr10_agree %>% filter(
     !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
@@
 )
+out_isva_icd10_cghr10 <- out_isva_cghr10 %>% filter(
+    !is.na(insilicova_icd10) & !is.null(insilicova_icd10)
+)
+out_isva_icd10_cghr10_agree <- out_isva_cghr10_agree %>% filter(
+    !is.na(insilicova_icd10) & !is.null(insilicova_icd10)
+)
 
 # Get insilicova icd10 coded records converted to cghr10
-out_isva_cghr10 <- out_isva_icd10 %>% filter(
+out_isva_xcghr10 <- out_isva_icd10 %>% filter(
     !is.na(insilicova_cghr10) & !is.null(insilicova_cghr10)
 )
-out_isva_cghr10_agree <- out_isva_icd10_agree %>% filter(
+out_isva_xcghr10_agree <- out_isva_icd10_agree %>% filter(
+    !is.na(insilicova_cghr10) & !is.null(insilicova_cghr10)
+)
+out_isva_xcghr10_cghr10 <- out_isva_icd10_cghr10 %>% filter(
+    !is.na(insilicova_cghr10) & !is.null(insilicova_cghr10)
+)
+out_isva_xcghr10_cghr10_agree <- out_isva_icd10_cghr10_agree %>% filter(
     !is.na(insilicova_cghr10) & !is.null(insilicova_cghr10)
@@
     "InSilicoVA WVA-2016 Output\n-------------------------",
-    "\nInSilicoVA ICD-10 Coded (Phy. ICD-10 Coded): ", out_isva %>% nrow,
-    "\nInSilicoVA ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_agree %>% nrow,
+    "\nInSilicoVA WVA-2016 Coded (Phy. ICD-10 Coded): ", out_isva %>% nrow,
+    "\nInSilicoVA WVA-2016 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_agree %>% nrow,
+    "\nInSilicoVA WVA-2016 Coded (Phy. CGHR-10 Coded): ", out_isva_cghr10 %>% nrow,
+    "\nInSilicoVA WVA-2016 Coded (Agree, Phy. CGHR-10 Coded): ", out_isva_cghr10_agree %>% nrow,
     "\n\nAfter Conversion from WVA-2016 to ICD-10\n----------------------------------------",
@@
     "\nInSilicoVA ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_icd10_agree %>% nrow,
+    "\nInSilicoVA ICD-10 Coded (Phy. CGHR-10 Coded): ", out_isva_icd10_cghr10 %>% nrow,
+    "\nInSilicoVA ICD-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_isva_icd10_cghr10_agree %>% nrow,
     "\n\nAfter Conversion from ICD-10 to CGHR-10\n---------------------------------------",
-    "\nInSilicoVA CGHR-10 Coded (Phy. ICD-10 Coded): ", out_isva_cghr10 %>% nrow,
-    "\nInSilicoVA CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_cghr10_agree %>% nrow
+    "\nInSilicoVA CGHR-10 Coded (Phy. ICD-10 Coded): ", out_isva_xcghr10 %>% nrow,
+    "\nInSilicoVA CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_xcghr10_agree %>% nrow,
+    "\nInSilicoVA CGHR-10 Coded (Phy. CGHR-10 Coded): ", out_isva_xcghr10_cghr10 %>% nrow,
+    "\nInSilicoVA CGHR-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_isva_xcghr10_cghr10_agree %>% nrow
 ))

### 2024-01-25 src/insilicova.R

@@ -10,9 +10,10 @@ start_time <- Sys.time()
 
 # Run InSilicoVA model
 model <- codeVA(
+    data = ova_input,
     data.type = "WHO2016",
     model = "InSilicoVA",
-    Nsim = 10000
+    Nsim = 9500
 )
 
 # Track end time

### 2024-01-26 src/insilicova.R
Add edits

@@ -22,7 +22,7 @@ end_time <- Sys.time()
 # Get the top COD assignment per record
 # Replace "tmp/healsl_rd1to2_cod_insilicova_v1.csv" with the path of your InSilicoVA output data
 insilicova_cod <- getTopCOD(model, n = 1, include.prob = TRUE)
-write.csv(insilicova_cod, "tmp/healsl_rd1to2_cod_insilicova_v1.csv")
+write.csv(insilicova_cod, "tmp/healsl_rd1to2_cod_insilicova_v1.csv", row.names = FALSE)
 
 # Print run time
 print(end_time - start_time)

### 2024-02-09 bin/setup_python.sh
Add python and r code versions

@@ -3,4 +3,4 @@ chmod +x ./bin/activate.sh
 chmod +x ./bin/deactivate.sh
 chmod +x ./bin/reinstall.sh
 chmod +x ./bin/uninstall.sh
-(source bin/activate.sh && pip install -r requirements.txt)
+(source bin/activate.sh && pip install -r src/requirements.txt)

### 2024-02-09 src/insilicova.R

@@ -1,3 +1,6 @@
+# R v4.3.1
+# openVA v1.1.1
+# InSilicoVA v1.4.0
 library(openVA)
 library(tidyverse)
 

### 2024-02-09 src/interva5.R

@@ -1,3 +1,6 @@
+# R v4.3.1
+# openVA v1.1.1
+# InterVA5 v1.1.3
 library(openVA)
 library(tidyverse)
 

### 2024-02-09 src/pycrossva.py

@@ -1,3 +1,5 @@
+# Python v3.11.4
+# pycrossva v0.97
 import pandas as pd
 from pycrossva.transform import transform
 

### 2024-02-12 src/plots.Rmd
Sanitized counts
Replace ChatGPT with GPT for accurate reference

--- 2024-01-17 src/plots.Rmd
@@
     "_" = " & ",
-    "chatgpt3" = "ChatGPT-3.5",
-    "chatgpt4" = "ChatGPT-4",
+    "gpt3" = "GPT-3.5",
+    "gpt4" = "GPT-4",
     "insilicova" = "InSilicoVA",
@@
     mutate( # Combine models
-        "chatgpt3_insilicova_cghr10" = if_else(
-            chatgpt3_cghr10 == physician_cghr10 | 
+        "gpt3_insilicova_cghr10" = if_else(
+            gpt3_cghr10 == physician_cghr10 | 
                 insilicova_cghr10 == physician_cghr10,
             physician_cghr10,
-            chatgpt3_cghr10
-        ),
-        "chatgpt4_insilicova_cghr10" = if_else(
-            chatgpt4_cghr10 == physician_cghr10 | 
+            gpt3_cghr10
+        ),
+        "gpt4_insilicova_cghr10" = if_else(
+            gpt4_cghr10 == physician_cghr10 | 
                 insilicova_cghr10 == physician_cghr10,
             physician_cghr10,
-            chatgpt4_cghr10
-        ),
-        "chatgpt3_interva5_cghr10" = if_else(
-            chatgpt3_cghr10 == physician_cghr10 | 
+            gpt4_cghr10
+        ),
+        "gpt3_interva5_cghr10" = if_else(
+            gpt3_cghr10 == physician_cghr10 | 
                 interva5_cghr10 == physician_cghr10,
             physician_cghr10,
-            chatgpt3_cghr10
-        ),
-        "chatgpt4_interva5_cghr10" = if_else(
-            chatgpt4_cghr10 == physician_cghr10 | 
+            gpt3_cghr10
+        ),
+        "gpt4_interva5_cghr10" = if_else(
+            gpt4_cghr10 == physician_cghr10 | 
                 interva5_cghr10 == physician_cghr10,
             physician_cghr10,
-            chatgpt4_cghr10
-        ),
-        "chatgpt3_insilicova_interva5_cghr10" = if_else(
-            chatgpt3_cghr10 == physician_cghr10 | 
+            gpt4_cghr10
+        ),
+        "gpt3_insilicova_interva5_cghr10" = if_else(
+            gpt3_cghr10 == physician_cghr10 | 
                 insilicova_cghr10 == physician_cghr10 |
@@
             physician_cghr10,
-            chatgpt3_cghr10
-        ),
-        "chatgpt4_insilicova_interva5_cghr10" = if_else(
-            chatgpt4_cghr10 == physician_cghr10 | 
+            gpt3_cghr10
+        ),
+        "gpt4_insilicova_interva5_cghr10" = if_else(
+            gpt4_cghr10 == physician_cghr10 | 
                 insilicova_cghr10 == physician_cghr10 |
@@
             physician_cghr10,
-            chatgpt4_cghr10
+            gpt4_cghr10
         )
@@
 print(head(df %>% select(
-    chatgpt3_insilicova_cghr10,
-    chatgpt4_insilicova_cghr10,
-    chatgpt3_interva5_cghr10,
-    chatgpt4_interva5_cghr10,
-    chatgpt3_insilicova_interva5_cghr10,
-    chatgpt4_insilicova_interva5_cghr10
+    gpt3_insilicova_cghr10,
+    gpt4_insilicova_cghr10,
+    gpt3_interva5_cghr10,
+    gpt4_interva5_cghr10,
+    gpt3_insilicova_interva5_cghr10,
+    gpt4_insilicova_interva5_cghr10
 )))

### 2024-02-12 src/preprocess.Rmd
Replace ChatGPT with GPT for accurate reference

@@
     ),
-    model_chatgpt3 = bind_rows(
+    model_gpt3 = bind_rows(
         read_csv(
-            "../tmp/healsl_rd1_rapid_chatgpt3_v1.csv",
+            "../tmp/healsl_rd1_rapid_gpt3_v1.csv",
             col_select = c("rowid", "round", "api_chat_icd")
@@
         read_csv(
-            "../tmp/healsl_rd2_rapid_chatgpt3_v1.csv",
+            "../tmp/healsl_rd2_rapid_gpt3_v1.csv",
             col_select = c("rowid", "round", "api_chat_icd")
         )
-    ) %>% rename(chatgpt3_icd10 = api_chat_icd),
-    model_chatgpt4 = bind_rows(
+    ) %>% rename(gpt3_icd10 = api_chat_icd),
+    model_gpt4 = bind_rows(
         read_csv(
-            "../tmp/healsl_rd1_rapid_chatgpt4_v1.csv",
+            "../tmp/healsl_rd1_rapid_gpt4_v1.csv",
             col_select = c("rowid", "round", "api_chat_icd")
@@
         read_csv(
-            "../tmp/healsl_rd2_rapid_chatgpt4_v1.csv",
+            "../tmp/healsl_rd2_rapid_gpt4_v1.csv",
             col_select = c("rowid", "round", "api_chat_icd")
         )
-    ) %>% rename(chatgpt4_icd10 = api_chat_icd),
+    ) %>% rename(gpt4_icd10 = api_chat_icd),
     model_insilicova = bind_rows(
@@
 
-# Get chatgpt3 coded records
+# Get gpt3 coded records
 out_cgpt3 <- out_coded %>% filter(
-    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
+    !is.na(gpt3_icd10) & !is.null(gpt3_icd10)
 )
 out_cgpt3_agree <- out_coded_agree %>% filter(
-    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
+    !is.na(gpt3_icd10) & !is.null(gpt3_icd10)
 )
 out_cgpt3_cghr10 <- out_coded_cghr10 %>% filter(
-    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
+    !is.na(gpt3_icd10) & !is.null(gpt3_icd10)
 )
 out_cgpt3_cghr10_agree <- out_coded_cghr10_agree %>% filter(
-    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
+    !is.na(gpt3_icd10) & !is.null(gpt3_icd10)
 )
 
-# Get chatgpt3 coded records converted to cghr10
+# Get gpt3 coded records converted to cghr10
 out_cgpt3_xcghr10 <- out_cgpt3 %>% filter(
-    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
+    !is.na(gpt3_cghr10) & !is.null(gpt3_cghr10)
 )
 out_cgpt3_xcghr10_agree <- out_cgpt3_agree %>% filter(
-    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
+    !is.na(gpt3_cghr10) & !is.null(gpt3_cghr10)
 )
 out_cgpt3_xcghr10_cghr10 <- out_cgpt3_cghr10 %>% filter(
-    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
+    !is.na(gpt3_cghr10) & !is.null(gpt3_cghr10)
 )
 out_cgpt3_xcghr10_cghr10_agree <- out_cgpt3_cghr10_agree %>% filter(
-    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
+    !is.na(gpt3_cghr10) & !is.null(gpt3_cghr10)
 )
@@
 
-# Get chatgpt4 coded records
+# Get gpt4 coded records
 out_cgpt4 <- out_coded %>% filter(
-    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
+    !is.na(gpt4_icd10) & !is.null(gpt4_icd10)
 )
 out_cgpt4_agree <- out_coded_agree %>% filter(
-    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
+    !is.na(gpt4_icd10) & !is.null(gpt4_icd10)
 )
 out_cgpt4_cghr10 <- out_coded_cghr10 %>% filter(
-    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
+    !is.na(gpt4_icd10) & !is.null(gpt4_icd10)
 )
 out_cgpt4_cghr10_agree <- out_coded_cghr10_agree %>% filter(
-    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
+    !is.na(gpt4_icd10) & !is.null(gpt4_icd10)
 )
 
-# Get chatgpt4 coded records converted to cghr10
+# Get gpt4 coded records converted to cghr10
 out_cgpt4_xcghr10 <- out_cgpt4 %>% filter(
-    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
+    !is.na(gpt4_cghr10) & !is.null(gpt4_cghr10)
 )
 out_cgpt4_xcghr10_agree <- out_cgpt4_agree %>% filter(
-    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
+    !is.na(gpt4_cghr10) & !is.null(gpt4_cghr10)
 )
 out_cgpt4_xcghr10_cghr10 <- out_cgpt4_cghr10 %>% filter(
-    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
+    !is.na(gpt4_cghr10) & !is.null(gpt4_cghr10)
 )
 out_cgpt4_xcghr10_cghr10_agree <- out_cgpt4_cghr10_agree %>% filter(
-    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
+    !is.na(gpt4_cghr10) & !is.null(gpt4_cghr10)
 )
@@
 )
-out_iva5_chr10_agree <- out_who_cghr10_agree %>% filter(
+out_iva5_cghr10_agree <- out_who_cghr10_agree %>% filter(
     !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
@@
 )
-out_isva_chr10_agree <- out_who_cghr10_agree %>% filter(
+out_isva_cghr10_agree <- out_who_cghr10_agree %>% filter(
     !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)

### 2024-02-13 src/plots.Rmd
Finish results

@@
 author: "Richard Wen <richard.wen@unityhealth.to>"
-output: html_notebook
 ---
@@
         ncod <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE & age == a) %>% nrow
-        pcod <- (ncod / nagree) * 100
+        pcod <- (ncod / arows) * 100
         pcod_label <- if (round(pcod) >= 1) round(pcod) else "<1"
@@
         width = if (a == "adult") 8 else NA,
-        height = if (a == "adult") 10 else NA
-    )
-}
-```
+        height = if (a == "adult") 9 else NA
+    )
+}
+```

### 2024-02-21 src/preprocess.Rmd
Finish results
Prep for andy gpt3 results

@@
         read_csv(
-            "../tmp/healsl_rd1_rapid_gpt3_v1.csv",
-            col_select = c("rowid", "round", "api_chat_icd")
-        ),
+            "../tmp/healsl_rd1_rapid_gpt3_v2.csv",
+            col_select = c("rowid", "cause1_icd10")
+        ) %>% mutate(round = 1),
         read_csv(
-            "../tmp/healsl_rd2_rapid_gpt3_v1.csv",
-            col_select = c("rowid", "round", "api_chat_icd")
-        )
-    ) %>% rename(gpt3_icd10 = api_chat_icd),
+            "../tmp/healsl_rd2_rapid_gpt3_v2.csv",
+            col_select = c("rowid", "cause1_icd10")
+        ) %>% mutate(round = 2)
+    ) %>% rename(gpt3_icd10 = cause1_icd10),
     model_gpt4 = bind_rows(

### 2024-03-18 src/preprocess.Rmd
Plotted gpt3 v2a results from andy for rd1to2
Update manuscript plots with gpt3 v2a results from andy
Final gpt3/4 results from andy - first icd as pred

@@
         read_csv(
-            "../tmp/healsl_rd1_rapid_gpt3_v2.csv",
+            "../tmp/healsl_rd1_rapid_gpt3_v2b_first.csv",
             col_select = c("rowid", "cause1_icd10")
-        ) %>% mutate(round = 1),
+        ) %>% mutate(
+            cause1_icd10 = str_sub(cause1_icd10, 1, 3),
+            round = 1
+        ),
         read_csv(
-            "../tmp/healsl_rd2_rapid_gpt3_v2.csv",
+            "../tmp/healsl_rd2_rapid_gpt3_v2b_first.csv",
             col_select = c("rowid", "cause1_icd10")
-        ) %>% mutate(round = 2)
+        ) %>% mutate(
+            cause1_icd10 = str_sub(cause1_icd10, 1, 3),
+            round = 2
+        )
     ) %>% rename(gpt3_icd10 = cause1_icd10),
@@
         read_csv(
-            "../tmp/healsl_rd1_rapid_gpt4_v1.csv",
-            col_select = c("rowid", "round", "api_chat_icd")
+            "../tmp/healsl_rd1_rapid_gpt4_v2b_first.csv",
+            col_select = c("rowid", "cause1_icd10")
+        ) %>% mutate(
+            cause1_icd10 = str_sub(cause1_icd10, 1, 3),
+            round = 1
         ),
         read_csv(
-            "../tmp/healsl_rd2_rapid_gpt4_v1.csv",
-            col_select = c("rowid", "round", "api_chat_icd")
+            "../tmp/healsl_rd2_rapid_gpt4_v2b_first.csv",
+            col_select = c("rowid", "cause1_icd10")
+        ) %>% mutate(
+            cause1_icd10 = str_sub(cause1_icd10, 1, 3),
+            round = 2
         )
-    ) %>% rename(gpt4_icd10 = api_chat_icd),
+    ) %>% rename(gpt4_icd10 = cause1_icd10),
     model_insilicova = bind_rows(

### 2024-03-18 src/preprocess.Rmd
Final gpt3/4 results from andy - sorted icd as pred - worse perf than first

@@
         read_csv(
-            "../tmp/healsl_rd1_rapid_gpt3_v2b_first.csv",
+            "../tmp/healsl_rd1_rapid_gpt3_v2b_sorted.csv",
             col_select = c("rowid", "cause1_icd10")
@@
         read_csv(
-            "../tmp/healsl_rd2_rapid_gpt3_v2b_first.csv",
+            "../tmp/healsl_rd2_rapid_gpt3_v2b_sorted.csv",
             col_select = c("rowid", "cause1_icd10")
@@
         read_csv(
-            "../tmp/healsl_rd1_rapid_gpt4_v2b_first.csv",
+            "../tmp/healsl_rd1_rapid_gpt4_v2b_sorted.csv",
             col_select = c("rowid", "cause1_icd10")
@@
         read_csv(
-            "../tmp/healsl_rd2_rapid_gpt4_v2b_first.csv",
+            "../tmp/healsl_rd2_rapid_gpt4_v2b_sorted.csv",
             col_select = c("rowid", "cause1_icd10")

### 2024-04-08 bin/py/gpt3.py
copying gpt executable over

@@ -1,0 +1,1502 @@
+import os
+import pandas as pd
+import numpy as np
+from openai import OpenAI
+import datetime
+import pytz
+import logging
+
+import textwrap
+import json
+import re
+
+# Global Variables
+TIMEZONE = pytz.timezone('America/Toronto')
+TEMP_DIR = "tmp\gpt"
+DATA_DIR = "tmp"
+OUTPUT_DIR = "tmp\output"
+INCLUDE_SAMPLING = True
+script_dir = os.path.dirname(__file__)
+
+# #############################################################################################
+# STAGE 1 Parameters
+# #############################################################################################
+
+# File Settings
+s1_out_csv_filename = "s1_output_full.csv"
+s1_out_sample_csv_filename = "s1_output_sample.csv"
+
+s1_in_dir = os.path.join(script_dir, DATA_DIR)
+s1_out_full_csv = os.path.join(script_dir, TEMP_DIR, s1_out_csv_filename)
+s1_out_smpl_csv = os.path.join(script_dir, TEMP_DIR, s1_out_sample_csv_filename)
+
+# Sampling Settings
+# How many samples and how many times to repeat each sample.
+N_SAMPLES = 100
+N_REPEAT_RESPONSES = 10
+
+# #############################################################################################
+# STAGE 2 Parameters
+# #############################################################################################
+
+# Demo mode artificially limits the number of rows from the import dataset for testing/demo purposes
+DEMO_MODE = False
+DEMO_RANDOM = False
+DEMO_SIZE_LIMIT = 5
+
+# Discard columns not recognized by the script before saving output file.
+# Set to True to retain only essential columns in the output file.
+# Set to False to retain all columns similar to the input file.
+DROP_EXCESS_COLUMNS = False
+
+# Number of API calls between saving the output file
+SAVE_FREQ = 3
+
+# Models Settings
+# GPT4 = "gpt-4-0613"
+# GPT3 = "gpt-3.5-turbo-0125"
+models = {
+    "gpt4": "gpt-4-0613",
+    "gpt3": "gpt-3.5-turbo-0125"
+}
+SELECTED_MODEL = "gpt3"
+MODEL_NAME = models[SELECTED_MODEL]
+TEMPERATURE = 0
+LOGPROBS = True
+MAX_TOKENS = 30
+
[…]

### 2024-04-08 bin/py/gpt4.py
adding gpt4 minor changes

@@ -57,7 +57,7 @@ models = {
     "gpt4": "gpt-4-0613",
     "gpt3": "gpt-3.5-turbo-0125"
 }
-SELECTED_MODEL = "gpt3"
+SELECTED_MODEL = "gpt4"
 MODEL_NAME = models[SELECTED_MODEL]
 TEMPERATURE = 0
 LOGPROBS = True
@@ -106,6 +106,7 @@ s4a_out_filename_template = "healsl_ROUND_rapid_MODELNAME_VERSION.csv"
 # #############################################################################################
 # STAGE 4b Parameters
 # #############################################################################################
+
 
 s4b_in_smpl_csv_filepath = s3_out_smpl_csv
 # smpl_analysis_in_csv_path = os.path.join(script_dir, OUTPUT_DIR, PROCESS_FILE)

### 2024-04-13 src/plots.Rmd
Clean up plots with overlapping labels

@@
         ),
+        "PCCC Mid Left" = if_else(
+          `PCCC Mid Value` <= 0.5,
+          `PCCC Mid`,
+          NA
+        ),
+        "PCCC Mid Right" = if_else(
+          `PCCC Mid Value` > 0.5,
+          `PCCC Mid`,
+          NA
+        ),
         "PCCC Min" = if_else( # Combine into one row if close PCCC
@@
     geom_text(
-        aes(label = `PCCC Mid`),
+        aes(label = `PCCC Mid Left`),
         color = "#4d4d4d",
@@
         position = position_nudge(y = -0.015, x = -0.3)
+    ) +
+    geom_text(
+        aes(label = `PCCC Mid Right`),
+        color = "#4d4d4d",
+        size = 2,
+        hjust = 0,
+        position = position_nudge(y = 0.015, x = -0.3)
     ) +
@@
             ),
+            "PCCC Mid Left" = if_else(
+                `PCCC Mid Value` <= 0.5,
+                `PCCC Mid`,
+                NA
+            ),
+            "PCCC Mid Right" = if_else(
+                `PCCC Mid Value` > 0.5,
+                `PCCC Mid`,
+                NA
+            ),
             "PCCC Min" = if_else( # Combine into one row if close PCCC
@@
         geom_text(
-            aes(label = `PCCC Mid`),
+            aes(label = `PCCC Mid Left`),
             color = "#4d4d4d",
@@
             position = position_nudge(y = -0.025, x = -0.35)
+        ) +
+        geom_text(
+            aes(label = `PCCC Mid Right`),
+            color = "#4d4d4d",
+            size = 2,
+            hjust = 0,
+            position = position_nudge(y = 0.025, x = -0.35)
         ) +

### 2024-04-15 src/plots.Rmd
Add general age range perf plots

@@
         by_age_range = TRUE,
+        by_age_range2 = TRUE,
         ...
@@
 
-    # Calc metric by age range
+    # Calc metric by detailed age range
     if (by_age_range) {
@@
 
+    # Calc metric by general age range
+    if (by_age_range2) {
+
+        # Get unique age ranges
+        age_ranges <- df %>%
+            pull(age_range2) %>%
+            unique
+
+        # Calc metric by age range
+        for (a in c("adult", "child", "neo")) {
+            for (ar in age_ranges) {
+
+                # Filter for age range
+                df_filter <- df %>% filter(
+                    age_range2 == ar & is_agreed == TRUE & age == a
+                )
+                metric_name <- sprintf(
+                    "%s %s Age2 Agree %s", name, str_to_title(a), ar
+                )
+
+                # Calc metric for cod
+                if (nrow(df_filter) > 0) {
+                    out[[metric_name]] <- calc_per_model(
+                        actual = df_filter %>%
+                            pull(physician_cghr10),
+                        pred = df_filter %>%
+                            select(ends_with("_cghr10"), -physician_cghr10),
+                        func = func,
+                        ...
+                    ) %>% rename(
+                         {{ metric_name }} := Metric
+                    )
+                }
+            }
+        }
+    }
+
     # Combine all pccc metrics
@@
         age_range
+    ),
+    "age_range2" = str_to_title(str_replace(
+        age_range2,
+        "\\s*\\(.*\\)",
+        ""
+    )),
+    "age_range2" = if_else(
+        !str_detect(age_range2, "Year|Years|Day|Days|month|Months|week|Weeks"),
+        paste0(age_range2, " Years"),
+        age_range2
     )
@@
 
-#### Age Range Performance
+#### Detailed Age Range Performance
 
@@
 
+#### General Age Range Performance
+
+Display a plot for each age group of performance for physician agreed records by age ranges.
+
+```{r}
+for (a in c("adult", "neo")) {
+
+    # Create label and ref for age group
+    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
+    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
+    atitle <- if (a == "neo") {
+        paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
+    } else {
+        paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
+    }
+    aref <- str_to_title(a)
+
+    # Get unique age range columns
+    arange_col <- out %>% select(starts_with(sprintf(
+            "PCCC %s Age2 Agree ",
+            aref
+        ))) %>%
+        names
+
+    # Create age range with counts
+    arange_remap <- list()
+    arange_counts <- list()
+    for (ar_col in arange_col) {
+
+        # Get cod without prefix
+        ar <- gsub(sprintf("PCCC %s Age2 Agree ", aref), "", ar_col)
+
+        # Calc num and perc cases for age range
+        narange <- df %>% filter(age_range2 == ar & is_agreed == TRUE & age == a) %>% nrow
+        parange <- (narange / arows) * 100
+        parange_label <- if (round(parange) >= 1) round(parange) else "<1"
+
+        # Add label for age ranges
+        arange_remap[[ar]] <- paste0(
+            ar,
+            "\n(n=", narange, ", ", parange_label, "%)"
+        )
+
+        # Store age range count data
+        arange_counts[[ar]] <- narange
+    }
+
+    # Prepare boxplot data
+    ar2data <- out %>%
+        select(
+            Model,
+            starts_with(sprintf("PCCC %s Age2 Agree", aref))
+        ) %>%
+        rename_at(
+             vars(-Model),
+             ~gsub(sprintf("PCCC %s Age2 Agree ", aref), "", .)
+        ) %>%
+        filter(!str_detect(Model, "&")) %>% # remove multi models
+        pivot_longer( # transform to long format
+            cols = -Model,
+            names_to = "Age Range",
+            values_to = "PCCC"
+        ) %>%
+        mutate( # rename cod with counts
+            "Age Range" = recode(`Age Range`, !!!arange_remap)
+        ) %>%
+        group_by(`Age Range`) %>%
+        mutate( # Make values less than 0 equal to 0
+            PCCC = if_else(PCCC <= 0, 0, PCCC)
+        ) %>%
+        mutate( # Add min, mid, and max model names to label
+            "PCCC Min" = if_else(
+                PCCC <= min(PCCC) + 0.05,
+                paste0(
+                    Model,
+                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
+                ),
+                NA
+            ),
+            "PCCC Max" = if_else(
+                PCCC >= max(PCCC) - 0.05,
+                paste0(
+                    Model,
+                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
+                ),
+                NA
+            ),
+            "PCCC Mid" = if_else(
+                is.na(`PCCC Min`) & is.na(`PCCC Max`),
+                paste0(Model, "\n(", round(PCCC, 2), ")"),
+                NA
+            ),
+            "PCCC Min" = if_else( # Combine into one row if close PCCC
+                `PCCC` == min(PCCC),
+                if_else(
+                    sum(!is.na(`PCCC Min`)) > 1,
+                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
+                    paste0(
+                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
+                        collapse = "\n"
+                    )
+                ),
+                NA
+            ),
+            "PCCC Max" = if_else(
+                `PCCC` == max(PCCC),
+                if_else(
+                    sum(!is.na(`PCCC Max`)) > 1,
+                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
+                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
+                           collapse = "\n")
+                ),
+                NA
+            )
+        )
+
+    # Create cod order based on max pccc
+    ar2order <- ar2data %>%
+        group_by(`Age Range`) %>%
+        summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
+        select(`Age Range`, `PCCC Max Value`) %>%
+        arrange(desc(`PCCC Max Value`)) %>%
+        pull(`Age Range`)
+    ardata$`Age Range` <- factor(ardata$`Age Range`, levels = rev(ar2order))
+
+    # Plot boxplot
+    ar2plot <- ar2data %>%
+        ggplot(aes(x = `Age Range`, y = PCCC)) +
+        geom_boxplot(
+            linewidth = 0.5,
+            width = 0.25
+        ) +
+        geom_text(
+            aes(label = `PCCC Min`),
+            color = "#4d4d4d",
+            size = 2.5,
+            hjust = 1,
+            position = position_nudge(y = -0.08)
+        ) +
+        geom_text(
+            aes(label = `PCCC Max`),
+            color = "#4d4d4d",
+            size = 2.5,
+            hjust = 0,
+            position = position_nudge(y = 0.08)
+        ) +
+        stat_summary( # min pccc txt on boxplot
+            geom = "text",
+            fun = min,
+            aes(label = sprintf("%1.2f", after_stat(y))),
+            position = position_nudge(y = -0.04),
+            size = 3
+        ) +
+        stat_summary( # max pccc txt on boxplot
+            geom = "text",
+            fun = max,
+            aes(label = sprintf("%1.2f", after_stat(y))),
+            position = position_nudge(y = 0.04),
+            size = 3
+        ) +
+        labs(
+            x = atitle,
+            y = "PCCC (0=Low, 1=High)"
+        ) +
+        ylim(0.1, 1) +
+        coord_flip() +
+        theme_minimal() +
+        theme(
+            panel.grid = element_blank(),
+            axis.line = element_blank(),
+            axis.line.y = element_blank(),
+            axis.title.x = element_text(margin = margin(t = 10)),
+            axis.title.y = element_text(margin = margin(r = 10)),
+            axis.line.x = element_line(
+                color = "black",
+                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
+            )
+        )
+
+    # Save the plot
+    print(ar2plot)
+    ggsave(
+        sprintf("../manuscript/fig-perf-agerange2-%s.pdf", a),
+        plot = ar2plot,
+        dpi = 300,
+        width = if (a == "adult") 6 else if (a == "neo") 6 else NA,
+        height = if (a == "adult") 8 else if (a == "neo") 2.5 else NA
+    )
+}
+```
+
 #### COD Performance
@@
 Plot model performance for physician agreed records by cause of death category.
+
+Remove causes of death with less than 10 samples.
 

### 2024-04-15 src/preprocess.Rmd
Add general age range perf plots

--- 2024-03-18 src/preprocess.Rmd
@@
 
+# Physician age cols
+phy_cols_age <- c(
+    "rowid",
+    "age_value_cod",
+    "age_unit_cod"
+)
+
 # Read data
@@
         read_csv(
-            "../tmp/healsl_rd1_adult_v1.csv",
+            "../tmp/healsl_rd1_adult_v2.csv",
             col_select = all_of(phy_adult_cols)
@@
         read_csv(
-            "../tmp/healsl_rd2_adult_v1.csv",
+            "../tmp/healsl_rd2_adult_v2.csv",
             col_select = all_of(phy_adult_cols)
@@
         read_csv(
-            "../tmp/healsl_rd1_child_v1.csv",
+            "../tmp/healsl_rd1_child_v2.csv",
             col_select = all_of(phy_cols)
@@
         read_csv(
-            "../tmp/healsl_rd2_child_v1.csv",
+            "../tmp/healsl_rd2_child_v2.csv",
             col_select = all_of(phy_cols)
@@
         read_csv(
-            "../tmp/healsl_rd1_neo_v1.csv",
+            "../tmp/healsl_rd1_neo_v2.csv",
             col_select = all_of(phy_cols)
@@
         read_csv(
-            "../tmp/healsl_rd2_neo_v1.csv",
+            "../tmp/healsl_rd2_neo_v2.csv",
             col_select = all_of(phy_cols)
@@
             rename(all_of(phy_rename))
+    ) %>% left_join(
+        bind_rows(
+            read_csv(
+                "../tmp/healsl_rd1_adult_age_v2.csv",
+                col_select = all_of(phy_cols_age)
+            ),
+            read_csv(
+                "../tmp/healsl_rd1_child_age_v2.csv",
+                col_select = all_of(phy_cols_age)
+            ),
+            read_csv(
+                "../tmp/healsl_rd1_neo_age_v2.csv",
+                col_select = all_of(phy_cols_age)
+            ),
+            read_csv(
+                "../tmp/healsl_rd2_adult_age_v2.csv",
+                col_select = all_of(phy_cols_age)
+            ),
+            read_csv(
+                "../tmp/healsl_rd2_child_age_v2.csv",
+                col_select = all_of(phy_cols_age)
+            ),
+            read_csv(
+                "../tmp/healsl_rd2_neo_age_v2.csv",
+                col_select = all_of(phy_cols_age)
+            )
+        ) %>% rename(
+            age_value = age_value_cod,
+            age_unit = age_unit_cod
+        ),
+        by = "rowid"
     ),
@@
         age_range,
+        age_value,
+        age_unit,
         sex,
@@
 }
+
+head(out)
+```
+
+### Generalize Age Range
+
+Manually generalize age ranges for each age group:
+
+```{r}
+out <- out %>% mutate(
+    age_range2 = case_when(
+        age_unit == "Days" &
+        age_value >= 0 &
+        age_value <= 1 ~
+            "0-1 Days",
+        age_unit == "Days" &
+        age_value >= 2 &
+        age_value <= 6 ~
+            "2-6 Days",
+        age_unit == "Days" &
+        age_value >= 7 &
+        age_value <= 24 ~
+            "7-24 Days",
+        age_unit == "Years" &
+        age_value >= 12 &
+        age_value <= 24 ~
+            "12-24",
+        age_unit == "Years" &
+        age_value >= 25 &
+        age_value <= 39 ~
+            "25-39",
+        age_unit == "Years" &
+        age_value >= 40 &
+        age_value <= 54 ~
+            "40-54",
+        age_unit == "Years" &
+        age_value >= 55 &
+        age_value <= 69 ~
+            "55-69",
+        .default = NA
+    ),
+    .after = age_range
+) %>%
+    select(
+        -age_value,
+        -age_unit
+    )
 

### 2024-04-15 src/plots.Rmd
Fix dim for gen agerange perf plots

@@
     alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
-    atitle <- if (a == "neo") {
-        paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
-    } else {
-        paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
-    }
+    atitle <- paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
     aref <- str_to_title(a)
@@
         width = if (a == "adult") 6 else if (a == "neo") 6 else NA,
-        height = if (a == "adult") 8 else if (a == "neo") 2.5 else NA
+        height = if (a == "adult") 3 else if (a == "neo") 2.5 else NA
     )

### 2024-04-16 src/plots.Rmd
Remove cods <10 samples for cod perf plots

@@
 
+    # Get cods with less than 10 samples
+    cod_low_counts <- cod_counts[cod_counts < 10]
+    cod_low_perc <- sapply(cod_low_counts, function(x) {
+        xprop <- (x / arows) * 100
+        if (xprop < 1) {
+            return("<1")
+        } else {
+            return(as.character(round(xprop)))
+        }
+    })
+    cod_low_label <- paste0(
+        names(cod_low_counts),
+        " (n=", cod_low_counts, ", ", cod_low_perc, "%)",
+        collapse = ", "
+    )
+
     # Prepare boxplot data
@@
             )
+        ) %>%
+        filter( # remove CODs with <10 samples
+            !str_detect(COD, paste0("^", names(cod_low_counts), collapse = "|"))
         )
@@
             x = atitle,
-            y = "PCCC (0=Low, 1=High)"
+            y = "PCCC (0=Low, 1=High)",
+            caption = paste0("CODs removed (n<10): ", cod_low_label, ".")
         ) +
@@
                 arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
-            )
+            ),
+            plot.caption = element_text(size = 6, face = "italic")
         )

### 2024-04-16 src/plots.Rmd
Add cod count for cod perf plots

@@
     alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
-    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
     aref <- str_to_title(a)
+
+    # Create title for causes
+    atitle <- paste0(
+        "Physician Agreed ",
+        alabel,
+        " Records (n=", arows, ", 100%)"
+    )
 
@@
             y = "PCCC (0=Low, 1=High)",
-            caption = paste0("CODs removed (n<10): ", cod_low_label, ".")
+            caption = if (length(cod_low_counts) > 0) paste0(
+                length(causes_col) - length(cod_low_counts),
+                " CODs shown / ",
+                length(cod_low_counts),
+                " CODs not shown (n<10): ",
+                cod_low_label,
+                "."
+            ) else NULL
         ) +
@@
             ),
-            plot.caption = element_text(size = 6, face = "italic")
+            plot.caption = element_text(size = 7, face = "italic")
         )

### 2024-04-16 src/preprocess.Rmd
Add 70+ for age ranges

@@
             "55-69",
+        age_unit == "Years" &
+        age_value >= 70 ~
+            "70+",
         .default = NA

### 2025-02-23 src/plots.Rmd
Working on discussion
Rearrange src code

@@
 
-Calculate Partial Chance Corrected Concordance (PCCC) to evaluate indivudal performance for each model by age and physician coding stage.
+Calculate Partial Chance Corrected Concordance (PCCC) to evaluate individual performance for each model by age and physician coding stage.
 
@@
 ```
+
+#### COD Sensitivty and Specificity
+
+Create heat map of sensitivity and specificity for each cause of death by model.
+
+Remove causes of death with less than 10 samples.
+
+```{r}
+```

### 2025-02-25 src/plots.Rmd
Working on plots

@@
 ---
-title: "Metrics"
+title: "Plots"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 
-## Libraries
+# Libraries
 
@@
 library(tidyverse)
+library(dplyr)
+library(ggrepel)
 ```
@@
 
-## Settings
+# Functions
+
+Functions for PCCC and CSMF Accuracy.
 
 ```{r}
-models_format <- c(
-    "_cghr10" = "",
-    "_" = " & ",
-    "gpt3" = "GPT-3.5",
-    "gpt4" = "GPT-4",
-    "insilicova" = "InSilicoVA",
-    "interva5" = "InterVA-5"
-)
-stage_format <- c(
-    "is_" = "",
-    "recon" = "Reconciliation",
-    "agreed" = "Agreement",
-    "adj" = "Adjudication"
-)
-```
-
-## Functions
-
-Functions for PCCC and CSMF Accuracy.
-
-```{r}
 
 # Calc PCCC
-calc_pccc <- function(actual, pred, k = 1, N = NULL) {
+calc_pccc <- function(actual, pred, k = 1, N = NULL, assume_zero = T) {
 
@@
     out <- (C - (k/N)) / (1 - (k/N))
+
+    # Scale negative numbers to 0 for easier plotting
+    out <- if (assume_zero & out < 0) 0 else out
     return(out)
@@
 }
-
-# Bulk calc per model
-calc_per_model <- function(actual, pred, func, name = "Metric", ...) {
-
-    # Prep data in long format grouped by model
-    out <- pred %>%
-        pivot_longer( # to long format
-            everything(),
-            names_to = "Model",
-            values_to = "prediction"
-        ) %>% group_by(Model)
-
-    # Calc k if pccc as it is diff for model combos
-    if (identical(func, calc_pccc)) {
-        out <- out %>%
-            summarise(
-                !!name := func(
-                    actual,
-                    prediction,
-                    k = str_count(unique(Model), "_"),
-                    ...
-                )
-            )
-    } else { # otherwise apply func
-        out <- out %>%
-            summarise(
-                !!name := func(
-                    actual,
-                    prediction,
-                    ...
-                )
-            )
-    }
-
-    # Format display and return
-    out <- out %>%
-        mutate(Model = str_replace_all(Model, models_format)) %>%
-        arrange(across({{name}}, desc))
-    return(out)
-}
-
-# Bulk calc per model based on age, physician coding stage, and cause of death
-calc_by <- function(
-        df,
-        func,
-        name = "Metric",
-        by_age = TRUE,
-        by_stage = TRUE,
-        by_sex = TRUE,
-        by_cod = TRUE,
-        by_age_range = TRUE,
-        by_age_range2 = TRUE,
-        ...
-    ) {
-    out <- list()
-
-    # Calc overall metric
-    out[[name]] <- calc_per_model(
-        actual = df %>% pull(physician_cghr10),
-        pred = df %>% select(ends_with("_cghr10"), -physician_cghr10),
-        func = func,
-        ...
-    ) %>% rename(
-        {{ name }} := Metric
-    )
-
-    # Calc metric for va coding stage
-    if (by_stage) {
-        for (stage in c("is_agreed", "is_recon", "is_adj")) {
-
-            # Filter data for stage
-            df_filter <- df %>% filter(.[[stage]] == TRUE)
-            metric_name = paste0(
-                name,
-                " ",
-                str_replace_all(stage, stage_format)
-            )
-
-            # Calc metric for stage
-            out[[metric_name]] <- calc_per_model(
-                actual = df_filter %>%
-                    pull(physician_cghr10),
-                pred = df_filter %>%
-                    select(ends_with("_cghr10"), -physician_cghr10),
-                func = func,
-                ...
-            ) %>% rename(
-                 {{ metric_name }} := Metric
-            )
-        }
-    }
-
-    # Calc pcc for each age group
-    if (by_age) {
-        for (age_group in c("adult", "child", "neo")) {
-
-            # Filter data for age
-            df_filter <- df %>% filter(age == age_group)
-            metric_name = paste0(
-                name,
-                " ",
-                str_to_title(age_group)
-            )
-
-            # Calc metric for age
-            out[[metric_name]] <- calc_per_model(
-                actual = df_filter %>%
-                    pull(physician_cghr10),
-                pred = df_filter %>%
-                    select(ends_with("_cghr10"), -physician_cghr10),
-                func = func,
-                ...
-            ) %>% rename(
-                 {{ metric_name }} := Metric
-            )
-
-            # Calc metric for each stage within age group
-            for (stage in c("is_agreed", "is_recon", "is_adj")) {
-
-                # Filter data for stage within age group
-                df_filter <- df %>% filter(
-                    .[[stage]] == TRUE & age == age_group
-                )
-                metric_name <- paste0(
-                    name,
-                    " ",
-                    str_to_title(age_group),
-                    " ",
-                    str_replace_all(stage, stage_format)
-                )
-
-                # Calc metric for stage within age group
-                out[[metric_name]] <- calc_per_model(
-                    actual = df_filter %>%
-                        pull(physician_cghr10),
-                    pred = df_filter %>%
-                        select(ends_with("_cghr10"), -physician_cghr10),
-                    func = func,
-                    ...
-                ) %>% rename(
-                     {{ metric_name }} := Metric
-                )
-            }
-        }
-    }
-
-    # Calc metric by sex for each age group
-    if (by_sex) {
-
-        # Calc metric by cod
-        for (a in c("adult", "child", "neo")) {
-            for (sx in c("Male", "Female")) {
-
-                # Filter data for cod
-                df_filter <- df %>% filter(
-                    sex == sx & is_agreed == TRUE & age == a
-                )
-                metric_name <- sprintf(
-                    "%s %s Sex Agree %s", name, str_to_title(a), sx
-                )
-
-                # Calc metric for cod
-                if (nrow(df_filter) > 0) {
-                    out[[metric_name]] <- calc_per_model(
-                        actual = df_filter %>%
-                            pull(physician_cghr10),
-                        pred = df_filter %>%
-                            select(ends_with("_cghr10"), -physician_cghr10),
-                        func = func,
-                        ...
-                    ) %>% rename(
-                         {{ metric_name }} := Metric
-                    )
-                }
-            }
-        }
-    }
-
-    # Calc metric by cause of death for each age group
-    if (by_cod) {
-
-        # Get unique causes of death
-        causes <- df %>%
-            select(ends_with("_cghr10")) %>%
-            pivot_longer(
-                everything(),
-                names_to = "column",
-                values_to = "cod"
-            ) %>%
-            distinct(cod) %>%
-            filter(!is.na(cod)) %>%
-            pull(cod)
-
-        # Calc metric by cod
-        for (a in c("adult", "child", "neo")) {
-            for (cod in causes) {
-
-                # Filter data for cod
-                df_filter <- df %>% filter(
-                    physician_cghr10 == cod & is_agreed == TRUE & age == a
-                )
-                metric_name <- sprintf(
-                    "%s %s COD Agree %s", name, str_to_title(a), cod
-                )
-
-                # Calc metric for cod
-                if (nrow(df_filter) > 0) {
-                    out[[metric_name]] <- calc_per_model(
-                        actual = df_filter %>%
-                            pull(physician_cghr10),
-                        pred = df_filter %>%
-                            select(ends_with("_cghr10"), -physician_cghr10),
-                        func = func,
-                        ...
-                    ) %>% rename(
-                         {{ metric_name }} := Metric
-                    )
-                }
-            }
-        }
-    }
-
-    # Calc metric by detailed age range
-    if (by_age_range) {
-
-        # Get unique age ranges
-        age_ranges <- df %>%
-            pull(age_range) %>%
-            unique
-
-        # Calc metric by age range
-        for (a in c("adult", "child", "neo")) {
-            for (ar in age_ranges) {
-
-                # Filter for age range
-                df_filter <- df %>% filter(
-                    age_range == ar & is_agreed == TRUE & age == a
-                )
-                metric_name <- sprintf(
-                    "%s %s Age Agree %s", name, str_to_title(a), ar
-                )
-
-                # Calc metric for cod
-                if (nrow(df_filter) > 0) {
-                    out[[metric_name]] <- calc_per_model(
-                        actual = df_filter %>%
-                            pull(physician_cghr10),
-                        pred = df_filter %>%
-                            select(ends_with("_cghr10"), -physician_cghr10),
-                        func = func,
-                        ...
-                    ) %>% rename(
-                         {{ metric_name }} := Metric
-                    )
-                }
-            }
-        }
-    }
-
-    # Calc metric by general age range
-    if (by_age_range2) {
-
-        # Get unique age ranges
-        age_ranges <- df %>%
-            pull(age_range2) %>%
-            unique
-
-        # Calc metric by age range
-        for (a in c("adult", "child", "neo")) {
-            for (ar in age_ranges) {
-
-                # Filter for age range
-                df_filter <- df %>% filter(
-                    age_range2 == ar & is_agreed == TRUE & age == a
-                )
-                metric_name <- sprintf(
-                    "%s %s Age2 Agree %s", name, str_to_title(a), ar
-                )
-
-                # Calc metric for cod
-                if (nrow(df_filter) > 0) {
-                    out[[metric_name]] <- calc_per_model(
-                        actual = df_filter %>%
-                            pull(physician_cghr10),
-                        pred = df_filter %>%
-                            select(ends_with("_cghr10"), -physician_cghr10),
-                        func = func,
-                        ...
-                    ) %>% rename(
-                         {{ metric_name }} := Metric
-                    )
-                }
-            }
-        }
-    }
-
-    # Combine all pccc metrics
-    out <- reduce(out,
-        function(x, y) left_join(x, y, by = "Model")
-    ) %>%
-        arrange(across({{ name }}, desc))
-    return(out)
-}
-```
-
-## Data
-
-### Raw Data
+```
+
+# Data
+
+## Raw Data
 
@@
 ```{r}
-raw_df <- read_csv("../data/healsl_rd1to2_cod_v1.csv")
-```
-
-```{r, echo=FALSE}
-cat("Cases: ", nrow(raw_df), "\n")
-print(head(raw_df))
-```
-
-### Clean Labels
-
-Clean `age_range` labels to include only values and unit of measure in titlecase.
+
+# Read preds
+df_raw <- read_csv("../data/healsl_rd1to2_cod_v1.csv")
+
+# Display preds
+cat("Cases: ", nrow(df_raw), "\n")
+print(head(df_raw))
+
+```
+
+## Physician Cases
+
+Filter for cases that were coded by physicians.
 
 ```{r}
-df <- raw_df %>% mutate(
-    "age_range" = str_to_title(str_replace(
-        age_range,
-        "\\s*\\(.*\\)",
-        ""
-    )),
-    "age_range" = if_else(
-        !str_detect(age_range, "Year|Years|Day|Days|month|Months|week|Weeks"),
-        paste0(age_range, " Years"),
-        age_range
-    ),
-    "age_range2" = str_to_title(str_replace(
-        age_range2,
-        "\\s*\\(.*\\)",
-        ""
-    )),
-    "age_range2" = if_else(
-        !str_detect(age_range2, "Year|Years|Day|Days|month|Months|week|Weeks"),
-        paste0(age_range2, " Years"),
-        age_range2
-    )
-)
+
+# Filter for phy cases
+df <- df_raw %>%
+    filter(!is.na(physician_cghr10) & !is.null(physician_cghr10))
+
+# Preview phy cases
+cat("Non-coded Cases: ", nrow(df_raw) - nrow(df))
+cat("\nPhysician Coded Cases: ", nrow(df))
 df
-```
-
-### Physician Cases
-
-Filter for cases that were coded by physicians.
+
+```
+
+## Combined Models
+
+Create model combinations where if any of the models have the physician code, then set the combined model's output for the case to be the physician code.
 
 ```{r}
+
+# Calc combine preds
 df <- df %>%
-    filter(!is.na(physician_cghr10) & !is.null(physician_cghr10))
-```
-
-```{r, echo=FALSE}
-cat("Physician Coded Cases: ", nrow(df))
-print(head(df))
-```
-
-### Combined Models
-
-Create model combinations where if any of the models have the physician code, then set the combined model's output for the case to be the physician code.
-
-```{r}
-df <- df %>%
-    mutate( # Combine models
+    mutate(
         "gpt3_insilicova_cghr10" = if_else(
@@
     )
-```
-
-```{r, echo=FALSE}
+
+# Display combine preds
 print(head(df %>% select(
@@
 )))
-```
-
-### Prepared Data
+
+```
+
+## Inspect Data
 
@@
 # Physician info
-raw_physicians <- raw_df$physician_cghr10
+raw_physicians <- df_raw$physician_cghr10
 cat(paste0(
@@
 # Physician agreed cases
-raw_physicians_agree <- raw_df %>%
+raw_physicians_agree <- df_raw %>%
     filter(is_agreed == TRUE) %>%
@@
 # Models cases
-raw_models <- raw_df %>% select(ends_with("_cghr10"), -physician_cghr10)
+raw_models <- df_raw %>% select(ends_with("_cghr10"), -physician_cghr10)
 for (mcol in colnames(raw_models)) {
@@
 
-## Metrics
-
-Calculate metrics from model outputs compared to physician codes.
+# Preparation
+
+Prepare data for plotting.
+
+## Agreed Cases
+
+Filter for agreed cases only.
 
 ```{r}
-metrics <- list()
-```
-
-### PCCC
-
-Calculate Partial Chance Corrected Concordance (PCCC) to evaluate individual performance for each model by age and physician coding stage.
+
+# Agreed cases only
+df <- df %>% filter(is_agreed == TRUE)
+
+```
+
+## COD Case Count
+
+Count the number and percentage of cases for each CGHR-10 COD.
 
@@
 
-# Get num of unique causes
-ncauses <- df %>%
-    select(ends_with("_cghr10")) %>%
-    pivot_longer(
-        everything(),
-        names_to = "column",
-        values_to = "cod"
-    ) %>%
-    distinct(cod) %>%
-    filter(!is.na(cod)) %>%
-    pull(cod) %>%
-    length
-
-# Calc pccc for age, stage, and cod
-metrics$pccc <- calc_by(df, calc_pccc, "PCCC", N = ncauses)
-metrics$pccc
+# Count cases per cod
+df <- df %>%
+    left_join( # count cases and add as column
+        df %>%
+            group_by(age, physician_cghr10) %>%
+            count(name = "physician_cghr10_n") %>%
+            group_by(age) %>%
+            mutate(
+                physician_cghr10_perc = (physician_cghr10_n / sum(physician_cghr10_n)) * 100
+            ),
+        by = c("age", "physician_cghr10")
+    )
+df %>% select(rowid, age, physician_cghr10, physician_cghr10_n)
+```
+
+# Plots
+
+Generate plots from the predictions.
+
+```{r}
+
+# Number of causes for each age group
+ncod_adult <- 19
+ncod_child <- 10
+ncod_neo <- 7
+
+# Model full name
+gpt3_name <- "GPT-3.5"
+gpt4_name <- "GPT-4"
+isva_name <- "InSilicoVA"
+iva5_name <- "InterVA-5"
+
+# Pivot data into long format for calc
+df_long <- df %>%
+    filter( # remove low count cod
+        physician_cghr10_n >= 10
+    ) %>%
+    pivot_longer( # long format
+        ends_with("_cghr10") & !starts_with("physician_"),
+        names_to = "model",
+        values_to = "model_cghr10"
+    ) %>%
+    mutate(
+        model = str_replace( # remove cghr10
+            model,
+            "_cghr10",
+            ""
+        ),
+        model_name = str_replace_all(model, "_", " or ") %>% # use full model names
+            str_replace(., "gpt3", gpt3_name) %>%
+            str_replace(., "gpt4", gpt4_name) %>%
+            str_replace(., "insilicova", isva_name) %>%
+            str_replace(., "interva5", iva5_name),
+        age_name = case_when( # use full age name
+            age == "adult" ~ "Adult",
+            age == "child" ~ "Child",
+            age == "neo" ~ "Neonate",
+            .default = NA
+        ),
+        cod = physician_cghr10,
+        cod_name = paste0(
+            cod,
+            "\n(n=", physician_cghr10_n, ", ", round(physician_cghr10_perc), "%)"
+        ),
+        ncod = case_when( # num of cods for each age group
+            age == "adult" ~ ncod_adult,
+            age == "child" ~ ncod_child,
+            age == "neo" ~ ncod_neo,
+            .default = NA
+        )
+    ) %>%
+    filter( # remove combine models
+        !str_detect(model_name, " or ")
+    )
+
+# Calc num of records for each age
+n_all <- df %>% group_by(age) %>% count
+n_adult <- n_all %>% filter(age == "adult") %>% pull(n)
+
+# Preview
+df_long
+
+```
+
+## PCCC by COD
+
+Age, stage, cod.
+
+```{r}
+
+# Calc pccc
+df_plot <- df_long %>%
+    group_by(age_name, cod_name, model_name, .drop = F) %>%
+    summarize( # calc pccc
+        pccc = calc_pccc(cod, model_cghr10, N = unique(ncod)[1])
+    ) %>%
+    mutate( # add pccc to model name
+        model_label = paste0(model_name, " (", round(pccc, 2), ")")
+    ) %>%
+    filter(age_name == "Adult")
+
+# Add min and max values for each cause of death
+df_ends <- df_plot %>%
+    group_by(cod_name) %>%
+    summarize(
+        min_pccc = min(pccc),
+        max_pccc = max(pccc),
+        model_min = model_name[which.min(pccc)],
+        model_max = model_name[which.max(pccc)]
+    ) %>%
+    arrange(max_pccc)
+
+# Sort cod by max model pccc
+df_plot <- df_plot %>%
+    mutate(cod_name = factor(cod_name, levels = df_ends$cod_name))
+df_ends <- df_ends %>%
+    mutate(cod_name = factor(cod_name, levels = df_ends$cod_name))
+
+# Filter out the mid models
+df_mids <- df_plot %>%
+    left_join(df_ends, by = "cod_name") %>%
+    filter(model_name != model_max & model_name != model_min)
+
+# Plot
+ggplot(df_plot, aes(x = pccc, y = cod_name)) +
+    geom_point( # mid points
+        data = df_mids,
+        color = "gray60",
+        size = 1
+    ) +
+    geom_point (# min points
+        data = df_ends,
+        aes(x = min_pccc),
+        size = 1.5
+    ) +
+    geom_point (# max points
+        data = df_ends,
+        aes(x = max_pccc),
+        size = 1.5
+    ) +
+    geom_segment( # min max lines
+        data = df_ends,
+        aes(
+            x = min_pccc,
+            xend = max_pccc,
+            y = cod_name,
+            yend = cod_name
+        ),
+        linewidth = 0.75
+    ) +
+    geom_text( # min model text
+        data = df_ends,
+        aes(
+            x = min_pccc,
+            y = cod_name,
+            label = paste0(model_min, " (", round(min_pccc, 2), ")")
+        ),
+        hjust = 1.2,
+        vjust = 0.5,
+        size = 3
+    ) +
+    geom_text( # max model text
+        data = df_ends,
+        aes(
+            x = max_pccc,
+            y = cod_name,
+            label = paste0(model_max, " (", round(max_pccc, 2), ")")
+        ),
+        hjust = -0.2,
+        vjust = 0.5,
+        size = 3
+    ) +
+    geom_text_repel( # mid model text
+        data = df_mids,
+        aes(label = model_label),
+        color = "gray60",
+        max.overlaps = Inf,
+        size = 2
+    ) +
+    scale_x_continuous(expand = expansion(add = 0.2)) +
+    labs(
+        x = "Partial Chance Corrected Concordance (PCCC)",
+        y = paste0(length(unique(df_plot$cod_name)), " Causes of Death for ", n_adult, " Adult Records")
+    ) +
+    theme_minimal() +
+    theme(
+        panel.border = element_rect(
+            color = "black",
+            fill = NA,
+            linewidth = 0.5
+        ),
+        legend.position = "none",
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank()
+    )
+
 ```
@@
 ```{r}
-metrics$csmf_acc <- calc_by(
-    df,
-    calc_csmf_acc,
-    "CSMF Accuracy",
-    by_cod = FALSE
-)
-metrics$csmf_acc
+
+# Create csmf for each age group
+csmf_adult <- list()
+csmf_child <- list()
+csmf_neo <- list()
+
 ```

### 2025-02-25 src/plots.Rmd
Working func with patchwork

@@
 ```{r, echo=FALSE, eval=FALSE}
-install.packages("tidyverse")
+#install.packages("tidyverse")
+#install.packages("dplyr")
+#install.packages("ggrepel")
+#install.packages("patchwork")
 ```
@@
 library(ggrepel)
+library(patchwork)
 ```
@@
 # Functions
+
+## Metric Functions
 
@@
 }
+```
+
+## Plot Functions
+
+Functions for generating plots.
+
+```{r}
+
+# Plot performance of models
+plot_perf <- function(
+        df_long,
+        f = calc_pccc,
+        group = "cod_name",
+        title = NULL,
+        x_title = NULL,
+        y_title = NULL,
+        text_mid_size = 2,
+        text_end_size = 3,
+        text_hjust = 0.2,
+        x_limits = c(0, 1),
+        ...
+    ) {
+
+    # Calc metric
+    df_plot <- df_long %>%
+        group_by(.data[[group]], model_name, .drop = F) %>%
+        summarize( # calc pccc
+            metric = f(cod, model_cghr10, N = unique(ncod)[1], ...)
+        ) %>%
+        mutate( # add pccc to model name
+            model_label = paste0(model_name, " (", round(metric, 2), ")")
+        )
+
+    # Add min and max values for each cause of death
+    df_ends <- df_plot %>%
+        group_by(.data[[group]]) %>%
+        summarize(
+            min_metric = min(metric),
+            max_metric = max(metric),
+            model_min = model_name[which.min(metric)],
+            model_max = model_name[which.max(metric)]
+        ) %>%
+        arrange(max_metric)
+
+    # Sort cod by max model metric
+    df_plot[[group]] <- factor(df_plot[[group]], levels = df_ends[[group]])
+    df_ends[[group]] <- factor(df_ends[[group]], levels = df_ends[[group]])
+
+    # Filter out the mid models
+    df_mids <- df_plot %>%
+        left_join(df_ends, by = group) %>%
+        filter(model_name != model_max & model_name != model_min)
+
+    # Plot metric for each model
+    out <- ggplot(df_plot, aes(x = metric, y = .data[[group]])) +
+        geom_point( # mid points
+            data = df_mids,
+            color = "gray60",
+            size = 1
+        ) +
+        geom_point (# min points
+            data = df_ends,
+            aes(x = min_metric),
+            size = 1.5
+        ) +
+        geom_point (# max points
+            data = df_ends,
+            aes(x = max_metric),
+            size = 1.5
+        ) +
+        geom_segment( # min max lines
+            data = df_ends,
+            aes(
+                x = min_metric,
+                xend = max_metric,
+                y = .data[[group]],
+                yend = .data[[group]]
+            ),
+            linewidth = 0.75
+        ) +
+        geom_text( # min model text
+            data = df_ends,
+            aes(
+                x = min_metric,
+                y = .data[[group]],
+                label = paste0(model_min, " (", round(min_metric, 2), ")")
+            ),
+            hjust = 1 + text_hjust,
+            vjust = 0.5,
+            size = text_end_size
+        ) +
+        geom_text( # max model text
+            data = df_ends,
+            aes(
+                x = max_metric,
+                y = .data[[group]],
+                label = paste0(model_max, " (", round(max_metric, 2), ")")
+            ),
+            hjust = 0 - text_hjust,
+            vjust = 0.5,
+            size = text_end_size
+        ) +
+        geom_text_repel( # mid model text
+            data = df_mids,
+            aes(label = model_label),
+            color = "gray60",
+            max.overlaps = Inf,
+            size = text_mid_size
+        ) +
+        scale_x_continuous(
+            limits = x_limits,
+            expand = expansion(add = 0.2)
+        ) +
+        labs(
+            title = title,
+            x = x_title,
+            y = y_title
+        ) +
+        theme_minimal() +
+        theme(
+            panel.border = element_rect(
+                color = "black",
+                fill = NA,
+                linewidth = 0.5
+            ),
+            legend.position = "none",
+            panel.grid.major = element_blank(),
+            panel.grid.minor = element_blank()
+        )
+    return(out)
+}
+
 ```
@@
 
+## Shorten COD Names
+
+Shorten long names into new lines.
+
+```{r}
+
+# Shorten COD names
+df <- df %>%
+    mutate(physician_cghr10 = str_wrap(physician_cghr10, width = 34))
+
+```
+
 ## COD Case Count
@@
 n_adult <- n_all %>% filter(age == "adult") %>% pull(n)
+n_child <- n_all %>% filter(age == "child") %>% pull(n)
+n_neo <- n_all %>% filter(age == "neo") %>% pull(n)
+
+# Calc num of cods for each age
+cod_all <- df_long %>% group_by(age) %>% summarize(n = n_distinct(cod))
+cod_adult <- cod_all %>% filter(age == "adult") %>% pull(n)
+cod_child <- cod_all %>% filter(age == "child") %>% pull(n)
+cod_neo <- cod_all %>% filter(age == "neo") %>% pull(n)
 
@@
 
-# Calc pccc
-df_plot <- df_long %>%
-    group_by(age_name, cod_name, model_name, .drop = F) %>%
-    summarize( # calc pccc
-        pccc = calc_pccc(cod, model_cghr10, N = unique(ncod)[1])
-    ) %>%
-    mutate( # add pccc to model name
-        model_label = paste0(model_name, " (", round(pccc, 2), ")")
-    ) %>%
-    filter(age_name == "Adult")
-
-# Add min and max values for each cause of death
-df_ends <- df_plot %>%
-    group_by(cod_name) %>%
-    summarize(
-        min_pccc = min(pccc),
-        max_pccc = max(pccc),
-        model_min = model_name[which.min(pccc)],
-        model_max = model_name[which.max(pccc)]
-    ) %>%
-    arrange(max_pccc)
-
-# Sort cod by max model pccc
-df_plot <- df_plot %>%
-    mutate(cod_name = factor(cod_name, levels = df_ends$cod_name))
-df_ends <- df_ends %>%
-    mutate(cod_name = factor(cod_name, levels = df_ends$cod_name))
-
-# Filter out the mid models
-df_mids <- df_plot %>%
-    left_join(df_ends, by = "cod_name") %>%
-    filter(model_name != model_max & model_name != model_min)
-
-# Plot
-ggplot(df_plot, aes(x = pccc, y = cod_name)) +
-    geom_point( # mid points
-        data = df_mids,
-        color = "gray60",
-        size = 1
-    ) +
-    geom_point (# min points
-        data = df_ends,
-        aes(x = min_pccc),
-        size = 1.5
-    ) +
-    geom_point (# max points
-        data = df_ends,
-        aes(x = max_pccc),
-        size = 1.5
-    ) +
-    geom_segment( # min max lines
-        data = df_ends,
-        aes(
-            x = min_pccc,
-            xend = max_pccc,
-            y = cod_name,
-            yend = cod_name
-        ),
-        linewidth = 0.75
-    ) +
-    geom_text( # min model text
-        data = df_ends,
-        aes(
-            x = min_pccc,
-            y = cod_name,
-            label = paste0(model_min, " (", round(min_pccc, 2), ")")
-        ),
-        hjust = 1.2,
-        vjust = 0.5,
-        size = 3
-    ) +
-    geom_text( # max model text
-        data = df_ends,
-        aes(
-            x = max_pccc,
-            y = cod_name,
-            label = paste0(model_max, " (", round(max_pccc, 2), ")")
-        ),
-        hjust = -0.2,
-        vjust = 0.5,
-        size = 3
-    ) +
-    geom_text_repel( # mid model text
-        data = df_mids,
-        aes(label = model_label),
-        color = "gray60",
-        max.overlaps = Inf,
-        size = 2
-    ) +
-    scale_x_continuous(expand = expansion(add = 0.2)) +
-    labs(
-        x = "Partial Chance Corrected Concordance (PCCC)",
-        y = paste0(length(unique(df_plot$cod_name)), " Causes of Death for ", n_adult, " Adult Records")
-    ) +
-    theme_minimal() +
-    theme(
-        panel.border = element_rect(
-            color = "black",
-            fill = NA,
-            linewidth = 0.5
-        ),
-        legend.position = "none",
-        panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank()
-    )
+# Plot perf for pccc
+plot_perf(
+    df_long %>% filter(age == "adult"),
+    calc_pccc,
+    title = paste0(cod_adult, " Causes of Death for ", n_adult, " Adult Records")
+) /
+    plot_perf(
+        df_long %>% filter(age == "child"),
+        calc_pccc,
+        title = paste0(cod_child, " Causes of Death for ", n_child, " Child Records")
+    ) /
+    plot_perf(
+        df_long %>% filter(age == "neo"),
+        calc_pccc,
+        title = paste0(cod_neo, " Causes of Death for ", n_neo, " Neonatal Records")
+    ) +
+    plot_layout(heights = c(2, 1, 1))
 

### 2025-02-25 install.R

@@ -1,2 +1,5 @@
 install.packages("openVA")
 install.packages("tidyverse")
+install.packages("dplyr")
+install.packages("ggrepel")
+install.packages("patchwork")

### 2025-02-25 src/plots.Rmd
Collect titles

@@
     calc_pccc,
-    title = paste0(cod_adult, " Causes of Death for ", n_adult, " Adult Records")
+    title = paste0("(a) Adult Records (n=", n_adult, ")"),
+    x_title = "Partial Chance Corrected Concordance (PCCC)",
+    y_title = "Cause of Death"
 ) /
@@
         calc_pccc,
-        title = paste0(cod_child, " Causes of Death for ", n_child, " Child Records")
+        title = paste0("(b) Child Records (n=", n_child, ")"),
+        x_title = "Partial Chance Corrected Concordance (PCCC)",
+        y_title = "Cause of Death"
     ) /
@@
         calc_pccc,
-        title = paste0(cod_neo, " Causes of Death for ", n_neo, " Neonatal Records")
-    ) +
-    plot_layout(heights = c(2, 1, 1))
+        title = paste0("(c) Neonatal Records (n=", n_child, ")"),
+        x_title = "Partial Chance Corrected Concordance (PCCC)",
+        y_title = "Cause of Death"
+    ) +
+    plot_layout(
+        heights = c(2, 1, 1),
+        axis_titles = "collect"
+    )
 

### 2025-02-25 src/plots.Rmd
Add plot adjustments

--- 2025-02-25 src/plots.Rmd
@@
         text_mid_size = 2,
+        text_mid_vjust = 2.5,
         text_end_size = 3,
         text_hjust = 0.2,
+        add_min_points = F,
+        add_max_points = F,
+        mid_points_size = 1.5,
+        min_points_size = 2,
+        max_points_size,
         x_limits = c(0, 1),
@@
             data = df_mids,
-            color = "gray60",
-            size = 1
-        ) +
-        geom_point (# min points
-            data = df_ends,
-            aes(x = min_metric),
-            size = 1.5
-        ) +
-        geom_point (# max points
-            data = df_ends,
-            aes(x = max_metric),
-            size = 1.5
+            size = mid_points_size
         ) +
@@
             color = "gray60",
+            vjust = text_mid_vjust,
             max.overlaps = Inf,
@@
         )
+
+    # Add min and max points
+    if (add_min_points) {
+        out <- out + geom_point( # min points
+            data = df_ends,
+            aes(x = min_metric),
+            size = 2
+        )
+    }
+    if (add_max_points) {
+        out <- out + geom_point( # max points
+            data = df_ends,
+            aes(x = max_metric),
+            size = 2
+        )
+    }
     return(out)
@@
 
+## Age Case Count
+
+Count the number and percentage of cases for each age group.
+
+```{r}
+```
+
 ## COD Case Count
@@
 
+## PCCC By Age
+
+```{r}
+plot_perf(
+    df_long,
+    calc_pccc,
+    group = "age_name",
+    x_title = "Partial Chance Corrected Concordance (PCCC)",
+    y_title = "Cause of Death",
+    text_mid_size = 2.5,
+    text_mid_vjust = 3
+)
+```
+
 ## PCCC by COD
@@
     calc_pccc,
-    title = paste0(cod_adult, " Causes of Death for ", n_adult, " Adult Records")
+    group = "cod_name",
+    title = paste0("(a) Adult Records (n=", n_adult, ")"),
+    x_title = "Partial Chance Corrected Concordance (PCCC)",
+    y_title = "Cause of Death"
 ) /
@@
         calc_pccc,
-        title = paste0(cod_child, " Causes of Death for ", n_child, " Child Records")
+        group = "cod_name",
+        title = paste0("(b) Child Records (n=", n_child, ")"),
+        x_title = "Partial Chance Corrected Concordance (PCCC)",
+        y_title = "Cause of Death"
     ) /
@@
         calc_pccc,
-        title = paste0(cod_neo, " Causes of Death for ", n_neo, " Neonatal Records")
-    ) +
-    plot_layout(heights = c(2, 1, 1))
-
-```
-
-### CSMF Accuracy
+        group = "cod_name",
+        title = paste0("(c) Neonatal Records (n=", n_child, ")"),
+        x_title = "Partial Chance Corrected Concordance (PCCC)",
+        y_title = "Cause of Death"
+    ) +
+    plot_layout(
+        heights = c(2, 1, 1),
+        axis_titles = "collect"
+    )
+
+```
+
+## CSMF Accuracy
 

### 2025-02-25 src/plots.Rmd
Add pccc age plot

@@
 
-## Age Case Count
-
-Count the number and percentage of cases for each age group.
-
-```{r}
-```
-
 ## COD Case Count
@@
 df %>% select(rowid, age, physician_cghr10, physician_cghr10_n)
+
 ```
@@
 
+# Calc perc of records for each age
+perc_adult <- (n_adult / nrow(df)) * 100
+perc_child <- (n_child / nrow(df)) * 100
+perc_neo <- (n_neo / nrow(df)) * 100
+
 # Calc num of cods for each age
@@
 plot_perf(
-    df_long,
+    df_long %>%
+        mutate(
+            age_label = case_when(
+                age_name == "Adult"
+                    ~ paste0(age_name, "\n12+ Years\n(n=", n_adult, ", ", round(perc_adult), "%)"),
+                age_name == "Child"
+                    ~ paste0(age_name, "\n28 Days to 11 Years\n(n=", n_child, ", ", round(perc_child), "%)"),
+                age_name == "Neonate"
+                    ~ paste0(age_name, "\n<28 Days\n(n=", n_neo, ", ", round(perc_neo), "%)"),
+                .default = age_name
+            )
+        ),
     calc_pccc,
-    group = "age_name",
+    group = "age_label",
     x_title = "Partial Chance Corrected Concordance (PCCC)",
-    y_title = "Cause of Death",
+    y_title = paste0("Physician Agreed Records (n=", nrow(df), ")"),
     text_mid_size = 2.5,
@@
     group = "cod_name",
-    title = paste0("(a) Adult Records (n=", n_adult, ")"),
+    title = paste0("(a) Adult, 12+ Years (n=", n_adult, ")"),
     x_title = "Partial Chance Corrected Concordance (PCCC)",
@@
         group = "cod_name",
-        title = paste0("(b) Child Records (n=", n_child, ")"),
+        title = paste0("(b) Child, 28 Days to 11 Years (n=", n_child, ")"),
         x_title = "Partial Chance Corrected Concordance (PCCC)",
@@
         group = "cod_name",
-        title = paste0("(c) Neonatal Records (n=", n_child, ")"),
+        title = paste0("(c) Neonatal, <28 Days (n=", n_child, ")"),
         x_title = "Partial Chance Corrected Concordance (PCCC)",
-        y_title = "Cause of Death"
+        y_title = "Cause of Death",
+        text_mid_vjust = 3
     ) +

### 2025-02-27 src/plots.Rmd
Finish most plots

@@
 
+## Data Functions
+
+```{r}
+
+# Order textual age ranges
+order_arange <- function(ages) {
+    out <- ages %>%
+        data.frame %>%
+        rename("age_range" = ".") %>%
+        separate( # sep into range and unit
+            age_range,
+            into = c("age_range", "unit"),
+            sep = " "
+        ) %>%
+        separate( # sep into min and max age
+            age_range,
+            into = c("age_min", "age_max"),
+            sep = "-"
+        ) %>%
+        mutate( # format into correct data types
+            age_min = as.integer(age_min),
+            age_max = as.integer(age_max),
+            unit = str_to_lower(unit) %>%
+                factor(., levels = c(
+                    "hours",
+                    "days",
+                    "weeks",
+                    "months",
+                    "years"
+                ))
+        ) %>%
+        arrange(unit, age_min, age_max) %>% # sort ages
+        mutate( # create ordered ages
+            age_range = paste0(age_min, "-", age_max, " ", unit)
+        ) %>%
+        pull(age_range)
+    return(out)
+}
+
+```
+
 ## Metric Functions
@@
 }
+
 ```
@@
 
-# Plot performance of models
+# Plot performance of models using lines and points
 plot_perf <- function(
@@
         group = "cod_name",
+        text_scale = 1,
         title = NULL,
+        title_size = 10,
         x_title = NULL,
         y_title = NULL,
-        text_mid_size = 2,
+        text_mid_size = 2 * text_scale,
         text_mid_vjust = 2.5,
-        text_end_size = 3,
-        text_hjust = 0.2,
+        text_end_size = 3 * text_scale,
+        text_hjust = 0.1,
         add_min_points = F,
@@
         x_limits = c(0, 1),
+        x_breaks = seq(0, 1, by = 0.1),
+        x_expand = expansion(add = 0.2),
+        x_title_size = 9 * text_scale,
+        y_title_size = 9 * text_scale,
+        x_text_size = 8 * text_scale,
+        y_text_size = 9 * text_scale,
+        sort_group = T,
         ...
@@
 
+    #  Group data
+    df_plot <- df_long %>%
+        group_by(.data[[group]], model_name, .drop = F)
+
     # Calc metric
-    df_plot <- df_long %>%
-        group_by(.data[[group]], model_name, .drop = F) %>%
-        summarize( # calc pccc
+    if (identical(f, calc_pccc)) {
+        df_plot <- df_plot %>%
+            summarize(
                 metric = f(cod, model_cghr10, N = unique(ncod)[1], ...)
-        ) %>%
-        mutate( # add pccc to model name
+            )
+    } else {
+        df_plot <- df_plot %>%
+            summarize(
+                metric = f(cod, model_cghr10, ...)
+            )
+    }
+
+    # Add metric value to model name
+    df_plot <- df_plot %>%
+        mutate( 
             model_label = paste0(model_name, " (", round(metric, 2), ")")
@@
 
-    # Add min and max values for each cause of death
+    # Add min and max values for each group
     df_ends <- df_plot %>%
@@
 
-    # Sort cod by max model metric
+    # Sort group by max model metric
+    if (sort_group) {
         df_plot[[group]] <- factor(df_plot[[group]], levels = df_ends[[group]])
         df_ends[[group]] <- factor(df_ends[[group]], levels = df_ends[[group]])
+    }
 
@@
             limits = x_limits,
-            expand = expansion(add = 0.2)
+            breaks = x_breaks,
+            expand = x_expand
         ) +
@@
                 fill = NA,
-                linewidth = 0.5
+                linewidth = 0.75
             ),
@@
             panel.grid.major = element_blank(),
-            panel.grid.minor = element_blank()
+            panel.grid.minor = element_blank(),
+            plot.title = element_text(size = title_size),
+            axis.title.x = element_text(size = x_title_size),
+            axis.title.y = element_text(size = y_title_size),
+            axis.text.x = element_text(size = x_text_size),
+            axis.text.y = element_text(size = y_text_size)
         )
@@
     return(out)
+}
+
+# Plot perf of models using trend lines
+plot_perf_trend <- function(
+        df_long,
+        f = calc_pccc,
+        group = "age_range",
+        text_scale = 1,
+        title = NULL,
+        x_title = NULL,
+        y_title = NULL,
+        title_size = 10,
+        x_title_size = 9 * text_scale,
+        y_title_size = 9 * text_scale,
+        x_text_size = 8 * text_scale,
+        y_text_size = 9 * text_scale,
+        legend_text_size = 9 * text_scale,
+        legend_position = "bottom",
+        legend_direction = "horizontal",
+        legend_spacing = unit(0, "pt")
+    ) {
+
+    # Calc metric
+    df_plot <- df_long %>%
+        group_by(.data[[group]], model_name, .drop = F) %>%
+        summarize( # calc pccc
+            age = paste0(unique(age), collapse = ","),
+            metric = f(cod, model_cghr10, N = unique(ncod)[1])
+        ) %>%
+        mutate( # add pccc to model name
+            model_label = paste0(model_name, " (", round(metric, 2), ")")
+        )
+
+    # Get custom colors for models
+    default_colors <- scales::hue_pal()(length(unique(df_plot$model_name)))
+    names(default_colors) <- unique(df_plot$model_name)
+    default_colors["Mean"] <- "black"
+
+    # Plot trend lines for each model
+    out <- ggplot(
+        df_plot,
+        aes(
+            x = .data[[group]],
+            y = metric,
+            color = model_name,
+            group = model_name
+        )
+    ) +
+        geom_line(linewidth = 0.75, alpha = 0.4) + 
+        geom_line(
+            data = df_plot %>%
+                group_by(.data[[group]]) %>%
+                summarize(
+                    metric = mean(metric),
+                    model_name = "Mean"
+                ),
+            aes(color = model_name),
+            se = F,
+            linewidth = 1.25
+        ) +
+        scale_color_manual(values = default_colors) +
+        labs(
+            title = title,
+            x = x_title,
+            y = y_title
+        ) +
+        theme_minimal() +
+        theme(
+            panel.border = element_rect(
+                color = "black",
+                fill = NA,
+                linewidth = 0.75
+            ),
+            legend.title = element_blank(),
+            legend.text = element_text(size = legend_text_size),
+            legend.position = legend_position, 
+            legend.direction = legend_direction,
+            legend.box.spacing = legend_spacing,
+            plot.title = element_text(size = title_size),
+            axis.title.x = element_text(size = x_title_size),
+            axis.title.y = element_text(size = y_title_size),
+            axis.text.x = element_text(size = x_text_size),
+            axis.text.y = element_text(size = y_text_size)
+        )
+    return(out)
+
 }
@@
 df <- df %>%
-    mutate(physician_cghr10 = str_wrap(physician_cghr10, width = 34))
+    mutate(across(
+        c(
+            physician_cghr10,
+            gpt3_cghr10,
+            gpt4_cghr10,
+            insilicova_cghr10,
+            interva5_cghr10
+        ),
+        ~ str_wrap(.x, width = 18)
+    ))
+
+```
+
+## Standardize Age Ranges
+
+Standardize age ranges to follow age range and unit format in lowercase.
+
+```{r}
+
+# Standardize ages to age range + unit
+df <- df %>%
+    mutate(
+        age_range = str_to_lower(age_range),
+        age_range = str_replace( # neo ages
+            age_range,
+            " \\(early neonatal\\)| \\(late neonatal\\)",
+            ""
+        ),
+        age_range = case_when( # adult ages
+            age == "adult" ~ paste0(age_range, " years"),
+            .default = age_range
+        )
+    )
+df$age_range %>% unique
+
+```
+
+## Order Age Ranges
+
+Order age ranges in sequential order.
+
+```{r}
+
+# Get age ranges for adult
+ages_adult <- df %>%
+    filter(age == "adult") %>%
+    pull(age_range) %>%
+    unique %>%
+    order_arange
+
+# Get age ranges for child
+ages_child <- df %>%
+    filter(age == "child") %>%
+    pull(age_range) %>%
+    unique %>%
+    order_arange
+
+# Get age ranges for neo
+ages_neo <- df %>%
+    filter(age == "neo") %>%
+    pull(age_range) %>%
+    unique %>%
+    order_arange
+
+# Order age ranges as factor
+df <- df %>%
+    mutate(
+        age_range = factor(
+            age_range,
+            levels = c(ages_neo, ages_child, ages_adult)
+        )
+    )
+df$age_range %>% unique
 
@@
 
-# Plots
-
-Generate plots from the predictions.
+## Format Data
+
+Format data into long form with each record consisting of one model.
+
+Also calculates supplementary information for plots and tables.
 
@@
 ncod_neo <- 7
+ncod_all <- ncod_adult + ncod_child + ncod_neo
 
@@
             str_replace(., "insilicova", isva_name) %>%
-            str_replace(., "interva5", iva5_name),
+            str_replace(., "interva5", iva5_name) %>%
+            factor(., levels = c(
+                gpt4_name,
+                gpt3_name,
+                isva_name,
+                iva5_name
+            )),
         age_name = case_when( # use full age name
@@
 
+# Plots
+
+Generate plots from the predictions.
+
+## PCCC and CSMF
+
+```{r}
+
+# Prep data
+df_plot <- df_long %>%
+    group_by(model_name) %>%
+    summarize(
+        pccc = calc_pccc(cod, model_cghr10, N = ncod_all),
+        csmf = calc_csmf_acc(cod, model_cghr10)
+    ) %>%
+    arrange(pccc) %>%
+    mutate(
+        model_name = factor(model_name, levels = model_name)
+    ) %>%
+    pivot_longer(
+        c(pccc, csmf),
+        names_to = "metric",
+        values_to = "metric_value"
+    ) %>%
+    mutate(
+        metric = str_to_upper(metric) %>%
+            str_replace(., "CSMF", "CSMF Accuracy") %>%
+            factor(., levels = rev(c("PCCC", "CSMF Accuracy"))),
+        metric_label = paste0(metric, "=", round(metric_value, 2)) %>%
+            str_replace(., " Accuracy", "")
+    )
+
+# Plot data
+fig_pccc_csmf <- ggplot(
+    df_plot,
+    aes(
+        x = metric_value,
+        y = model_name,
+        fill = metric
+    )
+) +
+    geom_bar(
+        stat = "identity",
+        position = position_dodge(),
+        color = "black",
+        width = 0.7
+    ) +
+    geom_label(
+        data = df_plot %>% filter(metric == "PCCC"),
+        aes(
+            label = metric_label,
+            x = 0.085
+        ),
+        color = "black",
+        fill = "white",
+        size = 3,
+        label.r = unit(0, "pt"),
+        vjust = -0.5
+    ) +
+    geom_label(
+        data = df_plot %>% filter(metric == "CSMF Accuracy"),
+        aes(
+            label = metric_label,
+            x = 0.085
+        ),
+        color = "black",
+        fill = "white",
+        size = 3,
+        label.r = unit(0, "pt"),
+        vjust = 1.5
+    ) +
+    scale_fill_manual(
+        values = c("black", "gray"),
+        guide = guide_legend(reverse = TRUE)
+    ) +
+    scale_x_continuous(
+        limits = c(0, 1),
+        breaks = seq(0, 1, 0.1)
+    ) +
+    labs(
+        title = NULL,
+        x = NULL,
+        y = NULL
+    ) +
+    theme_minimal() +
+    theme(
+        panel.border = element_rect(
+            color = "black",
+            fill = NA,
+            linewidth = 0.75
+        ),
+        legend.position = c(.875, .5),
+        legend.title = element_blank(),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        plot.title = element_text(size = 10),
+        axis.title.x = element_text(size = 9),
+        axis.title.y = element_text(size = 9),
+        axis.text.x = element_text(size = 8),
+        axis.text.y = element_text(size = 8)
+    )
+
+# Save plot
+ggsave(
+    "../manuscript/fig-pccc-csmf.pdf",
+    fig_pccc_csmf,
+    width = 170,
+    height = 100,
+    units = "mm",
+    dpi = 300
+)
+
+# Display plot
+fig_pccc_csmf
+
+```
+
 ## PCCC By Age
@@
 ```{r}
-plot_perf(
+
+# Plot perf for pccc by age groups
+fig_pccc <- plot_perf(
     df_long %>%
@@
                 .default = age_name
-            )
+            ) %>%
+                factor(., levels = unique(.) %>% sort %>% rev)
         ),
@@
     group = "age_label",
-    x_title = "Partial Chance Corrected Concordance (PCCC)",
-    y_title = paste0("Physician Agreed Records (n=", nrow(df), ")"),
-    text_mid_size = 2.5,
-    text_mid_vjust = 3
-)
-```
-
-## PCCC by COD
-
-Age, stage, cod.
-
-```{r}
-
-# Plot perf for pccc
-plot_perf(
+    x_title = "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
+    text_mid_vjust = 3,
+    sort_group = F,
+    x_limits = c(0.2, 0.8),
+    x_expand = waiver()
+)
+
+# Save plot
+ggsave(
+    "../manuscript/fig-pccc.pdf",
+    fig_pccc,
+    width = 170,
+    height = 60,
+    units = "mm",
+    dpi = 300
+)
+
+# Display plot
+fig_pccc
+
+```
+
+## PCCC by Age and COD
+
+### Adult
+
+```{r}
+
+# Plot adult perf for pccc by cod
+fig_pccc_cod_adult <- plot_perf(
     df_long %>% filter(age == "adult"),
@@
     group = "cod_name",
-    title = paste0("(a) Adult, 12+ Years (n=", n_adult, ")"),
-    x_title = "Partial Chance Corrected Concordance (PCCC)",
-    y_title = "Cause of Death"
-) /
-    plot_perf(
+    title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
+    x_title =  "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
+    text_mid_vjust = -1,
+    text_scale = 0.8
+)
+
+# Save plot
+ggsave(
+    "../manuscript/fig-pccc-cod-adult.pdf",
+    fig_pccc_cod_adult,
+    width = 170,
+    height = 225,
+    units = "mm",
+    dpi = 300
+)
+
+# Display plot
+fig_pccc_cod_adult
+
+```
+
+### Child
+
+```{r}
+
+# Plot child perf for pccc by cod
+fig_pccc_cod_child <- plot_perf(
     df_long %>% filter(age == "child"),
@@
     group = "cod_name",
-        title = paste0("(b) Child, 28 Days to 11 Years (n=", n_child, ")"),
-        x_title = "Partial Chance Corrected Concordance (PCCC)",
-        y_title = "Cause of Death"
-    ) /
-    plot_perf(
+    title = paste0("Child, 28 Days to 11 Years (n=", n_child, ")"),
+    x_title =  "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
+    text_scale = 0.95
+)
+
+# Save plot
+ggsave(
+    "../manuscript/fig-pccc-cod-child.pdf",
+    fig_pccc_cod_child,
+    width = 170,
+    height = 150,
+    units = "mm",
+    dpi = 300
+)
+
+# Display plot
+fig_pccc_cod_child
+
+```
+
+### Neonate
+
+```{r}
+
+# Plot neo perf for pccc by cod
+fig_pccc_cod_neo <- plot_perf(
     df_long %>% filter(age == "neo"),
@@
     group = "cod_name",
-        title = paste0("(c) Neonatal, <28 Days (n=", n_child, ")"),
-        x_title = "Partial Chance Corrected Concordance (PCCC)",
-        y_title = "Cause of Death",
-        text_mid_vjust = 3
-    ) +
-    plot_layout(
-        heights = c(2, 1, 1),
-        axis_titles = "collect"
-    )
-
-```
-
-## CSMF Accuracy
-
-Calculate Cause Specific Mortality Fraction (CSMF) Accuracy to evaluate population performance for each model by age and physician coding stage.
-
-```{r}
-
-# Create csmf for each age group
-csmf_adult <- list()
-csmf_child <- list()
-csmf_neo <- list()
-
-```
-
-## Plots
-
-Save calculated metrics to `data` folder.
-
-```{r}
-out <- reduce(metrics,
-              function(x, y) left_join(x, y, by = "Model")
-)
-write_csv(out, "../data/healsl_rd1to2_metrics_v1.csv")
-```
-
-### Exploration
-
-```{r}
-
-# Num and perc of agreed cases
-nall <- nrow(df)
-nagree <- nrow(df %>% filter(is_agreed == TRUE))
-pagree <- (nagree / nall) * 100
-
-# Create labels to axis titles
-y_title <- paste0("Physician Agreed Records (n=", nagree, ", 100%)")
-```
-
-#### Cases by Sex and Age Group
-
-Display a plot of cases by age group separated by sex.
-
-```{r}
-
-# Calc age and sex counts
-nadult <- nrow(df %>% filter(age == "adult" & is_agreed == TRUE))
-nchild <- nrow(df %>% filter(age == "child" & is_agreed == TRUE))
-nneo <- nrow(df %>% filter(age == "neo" & is_agreed == TRUE))
-
-# Calc age and sex perc
-padult <- (nadult / nagree) * 100
-pchild <- (nchild / nagree) * 100
-pneo <- (nneo / nagree) * 100
-
-# Create age with counts
-age_remap <- c(
-    "Adult" = paste0("Adult, 12+ years\n(n=", nadult, ", ", round(padult), "%)"),
-    "Child" = paste0("Child, 28 days to 11 years\n(n=", nchild, ", ", round(pchild), "%)"),
-    "Neo" = paste0("Neonatal, <28 days\n(n=", nneo, ", ", round(pneo), "%)")
-)
-
-# Format the data for plotting
-asdata <- df %>%
-    filter(is_agreed == TRUE) %>%
-    group_by(age, sex) %>%
-    summarize(count = n()) %>%
+    title = paste0("Neonatal, <28 Days (n=", n_neo, ")"),
+    x_title =  "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
+    text_mid_vjust = 3,
+    text_end_size = 2.25,
+    text_scale = 0.95
+)
+
+# Save plot
+ggsave(
+    "../manuscript/fig-pccc-cod-neo.pdf",
+    fig_pccc_cod_neo,
+    width = 170,
+    height = 100,
+    units = "mm",
+    dpi = 300
+)
+
+# Display plot
+fig_pccc_cod_neo
+
+```
+
+## PCCC by Age Range
+
+```{r}
+
+# Format levels of age range with breaks
+age_levels <- levels(df_long$age_range) %>%
+    str_replace(., " ", "\n")
+
+# Plot perf trend over age ranges
+fig_pccc_age <- plot_perf_trend(
+    df_long %>%
         mutate(
-        age = str_to_title(age),
-        sex = paste0(
-            sex, " (n=", count, ", ",
-            round(count / case_when(
-                age == "Adult" ~ nadult,
-                age == "Child" ~ nchild,
-                age == "Neo" ~ nneo
-            ) * 100), "%)"
-        )
-    ) %>%
-    mutate( # re-order age
-        age = factor(age, levels = c(
-            "Adult",
-            "Child",
-            "Neo"
-        ))
-    ) %>%
-    mutate( # rename ages with counts
-        age = recode(age, !!!age_remap)
-    )
-
-# Plot the data
-asplot <- asdata %>%
-    ggplot(aes(x = factor(age), y = count, fill = sex)) +
-    geom_bar(
-        stat = "identity",
-        fill = "white",
-        color = "black"
-    ) +
-    geom_text(
-        aes(label = sex),
-        position = position_stack(vjust = 0.5),
-        size = 2.5,
-        color = "black"
-    ) +
-    labs(
-        y = y_title,
-        x = element_blank(),
-        fill = "Sex"
-    ) +
-    theme_minimal() +
-    theme(
-        panel.grid = element_blank(),
-        axis.title.x = element_text(margin = margin(t = 10)),
-        axis.title.y = element_text(margin = margin(r = 10))
-    )
-
-# Save the plot
-asplot
-ggsave("../manuscript/fig-data-agesex.pdf", plot = asplot, dpi = 300)
-```
-
-#### Cases by Age Range
-
-Display a plot for each age group of cases by age range.
-
-```{r}
-for (a in c("adult", "child", "neo")) {
-
-    # Create label for age group
-    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
-    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
-    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
-
-    # Format plot data
-    eardata <- df %>%
-        filter(is_agreed == TRUE & age == a) %>%
-        group_by(age_range) %>%
-        summarize(count = n()) %>%
-        separate(
-            age_range,
-            into = c("age_range_value", "age_range_unit"),
-            sep = " "
-        ) %>%
-        separate(
-            age_range_value,
-            into = c("age_range_min", "age_range_max"),
-            sep = "-"
-        ) %>%
-        mutate(
-            age_range_min = as.integer(age_range_min),
-            age_range_max = as.integer(age_range_max),
-            age_range_unit = factor(age_range_unit, levels = c(
-                "Weeks",
-                "Days",
-                "Months",
-                "Years"
-            )),
-            age_range_label = paste0(
-                age_range_min,
-                "-",
-                age_range_max,
-                " ",
-                age_range_unit,
-                "\n(n=", count, ", ", round((count / arows) * 100), "%)"
-            )
-        ) %>%
-        arrange(age_range_unit, age_range_min, age_range_max) %>%
-        mutate(
-            age_range_label = factor(age_range_label, levels = unique(age_range_label))
-        )
-
-    # Plot the data
-    earplot <- eardata %>%
-        ggplot(aes(x = age_range_label, y = count)) +
-        geom_bar(
-            stat = "identity",
-            fill = "#1d1d1d",
-            color = "white",
-            width = 0.5
-        ) +
-        labs(
-            y = atitle,
-            x = element_blank()
-        ) +
-        theme_minimal() +
-        theme(
-            panel.grid = element_blank(),
-            axis.title.x = element_text(margin = margin(t = 10)),
-            axis.title.y = element_text(margin = margin(r = 10))
-        ) +
-        coord_flip()
-
-    # Save the plot
-    print(earplot)
+            age_range = str_replace(age_range, " ", "\n") %>%
+                factor(., levels = age_levels)
+        ),
+    title = "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
+    text_scale = 0.9
+)
+
+# Save plot
 ggsave(
-        sprintf("../manuscript/fig-data-agerange-%s.pdf", a),
-        plot = earplot,
+    "../manuscript/fig-pccc-age.pdf",
+    fig_pccc_age,
+    width = 170,
+    height = 100,
+    units = "mm",
     dpi = 300
 )
-}
-```
-
-#### Cases by COD
-
-Display a plot for each age group of cases by cause of death.
-
-```{r}
-for (a in c("adult", "child", "neo")) {
-
-    # Create label for age group
-    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
-    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
-    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
-
-    # Format plot data
-    ecoddata <- df %>%
-        filter(is_agreed == TRUE & age == a) %>%
-        group_by(physician_cghr10) %>%
-        summarize(count = n()) %>%
-        mutate(
-            cod_label = paste0(
-                if_else(
-                    str_count(physician_cghr10, "\\s+") > 3,
-                    str_replace(physician_cghr10, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n"),
-                    physician_cghr10
-                ),
-                "\n(n=", count, ", ",
-                if_else(
-                    ((count / arows) * 100) < 1,
-                    "<1",
-                    as.character(round((count / arows) * 100))
-                ), "%)"
-            )
-        ) %>%
-        arrange(count) %>%
-        mutate(
-            cod_label = factor(cod_label, levels = unique(cod_label))
-        )
-
-    # Plot the data
-    ecodplot <- ecoddata %>%
-        ggplot(aes(x = cod_label, y = count)) +
-        geom_bar(
-            stat = "identity",
-            fill = "#1d1d1d",
-            color = "white",
-            width = 0.5
-        ) +
-        labs(
-            y = atitle,
-            x = element_blank()
-        ) +
-        theme_minimal() +
-        theme(
-            panel.grid = element_blank(),
-            axis.title.x = element_text(margin = margin(t = 10)),
-            axis.title.y = element_text(margin = margin(r = 10)),
-            axis.text.x = element_text(hjust = 1)
-        ) +
-        coord_flip()
-
-    # Save the plot
-    print(ecodplot)
-    ggsave(
-        sprintf("../manuscript/fig-data-cod-%s.pdf", a),
-        plot = ecodplot,
-        dpi = 300,
-        width = if (a == "adult") 6 else NA,
-        height = if (a == "adult") 8 else NA
-    )
-}
-```
-
-### Performance
-
-#### All vs Agree Performance
-
-Display a plot of model performance for all records versus records where physicians agreed on the COD code.
-
-```{r, fig.height = 2.5, fig.width = 6}
-
-# Calc stage counts
-nall <- nrow(df)
-nagree <- nrow(df %>% filter(is_agreed == TRUE))
-nrecon <- nrow(df %>% filter(is_recon == TRUE))
-nadj <- nrow(df %>% filter(is_adj == TRUE))
-
-# Calc stage perc
-pagree <- (nagree / nall) * 100
-precon <- (nrecon / nall) * 100
-padj <- (nadj / nall) * 100
-
-# Create stage with counts
-stage_remap <- c(
-    "All" = paste0("All\nRecords\n(n=", nall, ", 100%)"),
-    "Agreed" = paste0("Physician Agreed\nRecords\n(n=", nagree, ", ", round(pagree), "%)"),
-    "Reconciled" = paste0("Reconciled\n(n=", nrecon, ", ", round(precon), "%)"),
-    "Adjudicated" = paste0("Adjudicated\n(n=", nadj, ", ", round(padj), "%)")
-)
-
-# Prepare boxplot data
-alldata <- out %>%
-    select(
-        Model,
-        `PCCC`,
-        `PCCC Agreement`,
-        `CSMF Accuracy`,
-        `CSMF Accuracy Agreement`
-    ) %>%
-    rename(
-         All = `PCCC`,
-         Agreed = `PCCC Agreement`
-    ) %>%
-    filter(!str_detect(Model, "&")) %>% # remove multi models
-    pivot_longer( # transform to long format
-        cols = -c(
-            Model,
-            `CSMF Accuracy`,
-            `CSMF Accuracy Agreement`
-        ),
-        names_to = "Stage",
-        values_to = "PCCC"
-    ) %>%
-    group_by(Stage) %>%
-    mutate( # Add min, mid, and max model names to label
-        "PCCC Min" = if_else(
-            PCCC <= min(PCCC) + 0.05,
-            paste0(
-                Model, "\n(",
-                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
-                "CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
-            NA
-        ),
-        "PCCC Max" = if_else(
-            PCCC >= max(PCCC) - 0.05,
-            paste0(
-                Model, "\n(",
-                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
-                "CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
-            NA
-        ),
-        "PCCC Mid" = if_else(
-            is.na(`PCCC Min`) & is.na(`PCCC Max`),
-            paste0(Model, "\n(", round(PCCC, 2), ", CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
-            NA
-        ),
-        "PCCC Mid Value" = if_else(
-            is.na(`PCCC Min`) & is.na(`PCCC Max`),
-            PCCC,
-            NA
-        ),
-        "PCCC Min" = if_else( # Combine into one row if close PCCC
-            `PCCC` == min(PCCC),
-            if_else(
-                sum(!is.na(`PCCC Min`)) > 1,
-                paste0(na.omit(`PCCC Min`), collapse = "\n"),
-                paste0(
-                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
-                    collapse = "\n"
-                )
-            ),
-            NA
-        ),
-        "PCCC Max" = if_else(
-            `PCCC` == max(PCCC),
-            if_else(
-                sum(!is.na(`PCCC Max`)) > 1,
-                paste0(na.omit(`PCCC Max`), collapse = "\n"),
-                paste0(
-                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
-                    collapse = "\n"
-                )
-            ),
-            NA
-        )
-    ) %>%
-    mutate( # re-order stage
-        Stage = factor(Stage, levels = c(
-            "Agreed",
-            "All"
-        ))
-    ) %>%
-    mutate( # rename stages with counts
-        Stage = recode(Stage, !!!stage_remap)
-    )
-
-# Plot boxplot
-allplot <- alldata %>%
-    ggplot(aes(x = Stage, y = PCCC)) +
-    geom_boxplot(
-        linewidth = 0.5,
-        width = 0.25
-    ) +
-    geom_point(
-        aes(y = `PCCC Mid Value`),
-        shape = 1,
-        size = 1.5,
-        fill = "white",
-        color = "darkgray",
-        alpha = 0.8,
-        position = position_nudge(x = -0.3)
-    ) +
-    geom_text(
-        aes(label = `PCCC Min`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 1,
-        position = position_nudge(y = -0.055)
-    ) +
-    geom_text(
-        aes(label = `PCCC Max`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 0,
-        position = position_nudge(y = 0.055)
-    ) +
-    geom_text(
-        aes(label = `PCCC Mid`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 1,
-        position = position_nudge(y = -0.015, x = -0.3)
-    ) +
-    stat_summary( # min pccc txt on boxplot
-        geom = "text",
-        fun = min,
-        aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = -0.025),
-        size = 3
-    ) +
-    stat_summary( # max pccc txt on boxplot
-        geom = "text",
-        fun = max,
-        aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = 0.025),
-        size = 3
-    ) +
-    labs(
-        x = element_blank(),
-        y = "PCCC (0=Low, 1=High)"
-    ) +
-    ylim(0.2, 0.85) +
-    coord_flip() +
-    theme_minimal() +
-    theme(
-        panel.grid = element_blank(),
-        axis.line = element_line(color = "black"),
-        axis.title.x = element_text(margin = margin(t = 10)),
-        axis.title.y = element_text(margin = margin(r = 10)),
-        axis.line.x = element_line(
-            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
-        ),
-        axis.line.y = element_blank()
-    )
-
-# Save the plot
-allplot
-ggsave("../manuscript/fig-perf-allvsagree.pdf", plot = allplot, dpi = 300)
-```
-
-#### Age Group Perfomance
-
-Display a plot of performance for physician agreed records by age group.
-
-```{r, fig.height = 3.5, fig.width = 6}
-
-# Calc age counts
-nagree <- nrow(df %>% filter(is_agreed == TRUE))
-nadult <- nrow(df %>% filter(age == "adult" & is_agreed == TRUE))
-nchild <- nrow(df %>% filter(age == "child" & is_agreed == TRUE))
-nneo <- nrow(df %>% filter(age == "neo" & is_agreed == TRUE))
-
-# Calc age perc
-padult <- (nadult / nagree) * 100
-pchild <- (nchild / nagree) * 100
-pneo <- (nneo / nagree) * 100
-
-# Create age with counts
-age_remap <- c(
-    "Adult" = paste0("Adult\n12+ years\n(n=", nadult, ", ", round(padult), "%)"),
-    "Child" = paste0("Child\n28 days to 11 years\n(n=", nchild, ", ", round(pchild), "%)"),
-    "Neonatal" = paste0("Neonatal\n<28 days\n(n=", nneo, ", ", round(pneo), "%)")
-)
-
-# Prepare boxplot data
-agedata <- out %>%
-    select(
-        Model,
-        `PCCC Adult Agreement`,
-        `PCCC Child Agreement`,
-        `PCCC Neo Agreement`,
-        `CSMF Accuracy Adult Agreement`,
-        `CSMF Accuracy Child Agreement`,
-        `CSMF Accuracy Neo Agreement`
-    ) %>%
-    rename(
-         Adult = `PCCC Adult Agreement`,
-         Child = `PCCC Child Agreement`,
-         Neonatal = `PCCC Neo Agreement`
-    ) %>%
-    filter(!str_detect(Model, "&")) %>% # remove multi models
-    pivot_longer( # transform to long format
-        cols = -c(
-            Model,
-            `CSMF Accuracy Adult Agreement`,
-            `CSMF Accuracy Child Agreement`,
-            `CSMF Accuracy Neo Agreement`
-        ),
-        names_to = "Age Group",
-        values_to = "PCCC"
-    ) %>%
-    group_by(`Age Group`) %>%
-    mutate( # Add min, mid, and max model names to label
-        "PCCC Min" = if_else(
-            PCCC <= min(PCCC) + 0.05,
-            paste0(
-                Model, "\n(",
-                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
-                "CSMF=", round(case_when(
-                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
-                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
-                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
-                ),2), ")"),
-            NA
-        ),
-        "PCCC Max" = if_else(
-            PCCC >= max(PCCC) - 0.05,
-            paste0(
-                Model, "\n(",
-                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
-                "CSMF=", round(case_when(
-                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
-                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
-                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
-                ),2), ")"),
-            NA
-        ),
-        "PCCC Mid" = if_else(
-            is.na(`PCCC Min`) & is.na(`PCCC Max`),
-            paste0(
-                Model, "\n(", round(PCCC, 2),
-                ", CSMF=", round(case_when(
-                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
-                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
-                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
-                ),2), ")"),
-            NA
-        ),
-        "PCCC Mid Value" = if_else(
-            is.na(`PCCC Min`) & is.na(`PCCC Max`),
-            PCCC,
-            NA
-        ),
-        "PCCC Mid Left" = if_else(
-          `PCCC Mid Value` <= 0.5,
-          `PCCC Mid`,
-          NA
-        ),
-        "PCCC Mid Right" = if_else(
-          `PCCC Mid Value` > 0.5,
-          `PCCC Mid`,
-          NA
-        ),
-        "PCCC Min" = if_else( # Combine into one row if close PCCC
-            `PCCC` == min(PCCC),
-            if_else(
-                sum(!is.na(`PCCC Min`)) > 1,
-                paste0(na.omit(`PCCC Min`), collapse = "\n"),
-                paste0(
-                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
-                    collapse = "\n"
-                )
-            ),
-            NA
-        ),
-        "PCCC Max" = if_else(
-            `PCCC` == max(PCCC),
-            if_else(
-                sum(!is.na(`PCCC Max`)) > 1,
-                paste0(na.omit(`PCCC Max`), collapse = "\n"),
-                paste0(
-                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
-                    collapse = "\n"
-                )
-            ),
-            NA
-        )
-    ) %>%
-    mutate( # re-order age
-        "Age Group" = factor(`Age Group`, levels = c(
-            "Neonatal",
-            "Child",
-            "Adult"
-        ))
-    ) %>%
-    mutate( # rename ages with counts
-        "Age Group" = recode(`Age Group`, !!!age_remap)
-    )
-
-# Plot boxplot
-ageplot <- agedata %>%
-    ggplot(aes(x = `Age Group`, y = PCCC)) +
-    geom_boxplot(
-        linewidth = 0.5,
-        width = 0.25
-    ) +
-    geom_point(
-        aes(y = `PCCC Mid Value`),
-        shape = 1,
-        size = 1.5,
-        fill = "white",
-        color = "darkgray",
-        alpha = 0.8,
-        position = position_nudge(x = -0.3)
-    ) +
-    geom_text(
-        aes(label = `PCCC Min`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 1,
-        position = position_nudge(y = -0.055)
-    ) +
-    geom_text(
-        aes(label = `PCCC Max`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 0,
-        position = position_nudge(y = 0.055)
-    ) +
-    geom_text(
-        aes(label = `PCCC Mid Left`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 1,
-        position = position_nudge(y = -0.015, x = -0.3)
-    ) +
-    geom_text(
-        aes(label = `PCCC Mid Right`),
-        color = "#4d4d4d",
-        size = 2,
-        hjust = 0,
-        position = position_nudge(y = 0.015, x = -0.3)
-    ) +
-    stat_summary( # min pccc txt on boxplot
-        geom = "text",
-        fun = min,
-        aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = -0.025),
-        size = 3
-    ) +
-    stat_summary( # max pccc txt on boxplot
-        geom = "text",
-        fun = max,
-        aes(label = sprintf("%1.2f", after_stat(y))),
-        position = position_nudge(y = 0.025),
-        size = 3
-    ) +
-    labs(
-        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
-        y = "PCCC (0=Low, 1=High)"
-    ) +
-    ylim(0.25, 0.9) +
-    coord_flip() +
-    theme_minimal() +
-    theme(
-        panel.grid = element_blank(),
-        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
-        axis.line = element_line(color = "black"),
-        axis.title.x = element_text(margin = margin(t = 10)),
-        axis.title.y = element_text(margin = margin(r = 10)),
-        axis.line.x = element_line(
-            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
-        ),
-        axis.line.y = element_blank()
-    )
-
-# Save the plot
-ageplot
-ggsave("../manuscript/fig-perf-agegroup.pdf", plot = ageplot, dpi = 300)
-```
-
-#### Sex Performance
-
-Display a plot for each age group of performance for physician agreed records by sex.
-
-```{r, fig.width = 6, fig.height = 2.5}
-for (a in c("adult", "child", "neo")) {
-
-    # Create label and ref for age group
-    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
-    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
-    atitle <- paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
-    aref <- str_to_title(a)
-
-    # Get unique sex columns
-    sex_col <- out %>% select(starts_with(sprintf(
-            "PCCC %s Sex Agree ",
-            aref
-        ))) %>%
-        names
-
-    # Create sex with counts
-    sex_remap <- list()
-    sex_counts <- list()
-    for (sx_col in sex_col) {
-
-        # Get sex without prefix
-        sx <- gsub(sprintf("PCCC %s Sex Agree ", aref), "", sx_col)
-
-        # Calc num and perc cases for age range
-        nsex <- df %>% filter(sex == sx & is_agreed == TRUE & age == a) %>% nrow
-        psex <- (nsex / arows) * 100
-        psex_label <- if (round(psex) >= 1) round(psex) else "<1"
-
-        # Add label for age ranges
-        sex_remap[[sx]] <- paste0(
-            sprintf("%s %s", alabel, sx),
-            "\n(n=", nsex, ", ", psex_label, "%)"
-        )
-
-        # Store age range count data
-        sex_counts[[sx]] <- nsex
-    }
-
-    # Prepare boxplot data
-    sxdata <- out %>%
-        select(
-            Model,
-            starts_with(sprintf("PCCC %s Sex Agree", aref))
-        ) %>%
-        rename_at(
-             vars(-Model),
-             ~gsub(sprintf("PCCC %s Sex Agree ", aref), "", .)
-        ) %>%
-        filter(!str_detect(Model, "&")) %>% # remove multi models
-        pivot_longer( # transform to long format
-            cols = -Model,
-            names_to = "Sex",
-            values_to = "PCCC"
-        ) %>%
-        mutate( # rename cod with counts
-            "Sex" = recode(Sex, !!!sex_remap)
-        ) %>%
-        group_by(Sex) %>%
-        mutate( # Make values less than 0 equal to 0
-            PCCC = if_else(PCCC <= 0, 0, PCCC)
-        ) %>%
-        mutate( # Add min, mid, and max model names to label
-            "PCCC Min" = if_else(
-                PCCC <= min(PCCC) + 0.05,
-                paste0(
-                    Model,
-                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
-                ),
-                NA
-            ),
-            "PCCC Max" = if_else(
-                PCCC >= max(PCCC) - 0.05,
-                paste0(
-                    Model,
-                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
-                ),
-                NA
-            ),
-            "PCCC Mid" = if_else(
-                is.na(`PCCC Min`) & is.na(`PCCC Max`),
-                paste0(Model, "\n(", round(PCCC, 2), ")"),
-                NA
-            ),
-            "PCCC Mid Value" = if_else(
-                is.na(`PCCC Min`) & is.na(`PCCC Max`),
-                PCCC,
-                NA
-            ),
-            "PCCC Mid Left" = if_else(
-                `PCCC Mid Value` <= 0.5,
-                `PCCC Mid`,
-                NA
-            ),
-            "PCCC Mid Right" = if_else(
-                `PCCC Mid Value` > 0.5,
-                `PCCC Mid`,
-                NA
-            ),
-            "PCCC Min" = if_else( # Combine into one row if close PCCC
-                `PCCC` == min(PCCC),
-                if_else(
-                    sum(!is.na(`PCCC Min`)) > 1,
-                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
-                    paste0(
-                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
-                        collapse = "\n"
-                    )
-                ),
-                NA
-            ),
-            "PCCC Max" = if_else(
-                `PCCC` == max(PCCC),
-                if_else(
-                    sum(!is.na(`PCCC Max`)) > 1,
-                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
-                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
-                           collapse = "\n")
-                ),
-                NA
-            )
-        )
-
-    # Create cod order based on max pccc
-    sxorder <- sxdata %>%
-        group_by(Sex) %>%
-        summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
-        select(Sex, `PCCC Max Value`) %>%
-        arrange(desc(`PCCC Max Value`)) %>%
-        pull(Sex)
-    sxdata$Sex <- factor(sxdata$Sex, levels = rev(sxorder))
-
-    # Plot boxplot
-    sxplot <- sxdata %>%
-        ggplot(aes(x = Sex, y = PCCC)) +
-        geom_boxplot(
-            linewidth = 0.5,
-            width = 0.25
-        ) +
-        geom_point(
-            aes(y = `PCCC Mid Value`),
-            shape = 1,
-            size = 1.5,
-            fill = "white",
-            color = "darkgray",
-            alpha = 0.8,
-            position = position_nudge(x = -0.35)
-        ) +
-        geom_text(
-            aes(label = `PCCC Min`),
-            color = "#4d4d4d",
-            size = 2.5,
-            hjust = 1,
-            position = position_nudge(y = -0.09)
-        ) +
-        geom_text(
-            aes(label = `PCCC Mid Left`),
-            color = "#4d4d4d",
-            size = 2,
-            hjust = 1,
-            position = position_nudge(y = -0.025, x = -0.35)
-        ) +
-        geom_text(
-            aes(label = `PCCC Mid Right`),
-            color = "#4d4d4d",
-            size = 2,
-            hjust = 0,
-            position = position_nudge(y = 0.025, x = -0.35)
-        ) +
-        geom_text(
-            aes(label = `PCCC Max`),
-            color = "#4d4d4d",
-            size = 2.5,
-            hjust = 0,
-            position = position_nudge(y = 0.09)
-        ) +
-        stat_summary( # min pccc txt on boxplot
-            geom = "text",
-            fun = min,
-            aes(label = sprintf("%1.2f", after_stat(y))),
-            position = position_nudge(y = -0.04),
-            size = 3
-        ) +
-        stat_summary( # max pccc txt on boxplot
-            geom = "text",
-            fun = max,
-            aes(label = sprintf("%1.2f", after_stat(y))),
-            position = position_nudge(y = 0.04),
-            size = 3
-        ) +
-        labs(
-            x = atitle,
-            y = "PCCC (0=Low, 1=High)"
-        ) +
-        ylim(0.1, 1) +
-        coord_flip() +
-        theme_minimal() +
-        theme(
-            panel.grid = element_blank(),
-            axis.line = element_blank(),
-            axis.line.y = element_blank(),
-            axis.title.x = element_text(margin = margin(t = 10)),
-            axis.title.y = element_text(margin = margin(r = 10)),
-            axis.line.x = element_line(
-                color = "black",
-                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
-            )
-        )
-
-    # Save the plot
-    print(sxplot)
-    ggsave(
-        sprintf("../manuscript/fig-perf-sex-%s.pdf", a),
-        plot = sxplot,
-        dpi = 300
-    )
-}
-```
-
-#### Detailed Age Range Performance
-
-Display a plot for each age group of performance for physician agreed records by age ranges.
-
-```{r}
-for (a in c("adult", "child", "neo")) {
-
-    # Create label and ref for age group
-    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
-    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
-    atitle <- if (a == "neo") {
-        paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
-    } else {
-        paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
-    }
-    aref <- str_to_title(a)
-
-    # Get unique age range columns
-    arange_col <- out %>% select(starts_with(sprintf(
-            "PCCC %s Age Agree ",
-            aref
-        ))) %>%
-        names
-
-    # Create age range with counts
-    arange_remap <- list()
-    arange_counts <- list()
-    for (ar_col in arange_col) {
-
-        # Get cod without prefix
-        ar <- gsub(sprintf("PCCC %s Age Agree ", aref), "", ar_col)
-
-        # Calc num and perc cases for age range
-        narange <- df %>% filter(age_range == ar & is_agreed == TRUE & age == a) %>% nrow
-        parange <- (narange / arows) * 100
-        parange_label <- if (round(parange) >= 1) round(parange) else "<1"
-
-        # Add label for age ranges
-        arange_remap[[ar]] <- paste0(
-            ar,
-            "\n(n=", narange, ", ", parange_label, "%)"
-        )
-
-        # Store age range count data
-        arange_counts[[ar]] <- narange
-    }
-
-    # Prepare boxplot data
-    ardata <- out %>%
-        select(
-            Model,
-            starts_with(sprintf("PCCC %s Age Agree", aref))
-        ) %>%
-        rename_at(
-             vars(-Model),
-             ~gsub(sprintf("PCCC %s Age Agree ", aref), "", .)
-        ) %>%
-        filter(!str_detect(Model, "&")) %>% # remove multi models
-        pivot_longer( # transform to long format
-            cols = -Model,
-            names_to = "Age Range",
-            values_to = "PCCC"
-        ) %>%
-        mutate( # rename cod with counts
-            "Age Range" = recode(`Age Range`, !!!arange_remap)
-        ) %>%
-        group_by(`Age Range`) %>%
-        mutate( # Make values less than 0 equal to 0
-            PCCC = if_else(PCCC <= 0, 0, PCCC)
-        ) %>%
-        mutate( # Add min, mid, and max model names to label
-            "PCCC Min" = if_else(
-                PCCC <= min(PCCC) + 0.05,
-                paste0(
-                    Model,
-                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
-                ),
-                NA
-            ),
-            "PCCC Max" = if_else(
-                PCCC >= max(PCCC) - 0.05,
-                paste0(
-                    Model,
-                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
-                ),
-                NA
-            ),
-            "PCCC Mid" = if_else(
-                is.na(`PCCC Min`) & is.na(`PCCC Max`),
-                paste0(Model, "\n(", round(PCCC, 2), ")"),
-                NA
-            ),
-            "PCCC Min" = if_else( # Combine into one row if close PCCC
-                `PCCC` == min(PCCC),
-                if_else(
-                    sum(!is.na(`PCCC Min`)) > 1,
-                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
-                    paste0(
-                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
-                        collapse = "\n"
-                    )
-                ),
-                NA
-            ),
-            "PCCC Max" = if_else(
-                `PCCC` == max(PCCC),
-                if_else(
-                    sum(!is.na(`PCCC Max`)) > 1,
-                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
-                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
-                           collapse = "\n")
-                ),
-                NA
-            )
-        )
-
-    # Create cod order based on max pccc
-    arorder <- ardata %>%
-        group_by(`Age Range`) %>%
-        summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
-        select(`Age Range`, `PCCC Max Value`) %>%
-        arrange(desc(`PCCC Max Value`)) %>%
-        pull(`Age Range`)
-    ardata$`Age Range` <- factor(ardata$`Age Range`, levels = rev(arorder))
-
-    # Plot boxplot
-    arplot <- ardata %>%
-        ggplot(aes(x = `Age Range`, y = PCCC)) +
-        geom_boxplot(
-            linewidth = 0.5,
-            width = 0.25
-        ) +
-        geom_text(
-            aes(label = `PCCC Min`),
-            color = "#4d4d4d",
-            size = 2.5,
-            hjust = 1,
-            position = position_nudge(y = -0.08)
-        ) +
-        geom_text(
-            aes(label = `PCCC Max`),
-            color = "#4d4d4d",
-            size = 2.5,
-            hjust = 0,
-            position = position_nudge(y = 0.08)
-        ) +
-        stat_summary( # min pccc txt on boxplot
-            geom = "text",
-            fun = min,
-            aes(label = sprintf("%1.2f", after_stat(y))),
-            position = position_nudge(y = -0.04),
-            size = 3
-        ) +
-        stat_summary( # max pccc txt on boxplot
-            geom = "text",
-            fun = max,
-            aes(label = sprintf("%1.2f", after_stat(y))),
-            position = position_nudge(y = 0.04),
-            size = 3
-        ) +
-        labs(
-            x = atitle,
-            y = "PCCC (0=Low, 1=High)"
-        ) +
-        ylim(0.1, 1) +
-        coord_flip() +
-        theme_minimal() +
-        theme(
-            panel.grid = element_blank(),
-            axis.line = element_blank(),
-            axis.line.y = element_blank(),
-            axis.title.x = element_text(margin = margin(t = 10)),
-            axis.title.y = element_text(margin = margin(r = 10)),
-            axis.line.x = element_line(
-                color = "black",
-                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
-            )
-        )
-
-    # Save the plot
-    print(arplot)
-    ggsave(
-        sprintf("../manuscript/fig-perf-agerange-%s.pdf", a),
-        plot = arplot,
-        dpi = 300,
-        width = if (a == "adult") 6 else if (a == "neo") 6 else NA,
-        height = if (a == "adult") 8 else if (a == "neo") 2.5 else NA
-    )
-}
-```
-
-#### General Age Range Performance
-
-Display a plot for each age group of performance for physician agreed records by age ranges.
-
-```{r}
-for (a in c("adult", "neo")) {
-
-    # Create label and ref for age group
-    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
-    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
-    atitle <- paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
-    aref <- str_to_title(a)
-
-    # Get unique age range columns
-    arange_col <- out %>% select(starts_with(sprintf(
-            "PCCC %s Age2 Agree ",
-            aref
-        ))) %>%
-        names
-
-    # Create age range with counts
-    arange_remap <- list()
-    arange_counts <- list()
-    for (ar_col in arange_col) {
-
-        # Get cod without prefix
-        ar <- gsub(sprintf("PCCC %s Age2 Agree ", aref), "", ar_col)
-
-        # Calc num and perc cases for age range
-        narange <- df %>% filter(age_range2 == ar & is_agreed == TRUE & age == a) %>% nrow
-        parange <- (narange / arows) * 100
-        parange_label <- if (round(parange) >= 1) round(parange) else "<1"
-
-        # Add label for age ranges
-        arange_remap[[ar]] <- paste0(
-            ar,
-            "\n(n=", narange, ", ", parange_label, "%)"
-        )
-
-        # Store age range count data
-        arange_counts[[ar]] <- narange
-    }
-
-    # Prepare boxplot data
-    ar2data <- out %>%
-        select(
-            Model,
-            starts_with(sprintf("PCCC %s Age2 Agree", aref))
-        ) %>%
-        rename_at(
-             vars(-Model),
-             ~gsub(sprintf("PCCC %s Age2 Agree ", aref), "", .)
-        ) %>%
-        filter(!str_detect(Model, "&")) %>% # remove multi models
-        pivot_longer( # transform to long format
-            cols = -Model,
-            names_to = "Age Range",
-            values_to = "PCCC"
-        ) %>%
-        mutate( # rename cod with counts
-            "Age Range" = recode(`Age Range`, !!!arange_remap)
-        ) %>%
-        group_by(`Age Range`) %>%
-        mutate( # Make values less than 0 equal to 0
-            PCCC = if_else(PCCC <= 0, 0, PCCC)
-        ) %>%
-        mutate( # Add min, mid, and max model names to label
-            "PCCC Min" = if_else(
-                PCCC <= min(PCCC) + 0.05,
-                paste0(
-                    Model,
-                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
-                ),
-                NA
-            ),
-            "PCCC Max" = if_else(
-                PCCC >= max(PCCC) - 0.05,
-                paste0(
-                    Model,
-                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
-                ),
-                NA
-            ),
-            "PCCC Mid" = if_else(
-                is.na(`PCCC Min`) & is.na(`PCCC Max`),
-                paste0(Model, "\n(", round(PCCC, 2), ")"),
-                NA
-            ),
-            "PCCC Min" = if_else( # Combine into one row if close PCCC
-                `PCCC` == min(PCCC),
-                if_else(
-                    sum(!is.na(`PCCC Min`)) > 1,
-                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
-                    paste0(
-                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
-                        collapse = "\n"
-                    )
-                ),
-                NA
-            ),
-            "PCCC Max" = if_else(
-                `PCCC` == max(PCCC),
-                if_else(
-                    sum(!is.na(`PCCC Max`)) > 1,
-                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
-                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
-                           collapse = "\n")
-                ),
-                NA
-            )
-        )
-
-    # Create cod order based on max pccc
-    ar2order <- ar2data %>%
-        group_by(`Age Range`) %>%
-        summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
-        select(`Age Range`, `PCCC Max Value`) %>%
-        arrange(desc(`PCCC Max Value`)) %>%
-        pull(`Age Range`)
-    ardata$`Age Range` <- factor(ardata$`Age Range`, levels = rev(ar2order))
-
-    # Plot boxplot
-    ar2plot <- ar2data %>%
-        ggplot(aes(x = `Age Range`, y = PCCC)) +
-        geom_boxplot(
-            linewidth = 0.5,
-            width = 0.25
-        ) +
-        geom_text(
-            aes(label = `PCCC Min`),
-            color = "#4d4d4d",
-            size = 2.5,
-            hjust = 1,
-            position = position_nudge(y = -0.08)
-        ) +
-        geom_text(
-            aes(label = `PCCC Max`),
-            color = "#4d4d4d",
-            size = 2.5,
-            hjust = 0,
-            position = position_nudge(y = 0.08)
-        ) +
-        stat_summary( # min pccc txt on boxplot
-            geom = "text",
-            fun = min,
-            aes(label = sprintf("%1.2f", after_stat(y))),
-            position = position_nudge(y = -0.04),
-            size = 3
-        ) +
-        stat_summary( # max pccc txt on boxplot
-            geom = "text",
-            fun = max,
-            aes(label = sprintf("%1.2f", after_stat(y))),
-            position = position_nudge(y = 0.04),
-            size = 3
-        ) +
-        labs(
-            x = atitle,
-            y = "PCCC (0=Low, 1=High)"
-        ) +
-        ylim(0.1, 1) +
-        coord_flip() +
-        theme_minimal() +
-        theme(
-            panel.grid = element_blank(),
-            axis.line = element_blank(),
-            axis.line.y = element_blank(),
-            axis.title.x = element_text(margin = margin(t = 10)),
-            axis.title.y = element_text(margin = margin(r = 10)),
-            axis.line.x = element_line(
-                color = "black",
-                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
-            )
-        )
-
-    # Save the plot
-    print(ar2plot)
-    ggsave(
-        sprintf("../manuscript/fig-perf-agerange2-%s.pdf", a),
-        plot = ar2plot,
-        dpi = 300,
-        width = if (a == "adult") 6 else if (a == "neo") 6 else NA,
-        height = if (a == "adult") 3 else if (a == "neo") 2.5 else NA
-    )
-}
-```
-
-#### COD Performance
-
-Plot model performance for physician agreed records by cause of death category.
-
-Remove causes of death with less than 10 samples.
-
-```{r}
-for (a in c("adult", "child", "neo")) {
-
-    # Create label for age group
-    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
-    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
-    aref <- str_to_title(a)
-
-    # Create title for causes
-    atitle <- paste0(
-        "Physician Agreed ",
-        alabel,
-        " Records (n=", arows, ", 100%)"
-    )
-
-    # Get unique cause columns
-    causes_col <- out %>% select(starts_with(sprintf(
-        "PCCC %s COD Agree ", aref
-    ))) %>% names
-
-    # Create cod with counts
-    cod_remap <- list()
-    cod_counts <- list()
-    for (cod_col in causes_col) {
-
-        # Get cod without prefix
-        cod <- gsub(sprintf("PCCC %s COD Agree ", aref), "", cod_col)
-
-        # Calculate num and perc cases for cod
-        ncod <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE & age == a) %>% nrow
-        pcod <- (ncod / arows) * 100
-        pcod_label <- if (round(pcod) >= 1) round(pcod) else "<1"
-
-        # Break cod into newlines if more than 3 words
-        if (str_count(cod, "\\s+") > 3) {
-            cod_label <- str_replace(cod, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
-        } else {
-            cod_label <- cod
-        }
-
-        # Add label for cod
-        cod_remap[[cod]] <- paste0(cod_label, "\n(n=", ncod, ", ", pcod_label, "%)")
-
-        # Store cod count data
-        cod_counts[[cod]] <- ncod
-    }
-
-    # Get cods with less than 10 samples
-    cod_low_counts <- cod_counts[cod_counts < 10]
-    cod_low_perc <- sapply(cod_low_counts, function(x) {
-        xprop <- (x / arows) * 100
-        if (xprop < 1) {
-            return("<1")
-        } else {
-            return(as.character(round(xprop)))
-        }
-    })
-    cod_low_label <- paste0(
-        names(cod_low_counts),
-        " (n=", cod_low_counts, ", ", cod_low_perc, "%)",
-        collapse = ", "
-    )
-
-    # Prepare boxplot data
-    coddata <- out %>%
-        select(
-            Model,
-            starts_with(sprintf("PCCC %s COD Agree ", aref))
-        ) %>%
-        rename_at(
-             vars(-Model),
-             ~gsub(sprintf("PCCC %s COD Agree ", aref), "", .)
-        ) %>%
-        filter(!str_detect(Model, "&")) %>% # remove multi models
-        pivot_longer( # transform to long format
-            cols = -Model,
-            names_to = "COD",
-            values_to = "PCCC"
-        ) %>%
-        mutate( # rename cod with counts
-            "COD" = recode(`COD`, !!!cod_remap)
-        ) %>%
-        group_by(`COD`) %>%
-        mutate( # Make values less than 0 equal to 0
-            PCCC = if_else(PCCC <= 0, 0, PCCC)
-        ) %>%
-        mutate( # Add min, mid, and max model names to label
-            "PCCC Min" = if_else(
-                PCCC <= min(PCCC) + 0.05,
-                paste0(
-                    Model,
-                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
-                ),
-                NA
-            ),
-            "PCCC Max" = if_else(
-                PCCC >= max(PCCC) - 0.05,
-                paste0(
-                    Model,
-                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
-                ),
-                NA
-            ),
-            "PCCC Mid" = if_else(
-                is.na(`PCCC Min`) & is.na(`PCCC Max`),
-                paste0(Model, "\n(", round(PCCC, 2), ")"),
-                NA
-            ),
-            "PCCC Min" = if_else( # Combine into one row if close PCCC
-                `PCCC` == min(PCCC),
-                if_else(
-                    sum(!is.na(`PCCC Min`)) > 1,
-                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
-                    paste0(
-                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
-                        collapse = "\n"
-                    )
-                ),
-                NA
-            ),
-            "PCCC Max" = if_else(
-                `PCCC` == max(PCCC),
-                if_else(
-                    sum(!is.na(`PCCC Max`)) > 1,
-                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
-                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
-                           collapse = "\n")
-                ),
-                NA
-            )
-        ) %>%
-        filter( # remove CODs with <10 samples
-            !str_detect(COD, paste0("^", names(cod_low_counts), collapse = "|"))
-        )
-
-    # Create cod order based on max pccc
-    codorder <- coddata %>%
-        group_by(COD) %>%
-        summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
-        select(COD, `PCCC Max Value`) %>%
-        arrange(desc(`PCCC Max Value`)) %>%
-        pull(COD)
-    coddata$COD <- factor(coddata$COD, levels = rev(codorder))
-
-    # Plot boxplot
-    codplot <- coddata %>%
-        ggplot(aes(x = COD, y = PCCC)) +
-        geom_boxplot(
-            linewidth = 0.5,
-            width = 0.25
-        ) +
-        geom_text(
-            aes(label = `PCCC Min`),
-            color = "#4d4d4d",
-            size = 2.5,
-            hjust = 1,
-            position = position_nudge(y = -0.12)
-        ) +
-        geom_text(
-            aes(label = `PCCC Max`),
-            color = "#4d4d4d",
-            size = 2.5,
-            hjust = 0,
-            position = position_nudge(y = 0.12)
-        ) +
-        stat_summary( # min pccc txt on boxplot
-            geom = "text",
-            fun = min,
-            aes(label = sprintf("%1.2f", after_stat(y))),
-            position = position_nudge(y = -0.06),
-            size = 3
-        ) +
-        stat_summary( # max pccc txt on boxplot
-            geom = "text",
-            fun = max,
-            aes(label = sprintf("%1.2f", after_stat(y))),
-            position = position_nudge(y = 0.06),
-            size = 3
-        ) +
-        labs(
-            x = atitle,
-            y = "PCCC (0=Low, 1=High)",
-            caption = if (length(cod_low_counts) > 0) paste0(
-                length(causes_col) - length(cod_low_counts),
-                " CODs shown / ",
-                length(cod_low_counts),
-                " CODs not shown (n<10): ",
-                cod_low_label,
-                "."
-            ) else NULL
-        ) +
-        ylim(-0.3, 1.3) +
-        coord_flip() +
-        theme_minimal() +
-        theme(
-            panel.grid = element_blank(),
-            axis.line = element_blank(),
-            axis.line.y = element_blank(),
-            axis.title.x = element_text(margin = margin(t = 10)),
-            axis.title.y = element_text(margin = margin(r = 10)),
-            axis.line.x = element_line(
-                color = "black",
-                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
-            ),
-            plot.caption = element_text(size = 7, face = "italic")
-        )
-
-    # Save the plot
-    print(codplot)
-    ggsave(
-        sprintf("../manuscript/fig-perf-cod-%s.pdf", a),
-        plot = codplot,
-        dpi = 300,
-        width = if (a == "adult") 8 else NA,
-        height = if (a == "adult") 9 else NA
-    )
-}
-```
-
-#### COD Sensitivty and Specificity
-
-Create heat map of sensitivity and specificity for each cause of death by model.
-
-Remove causes of death with less than 10 samples.
-
-```{r}
-```
+
+# Display plot
+fig_pccc_age
+
+```

### 2025-02-27 src/plots.Rmd
Use PCCC abbrv for plots:

@@
     cat(paste0(
-        str_replace_all(mcol, models_format), " Predicted Cases (", 
+        mcol, " Predicted Cases (", 
         length(unique(na.omit(m))), " CODs): ",
@@
     cat(paste0(
-        str_replace_all(mcol, models_format), " Agreed Predicted Cases (", 
+        mcol, " Agreed Predicted Cases (", 
         length(unique(na.omit(m))), " CODs): ",
@@
     group = "age_label",
-    x_title = "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
+    x_title = "PCCC",
     text_mid_vjust = 3,
@@
     title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
-    x_title =  "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
+    x_title =  "PCCC",
     text_mid_vjust = -1,
@@
     title = paste0("Child, 28 Days to 11 Years (n=", n_child, ")"),
-    x_title =  "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
+    x_title = "PCCC",
     text_scale = 0.95
@@
     title = paste0("Neonatal, <28 Days (n=", n_neo, ")"),
-    x_title =  "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
+    x_title = "PCCC",
     text_mid_vjust = 3,
@@
         ),
-    title = "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
+    title = "PCCC",
     text_scale = 0.9

### 2025-05-08 src/plots.Rmd
Replaced main text figures, working on editing text

@@
     names(default_colors) <- unique(df_plot$model_name)
-    default_colors["Mean"] <- "black"
+    default_colors["Mean Across Models"] <- "black"
 
@@
                     metric = mean(metric),
-                    model_name = "Mean"
+                    model_name = "Mean Across Models"
                 ),

### 2025-05-23 src/plots.Rmd
Added data profile by cod

@@
 ```{r, echo=FALSE, eval=FALSE}
+#install.packages("openVA")
 #install.packages("tidyverse")
@@
 #install.packages("patchwork")
+#install.packages("glue")
 ```
@@
 library(patchwork)
+library(glue)
 ```
@@
 ```
+
+# Tables
+
+```{r}
+
+# Get n records by age group
+tab_agegroup <- df %>%
+    group_by(age) %>%
+    summarize(
+        n = n(),
+        n_cod_uniq = n_distinct(physician_cghr10)
+    )
+
+# Get n records by age group and sex
+tab_agegroup_sex <- df %>%
+    group_by(age, sex) %>%
+    summarize(n_sex = n()) %>%
+    pivot_wider(
+        names_from = sex,
+        values_from = n_sex,
+        names_glue = "n_{str_to_lower(sex)}"
+    )
+
+```
+
+## Records by COD
+
+```{r}
+
+# Get n records by cod
+tab_cod_n <- df %>%
+    group_by(age, physician_cghr10) %>%
+    summarize(n_cod = n())
+
+# Get n records by cod and sex
+tab_cod_sex <- df %>%
+    group_by(age, physician_cghr10, sex) %>%
+    summarize(n_cod_sex = n()) %>%
+    pivot_wider(
+        names_from = sex,
+        values_from = n_cod_sex,
+        names_glue = "n_cod_{str_to_lower(sex)}"
+    )
+
+# Combine all
+tab_cod <- tab_cod_n %>%
+    left_join(tab_agegroup, by = "age") %>%
+    left_join(tab_agegroup_sex, by = "age") %>%
+    left_join(tab_cod_sex, by = c("age", "physician_cghr10"))
+
+# Calc perc
+tab_cod <- tab_cod %>%
+    mutate(
+        n_perc = round(n / nrow(df) * 100, 1),
+        n_male_perc = round(n_male / n * 100, 1),
+        n_female_perc = round(n_female / n * 100, 1),
+        n_cod_perc = round(n_cod / n * 100, 1),
+        n_cod_male_perc = round(n_cod_male / n_cod * 100, 1),
+        n_cod_female_perc = round(n_cod_female / n_cod * 100, 1)
+    ) %>%
+    ungroup
+
+# Add labels to combined
+tab_cod <- tab_cod %>%
+    mutate(
+        age = if_else(age == "neo", "Neonate", str_to_title(age)),
+        `Age Group` = glue(
+            "{age} (n={n}, {n_perc}%, {n_cod_uniq} CODs)\n{age} Female (n={n_female}, {n_female_perc}%)\n{age} Male (n={n_male}, {n_male_perc}%)"
+        ),
+        `Cause of Death (COD)` = glue(
+            "{str_to_title(physician_cghr10)}"
+        ),
+        `Female` = glue("{n_cod_female} ({n_cod_female_perc}%)"),
+        `Male` = glue("{n_cod_male} ({n_cod_male_perc}%)"),
+        `Total` = glue("{n_cod} ({n_cod_perc}%)")
+    ) %>%
+    mutate(across(
+        c(`Female`, `Male`, `Total`),
+        ~ if_else(.x == "NA (NA%)", NA, .x)
+    ))
+
+# Save table
+write_csv(tab_cod, "../data/healsl_rd1to2_cod_profile_v1.csv", na = "")
+
+# Display table
+tab_cod
+```
+
+```{r}
+
+# Prepare and format the data
+tab_cod_format <- tab_cod %>%
+    ungroup %>%
+    select(`Age Group`, `Cause of Death (COD)`, Female, Male, Total) %>%
+    mutate(
+        `Age Group` = str_replace_all(`Age Group`, "\\\\n|\\n", "<br>"),
+        `Cause of Death (COD)` = str_replace_all(`Cause of Death (COD)`, "\\\\n|\\n", "<br>")
+    ) %>%
+    group_by(`Age Group`) %>%
+    mutate(`Age Group` = ifelse(row_number() == 1, `Age Group`, "")) %>%
+    ungroup()
+
+# Build the table
+tab_cod_html <- tab_cod_format %>%
+    kable(format = "html", escape = FALSE, align = "l") %>%
+    kable_styling(full_width = FALSE, position = "left", html_font = "Arial") %>%
+    row_spec(0, extra_css = "border-top: 2px solid; border-bottom: 1px solid;") %>%     # thick top border
+    row_spec(nrow(df_selected), extra_css = "border-bottom: 2px solid;")
+tab_cod_html
+```
+
+## Records by Age
+
+```{r}
+
+# Get n records by age
+tab_age_n <- df %>%
+    group_by(age, physician_cghr10) %>%
+    summarize(n_cod = n())
+
+```

### 2025-05-23 install.R

@@ -3,3 +3,4 @@ install.packages("tidyverse")
 install.packages("dplyr")
 install.packages("ggrepel")
 install.packages("patchwork")
+install.packages("glue")

### 2025-05-23 src/plots.Rmd
Added data profile by age range

@@
     row_spec(0, extra_css = "border-top: 2px solid; border-bottom: 1px solid;") %>%     # thick top border
-    row_spec(nrow(df_selected), extra_css = "border-bottom: 2px solid;")
+    row_spec(nrow(tab_cod_format), extra_css = "border-bottom: 2px solid;")
 tab_cod_html
+
 ```
@@
 tab_age_n <- df %>%
-    group_by(age, physician_cghr10) %>%
-    summarize(n_cod = n())
-
-```
+    group_by(age, age_range) %>%
+    summarize(n_age = n())
+
+# Get n records by age and sex
+tab_age_sex <- df %>%
+    group_by(age, age_range, sex) %>%
+    summarize(n_age_sex = n()) %>%
+    pivot_wider(
+        names_from = sex,
+        values_from = n_age_sex,
+        names_glue = "n_age_{str_to_lower(sex)}"
+    )
+
+# Combine all
+tab_age <- tab_age_n %>%
+    left_join(tab_agegroup, by = "age") %>%
+    left_join(tab_agegroup_sex, by = "age") %>%
+    left_join(tab_age_sex, by = c("age", "age_range"))
+
+# Calc perc
+tab_age <- tab_age %>%
+    mutate(
+        n_perc = round(n / nrow(df) * 100, 1),
+        n_male_perc = round(n_male / n * 100, 1),
+        n_female_perc = round(n_female / n * 100, 1),
+        n_age_perc = round(n_age / n * 100, 1),
+        n_age_male_perc = round(n_age_male / n_age * 100, 1),
+        n_age_female_perc = round(n_age_female / n_age * 100, 1)
+    ) %>%
+    ungroup
+
+# Add labels to combined
+tab_age <- tab_age %>%
+    mutate(
+        age = if_else(age == "neo", "Neonate", str_to_title(age)),
+        `Age Group` = glue(
+            "{age} (n={n}, {n_perc}%, {n_cod_uniq} CODs)\n{age} Female (n={n_female}, {n_female_perc}%)\n{age} Male (n={n_male}, {n_male_perc}%)"
+        ),
+        `Age Range` = glue(
+            "{str_to_title(age_range)}"
+        ),
+        `Female` = glue("{n_age_female} ({n_age_female_perc}%)"),
+        `Male` = glue("{n_age_male} ({n_age_male_perc}%)"),
+        `Total` = glue("{n_age} ({n_age_perc}%)")
+    ) %>%
+    mutate(across(
+        c(`Female`, `Male`, `Total`),
+        ~ if_else(.x == "NA (NA%)", NA, .x)
+    ))
+
+# Save table
+write_csv(tab_age, "../data/healsl_rd1to2_age_profile_v1.csv", na = "")
+
+# Display table
+tab_age
+
+```
+
+```{r}
+
+# Prepare and format the data
+tab_age_format <- tab_age %>%
+    ungroup %>%
+    select(`Age Group`, `Age Range`, Female, Male, Total) %>%
+    mutate(
+        `Age Group` = str_replace_all(`Age Group`, "\\\\n|\\n", "<br>"),
+        `Age Range` = str_replace_all(`Age Range`, "\\\\n|\\n", "<br>")
+    ) %>%
+    group_by(`Age Group`) %>%
+    mutate(`Age Group` = ifelse(row_number() == 1, `Age Group`, "")) %>%
+    ungroup()
+
+# Build the table
+tab_age_html <- tab_age_format %>%
+    kable(format = "html", escape = FALSE, align = "l") %>%
+    kable_styling(full_width = FALSE, position = "left", html_font = "Arial") %>%
+    row_spec(0, extra_css = "border-top: 2px solid; border-bottom: 1px solid;") %>%     # thick top border
+    row_spec(nrow(tab_age_format), extra_css = "border-bottom: 2px solid;")
+tab_age_html
+
+```

### 2025-05-26 src/plots.Rmd
Add color and fix fig 1 brief methods v2

@@
 #install.packages("glue")
+#install.packages("kableExtra)
 ```
@@
 library(glue)
+library(kableExtra)
 ```
@@
         group = "cod_name",
+        color = "model_name",
         text_scale = 1,
@@
         add_max_points = F,
-        mid_points_size = 1.5,
+        mid_points_size = 2.5,
         min_points_size = 2,
@@
         sort_group = T,
+        legend_position = "bottom",
+        legend_title = element_blank(),
+        legend_margin = margin(c(-8, -2, -2, -2)),
         ...
@@
     out <- ggplot(df_plot, aes(x = metric, y = .data[[group]])) +
-        geom_point( # mid points
-            data = df_mids,
-            size = mid_points_size
-        ) +
         geom_segment( # min max lines
@@
         ) +
+        geom_point( # mid points
+            aes(color = .data[[color]]),
+            size = mid_points_size
+        ) +
         geom_text( # min model text
@@
             ),
-            legend.position = "none",
+            legend.position = legend_position,
+            legend.title = legend_title,
+            legend.margin = legend_margin,
             panel.grid.major = element_blank(),
@@
     ) +
-    scale_fill_manual(
-        values = c("black", "gray"),
-        guide = guide_legend(reverse = TRUE)
-    ) +
     scale_x_continuous(
@@
     x_limits = c(0.2, 0.8),
+    legend_margin = margin(-8, -2, -2, -2),
     x_expand = waiver()

### 2025-05-26 install.R

@@ -4,3 +4,4 @@ install.packages("dplyr")
 install.packages("ggrepel")
 install.packages("patchwork")
 install.packages("glue")
+install.packages("kableExtra")

### 2025-06-13 src/plots.Rmd
Adjust plots to prabhat's feedback

@@
         text_mid_vjust = 2.5,
-        text_end_size = 3 * text_scale,
+        text_start_size = 3 * text_scale,
+        text_end_size = 4 * text_scale,
         text_hjust = 0.1,
@@
         ) +
-        geom_point( # mid points
-            aes(color = .data[[color]]),
+        geom_point( # points
+            shape = 21,
+            color = "black",
+            aes(fill = .data[[color]]),
             size = mid_points_size
@@
             vjust = 0.5,
-            size = text_end_size
+            size = text_start_size
         ) +
@@
         theme(
-            panel.border = element_rect(
-                color = "black",
-                fill = NA,
-                linewidth = 0.75
-            ),
             legend.position = legend_position,
@@
         theme(
-            panel.border = element_rect(
-                color = "black",
-                fill = NA,
-                linewidth = 0.75
-            ),
             legend.title = element_blank(),
@@
 
+## Rename COD Names
+
+Rename COD names into simpler names.
+
+```{r}
+
+# Rename COD names
+df <- df %>%
+    mutate(across(
+        c(
+            physician_cghr10,
+            gpt3_cghr10,
+            gpt4_cghr10,
+            insilicova_cghr10,
+            interva5_cghr10
+        ),
+        ~ case_when(
+            .x == "Maternal conditions" ~ "Maternal",
+            .x == "Acute respiratory infections" ~ "Pneumonia",
+            .x == "Neonatal infections" ~ "Infections",
+            .default = .x
+        ) %>%
+            str_replace_all(" diseases| disease", "")
+    ))
+
+```
+
 ## Shorten COD Names
@@
     unique %>%
+    str_replace(., "10-14 years", "12-14 years") %>%
     order_arange
@@
         age_range = factor(
-            age_range,
+            age_range %>%
+                str_replace(., "10-14 years", "12-14 years"),
             levels = c(ages_neo, ages_child, ages_adult)
@@
     ) +
-    geom_label(
-        data = df_plot %>% filter(metric == "PCCC"),
+    geom_text(
+        data = df_plot,
         aes(
-            label = metric_label,
-            x = 0.085
-        ),
+            label = round(metric_value, 2)
+        ),
+        position = position_dodge(width = 0.7),
         color = "black",
@@
         label.r = unit(0, "pt"),
-        vjust = -0.5
-    ) +
-    geom_label(
-        data = df_plot %>% filter(metric == "CSMF Accuracy"),
-        aes(
-            label = metric_label,
-            x = 0.085
-        ),
-        color = "black",
-        fill = "white",
-        size = 3,
-        label.r = unit(0, "pt"),
-        vjust = 1.5
+        vjust = 0.5,
+        hjust = -0.25
     ) +
@@
     theme(
-        panel.border = element_rect(
-            color = "black",
-            fill = NA,
-            linewidth = 0.75
-        ),
+        # panel.border = element_rect(
+        #     color = "black",
+        #     fill = NA,
+        #     linewidth = 0.75
+        # ),
         legend.position = c(.875, .5),
@@
                 age_name == "Adult"
-                    ~ paste0(age_name, "\n12+ Years\n(n=", n_adult, ", ", round(perc_adult), "%)"),
+                    ~ paste0(age_name, "\n12+ Years\n(n=", n_adult, ")"),
                 age_name == "Child"
-                    ~ paste0(age_name, "\n28 Days to 11 Years\n(n=", n_child, ", ", round(perc_child), "%)"),
+                    ~ paste0(age_name, "\n28 Days to 11 Years\n(n=", n_child, ")"),
                 age_name == "Neonate"
-                    ~ paste0(age_name, "\n<28 Days\n(n=", n_neo, ", ", round(perc_neo), "%)"),
+                    ~ paste0(age_name, "\n<28 Days\n(n=", n_neo, ")"),
                 .default = age_name
@@
     group = "age_label",
-    x_title = "PCCC",
+    x_title = "Partial Chance Corrected Concordance (PCCC)",
     text_mid_vjust = 3,
@@
     title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
-    x_title =  "PCCC",
+    x_title =  "Partial Chance Corrected Concordance (PCCC)",
     text_mid_vjust = -1,
@@
     title = paste0("Child, 28 Days to 11 Years (n=", n_child, ")"),
-    x_title = "PCCC",
+    x_title = "Partial Chance Corrected Concordance (PCCC)",
     text_scale = 0.95
@@
     title = paste0("Neonatal, <28 Days (n=", n_neo, ")"),
-    x_title = "PCCC",
+    x_title = "Partial Chance Corrected Concordance (PCCC)",
     text_mid_vjust = 3,
@@
         ),
-    title = "PCCC",
+    title = "Partial Chance Corrected Concordance (PCCC)",
     text_scale = 0.9

### 2025-06-13 src/plots.Rmd
Working on prabhat's feedback 2

@@
             legend.box.spacing = legend_spacing,
+            panel.grid.major = element_blank(),
+            panel.grid.minor = element_blank(),
             plot.title = element_text(size = title_size),

### 2025-06-18 src/plots.Rmd
Cleaner plots

--- 2025-06-13 src/plots.Rmd
@@
         y_title = NULL,
-        text_mid_size = 2 * text_scale,
+        text_mid_size = 2.25 * text_scale,
         text_mid_vjust = 2.5,
@@
         text_end_size = 4 * text_scale,
-        text_hjust = 0.1,
+        text_hjust = 0.2,
         add_min_points = F,
@@
         min_points_size = 2,
-        max_points_size,
+        max_points_size = 3,
         x_limits = c(0, 1),
@@
         x_expand = expansion(add = 0.2),
+        x_color_labels = c(
+            "G3" = "GPT-3.5 (G3)",
+            "G4" = "GPT-4 (G4)",
+            "ISV" = "InSilicoVA (ISV)",
+            "I5" = "InterVA-5 (I5)"
+        ),
         x_title_size = 9 * text_scale,
@@
         mutate( 
-            model_label = paste0(model_name, " (", round(metric, 2), ")")
+            model_label = paste0(model_name, ": ", round(metric, 2))
         )
@@
                 y = .data[[group]],
-                label = paste0(model_min, " (", round(min_metric, 2), ")")
+                label = paste0(model_min, ": ", round(min_metric, 2))
             ),
@@
                 y = .data[[group]],
-                label = paste0(model_max, " (", round(max_metric, 2), ")")
+                label = paste0(model_max, ": ", round(max_metric, 2))
             ),
@@
             size = text_mid_size
+        ) +
+        scale_fill_discrete(
+            labels = x_color_labels
         ) +
@@
         legend_direction = "horizontal",
-        legend_spacing = unit(0, "pt")
+        legend_spacing = unit(0, "pt"),
+        x_color_labels = c(
+            "G3" = "GPT-3.5",
+            "G4" = "GPT-4",
+            "ISV" = "InSilicoVA",
+            "I5" = "InterVA-5"
+        )
     ) {
@@
         ) +
-        scale_color_manual(values = default_colors) +
+        scale_color_manual(values = default_colors, labels = x_color_labels) +
         labs(
@@
 # Model full name
-gpt3_name <- "GPT-3.5"
-gpt4_name <- "GPT-4"
-isva_name <- "InSilicoVA"
-iva5_name <- "InterVA-5"
+gpt3_name <- "G3"
+gpt4_name <- "G4"
+isva_name <- "ISV"
+iva5_name <- "I5"
 
@@
     mutate(
-        model_name = factor(model_name, levels = model_name)
+        model_name = model_name %>%
+            case_when(
+                . == "G3" ~ "GPT-3.5",
+                . == "G4" ~ "GPT-4",
+                . == "ISV" ~ "InSilicoVA",
+                . == "I5" ~ "InterVA-5",
+                .default = .
+            ) %>%
+            factor(., levels = .)
     ) %>%
@@
     x_title = "Partial Chance Corrected Concordance (PCCC)",
-    text_mid_vjust = 3,
+    text_mid_vjust = 2,
     sort_group = F,
@@
     legend_margin = margin(-8, -2, -2, -2),
-    x_expand = waiver()
+    x_expand = waiver(),
+    text_scale = 1.25
 )
@@
     width = 170,
-    height = 60,
+    height = 75,
     units = "mm",
@@
     text_mid_vjust = -1,
-    text_scale = 0.8
+    text_scale = 1
 )
@@
     x_title = "Partial Chance Corrected Concordance (PCCC)",
-    text_scale = 0.95
+    text_mid_vjust = 4,
+    text_scale = 1.15
 )
@@
     text_mid_vjust = 3,
-    text_end_size = 2.25,
-    text_scale = 0.95
+    text_scale = 1.25
 )

### 2025-06-18 src/plots.Rmd
Remove we

@@
         add_max_points = F,
-        mid_points_size = 2.5,
-        min_points_size = 2,
-        max_points_size = 3,
+        mid_points_size = 4,
+        min_points_size = 4,
+        max_points_size = 4,
         x_limits = c(0, 1),
@@
     ) +
-        geom_line(linewidth = 0.75, alpha = 0.4) + 
+        geom_line(linewidth = 1.15, alpha = 0.5) + 
         geom_line(
@@
             se = F,
-            linewidth = 1.25
+            linewidth = 1.5
         ) +
@@
         fill = "white",
-        size = 3,
+        size = 4.5,
         label.r = unit(0, "pt"),
@@
         # ),
-        legend.position = c(.875, .5),
+        legend.position = c(.875, .45),
         legend.title = element_blank(),
+        legend.text = element_text(size = 12),
         panel.grid.major = element_blank(),
@@
         axis.title.y = element_text(size = 9),
-        axis.text.x = element_text(size = 8),
-        axis.text.y = element_text(size = 8)
+        axis.text.x = element_text(size = 12),
+        axis.text.y = element_text(size = 12)
     )
@@
     x_title =  "Partial Chance Corrected Concordance (PCCC)",
-    text_mid_vjust = -1,
-    text_scale = 1
+    text_mid_vjust = 2,
+    text_scale = 1.25
 )
@@
     width = 170,
-    height = 225,
+    height = 250,
     units = "mm",

### 2025-06-23 src/plots.Rmd
Add range to perf plots

@@
         title_size = 10,
-        x_title = NULL,
+        x_title = "Partial Chance Corrected Concordance (PCCC) / R = PCCC Range",
         y_title = NULL,
@@
         text_mid_vjust = 2.5,
-        text_start_size = 3 * text_scale,
-        text_end_size = 4 * text_scale,
+        text_start_size = 2.75 * text_scale,
+        text_end_size = 3.5 * text_scale,
         text_hjust = 0.2,
@@
         max_points_size = 4,
-        x_limits = c(0, 1),
+        x_limits = c(0, 1.15),
         x_breaks = seq(0, 1, by = 0.1),
@@
             model_min = model_name[which.min(metric)],
-            model_max = model_name[which.max(metric)]
+            model_max = model_name[which.max(metric)],
+            group_range = diff(range(metric))
         ) %>%
@@
                 y = .data[[group]],
-                label = paste0(model_max, ": ", round(max_metric, 2))
+                label = paste0(
+                    model_max, ": ", round(max_metric, 2),
+                    " (R=", round(group_range, 2), ")"
+                )
             ),
@@
             .x == "Neonatal infections" ~ "Infections",
+            .x == "Road and transport injuries" ~ "Road/transport injuries",
+            .x == "Liver and alcohol related diseases" ~ "Liver/alcohol",
+            .x == "Birth asphyxia and trauma" ~ "Birth asphyxia/trauma",
             .default = .x
@@
     ) +
+    guides(
+        fill = guide_legend(reverse = TRUE)
+    ) +
     theme_minimal() +
     theme(
-        # panel.border = element_rect(
-        #     color = "black",
-        #     fill = NA,
-        #     linewidth = 0.75
-        # ),
         legend.position = c(.875, .45),
@@
     group = "age_label",
-    x_title = "Partial Chance Corrected Concordance (PCCC)",
     text_mid_vjust = 2,
     sort_group = F,
-    x_limits = c(0.2, 0.8),
+    x_limits = c(0.2, 0.9),
     legend_margin = margin(-8, -2, -2, -2),
@@
     title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
-    x_title =  "Partial Chance Corrected Concordance (PCCC)",
     text_mid_vjust = 2,
-    text_scale = 1.25
+    text_scale = 1
 )
@@
     fig_pccc_cod_adult,
-    width = 170,
-    height = 250,
+    width = 170, # min 170 mm full / 85 mm half
+    height = 225, # max 225 mm
     units = "mm",
@@
     title = paste0("Child, 28 Days to 11 Years (n=", n_child, ")"),
-    x_title = "Partial Chance Corrected Concordance (PCCC)",
     text_mid_vjust = 4,
-    text_scale = 1.15
+    text_scale = 1
 )

### 2025-06-25 src/plots.Rmd
Workaround to convert tex to docx; Convert pdf in word, then use pandoc with zotero lua to get citations for copy/paste

@@
 ggsave(
-    "../manuscript/fig-pccc-csmf.pdf",
+    "../manuscript/figures/fig-pccc-csmf.pdf",
     fig_pccc_csmf,
@@
 ggsave(
-    "../manuscript/fig-pccc.pdf",
+    "../manuscript/figures/fig-pccc.pdf",
     fig_pccc,
@@
 ggsave(
-    "../manuscript/fig-pccc-cod-adult.pdf",
+    "../manuscript/figures/fig-pccc-cod-adult.pdf",
     fig_pccc_cod_adult,
@@
 ggsave(
-    "../manuscript/fig-pccc-cod-child.pdf",
+    "../manuscript/figures/fig-pccc-cod-child.pdf",
     fig_pccc_cod_child,
@@
 ggsave(
-    "../manuscript/fig-pccc-cod-neo.pdf",
+    "../manuscript/figures/fig-pccc-cod-neo.pdf",
     fig_pccc_cod_neo,
@@
 ggsave(
-    "../manuscript/fig-pccc-age.pdf",
+    "../manuscript/figures/fig-pccc-age.pdf",
     fig_pccc_age,

### 2025-06-25 bin/tex2docx.sh

@@ -1,0 +1,7 @@
+pandoc manuscript/latex/manuscript.tex \
+  --from latex \
+  --to docx \
+  --output manuscript/latex/manuscript-zotero.docx \
+  --lua-filter=manuscript/latex/zotero.lua \
+--citeproc \
+--bibliography manuscript/latex/bibliography.bib

### 2025-06-26 bin/tex2docx.sh
Working on docx

@@ -1,7 +1,0 @@
-pandoc manuscript/latex/manuscript.tex \
-  --from latex \
-  --to docx \
-  --output manuscript/latex/manuscript-zotero.docx \
-  --lua-filter=manuscript/latex/zotero.lua \
---citeproc \
---bibliography manuscript/latex/bibliography.bib

### 2025-06-26 manuscript/latex/tex2docx.sh

@@ -1,0 +1,7 @@
+pandoc manuscript.tex \
+  --from latex \
+  --to docx \
+  --output manuscript-zotero.docx \
+  --lua-filter=zotero.lua \
+--citeproc \
+--bibliography bibliography.bib

### 2025-08-02 src/plots.Rmd
Change plots for b/w print per pj suggestion

@@
 library(ggrepel)
+library(ggpattern)
 library(patchwork)
@@
         title_size = 10,
-        x_title = "Partial Chance Corrected Concordance (PCCC) / R = PCCC Range",
+        x_title = "Partial Chance Corrected Concordance (PCCC)",
         y_title = NULL,
@@
         ),
+        x_shapes = 21:25,
         x_title_size = 9 * text_scale,
@@
         legend_title = element_blank(),
-        legend_margin = margin(c(-8, -2, -2, -2)),
+        legend_margin = margin(c(-8, -2, -2, -50)),
+        legend_add = c("R = Range"),
         ...
@@
 
+    # Add blank legend items
+    if (!is.null(legend_add)) {
+
+        # Add to manual color labels
+        for (i in legend_add) {
+            x_color_labels[i] <- i
+        }
+
+        # Add to factor levels
+        df_plot[[color]] <- factor(
+            df_plot[[color]],
+            levels = c(levels(df_plot[[color]]), legend_add)
+        )
+    }
+
     # Plot metric for each model
@@
         geom_point( # points
-            shape = 21,
             color = "black",
-            aes(fill = .data[[color]]),
+            aes(
+                shape = .data[[color]],
+                fill = .data[[color]]
+            ),
             size = mid_points_size
@@
         ) +
+        scale_shape_manual(
+            values = x_shapes,
+            labels = x_color_labels,
+            drop = ifelse(is.null(legend_add), T, F)
+        ) +
         scale_fill_discrete(
-            labels = x_color_labels
+            labels = x_color_labels,
+            drop = ifelse(is.null(legend_add), T, F)
         ) +
@@
         metric_label = paste0(metric, "=", round(metric_value, 2)) %>%
-            str_replace(., " Accuracy", "")
+            str_replace(., " Accuracy", ""),
+        metric_pattern = case_when(
+            metric == "PCCC" ~ "stripe",
+            metric == "CSMF Accuracy" ~ "none"
+        )
     )
@@
 ) +
-    geom_bar(
+    geom_bar_pattern(
+        aes(pattern = metric_pattern),
         stat = "identity",
@@
         color = "black",
-        width = 0.7
+        width = 0.7,
+        pattern_fill = "black",
+        pattern_angle = 45,
+        pattern_spacing = 0.05,
+        pattern_colour = "black"
     ) +
@@
     ) +
+    scale_pattern_manual(values = c(
+        "stripe" = "stripe",
+        "none" = "none"
+    )) +
     labs(
@@
     guides(
-        fill = guide_legend(reverse = TRUE)
+        pattern = "none",
+        fill = guide_legend(
+            reverse = TRUE,
+            override.aes = list(
+                pattern = c("stripe", "none")
+            )
+        )
     ) +
@@
     theme(
-        legend.position = c(.875, .45),
+        legend.position = "bottom",
+        legend.margin = margin(c(-8, -2, -2, -2)),
         legend.title = element_blank(),
-        legend.text = element_text(size = 12),
+        legend.text = element_text(size = 9),
         panel.grid.major = element_blank(),
@@
     x_limits = c(0.2, 0.9),
-    legend_margin = margin(-8, -2, -2, -2),
     x_expand = waiver(),

### 2025-08-02 src/plots.Rmd
Bold max perf pccc plots

@@
             vjust = 0.5,
-            size = text_end_size
+            size = text_end_size,
+            fontface = "bold"
         ) +

### 2025-08-13 src/plots.Rmd
Fix figures, working on better captions/legends

@@
             "I5" = "InterVA-5"
-        )
+        ),
+        x_linetypes = c(
+            "solid",
+            "solid",
+            "dashed",
+            "dotted"
+        ),
+        plot_mean = F
     ) {
@@
     ) +
-        geom_line(linewidth = 1.15, alpha = 0.5) + 
         geom_line(
-            data = df_plot %>%
-                group_by(.data[[group]]) %>%
-                summarize(
-                    metric = mean(metric),
-                    model_name = "Mean Across Models"
-                ),
-            aes(color = model_name),
-            se = F,
-            linewidth = 1.5
-        ) +
-        scale_color_manual(values = default_colors, labels = x_color_labels) +
+            aes(
+                linetype = model_name,
+                alpha = model_name
+            ),
+            linewidth = 1.15
+        ) + 
+        scale_color_manual(
+            values = default_colors,
+            labels = x_color_labels
+        ) +
+        scale_linetype_manual(
+            values = x_linetypes,
+            labels = x_color_labels
+        ) +
+        scale_alpha_manual(
+            values = c(1, 0.35, 0.9, 0.9),
+            labels = x_color_labels
+        ) +
         labs(
@@
         theme(
+            legend.key.width = unit(32, "pt"),
             legend.title = element_blank(),
@@
         )
+
+    # Add mean line
+    if (plot_mean) {
+        out <- out +
+            geom_line(
+                data = df_plot %>%
+                    group_by(.data[[group]]) %>%
+                    summarize(
+                        metric = mean(metric),
+                        model_name = "Mean Across Models"
+                    ),
+                aes(color = model_name),
+                se = F,
+                linewidth = 1.5
+            )
+    }
     return(out)
@@
         metric = str_to_upper(metric) %>%
-            str_replace(., "CSMF", "CSMF Accuracy") %>%
-            factor(., levels = rev(c("PCCC", "CSMF Accuracy"))),
+            str_replace(., "CSMF", "Cause Specific Mortality Fraction (CSMF) Accuracy") %>%
+            str_replace(., "PCCC", "Partial Chance Corrected Concordance (PCCC)") %>%
+            factor(., levels = rev(c("Partial Chance Corrected Concordance (PCCC)", "Cause Specific Mortality Fraction (CSMF) Accuracy"))),
         metric_label = paste0(metric, "=", round(metric_value, 2)) %>%
@@
         metric_pattern = case_when(
-            metric == "PCCC" ~ "stripe",
-            metric == "CSMF Accuracy" ~ "none"
+            metric == "Partial Chance Corrected Concordance (PCCC)" ~ "stripe",
+            metric == "Cause Specific Mortality Fraction (CSMF) Accuracy" ~ "none"
         )
@@
         legend.position = "bottom",
-        legend.margin = margin(c(-8, -2, -2, -2)),
+        legend.margin = margin(c(-8, -2, -2, -60)),
         legend.title = element_blank(),

### 2025-08-13 src/install.R

@@ -2,6 +2,7 @@ install.packages("openVA")
 install.packages("tidyverse")
 install.packages("dplyr")
 install.packages("ggrepel")
+install.packages("ggpattern")
 install.packages("patchwork")
 install.packages("glue")
 install.packages("kableExtra")

### 2025-08-13 src/plots.Rmd
Finished initial draft of v2

@@
     title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
-    text_mid_vjust = 2,
+    text_mid_vjust = 2.5,
     text_scale = 1
@@
     x_title = "Partial Chance Corrected Concordance (PCCC)",
-    text_mid_vjust = 3,
+    text_mid_vjust = 3.5,
     text_scale = 1.25
@@
         ),
-    title = "Partial Chance Corrected Concordance (PCCC)",
+    y_title = "Partial Chance Corrected Concordance (PCCC)",
     text_scale = 0.9

### 2025-08-15 src/plots.Rmd
Add line numbers and png figures to v2 draft

@@
 )
+ggsave(
+    "../manuscript/figures/png/fig-pccc-csmf.png",
+    fig_pccc_csmf,
+    width = 170,
+    height = 100,
+    units = "mm",
+    dpi = 300
+)
 
@@
 )
+ggsave(
+    "../manuscript/figures/png/fig-pccc.png",
+    fig_pccc,
+    width = 170,
+    height = 75,
+    units = "mm",
+    dpi = 300
+)
 
@@
 )
+ggsave(
+    "../manuscript/figures/png/fig-pccc-cod-adult.png",
+    fig_pccc_cod_adult,
+    width = 170, # min 170 mm full / 85 mm half
+    height = 225, # max 225 mm
+    units = "mm",
+    dpi = 300
+)
 
@@
     "../manuscript/figures/fig-pccc-cod-child.pdf",
+    fig_pccc_cod_child,
+    width = 170,
+    height = 150,
+    units = "mm",
+    dpi = 300
+)
+ggsave(
+    "../manuscript/figures/png/fig-pccc-cod-child.png",
     fig_pccc_cod_child,
@@
 )
+ggsave(
+    "../manuscript/figures/png/fig-pccc-cod-neo.png",
+    fig_pccc_cod_neo,
+    width = 170,
+    height = 100,
+    units = "mm",
+    dpi = 300
+)
 
@@
 )
+ggsave(
+    "../manuscript/figures/png/fig-pccc-age.png",
+    fig_pccc_age,
+    width = 170,
+    height = 100,
+    units = "mm",
+    dpi = 300
+)
 

### 2025-08-27 src/plots.Rmd
Finish v3 edits from pj and pb

@@
 
+    # Get custom colors for models
+    default_colors <- scales::hue_pal()(length(unique(df_plot[[color]])))
+    default_colors <- c(default_colors, rep(NA, length(legend_add)))
+    names(default_colors) <- c(unique(as.character(df_plot[[color]])), legend_add)
+
     # Plot metric for each model
@@
         ) +
+        scale_fill_manual(
+            values = default_colors,
+            labels = x_color_labels,
+            drop = ifelse(is.null(legend_add), T, F)
+        ) +
         scale_shape_manual(
             values = x_shapes,
-            labels = x_color_labels,
-            drop = ifelse(is.null(legend_add), T, F)
-        ) +
-        scale_fill_discrete(
             labels = x_color_labels,

### 2025-08-29 bin/setup_pycrossva.sh
Add pycrossva and open ai api key instructions

@@ -1,0 +1,1 @@
+pip install -e ./bin/pycrossva-v0.97

### 2025-08-29 bin/setup_python.sh

@@ -1,6 +1,3 @@
 python3.11 -m venv tmp/venv
 chmod +x ./bin/activate.sh
-chmod +x ./bin/deactivate.sh
-chmod +x ./bin/reinstall.sh
-chmod +x ./bin/uninstall.sh
 (source bin/activate.sh && pip install -r src/requirements.txt)

### 2025-08-29 src/models/gpt3.py

@@ -2,6 +2,7 @@ import os
 import pandas as pd
 import numpy as np
 from openai import OpenAI
+from dotenv import load_dotenv
 import datetime
 import pytz
 import logging
@@ -9,6 +10,9 @@ import logging
 import textwrap
 import json
 import re
+
+# Load environment variables from .env file
+load_dotenv()
 
 # Global Variables
 TIMEZONE = pytz.timezone('America/Toronto')

### 2025-10-09 src/models/gpt3.py
completed 1st run of 100 records in chatgpt3 with seed 1234

@@ -44,9 +44,9 @@ N_REPEAT_RESPONSES = 10
 # #############################################################################################
 
 # Demo mode artificially limits the number of rows from the import dataset for testing/demo purposes
-DEMO_MODE = False
+DEMO_MODE = True
 DEMO_RANDOM = False
-DEMO_SIZE_LIMIT = 5
+DEMO_SIZE_LIMIT = 100
 
 # Discard columns not recognized by the script before saving output file.
 # Set to True to retain only essential columns in the output file.
@@ -55,6 +55,9 @@ DROP_EXCESS_COLUMNS = False
 
 # Number of API calls between saving the output file
 SAVE_FREQ = 3
+
+# Random seed for reproducibility
+SEED = 1234
 
 # Models Settings
 models = {
@@ -554,6 +557,7 @@ def stage_2_generate_gpt_responses(
         tools=None,
         logprobs=None,
         top_logprobs=None,
+        seed=1234
     ) -> str:
         """
         Generates a completion using the OpenAI Chat API.
@@ -578,6 +582,7 @@ def stage_2_generate_gpt_responses(
             "temperature": temperature,
             "logprobs": logprobs,
             "top_logprobs": top_logprobs,
+            "seed": seed
         }
         if tools:
             params["tools"] = tools
@@ -655,7 +660,8 @@ def stage_2_generate_gpt_responses(
                 model=MODEL_NAME,
                 logprobs=LOGPROBS,
                 temperature=TEMPERATURE,
-                max_tokens=MAX_TOKENS
+                max_tokens=MAX_TOKENS,
+                seed=SEED
             )
             
  
@@ -670,7 +676,8 @@ def stage_2_generate_gpt_responses(
                 'param_max_tokens': MAX_TOKENS,
                 'param_system_prompt': SYS_PROMPT,
                 'param_user_prompt': prompt,
-                'timestamp': current_time,
+                'param_seed': SEED,
+                'timestamp': current_time,                
                 'output': recursive_dict(completion),
             }
 

### 2025-10-10 src/models/gpt3.py
Include seed param for gpt3 and gpt4

@@ -44,9 +44,9 @@ N_REPEAT_RESPONSES = 10
 # #############################################################################################
 
 # Demo mode artificially limits the number of rows from the import dataset for testing/demo purposes
-DEMO_MODE = True
+DEMO_MODE = False
 DEMO_RANDOM = False
-DEMO_SIZE_LIMIT = 100
+DEMO_SIZE_LIMIT = 5
 
 # Discard columns not recognized by the script before saving output file.
 # Set to True to retain only essential columns in the output file.
@@ -570,6 +570,7 @@ def stage_2_generate_gpt_responses(
             tools (str, optional): Additional tools to use for generating the completion. Defaults to None.
             logprobs (int, optional): Include log probabilities in the response. Defaults to None.
             top_logprobs (int, optional): Include top log probabilities in the response. Defaults to None.
+            seed (int, optional): Random seed to improve reproducibility.
 
         Returns:
             str: The generated completion.

### 2025-10-10 src/models/gpt4.py

@@ -56,6 +56,9 @@ DROP_EXCESS_COLUMNS = False
 # Number of API calls between saving the output file
 SAVE_FREQ = 3
 
+# Random seed for reproducibility
+SEED = 1234
+
 # Models Settings
 models = {
     "gpt4": "gpt-4-0613",
@@ -555,6 +558,7 @@ def stage_2_generate_gpt_responses(
         tools=None,
         logprobs=None,
         top_logprobs=None,
+        seed=1234
     ) -> str:
         """
         Generates a completion using the OpenAI Chat API.
@@ -567,6 +571,7 @@ def stage_2_generate_gpt_responses(
             tools (str, optional): Additional tools to use for generating the completion. Defaults to None.
             logprobs (int, optional): Include log probabilities in the response. Defaults to None.
             top_logprobs (int, optional): Include top log probabilities in the response. Defaults to None.
+            seed (int, optional): Random seed to improve reproducibility.
 
         Returns:
             str: The generated completion.
@@ -579,6 +584,7 @@ def stage_2_generate_gpt_responses(
             "temperature": temperature,
             "logprobs": logprobs,
             "top_logprobs": top_logprobs,
+            "seed": seed
         }
         if tools:
             params["tools"] = tools

### 2025-10-12 src/data.Rmd
Include gpt5 data

--- 2024-04-16 src/preprocess.Rmd
@@
     ) %>% rename(gpt4_icd10 = cause1_icd10),
+    model_gpt5 =
+        read_csv(
+            "../tmp/healsl_rd1to2_rapid_gpt5_v1.csv",
+            col_select = c("rowid", "cause1_icd10", "round")
+        ) %>% mutate(
+            cause1_icd10 = str_sub(cause1_icd10, 1, 3),
+            round = as.integer(substr(round, 3, 3))
+        ) %>% rename(gpt5_icd10 = cause1_icd10),
     model_insilicova = bind_rows(
@@
 
+### ChatGPT-5 Counts
+
+Check ChatGPT-5 Counts:
+
+```{r}
+
+# Get phy coded icd10 records only
+out_coded <- out %>% filter(
+    !is.na(physician_icd10) & !is.null(physician_icd10)
+)
+out_coded_agree <- out_coded %>% filter(is_agreed == TRUE)
+
+# Get phy coded cghr10 records only
+out_coded_cghr10 <- out_coded %>% filter(
+    !is.na(physician_cghr10) & !is.null(physician_cghr10)
+)
+out_coded_cghr10_agree <- out_coded_cghr10 %>% filter(is_agreed == TRUE)
+
+# Get gpt5 coded records
+out_cgpt5 <- out_coded %>% filter(
+    !is.na(gpt5_icd10) & !is.null(gpt5_icd10)
+)
+out_cgpt5_agree <- out_coded_agree %>% filter(
+    !is.na(gpt5_icd10) & !is.null(gpt5_icd10)
+)
+out_cgpt5_cghr10 <- out_coded_cghr10 %>% filter(
+    !is.na(gpt5_icd10) & !is.null(gpt5_icd10)
+)
+out_cgpt5_cghr10_agree <- out_coded_cghr10_agree %>% filter(
+    !is.na(gpt5_icd10) & !is.null(gpt5_icd10)
+)
+
+# Get gpt5 coded records converted to cghr10
+out_cgpt5_xcghr10 <- out_cgpt5 %>% filter(
+    !is.na(gpt5_cghr10) & !is.null(gpt5_cghr10)
+)
+out_cgpt5_xcghr10_agree <- out_cgpt5_agree %>% filter(
+    !is.na(gpt5_cghr10) & !is.null(gpt5_cghr10)
+)
+out_cgpt5_xcghr10_cghr10 <- out_cgpt5_cghr10 %>% filter(
+    !is.na(gpt5_cghr10) & !is.null(gpt5_cghr10)
+)
+out_cgpt5_xcghr10_cghr10_agree <- out_cgpt5_cghr10_agree %>% filter(
+    !is.na(gpt5_cghr10) & !is.null(gpt5_cghr10)
+)
+
+# Print results
+cat(paste0(
+    "ICD-10 Output\n-------------",
+    "\nChatGPT-5 ICD-10 Coded (Phy. ICD-10 Coded): ", out_cgpt5 %>% nrow,
+    "\nChatGPT-5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt5_agree %>% nrow,
+    "\nChatGPT-5 ICD-10 Coded (Phy. CGHR-10 Coded): ", out_cgpt5_cghr10 %>% nrow,
+    "\nChatGPT-5 ICD-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_cgpt5_cghr10_agree %>% nrow,
+    "\n\nAfter Conversion to CGHR-10\n---------------------------",
+    "\nChatGPT-5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt5_xcghr10 %>% nrow,
+    "\nChatGPT-5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt5_xcghr10_agree %>% nrow,
+    "\nChatGPT-5 CGHR-10 Coded (Phy. CGHR-10 Coded): ", out_cgpt5_xcghr10_cghr10 %>% nrow,
+    "\nChatGPT-5 CGHR-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_cgpt5_xcghr10_cghr10_agree %>% nrow
+))
+```
+
 ### InterVA-5 Counts
@@
 ```{r}
-write_csv(out, "../data/healsl_rd1to2_cod_v1.csv")
+write_csv(out, "../data/healsl_rd1to2_cod_v2.csv")
 ```

### 2025-10-12 src/plots.Rmd
Workng on gpt5 plots

@@
             "G4" = "GPT-4 (G4)",
+            "G5" = "GPT-5 (G5)",
             "ISV" = "InSilicoVA (ISV)",
@@
         ),
-        x_shapes = 21:25,
+        x_shapes = 21:26,
         x_title_size = 9 * text_scale,
@@
             "G4" = "GPT-4",
+            "G5" = "GPT-5",
             "ISV" = "InSilicoVA",
@@
             "dashed",
+            "dotted",
             "dotted"
@@
 # Read preds
-df_raw <- read_csv("../data/healsl_rd1to2_cod_v1.csv")
+df_raw <- read_csv("../data/healsl_rd1to2_cod_v2.csv")
 
@@
 df
-
-```
-
-## Combined Models
-
-Create model combinations where if any of the models have the physician code, then set the combined model's output for the case to be the physician code.
-
-```{r}
-
-# Calc combine preds
-df <- df %>%
-    mutate(
-        "gpt3_insilicova_cghr10" = if_else(
-            gpt3_cghr10 == physician_cghr10 | 
-                insilicova_cghr10 == physician_cghr10,
-            physician_cghr10,
-            gpt3_cghr10
-        ),
-        "gpt4_insilicova_cghr10" = if_else(
-            gpt4_cghr10 == physician_cghr10 | 
-                insilicova_cghr10 == physician_cghr10,
-            physician_cghr10,
-            gpt4_cghr10
-        ),
-        "gpt3_interva5_cghr10" = if_else(
-            gpt3_cghr10 == physician_cghr10 | 
-                interva5_cghr10 == physician_cghr10,
-            physician_cghr10,
-            gpt3_cghr10
-        ),
-        "gpt4_interva5_cghr10" = if_else(
-            gpt4_cghr10 == physician_cghr10 | 
-                interva5_cghr10 == physician_cghr10,
-            physician_cghr10,
-            gpt4_cghr10
-        ),
-        "gpt3_insilicova_interva5_cghr10" = if_else(
-            gpt3_cghr10 == physician_cghr10 | 
-                insilicova_cghr10 == physician_cghr10 |
-                interva5_cghr10 == physician_cghr10,
-            physician_cghr10,
-            gpt3_cghr10
-        ),
-        "gpt4_insilicova_interva5_cghr10" = if_else(
-            gpt4_cghr10 == physician_cghr10 | 
-                insilicova_cghr10 == physician_cghr10 |
-                interva5_cghr10 == physician_cghr10,
-            physician_cghr10,
-            gpt4_cghr10
-        )
-    )
-
-# Display combine preds
-print(head(df %>% select(
-    gpt3_insilicova_cghr10,
-    gpt4_insilicova_cghr10,
-    gpt3_interva5_cghr10,
-    gpt4_interva5_cghr10,
-    gpt3_insilicova_interva5_cghr10,
-    gpt4_insilicova_interva5_cghr10
-)))
 
@@
             gpt4_cghr10,
+            gpt5_cghr10,
             insilicova_cghr10,
@@
 gpt4_name <- "G4"
+gpt5_name <- "G5"
 isva_name <- "ISV"
@@
             str_replace(., "gpt4", gpt4_name) %>%
+            str_replace(., "gpt5", gpt5_name) %>%
             str_replace(., "insilicova", isva_name) %>%
@@
             factor(., levels = c(
+                gpt5_name,
                 gpt4_name,
@@
                 . == "G4" ~ "GPT-4",
+                . == "G5" ~ "GPT-5",
                 . == "ISV" ~ "InSilicoVA",

### 2025-10-15 src/models/gpt5.py
Add req txt from thomas, checked for reprod

@@ -557,16 +557,18 @@ def stage_2_generate_gpt_responses(
         tools = None
     ) -> str:
         """
-        2025-Oct-02 updated: create a model response using the Responses API.
+        Creates an OpenAI model response using the Responses API (updated October 2, 2025).
 
         Args:
             messages (list[dict[str, str]]): A list of messages in the conversation.
             model (str, optional): The model to use for generating the completion. Defaults to "gpt-3.5-turbo-0125".
-            max_tokens (int, optional): The maximum number of tokens in the generated completion. Defaults to 30.
+            max_output_tokens (int, optional): The maximum number of tokens in the generated completion. Defaults to 30.
             temperature (float, optional): Controls the randomness of the generated completion. Defaults to 0.
             tools (str, optional): Additional tools to use for generating the completion. Defaults to None.
             logprobs (int, optional): Include log probabilities in the response. Defaults to None.
             top_logprobs (int, optional): Include top log probabilities in the response. Defaults to None.
+            reasoning (str, optional): ability for model to reason with thinking steps. Defaults to minimal reasoning.
+            text (dict[str], optional): additional parameters related to text. Defaults to low verbosity.
 
         Returns:
             str: The generated completion.

### 2025-10-17 src/plots.Rmd
Use bar plots instead of lines and symbols, reorganized plots

@@
         x_breaks = seq(0, 1, by = 0.1),
-        x_expand = expansion(add = 0.2),
+        x_expand = expansion(add = 0.1),
         x_color_labels = c(
@@
     }
+    return(out)
+}
+
+# Plot performance of models using grouped bars
+plot_perf_bar <- function(
+        df_long,
+        f = calc_pccc,
+        group = "cod_name",
+        color = "model_name",
+        text_scale = 1,
+        title = NULL,
+        title_size = 10,
+        x_title = "Partial Chance Corrected Concordance (PCCC)",
+        y_title = NULL,
+        x_hpos = -0.23 * text_scale,
+        x_limits = c(0, 1),
+        x_breaks = seq(0, 1, by = 0.1),
+        x_expand = expansion(add = ((x_hpos * -1) + 0.02) * text_scale),
+        x_shapes = 21:26,
+        x_title_size = 9 * text_scale,
+        y_title_size = 9 * text_scale,
+        x_text_size = 8 * text_scale,
+        x_color_size = 3 * text_scale,
+        y_text_size = 9 * text_scale,
+        legend_position = "bottom",
+        legend_title = element_blank(),
+        legend_margin = margin(c(-8, -2, -2, -50)),
+        legend_key_size = 0.5,
+        ...
+    ) {
+
+    #  Group data
+    df_plot <- df_long %>%
+        group_by(.data[[group]], model_name, .drop = F)
+
+    # Calc metric
+    if (identical(f, calc_pccc)) {
+        df_plot <- df_plot %>%
+            summarize(
+                metric = f(cod, model_cghr10, N = unique(ncod)[1], ...)
+            )
+    } else {
+        df_plot <- df_plot %>%
+            summarize(
+                metric = f(cod, model_cghr10, ...)
+            )
+    }
+
+    # Add metric value to model name
+    df_plot <- df_plot %>%
+        mutate( 
+            model_label = paste0(model_name, ": ", round(metric, 2))
+        )
+
+    # Get custom colors for models
+    default_colors <- scales::hue_pal()(length(unique(df_plot[[color]])))
+    names(default_colors) <- c(unique(as.character(df_plot[[color]])))
+
+    # Format plot data
+    df_plot <- df_plot %>%
+        mutate(
+            x = metric,
+            y = .data[[group]],
+            color = .data[[color]]
+        )
+
+    # Sort bars within groups (ascending)
+    df_pos <- df_plot %>%
+        group_by(y) %>%
+        arrange(x, .by_group = TRUE) %>%  
+        mutate(
+            rank_in_group = row_number(),
+            n_colors = n()
+        ) %>%
+        ungroup()
+
+    # Reverse sort groups by highest-performing bar
+    group_levels_order <- df_pos %>%
+        group_by(y) %>%
+        summarize(max_x = max(x)) %>%
+        arrange(max_x) %>%
+        pull(y)
+
+    df_pos <- df_pos %>%
+        mutate(
+            y = factor(y, levels = group_levels_order),
+            group_center = as.numeric(y)
+        )
+
+    # Bar width and offset
+    group_width <- 0.8
+    max_items <- max(df_pos$n_colors)
+    bar_width <- group_width / max_items
+
+    df_pos <- df_pos %>%
+        mutate(
+            offset = (rank_in_group - (n_colors + 1)/2) * bar_width,
+            x_pos = group_center + offset,
+            label_text = paste0(color, ": ", format(round(x, 2), nsmall = 2)),
+            label_x = x_pos
+        )
+
+    # Identify top-performing model in each group
+    df_pos <- df_pos %>%
+        group_by(y) %>%
+        mutate(
+            top_model = x == max(x),
+            fontface = ifelse(top_model, "bold", "plain"),
+            alpha_val = ifelse(top_model, 1, 0.35),       # transparency for non-top bars
+            outline_color = ifelse(top_model, "black", NA) # black outline for top bars
+        ) %>%
+        ungroup()
+
+    # Compute range and modify group labels using square brackets
+    group_labels <- df_pos %>%
+        group_by(y) %>%
+        summarize(range_x = max(x) - min(x)) %>%
+        mutate(label = paste0(as.character(y), "\n[Range=", format(round(range_x, 2), nsmall = 2), "]")) %>%
+        arrange(match(y, levels(df_pos$y)))
+
+    # Replace factor levels with new labels including range
+    levels(df_pos$y) <- group_labels$label
+
+    # Plot metric for each model
+    out <- ggplot(df_pos, aes(x = x_pos, y = x, fill = color)) +
+        geom_col(
+            width = bar_width * 0.9,
+            position = "identity",
+            color = df_pos$outline_color,
+            alpha = df_pos$alpha_val
+        ) +
+        geom_text(
+            aes(
+                x = label_x,
+                label = label_text,
+                fontface = fontface
+            ),
+            y = x_hpos,
+            hjust = 0,
+            vjust = 0.5,
+            size = x_color_size
+        ) +
+        coord_flip() +
+        scale_fill_manual(
+            values = default_colors
+        ) +
+        scale_x_continuous(
+            breaks = seq_along(levels(df_pos$y)),
+            labels = levels(df_pos$y),
+            expand = c(0, 0)
+        ) +
+        scale_y_continuous(
+            expand = x_expand,
+            breaks = x_breaks,
+            limits = x_limits
+        ) +
+        labs(
+            title = title,
+            x = y_title,
+            y = x_title
+        ) +
+        theme_minimal() +
+        theme(
+            legend.position = legend_position,
+            legend.title = legend_title,
+            legend.margin = legend_margin,
+            legend.key.size = unit(legend_key_size, "lines"),
+            panel.grid.major = element_blank(),
+            panel.grid.minor = element_blank(),
+            plot.title = element_text(size = title_size),
+            axis.title.x = element_text(size = x_title_size),
+            axis.title.y = element_text(size = y_title_size),
+            axis.text.x = element_text(size = x_text_size),
+            axis.text.y = element_text(size = y_text_size)
+        )
     return(out)
@@
 # Model full name
-gpt3_name <- "G3"
-gpt4_name <- "G4"
-gpt5_name <- "G5"
-isva_name <- "ISV"
-iva5_name <- "I5"
+gpt3_name <- "GPT-3.5"
+gpt4_name <- "GPT-4"
+gpt5_name <- "GPT-5"
+isva_name <- "InSilicoVA"
+iva5_name <- "InterVA-5"
 
@@
 # Plot perf for pccc by age groups
-fig_pccc <- plot_perf(
+fig_pccc <- plot_perf_bar(
     df_long %>%
@@
     group = "age_label",
-    text_mid_vjust = 2,
-    sort_group = F,
-    x_limits = c(0.2, 0.9),
-    x_expand = waiver(),
-    text_scale = 1.25
+    x_hpos = -0.24,
+    x_expand = expansion(add = 0.25),
+    text_scale = 0.95
 )
@@
 # Plot adult perf for pccc by cod
-fig_pccc_cod_adult <- plot_perf(
+fig_pccc_cod_adult <- plot_perf_bar(
     df_long %>% filter(age == "adult"),
@@
     title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
-    text_mid_vjust = 2.5,
-    text_scale = 1
+    text_scale = 0.7,
+    x_hpos = -0.15,
+    x_expand = expansion(add = 0.15)
 )
@@
 # Plot child perf for pccc by cod
-fig_pccc_cod_child <- plot_perf(
+fig_pccc_cod_child <- plot_perf_bar(
     df_long %>% filter(age == "child"),
@@
     title = paste0("Child, 28 Days to 11 Years (n=", n_child, ")"),
-    text_mid_vjust = 4,
-    text_scale = 1
+    text_scale = 0.92,
+    x_hpos = -0.24,
+    x_expand = expansion(add = 0.25)
 )
@@
 # Plot neo perf for pccc by cod
-fig_pccc_cod_neo <- plot_perf(
+fig_pccc_cod_neo <- plot_perf_bar(
     df_long %>% filter(age == "neo"),
@@
     x_title = "Partial Chance Corrected Concordance (PCCC)",
-    text_mid_vjust = 3.5,
-    text_scale = 1.25
+    text_scale = 0.92,
+    x_hpos = -0.24,
+    x_expand = expansion(add = 0.25)
 )

### 2025-10-17 src/models/gpt4.py
completed the run of 1000 records in chatgpt4 with seed 1234

@@ -44,9 +44,9 @@ N_REPEAT_RESPONSES = 10
 # #############################################################################################
 
 # Demo mode artificially limits the number of rows from the import dataset for testing/demo purposes
-DEMO_MODE = False
+DEMO_MODE = True
 DEMO_RANDOM = False
-DEMO_SIZE_LIMIT = 5
+DEMO_SIZE_LIMIT = 1000
 
 # Discard columns not recognized by the script before saving output file.
 # Set to True to retain only essential columns in the output file.
@@ -119,7 +119,7 @@ s4b_in_smpl_csv_filepath = s3_out_smpl_csv
 # smpl_analysis_in_csv_path = os.path.join(script_dir, OUTPUT_DIR, PROCESS_FILE)
 
 # Path to export file after sample analysis
-s4b_out_csv_filename = "healsl_rd1to2_rapid_gpt3_sample100_v1.csv"
+s4b_out_csv_filename = "healsl_rd1to2_rapid_gpt4_sample100_v1.csv"
 s4b_out_csv_filepath = os.path.join(script_dir, OUTPUT_DIR, s4b_out_csv_filename)
 # analyzed_out_csv_filename = PROCESS_FILE.replace(".csv", "_aggregated.csv")
 

### 2025-10-20 src/plots.Rmd
Finish gpt5 revisions, finish reviewer1 responses, working on reviewer2 responses

@@
         legend_spacing = unit(0, "pt"),
+        y_limits = c(0, 1.15),
+        y_breaks = seq(0, 1, by = 0.1),
         x_color_labels = c(
@@
             "dotted"
+        ),
+        x_linealpha = c(
+            1,
+            0.5,
+            0.9,
+            0.9,
+            0.7
+        ),
+        x_linewidths = c(
+            2,
+            1,
+            1.15,
+            2,
+            1.15
         ),
@@
                 linetype = model_name,
-                alpha = model_name
-            ),
-            linewidth = 1.15
+                alpha = model_name,
+                linewidth = model_name
+            )
+        ) + 
+        scale_y_continuous(
+            limits = y_limits,
+            breaks = y_breaks
         ) +
@@
         ) +
+        scale_linewidth_manual(
+           values = x_linewidths,
+           labels = x_color_labels
+        ) +
         scale_alpha_manual(
-            values = c(1, 0.35, 0.9, 0.9),
+            values = x_linealpha,
             labels = x_color_labels
@@
     group = "cod_name",
-    title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
+    title = paste0("Adult Causes of Death, 12+ Years (n=", n_adult, ")"),
     text_scale = 0.7,
@@
     group = "cod_name",
-    title = paste0("Child, 28 Days to 11 Years (n=", n_child, ")"),
+    title = paste0("Child Causes of Death, 28 Days to 11 Years (n=", n_child, ")"),
     text_scale = 0.92,
@@
     group = "cod_name",
-    title = paste0("Neonatal, <28 Days (n=", n_neo, ")"),
+    title = paste0("Neonatal Causes of Death, <28 Days (n=", n_neo, ")"),
     x_title = "Partial Chance Corrected Concordance (PCCC)",
@@
     y_title = "Partial Chance Corrected Concordance (PCCC)",
-    text_scale = 0.9
+    text_scale = 0.9,
+    y_limits = c(0.2, 0.9),
+    y_breaks = seq(0, 1, by = 0.05),
 )

### 2025-10-21 src/models/gpt5.py
Working on reviewer2 responses

@@ -554,6 +554,8 @@ def stage_2_generate_gpt_responses(
         max_tokens = 30,        
         reasoning_effort = "minimal",
         text_verbosity = "low",
+        state = False,
+        include = ['reasoning.encrypted_content'],
         tools = None
     ) -> str:
         """
@@ -568,6 +570,9 @@ def stage_2_generate_gpt_responses(
             logprobs (int, optional): Include log probabilities in the response. Defaults to None.
             top_logprobs (int, optional): Include top log probabilities in the response. Defaults to None.
             reasoning (str, optional): ability for model to reason with thinking steps. Defaults to minimal reasoning.
+            text_verbosity (str, optional): amount of detail for model to output. Defaults to low verbosity.
+            state (boolean, optional): whether to save the state for future calls or not. Defaults to stateless (false).
+            include (array, optional): used to do stateless calls.
             text (dict[str], optional): additional parameters related to text. Defaults to low verbosity.
 
         Returns:
@@ -579,7 +584,9 @@ def stage_2_generate_gpt_responses(
             "instructions": instructions,
             "input": input,            
             "reasoning" : { "effort" : reasoning_effort },
-            "text": { "verbosity": text_verbosity },            
+            "text": { "verbosity": text_verbosity },
+            "state": state,
+            "include" include,
             "max_output_tokens": max_tokens             
         }
         if tools:

### 2025-10-22 src/data.Rmd
Use and rerun for stateless gpt5

@@
 date: "`r format(Sys.time(), '%B %d, %Y')`"
-author: "Richard Wen <richard.wen@unityhealth.to>"
+author: "Richard Wen <rrwen.dev@gmail.com>"
 ---
@@
     ) %>% rename(gpt4_icd10 = cause1_icd10),
-    model_gpt5 =
+    model_gpt5 = bind_rows(
         read_csv(
-            "../tmp/healsl_rd1to2_rapid_gpt5_v1.csv",
-            col_select = c("rowid", "cause1_icd10", "round")
+            "../tmp/healsl_rd1_rapid_gpt5_v2.csv",
+            col_select = c("rowid", "cause1_icd10")
         ) %>% mutate(
             cause1_icd10 = str_sub(cause1_icd10, 1, 3),
-            round = as.integer(substr(round, 3, 3))
+            round = 1
+        ),
+        read_csv(
+            "../tmp/healsl_rd2_rapid_gpt5_v2.csv",
+            col_select = c("rowid", "cause1_icd10")
+        ) %>% mutate(
+            cause1_icd10 = str_sub(cause1_icd10, 1, 3),
+            round = 2
+        )
     ) %>% rename(gpt5_icd10 = cause1_icd10),

### 2025-10-22 bin/setup_python.sh

@@ -1,3 +1,3 @@
 python3.11 -m venv tmp/venv
 chmod +x ./bin/activate.sh
-(source bin/activate.sh && pip install -r src/requirements.txt)
+(source bin/activate.sh && pip install -r src/requirements.txt && pip uninstall -y openai && pip install -y openai)

### 2025-10-22 src/models/gpt5.py

@@ -19,7 +19,7 @@ TIMEZONE = pytz.timezone('America/Toronto')
 TEMP_DIR = "../../tmp"
 DATA_DIR = "../../tmp"
 OUTPUT_DIR = "../../tmp"
-INCLUDE_SAMPLING = False
+INCLUDE_SAMPLING = True
 script_dir = os.path.dirname(__file__)
 
 # #############################################################################################
@@ -554,8 +554,7 @@ def stage_2_generate_gpt_responses(
         max_tokens = 30,        
         reasoning_effort = "minimal",
         text_verbosity = "low",
-        state = False,
-        include = ['reasoning.encrypted_content'],
+        store = False,
         tools = None
     ) -> str:
         """
@@ -571,8 +570,7 @@ def stage_2_generate_gpt_responses(
             top_logprobs (int, optional): Include top log probabilities in the response. Defaults to None.
             reasoning (str, optional): ability for model to reason with thinking steps. Defaults to minimal reasoning.
             text_verbosity (str, optional): amount of detail for model to output. Defaults to low verbosity.
-            state (boolean, optional): whether to save the state for future calls or not. Defaults to stateless (false).
-            include (array, optional): used to do stateless calls.
+            store (boolean, optional): whether to save the state for future calls or not. Defaults to stateless (false).
             text (dict[str], optional): additional parameters related to text. Defaults to low verbosity.
 
         Returns:
@@ -585,8 +583,7 @@ def stage_2_generate_gpt_responses(
             "input": input,            
             "reasoning" : { "effort" : reasoning_effort },
             "text": { "verbosity": text_verbosity },
-            "state": state,
-            "include" include,
+            "store": store,
             "max_output_tokens": max_tokens             
         }
         if tools:

### 2025-10-24 src/plots.Rmd
Use and rerun for stateless gpt5
Add conf intervals, working on last respones to reviewer2

@@
 #install.packages("kableExtra)
+#install.packages("boot")
 ```
@@
 library(kableExtra)
+library(boot)
 ```
@@
     # Calc PCCC
+    if (!all(TP)) {
         out <- (C - (k/N)) / (1 - (k/N))
+    } else { # avoid division by 0 when max pccc
+        out <- 1
+    }
 
@@
     out <- 1 - (sum(abs(csmf_true - csmf_pred)) / csmf_max_error)
+    return(out)
+}
+
+# Calc bootstrapped cis for a metric
+calc_ci <- function(
+        x,
+        f = calc_pccc,
+        n_boot = 1000,
+        conf_level = 0.95,
+        col_actual = "cod",
+        col_pred = "model_cghr10",
+        ...
+    ) {
+
+    # Function to compute metric on a bootstrap sample
+    f_boot <- function(df, i) {
+        f(df[[col_actual]][i], df[[col_pred]][i], ...)
+    }
+
+    # Run bootstrap using the 'boot' package
+    boot_res <- boot(data = x, statistic = f_boot, R = n_boot)
+
+    # Compute percentile-based confidence interval
+    ci <- boot.ci(boot_res, type = "perc", conf = conf_level)$percent[4:5]
+
+    # Return named vector with metric and CI
+    out <- c(ci_mean = mean(boot_res$t), ci_low = ci[1], ci_hi = ci[2])
     return(out)
@@
         y_title = NULL,
-        x_hpos = -0.23 * text_scale,
+        x_hpos = -0.47 * text_scale,
         x_limits = c(0, 1),
         x_breaks = seq(0, 1, by = 0.1),
-        x_expand = expansion(add = ((x_hpos * -1) + 0.02) * text_scale),
+        x_expand = expansion(add = ((x_hpos * -1) + 0.03)),
         x_shapes = 21:26,
-        x_title_size = 9 * text_scale,
-        y_title_size = 9 * text_scale,
-        x_text_size = 8 * text_scale,
-        x_color_size = 3 * text_scale,
-        y_text_size = 9 * text_scale,
+        x_title_size = 8 * text_scale,
+        y_title_size = 8 * text_scale,
+        x_text_size = 7 * text_scale,
+        x_color_size = 2.5 * text_scale,
+        y_text_size = 8 * text_scale,
         legend_position = "bottom",
@@
         legend_key_size = 0.5,
-        ...
+        legend_text_size = 7 * text_scale,
+        legend_spacing_x = unit(58, "pt"),
+        n_boot = 1000,
+        error_bar = T,
+        error_bar_width = 0.05,
+        error_bar_size = 0.3,
+        error_bar_label = "95% Confidence Interval (Bootstrap, 1000 Resamples)"
     ) {
@@
         df_plot <- df_plot %>%
-            summarize(
-                metric = f(cod, model_cghr10, N = unique(ncod)[1], ...)
-            )
+            group_map(~{
+
+                # Calc metric
+                out <- c(
+                    metric = f(.x$cod, .x$model_cghr10, N = unique(.x$ncod)[1])
+                )
+
+                # Include ci if error bar
+                if (error_bar) {
+                    out <- c(.y, out, calc_ci(.x, n_boot = n_boot))
+                }
+                return(out)
+
+            }, .keep = T) %>%
+            bind_rows
+
     } else {
         df_plot <- df_plot %>%
-            summarize(
-                metric = f(cod, model_cghr10, ...)
-            )
-    }
-
-    # Add metric value to model name
-    df_plot <- df_plot %>%
-        mutate( 
-            model_label = paste0(model_name, ": ", round(metric, 2))
-        )
+            group_map(~{
+
+                # Calc metric
+                out <- c(
+                    metric = f(.x$cod, .x$model_cghr10)
+                )
+
+                # Include ci if error bar
+                if (error_bar) {
+                    out <- c(.y, out, calc_ci(.x, n_boot = n_boot))
+                }
+                return(out)
+
+            }, .keep = T) %>%
+            bind_rows
+    }
 
@@
         pull(y)
-
     df_pos <- df_pos %>%
@@
     bar_width <- group_width / max_items
-
     df_pos <- df_pos %>%
@@
         )
+
+    # Add ci to model label
+    if (error_bar) {
+        df_pos <- df_pos %>%
+            mutate(
+                label_text = paste0(label_text, " (", round(ci_low, 2), ",", round(ci_hi, 2), ")")
+            )
+    }
 
@@
     # Plot metric for each model
+    df_pos$ci_label <- error_bar_label # dummy label for legend
     out <- ggplot(df_pos, aes(x = x_pos, y = x, fill = color)) +
@@
             legend.key.size = unit(legend_key_size, "lines"),
+            legend.text = element_text(size = legend_text_size),
+            legend.spacing.x = legend_spacing_x,
             panel.grid.major = element_blank(),
@@
         )
+
+    # Show error bars
+    if (error_bar) {
+        out <- out +
+            geom_errorbar(
+                aes(ymin = ci_low, ymax = ci_hi, color = ci_label),
+                width = error_bar_width,
+                size = error_bar_size
+            ) +
+            scale_color_manual(name = "", values = "black") +
+            guides(
+                fill = guide_legend(order = 1), # bar legend first
+                color = guide_legend(order = 2) # ci legend last
+            )
+    }
     return(out)
@@
     group = "age_label",
-    x_hpos = -0.24,
-    x_expand = expansion(add = 0.25),
     text_scale = 0.95
@@
     text_scale = 0.7,
-    x_hpos = -0.15,
-    x_expand = expansion(add = 0.15)
+    x_hpos = -0.27
 )
@@
     text_scale = 0.92,
-    x_hpos = -0.24,
-    x_expand = expansion(add = 0.25)
+    x_hpos = -0.43
 )

### 2025-10-25 src/plots.Rmd
Add agreement to tables b4/b5

@@
 #install.packages("boot")
+#install.pacakges("scales")
 ```
@@
 library(boot)
+library(scales)
 ```
@@
 
+# Rename raw COD names
+df_raw <- df_raw %>%
+    mutate(across(
+        c(
+            physician_cghr10,
+            gpt3_cghr10,
+            gpt4_cghr10,
+            gpt5_cghr10,
+            insilicova_cghr10,
+            interva5_cghr10
+        ),
+        ~ case_when(
+            .x == "Maternal conditions" ~ "Maternal",
+            .x == "Acute respiratory infections" ~ "Pneumonia",
+            .x == "Neonatal infections" ~ "Infections",
+            .x == "Road and transport injuries" ~ "Road/transport injuries",
+            .x == "Liver and alcohol related diseases" ~ "Liver/alcohol",
+            .x == "Birth asphyxia and trauma" ~ "Birth asphyxia/trauma",
+            .default = .x
+        ) %>%
+            str_replace_all(" diseases| disease", "")
+    ))
+
 ```
@@
 
+# Shorten raw COD names
+df_raw <- df_raw %>%
+    mutate(across(
+        c(
+            physician_cghr10,
+            gpt3_cghr10,
+            gpt4_cghr10,
+            gpt5_cghr10,
+            insilicova_cghr10,
+            interva5_cghr10
+        ),
+        ~ str_wrap(.x, width = 18)
+    ))
+
 ```
@@
 ```{r}
+
+# Standardize raw ages to age range + unit
+df_raw <- df_raw %>%
+    mutate(
+        age_range_orig = age_range,
+        age_range = str_to_lower(age_range),
+        age_range = str_replace( # neo ages
+            age_range,
+            " \\(early neonatal\\)| \\(late neonatal\\)",
+            ""
+        ),
+        age_range = case_when( # adult ages
+            age == "adult" ~ paste0(age_range, " years"),
+            .default = age_range
+        )
+    )
 
@@
     order_arange
+
+# Order raw age ranges as factor
+df_raw <- df_raw %>%
+    mutate(
+        age_range = factor(
+            age_range %>%
+                str_replace(., "10-14 years", "12-14 years"),
+            levels = c(ages_neo, ages_child, ages_adult)
+        )
+    )
 
@@
 
+# Get total records
+tab_all <- df_raw %>%
+    filter(!is.na(physician_cghr10) & !is.null(physician_cghr10)) # remove uncoded cases
+tab_all_n <- tab_all %>% nrow
+
 # Get n records by age group
@@
         n_cod_uniq = n_distinct(physician_cghr10)
+    ) %>%
+    ungroup %>%
+    left_join(
+        tab_all %>%
+            group_by(age) %>%
+            summarize(n_all = n()) %>%
+            ungroup,
+        by = "age"
+    ) %>%
+    mutate(
+        n_agree_perc = round(n / n_all * 100, 1) 
     )
@@
     group_by(age, physician_cghr10) %>%
-    summarize(n_cod = n())
+    summarize(n_cod = n()) %>%
+    left_join(
+        tab_all %>%
+        group_by(age, physician_cghr10) %>%
+        summarize(n_cod_all = n()) %>%
+        ungroup,
+        by = c("age", "physician_cghr10")
+    ) %>%
+    mutate(
+        n_cod_agree_perc = round(n_cod / n_cod_all * 100 , 1)
+    )
 
@@
         `Age Group` = glue(
-            "{age} (n={n}, {n_perc}%, {n_cod_uniq} CODs)\n{age} Female (n={n_female}, {n_female_perc}%)\n{age} Male (n={n_male}, {n_male_perc}%)"
+            "{age} (n={n}, {n_perc}%, {n_cod_uniq} CODs)\n- Female (n={n_female}, {n_female_perc}%)\n- Male (n={n_male}, {n_male_perc}%)\n- Agree ({n_agree_perc}% of {n_all})"
         ),
@@
         ),
+        `Agree` = glue("{n_cod_agree_perc}% of {n_cod_all}"),
         `Female` = glue("{n_cod_female} ({n_cod_female_perc}%)"),
@@
     ungroup %>%
-    select(`Age Group`, `Cause of Death (COD)`, Female, Male, Total) %>%
+    select(`Age Group`, `Cause of Death (COD)`, Agree, Female, Male, Total) %>%
     mutate(
         `Age Group` = str_replace_all(`Age Group`, "\\\\n|\\n", "<br>"),
-        `Cause of Death (COD)` = str_replace_all(`Cause of Death (COD)`, "\\\\n|\\n", "<br>")
+        `Cause of Death (COD)` = str_replace_all(`Cause of Death (COD)`, "\\\\n|\\n", "<br>"),
+        Agree =  str_replace_all(Agree, "\\\\n|\\n", "<br>")
     ) %>%
@@
     group_by(age, age_range) %>%
-    summarize(n_age = n())
+    summarize(n_age = n()) %>%
+    left_join(
+        tab_all %>%
+        group_by(age, age_range) %>%
+        summarize(n_age_all = n()) %>%
+        ungroup,
+        by = c("age", "age_range")
+    ) %>%
+    mutate(
+        n_age_agree_perc = round(n_age / n_age_all * 100 , 1)
+    )
 
@@
         ),
+        `Agree` = glue("{n_age_agree_perc}% of {n_age_all}"),
         `Female` = glue("{n_age_female} ({n_age_female_perc}%)"),
@@
     ungroup %>%
-    select(`Age Group`, `Age Range`, Female, Male, Total) %>%
+    select(`Age Group`, `Age Range`, Agree, Female, Male, Total) %>%
     mutate(
         `Age Group` = str_replace_all(`Age Group`, "\\\\n|\\n", "<br>"),
-        `Age Range` = str_replace_all(`Age Range`, "\\\\n|\\n", "<br>")
+        `Age Range` = str_replace_all(`Age Range`, "\\\\n|\\n", "<br>"),
+        `Agree` = str_replace_all(`Agree`, "\\\\n|\\n", "<br>")
     ) %>%
